### 2018-09-06 tex/evaluation.tex
Add paper

\section{Evaluation}\label{evaluation}
This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
{\color{blue}In Spark with SCache, }
first we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.
{\color{blue}To verify the universality of Scache, we also implemented SCache on Hadoop MapReduce. We use Terasort to evaluate the performance of SCache on Hadoop MapReduce.}

\begin{figure}
	\includegraphics[width=\linewidth]{fig/scache_util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application With SCache}
	\label{fig:scache_util}
\end{figure}

In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
At last, we measure the overhead of weighted reservoir sampling. 
{\color{blue}In terms of universality, we implemented SCache on Hadoop MapReduce and Spark respectively. It can be proved that the optimization scheme provided by SCache can adapt to the current mainstream distributed DAG framework without a lot of change cost.}
In short, SCache can decrease ~$89\%$ time of Spark shuffle. Furthermore, SCache achieves a ~$75\%$ and ~$50\%$ improvement of reduce stage completion time respectively in simple DAG application and Terasort without introducing extra network traffic. More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\%}

% Because a complex Spark application consists of multiple stages. The completion time of each stage varies under different input data, configurations and different number of stages. This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison. To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
\begin{figure*}
	\centering
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymapstage}
				\caption{Map Stage Completion Time}
				\label{fig:mapstage}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
				\caption{Reduce Stage Completion Time}
				\label{fig:reducestage}	
			\end{minipage}
		\end{subfigure}
		\caption{Stage Completion Time of Single Shuffle Test}
		\label{fig:singleshuffle}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbymaptask}
				\caption{Median Task in Map Stages}
				\label{fig:maptask}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
				\caption{Median Task in Reduce Stages}
				\label{fig:reducetask}
			\end{minipage}
		\end{subfigure}
		\caption{Median Task Completion Time of Single Shuffle Test}
		\label{fig:singleshuffletask}
	\end{minipage}	
	\begin{minipage}[t]{.32\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera}
				\caption{Reduce Stage of First Shuffle}
				\label{fig:terasort}
			\end{minipage}

			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/tera_shuffle}
				\caption{Network Traffic of Second Shuffle}
				\label{fig:terashuffle}
			\end{minipage}
		\end{subfigure}
		\caption{Terasort Evaluation}
	\end{minipage}
\end{figure*}

\subsection{Setup}\label{stepup}
We implement a Spark demon to enable shuffle optimization as a representative.
We run our experiments on a 50 m4.xlarge nodes cluster on Amazon EC2 \footnote{http://aws.amazon.com/ec2/}. Each node has 16GB memory and 4 CPUs. The network bandwidth is not specifically provided by Amazon. Our evaluations reveal the bandwidth is about 300 Mbps (see Figure \ref{fig:util}).

\subsection{Simple DAG Analysis}
%\subsubsection{Hardware Utilization}
We first run the same single shuffle test as mentioned in Figure \ref{fig:util}. As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. That is, SCache prevents the computing process from being cutting off by the I/O operations with a fine-grained resource allocation. It ensures the overall CPU utilization of the cluster stays in a high level. In addition, the decoupling of shuffle write helps free the CPU earlier and leads to a faster map task computation. At the same time, the shuffle pre-fetching in the early stage of map phase shifts the network transfer completion time, which decreases reduce stage completion time. The combination is the main performance gain we achieved on the scope of hardware utilization by SCache.
% \begin{figure}
% 	%\vspace*{-0.01cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymapstage}
% 		\caption{Map Stage Completion Time Comparison}
% 		\label{fig:mapstage}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducestage}
% 		\caption{Reduce Stage Completion Time Comparison}
% 		\label{fig:reducestage}
% 	\end{subfigure}
% 	\caption{Stage Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffle}
% \end{figure}

% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
% 		\caption{Median Task Details in Map Stages}
% 		\label{fig:maptask}
% 	\end{subfigure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
% 		\caption{Median Task Details in Reduce Stages}
% 		\label{fig:reducetask}
% 	\end{subfigure}
% 	\caption{Median Task Completion Time of Single Shuffle Test}
% 	\label{fig:singleshuffletask}
% \end{figure}
The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our analysis on hardware utilization. For each stage, we run 5 rounds of tasks with different input size. By running spark with SCache, the completion time of map stage can be reduced $10\%$ on average. For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.

A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. For each stage, we pick the median task. About 40\% of shuffle write time can be eliminated by SCache (Figure \ref{fig:maptask}) in a map task. Because the serialization of data is CPU intensive \cite{makingsense} and it is inevitable while moving data out of JVM, SCache can not eliminate the whole phase of shuffle write. It results in a less performance gain in the map stage.
On the other hand, the network transfer introduces a significantly latency in shuffle read of reduce task (Figure \ref{fig:reducetask}). By doing shuffle data pre-fetching for the reduce tasks, the shuffle read time decreases ~$100\%$. That is, the explicit network transfer is perfectly overlapped by SCache shuffle pre-fetching. In overall, SCache can help Spark decrease by ~$89\%$ time in the whole shuffle process. In addition, heuristic reduce tasks scheduling achieves better load balance in cluster than the Spark default FIFO scheduling which may randomly assign two heavy tasks on a single node. So that we can have a significant performance gain in the completion time of the reduce stage.

\subsection{Terasort}
We also evaluate Terasort \cite{spark-tera} --- a recognized shuffle intensive benchmark for distributed system analysis.
Terasort consists of two consecutive shuffles. The first shuffle reads the input data and uses a customized hash partition function for re-partitioning. The second shuffle partitions the data through a range partitioner. As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task. So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.

As shown in Figure \ref{fig:terasort}, we present the first shuffle as the evaluation of shuffle optimization. At the same time, we use the second shuffle to evaluate in the dimension of scheduling locality (Figure \ref{fig:terashuffle}). For the first shuffle, Spark with SCache runs 2 $\times$ faster during the reduce stage with the input data in a range from 10GB to 200GB. At the same time, Figure \ref{fig:terashuffle} reveals that SCache pre-scheduling produces exactly same network traffic of the second shuffle as Spark, which implies that SCache pre-scheduling can obtain the best locality while balancing the load. In contrast, Spark delays scheduling reduce tasks with the shuffle map output to achieve this optimum.

\begin{figure*}
	\includegraphics[width=0.85\textwidth]{fig/tpcds}
	\caption{TPC-DS Benchmark Evaluation}
	\label{fig:tpcds}
	\vspace{-1em}
\end{figure*}
\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sampling}
	\caption{Sampling Overhead}
	\label{fig:sampling}
	\vspace{-1em}
\end{figure}

{\color{blue}
\subsection{Hadoop}

We also implemented Scache on Hadoop MapReduce to verify the universality of SCache. We use Terasort to evaluate the performance of scache on Hadoop MapReduce. Terasort's implementation of Hadoop Mapreduce only includes one Shuffle process from the Map phase to the Reduce phase. Terasort is a task that requires a lot of data shuffle. All input data for the Job will be shuffled.

Figure \ref{fig:hadoop_terasort_origin} shows the hardware resource utilization of the original Hadoop Mapreduce running Terasort. Figure \ref{fig:hadoop_terasort_scache} shows the hardware resource utilization with SCache. Both figures have the same proportion of time. Hadoop MapReduce with SCache brings 25\% of total time optimization with input data size 256GB. Without SCache, Hadoop writes intermediate data locally in the Map phase. Hadoop began to shuffle in the reduce stage. Because the large amount of shuffle data reaches the network bottleneck, Hadoop needs to wait for network transfer in the front of reduce stage. This causes the CPU resources to be idle. As shown in the Figure \ref{fig:hadoop_terasort_scache}, the job with SCache pre-fetch shuffle data in the Map phase. This avoids the job waiting for the shuffle transmission in the Reduce phase. Furthermore, prefetching shuffle data utilize the idle IO throughput in the Map phase. As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\% with input data sizes from 128GB to 512GB.
}

\begin{figure}
	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
	\caption{\color{blue}Hadoop Mapreduce Terasort completion time}
	\label{fig:hadoop_terasort_time}
\end{figure}

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
				\caption{\color{blue}Hadoop Mapreduce With SCache}
				\label{fig:hadoop_terasort_scache}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
				\caption{\color{blue}Hadoop Mapreduce Without SCache}
				\label{fig:hadoop_terasort_origin}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop Mapreduce Terasort job}
		\label{fig:hadoop_terasort}
	\end{minipage}
\end{figure}

\subsection{Production Workload}
We also evaluate some shuffle heavy queries from TPC-DS \cite{tpcds}. TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time. Spark with SCache outperforms the original Spark in almost all the queries. Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. The overall reduction portion of query time that SCache achieved is 40\% on average. Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
% \begin{figure}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera}
% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
% 		\label{fig:terasort}
% 	\end{subfigure}
% 	\vspace{0.08cm}
% 	\begin{subfigure}{\linewidth}
% 		\centering
% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
% 		\label{fig:terashuffle}
% 	\end{subfigure}
% 	\caption{Terasort Evaluation}
% \end{figure}
\subsection{Overhead of Sampling}
In this part, we evaluate the overhead of sampling with different input data sizes on one node and cluster scales. In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node. But it remains relatively stable when the cluster size scales up. It makes SCache a scalable system in cluster.

### 2018-09-06 tex/intro.tex
Add IEEEPARstart

\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
\IEEEPARstart{R}{ecent} years have witnessed widespread use of sophisticated frameworks such as Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. Such shuffle phase places significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs\cite{managing}.

Although continued efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, the shuffle is often poorly optimized in practice.
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in a lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stage (i.e., map task).  And the \textit{shuffle read} fetches intermediate results from \emph{remote} disks through network, which is commonly integrated as part of the tasks in descendant stage (i.e., reduce task).  Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to each of the computation task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since each phase receives a fixed bundle of resources, attaching the \emph{I/O intensive} shuffle phase to the \emph{CPU/memory intensive} computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after all the data from its ancestor stage by default. As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop \cite{hadoop}. However, such early start is by no means a panacea. This is because although the reduce tasks can start fetching data earlier, the computation can only take place after all the data is ready. Since each phase receives a fixed bundle of resources, starting a reduce task early always introduces an unnecessary early allocation of slot.

%In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.

%For example, Apache Hadoop \cite{hadoop} provides an \emph{early start} mechanism that launches reduce tasks after a certain portion (5\% by default) of map tasks has completed, which is adopted in many of the recent works \cite{ihadoop, ishuffle, dynmr}.
% DAG computing framworks deriving from MapReduce \cite{mapreduce} contains a hard barrier between computing stages. The terminology of this barrier is \textit{shuffle}. Shuffle contains two parts on the connecting stages -- \textit{shuffle write} and \textit{shuffle read}. On the side of ancestor stages, \textit{shuffle write} is resoponsible for writing intermediate results to disk. On the side of descendant stage, \textit{shuffle read} fetches intermediate results from remote disks through network. Although highly optimized in other factors, the shuffle of framework is still primitive.  The coarse design of shuffle introduce a significiant performance overhead.
% % design inconsistent
% For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
% shuffle operations
% three resource coordinate 不好
% 计算和I/O couple, why
% why disk, reason!!!, 不重视
% common problems

To make things worse, we note that the above deficiencies generally exist in most of the DAG computing frameworks. As a result, even we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.

% The main defect of current shuffle design is coarse granularity of resource allocation during the task scheduling.
% Nearly all task scheduling algorithms in DAG frameworks use time slotted model. Specifically, when a task is launched, the framework offers it a bundle of resources (i.e. CPU and memory), which are dedicated to this task during the time in its "slot".
% But for a task, the resources demand changes during different phases. The computing phase is CPU and memory intensive. The shuffle, instead, is I/O intensive.
% As shown in the upper part of Figure \ref{fig:workflow}, this "slot" can be released until the map tasks finish \textit{shuffle write} on disk. And the "slot" is occupied when the reduce tasks begin to read shuffle data from remote nodes through network, which is presented as \textit{shuffle read}. This inconsistency between demands and allocation results in a severe resource underutilization, which slow down the framework.

% Another drawback of current shuffle is the synchronized shuffle read. When all the reduce tasks are scheduled, the shuffle fetch of each task starts almost simultaneously, which may cause congestion of network and delay the shuffle read. The straight forward way to avoid network burst is to start reduce tasks earlier. Apache Hadoop \cite{hadoop} provides a mechanism that schedules reduce tasks when a certain portion of map tasks completed. So that the shuffle delay can be mitigated. Other publications also purpose solutions to pre-schedule reduce tasks \cite{ihadoop, ishuffle, dynmr}. However this early scheduling of reduce tasks occupies new task slots, which degrades system performance. To this end, we proposed a question for this cross-frameworks issue, \textit{can we efficiently optimize shuffle without manually change every DAG framework?}

% 针对性的提出这三个点
% three resource coordinate 不好
% 计算和I/O couple, why
% why disk, reason, 不重视
% common problems
% 总起：普适性工具
% pre-fetch but not pre-execute
% byproduct: more balance
% memory instead of disk

% challenge point by point, inside the problem

Can we efficiently optimize the data shuffling without significantly changing every framework?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle read and write from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks and pre-fetches the shuffle data to the location of the reduce tasks without launching them.
Such pre-scheduling and pre-fetching effectively desynchronize the network I/O operation, while avoiding the waste of computational resources compared to the early start mechanism.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

The workflow of DAG framework with SCache is presented in Figure \ref{fig:workflow}. SCache hijacks the intermediate data of a map task in memory space. The disk operation is skipped and the slot is released after memory copy. The in-memory intermediate data is immediately pre-fetched through network after pre-scheduling. By releasing the slot earlier and starting the network transfer ahead of reduce tasks, SCache can help the DAG framework achieve a significant performance gain. A by-product optimization of pre-scheduling is that SCache can provide a more balanced load for each node and further benefit the reduce stage by avoiding data skew.

The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks}. It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}. Unfortunately the complexity of DAG can amplify the defects of na\"{i}ve pre-scheduling schemes. In particular, randomly assign reduce tasks might result in a collision of two heavy tasks on one node. This collision can aggravate data skew, thus hurting the performance. To address this challenge, we propose a heuristic scheme to predict the shuffle output distribution and pre-schedule reduce tasks (Section \ref{opt}).

The second challenge is the \textit{in-memory data management}. To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. However, the memory is a precious resource for DAG computing. To minimize the reserved memory while maximizing the performance gain of optimization and memory utilization, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.

We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.

### 2018-09-26 tex/model.tex
Add model.

{\color{blue}
\section{Model}\label{model}

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{blue}??? Model}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}

This chapter presents a completely new model to describe the performance of distributed parallel computatino. The model analyzes the relationship between the computation stage and the shuffle stage from perspective of computation and IO resources scheduling. The model can help us evaluate the performance of the computing framework. We will first introduce model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use model to describe three different computation job and analyze their performance.

\subsection{Model Overview}\label{model_overview}
The current distributed parallel computation frameworks mostly use DAG(Directed acyclic graph) to describe computation logic. A shuffle stage is required between each adjacent DAG computation phase. In order to better analyze the relationship between the computation stage and the shuffle stage, we propose ??? model. ??? model describes the scheduling of computation resources and IO resources when framework is performing a computation job. ??? model can help us evaluate the performance of the framework when using different resource scheduling strategies. In this section we introduce the model by taking a simple MapReduce as an example.

Figure \ref{fig:model_basic} shows how the ??? model describes a MapReduce computing task. The model has five input parameters:
\begin{itemize}
	\item Input Data Size\((D)\): The data size of the computation stage.
	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation stage. This conversion rate depends on the algorithm used in the computation stage.
    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation stage using the current computation resources. The number of rounds depends on the current computation resources and the settings of the computation job. Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map Stage consists of 200 map tasks. Then we need 4 rounds of computation to complete the Map phase.
    \item Computation Speed\((V_{i})\): 
    The computation speed for each computation stage. The computation speed depends on the algorithm used in the computation stage.
    \item Shuffle Speed\((V_{Shuffle})\): 
    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
\end{itemize}

We can estimate the execution time of each stage of the job with these five parameters. Obviously, the total execution time of job in this case is the sum of the Map stage time and Reduce stage time.
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}
Map stage time depends on input data size and Map computation speed:
\begin{equation}
\label{equation_Tmap}
\begin{aligned}
    T_{Map} &= {{\frac{D}{V_{Map}}}}
\end{aligned}
\end{equation}
The Reduce phase time formula is as follows:
\begin{equation}
\label{equation_Treduce}
\begin{aligned}
    T_{Reduce} &= {{\frac{D \times R}{V_{Reduce}} + Overhead}}
\end{aligned}
\end{equation}
The \(Overhead\) depends on the parallel time of shuffle stage and the Reduce stage. The parallel time is denoted by \(T_{P\_Shuffle}\). The overall shuffle time is represented by \(T_{Shuffle}\). \(Overhead\) increases in proportion to \(T_{P\_Shuffle}\). This is because the computatinon of the Reduce stage relies on the data transfer results of the Shuffle stage. A portion of the computation in the Reduce stage need to wait for the transfer results. The overhead is caused by these waiting.

For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\). Improving IO speed is a effective way to reduce shuffle time. Another optimization method is to use the idle IO resources in the Map stage for pre-fetching(see Figure \ref{fig:model_basic}). Both of the above methods can effectively reduce \(T_{P\_Shuffle}\). When using ??? model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework. Different computing frameworks may use different resource scheduling strategies. ??? model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.

\subsection{Model Analysis}\label{model_analysis}

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_original}
				\caption{\color{blue}Full Serial Mapreduce}
				\label{fig:model_original}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_hadoop}
				\caption{\color{blue}Hadoop Mapreduce}
				\label{fig:model_hadoop}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}??? Model With Different Scheduling Strategies}
		\label{fig:model_strategies}
	\end{minipage}
\end{figure}

The model can describe a variety of resource scheduling strategies. First, we analyze a naive scheduling strategy. As shown in Figure \ref{fig:model_original}, the model describes a Mapreduce job that is fully serially executed. The parallel time of shuffle stage and the Reduce stage is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\). Therefore, the overhead of the Reduce stage is 0. But since shuffle and computation are serial execution, the total execution time of job becomes longer:
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
\end{aligned}
\end{equation}
Obviously, this is an inefficient scheduling strategy. No computing framework uses this scheduling method. Due to serialization, the IO resource is idle during the Reduce stage and Map stage. The scheduling strategy is naive and has a lot of room for optimization.

Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop Mapreduce. In Hadoop Mapreduce, Shuffle stage and Reduce stage start at the same time. In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\). Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase(see equation \ref{equation_Treduce}). Because the Shuffle stage and the computation stage are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\)(see equation \ref{equation_Tjob}). The execution time of Shuffle stage is hidden in the Reduce stage. This scheduling strategy is much more efficient than the one in Figure 1. However, after analyzing this model, we found that the IO resource in the Map stage is idle. This scheduling strategy can be optimized.

\begin{figure}
	\centering
	\begin{minipage}[hb]{\linewidth}
		\begin{subfigure}{\linewidth}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache1}
				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
				\label{fig:model_scache1}
			\end{minipage}
			\begin{minipage}{\linewidth}
				\includegraphics[width=\linewidth]{fig/model_scache2}
				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
				\label{fig:model_scache2}
			\end{minipage}
		\end{subfigure}
		\caption{\color{blue}??? Model With SCache}
		\label{fig:model_scache}
	\end{minipage}
\end{figure}

Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop Mapreduce with SCache (Suppose N is 4). SCache starts pre-fetching and pre-scheduling in the Map stage. This scheduling strategy can make better use of resources and avoid IO resources being idle in the Map stage. According to the experiment, we found that using the model to describe the scheduling strategy of SCache needs to distinguish two situations:

\begin{itemize}
    \item 
    \(V_{Map} \times R \ge V_{Shuffle}\)(Figure \ref{fig:model_scache1}): 
    The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated. The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)). When the Round1 of the Map phase ends, the SCache starts shuffling data until the end of the shuffle stage. Due to shuffle speed is slower, the shuffle stage is uninterrupted.
    \item \(V_{Map} \times R < V_{Shuffle}\)(Figure \ref{fig:model_scache2}): 
    When the speed of generating shuffle data(\(V_{Map} \times R\)) is less than the shuffle speed(\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle stage will be interrupted in each Round.
\end{itemize}

After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
\begin{equation}
    \label{equation_Tpshuffle}
    \begin{aligned}
    T_{P\_Shuffle} &=
        \begin{cases} 
        T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
        T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
        \end{cases}
    \end{aligned}
\end{equation}
If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of Map stage during the Reduce phase. Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle stage. If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map stage.

Compared to the original Hadoop Mapreduce resource scheduling strategy, Hadoop Mapreduce with SCache reduces \(T_{P\_Shuffle}\) and thus reduces Reduce time(\(T_{Reduce}\)). This is how pre-fetching optimizes the total execution time of job.

% \subsection{Performance Analysis}\label{model_performance_analysis}
}

### 2018-10-08 tex/abstract.tex
version 0.1

\begin{abstract}

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
{\color{red}
We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
}
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

### 2018-10-08 tex/evaluation.tex
update
version 0.1

@@
 \begin{figure*}
+	\centering
 	\includegraphics[width=0.85\textwidth]{fig/tpcds}
@@
 
-We also implemented Scache on Hadoop MapReduce to verify the universality of SCache.
-We use Terasort to evaluate the performance of scache on Hadoop MapReduce.
-Terasort's implementation of Hadoop Mapreduce only includes one Shuffle process from the Map phase to the Reduce phase.
-Terasort is a task that requires a lot of data shuffle.
-All input data for the Job will be shuffled.
+To prove SCache compatibility as a plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler.
+Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy job on Hadoop can still be optimized.
 
-Figure \ref{fig:hadoop_terasort_origin} shows the hardware resource utilization of the original Hadoop Mapreduce running Terasort.
-Figure \ref{fig:hadoop_terasort_scache} shows the hardware resource utilization with SCache.
+Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort.
 Both figures have the same proportion of time.
-Hadoop MapReduce with SCache brings 25\% of total time optimization with input data size 256GB.
+Hadoop MapReduce with SCache brings 15\% of total time optimization with input data size 384GB.
 Without SCache, Hadoop writes intermediate data locally in the Map phase.
@@
 This causes the CPU resources to be idle.
-As shown in the Figure \ref{fig:hadoop_terasort_scache}, the job with SCache pre-fetch shuffle data in the Map phase.
-This avoids the job waiting for the shuffle transmission in the Reduce phase.
-Furthermore, prefetching shuffle data utilize the idle IO throughput in the Map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\% with input data sizes from 128GB to 512GB.
+As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching and pre-scheduling in the Map phase.
+This avoids the Reduce phase waiting for the shuffle data.
+Furthermore, pre-fetching  utilize the idle IO throughput in the Map phase.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
 }

### 2018-10-08 tex/intro.tex
version 0.1

@@
 
+{\color{blue}
+In order to visually describe above-mentioned resources scheduling and analyze deficiencies, we propose \textit{Framework Resources Quantification}(FRQ) model.
+FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension.
+We use FRQ model to help us analyze the deficiencies of resources scheduling and optimize it.
+}
+
 Can we efficiently optimize the data shuffling without significantly changing every framework?
@@
 
+{\color{red}
 We have implemented SCache and a customized Apache Spark \cite{apachespark}.
@@
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
+}
+
+{\color{blue}
+We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
+We have also designed a mathematic model called \textit{Framework Resources Quantification}(FRQ) model.
+We use FRQ model to analyze the principle of SCache and calculate the time of each phase of computing job.
+The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
+On Apache Spark, we conduct basic test GroupByTest.
+We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling.
+On Apache Hadoop, we focus on Terasort benchmark.
+In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios.
+More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark.
+On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
+}

### 2018-10-08 tex/model.tex
version 0.1

@@
 {\color{blue}
-\section{Model}\label{model}
+\section{Framework Resources Quantification Model}\label{model}
 
@@
 	\includegraphics[width=0.85\textwidth]{fig/model_basic}
-	\caption{\color{blue}??? Model}
+	\caption{\color{blue}FRQ Model}
     \label{fig:model_basic}
@@
 
-This chapter presents a completely new model to describe the performance of distributed parallel computatino.
-The model analyzes the relationship between the computation stage and the shuffle stage from perspective of computation and IO resources scheduling.
-The model can help us evaluate the performance of the computing framework.
-We will first introduce model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we will use model to describe three different computation job and analyze their performance.
+In this chapter, we introduce \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
+FRQ model quantifies computing and I/O resources and displays them in time dimension.
+According to FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG framework, hardware environment, and so on.
+Therefore FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
+We will first introduce FRQ model in Subsection \ref{model_overview}.
+In the following Subsection \ref{model_analysis}, we will use FRQ model to describe three different computation job and analyze their performance.
+In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
 
-\subsection{Model Overview}\label{model_overview}
-The current distributed parallel computation frameworks mostly use DAG(Directed acyclic graph) to describe computation logic.
-A shuffle stage is required between each adjacent DAG computation phase.
-In order to better analyze the relationship between the computation stage and the shuffle stage, we propose ???
-model.
-???
-model describes the scheduling of computation resources and IO resources when framework is performing a computation job.
-???
-model can help us evaluate the performance of the framework when using different resource scheduling strategies.
-In this section we introduce the model by taking a simple MapReduce as an example.
+\subsection{The FRQ Model}\label{model_overview}
+The current distributed parallel computing frameworks mostly use DAG(Directed acyclic graph) to describe computation logic.
+A shuffle phase is required between each adjacent DAG computation phase.
+In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model.
+After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies.
+For convenience, we introduce FRQ model by taking a simple MapReduce as an example in this section.
 
-Figure \ref{fig:model_basic} shows how the ??? model describes a MapReduce computing task. The model has five input parameters:
+Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
 \begin{itemize}
-	\item Input Data Size\((D)\): The data size of the computation stage.
-	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation stage. This conversion rate depends on the algorithm used in the computation stage.
-    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation stage using the current computation resources.
+	\item Input Data Size\((D)\): The data size of the computation phase.
+	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
+    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation phase using the current computation resources.
 The number of rounds depends on the current computation resources and the settings of the computation job.
-Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map Stage consists of 200 map tasks.
+Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map phase consists of 200 map tasks.
 Then we need 4 rounds of computation to complete the Map phase.
     \item Computation Speed\((V_{i})\): 
-    The computation speed for each computation stage. The computation speed depends on the algorithm used in the computation stage.
+    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
     \item Shuffle Speed\((V_{Shuffle})\): 
@@
 
-We can estimate the execution time of each stage of the job with these five parameters. Obviously, the total execution time of job in this case is the sum of the Map stage time and Reduce stage time.
+We can calculate the execution time of each phase of the job with these five parameters. Obviously, the total execution time of job in this case is the sum of the Map phase time and Reduce phase time:
 \begin{equation}
@@
 \end{equation}
-Map stage time depends on input data size and Map computation speed:
+Map phase time depends on input data size and Map computation speed:
 \begin{equation}
@@
 \begin{aligned}
-    T_{Reduce} &= {{\frac{D \times R}{V_{Reduce}} + Overhead}}
+    T_{Reduce} &= \frac{D \times R}{V_{Reduce}} + K \times T_{P\_Shuffle}
 \end{aligned}
 \end{equation}
-The \(Overhead\) depends on the parallel time of shuffle stage and the Reduce stage.
-The parallel time is denoted by \(T_{P\_Shuffle}\).
-The overall shuffle time is represented by \(T_{Shuffle}\).
-\(Overhead\) increases in proportion to \(T_{P\_Shuffle}\).
-This is because the computatinon of the Reduce stage relies on the data transfer results of the Shuffle stage.
-A portion of the computation in the Reduce stage need to wait for the transfer results.
+\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time, and \(K \times T_{P\_Shuffle}\) represents the calculated overhead.
+\(K\) is empirical value.The overhead depends on the parallel time of shuffle phase and the Reduce phase.The parallel time is denoted by \(T_{P\_Shuffle}\).
+And the total time of shuffle phase is represented by \(T_{Shuffle}\).
+Because the computatinon of the Reduce phase relies on the data transfer results of the Shuffle phase, a portion of the computation in the Reduce phase need to wait for the transfer results.
 The overhead is caused by these waiting.
+The FRQ model uses K to indicate the extent of the waiting.
+
+\begin{equation}
+\label{equation_Tshuffle}
+\begin{aligned}
+    T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
+\end{aligned}
+\end{equation}
 
@@
 Improving IO speed is a effective way to reduce shuffle time.
-Another optimization method is to use the idle IO resources in the Map stage for pre-fetching(see Figure \ref{fig:model_basic}).
+Another optimization method is to use the idle IO resources in the Map phase for pre-fetching(see Figure \ref{fig:model_basic}).
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
-When using ???
-model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework.
+When using FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework.
 Different computing frameworks may use different resource scheduling strategies.
-???
-model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.
+FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.
 
@@
 		\end{subfigure}
-		\caption{\color{blue}??? Model With Different Scheduling Strategies}
+		\caption{\color{blue}FRQ Model With Different Scheduling Strategies}
 		\label{fig:model_strategies}
@@
 
-The model can describe a variety of resource scheduling strategies.
+FRQ model can describe a variety of resource scheduling strategies.
 First, we analyze a naive scheduling strategy.
-As shown in Figure \ref{fig:model_original}, the model describes a Mapreduce job that is fully serially executed.
-The parallel time of shuffle stage and the Reduce stage is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
-Therefore, the overhead of the Reduce stage is 0.
+As shown in Figure \ref{fig:model_original}, FRQ model describes a Mapreduce job that is fully serially executed.
+The parallel time of shuffle phase and the Reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
+Therefore, the overhead of the Reduce phase is 0.
 But since shuffle and computation are serial execution, the total execution time of job becomes longer:
 \begin{equation}
-\label{equation_Tjob}
+\label{equation_Tjob2}
 \begin{aligned}
@@
 No computing framework uses this scheduling method.
-Due to serialization, the IO resource is idle during the Reduce stage and Map stage.
+Due to serialization, the IO resource is idle during the Reduce phase and Map phase.
 The scheduling strategy is naive and has a lot of room for optimization.
@@
 Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop Mapreduce.
-In Hadoop Mapreduce, Shuffle stage and Reduce stage start at the same time.
+In Hadoop Mapreduce, Shuffle phase and Reduce phase start at the same time.
 In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\).
 Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase(see equation \ref{equation_Treduce}).
-Because the Shuffle stage and the computation stage are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\)(see equation \ref{equation_Tjob}).
-The execution time of Shuffle stage is hidden in the Reduce stage.
+Because the Shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\)(see equation \ref{equation_Tjob}).
+The execution time of Shuffle phase is hidden in the Reduce phase.
 This scheduling strategy is much more efficient than the one in Figure 1.
-However, after analyzing this model, we found that the IO resource in the Map stage is idle.
+However, after analyzing this model, we found that the IO resource in the Map phase is idle.
 This scheduling strategy can be optimized.
@@
 		\end{subfigure}
-		\caption{\color{blue}??? Model With SCache}
+		\caption{\color{blue}FRQ Model With SCache}
 		\label{fig:model_scache}
@@
 Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop Mapreduce with SCache (Suppose N is 4).
-SCache starts pre-fetching and pre-scheduling in the Map stage.
-This scheduling strategy can make better use of resources and avoid IO resources being idle in the Map stage.
-According to the experiment, we found that using the model to describe the scheduling strategy of SCache needs to distinguish two situations:
+SCache starts pre-fetching and pre-scheduling in the Map phase.
+This scheduling strategy can make better use of resources and avoid IO resources being idle in the Map phase.
+According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
 
@@
 The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)).
-When the Round1 of the Map phase ends, the SCache starts shuffling data until the end of the shuffle stage.
-Due to shuffle speed is slower, the shuffle stage is uninterrupted.
+When the Round1 of the Map phase ends, the SCache starts shuffling data until the end of the shuffle phase.
+Due to shuffle speed is slower, the shuffle phase is uninterrupted.
+SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase.
+Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
+	\begin{equation}
+		\label{equation_Tpshuffle1}
+		\begin{aligned}
+			T_{P\_Shuffle} &= T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N}
+		\end{aligned}
+	\end{equation}
+
     \item \(V_{Map} \times R < V_{Shuffle}\)(Figure \ref{fig:model_scache2}): 
 	When the speed of generating shuffle data(\(V_{Map} \times R\)) is less than the shuffle speed(\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated.
-As Figure \ref{fig:model_scache2} shown, the shuffle stage will be interrupted in each Round.
+As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round.
+Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase:
+	\begin{equation}
+		\label{equation_Tpshuffle2}
+		\begin{aligned}
+			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
+		\end{aligned}
+	\end{equation}
 \end{itemize}
 
-After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
+% After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
+% \begin{equation}
+%     \label{equation_Tpshuffle}
+%     \begin{aligned}
+%     T_{P\_Shuffle} &=
+%         \begin{cases} 
+%         T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
+%         T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
+%         \end{cases}
+%     \end{aligned}
+% \end{equation}
+% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase.
+Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase.
+
+% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase.
+
+Compared to the original Hadoop Mapreduce resource scheduling strategy, Hadoop Mapreduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \textit{Reduce Time}(\(T_{Reduce}\)).
+This is how pre-fetching optimizes the total execution time of job.
+
+\begin{table*}[!t]
+\renewcommand{\arraystretch}{1.3}
+\caption{\color{blue}Hadoop Mapreduce on 4 nodes cluster in FRQ model}
+\label{table1}
+\centering
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+\hline
+ &
+\(D\) &	
+\(R\) &	
+\(N\) &	
+\(V_{Map}\) &	
+\(V_{Reduce}\) &	
+\(V_{Shuffle}\) &	
+\(K\) &	
+\(T_{Map}\) &	
+\(T_{Shuffle}\) &	
+\(T_{P\_Shuffle}\) &
+\(T_{Reduce}\) & 
+\(T_{Job}\) & 
+\(Exp T_{Job}\) &
+\(Error\)\\
+
+\hline
+ & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
+ SCache
+ & 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
+ & 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
+ & 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
+ \hline
+ & 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
+ Legacy
+ & 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
+ & 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
+ & 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
+\hline
+\end{tabular}
+\end{table*}
+% \subsection{Performance Analysis}\label{model_performance_analysis}
+
+\begin{table*}[!t]
+
+\renewcommand{\arraystretch}{1.3}
+\caption{\color{blue}Hadoop Mapreduce on 50 AWS m4.xlarge nodes cluster in FRQ model}
+\label{table2}
+\centering
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+\hline
+ &
+\(D\) &	
+\(R\) &	
+\(N\) &	
+\(V_{Map}\) &	
+\(V_{Reduce}\) &	
+\(V_{Shuffle}\) &	
+\(K\) &	
+\(T_{Map}\) &	
+\(T_{Shuffle}\) &	
+\(T_{P\_Shuffle}\) &
+\(T_{Reduce}\) & 
+\(T_{Job}\) & 
+\(Exp T_{Job}\) &
+\(Error\)\\
+
+\hline
+& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
+SCache
+& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
+& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
+% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
+\hline
+& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
+Legacy
+& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
+& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
+% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
+
+\hline
+\end{tabular}
+\end{table*}
+
+\subsection{Model Verification}\label{model_verification}
+In order to verify FRQ model, we run experiment on two environments.
+The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}.
+Another environment is in our lab.
+Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs.
+To simplify the calculation of the FRQ model, we use Hadoop Mapreduce as framwork(only three phases: \textit{Map, Shuffle,} and \textit{Reduce}) and Terasort as experimental application.
+We deploye Hadoop with SCache and without SCache on both environments.
+
+Table \ref{table1} shows the calculational results of FRQ model in the lab environment.
+Workload is from 16 GB to 64 GB.
+\(D\) and \(N\) are set according to the application parameters.
+\(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results.
+K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the Reduce phase in the case of SCache.
+The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
+In the case of SCache, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache1}(\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
+In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}).
+\(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
+The formular of \(Error\) is:
 \begin{equation}
-    \label{equation_Tpshuffle}
+	\label{equation_error}
 	\begin{aligned}
-    T_{P\_Shuffle} &=
-        \begin{cases} 
-        T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
-        T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
-        \end{cases}
+		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
 	\end{aligned}
 \end{equation}
-If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of Map stage during the Reduce phase.
-Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle stage.
-If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map stage.
 
-Compared to the original Hadoop Mapreduce resource scheduling strategy, Hadoop Mapreduce with SCache reduces \(T_{P\_Shuffle}\) and thus reduces Reduce time(\(T_{Reduce}\)).
-This is how pre-fetching optimizes the total execution time of job.
+Table \ref{table2} shows the calculational results of FRQ model in Amazon EC2 environment.
+\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
+We also set K to the same empirical value.
+The formulas in the table are all the same except \(T_{P\_Shuffle}\).
+In this environment, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
+In the case of Legacy, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).
 
-% \subsection{Performance Analysis}\label{model_performance_analysis}
+\begin{figure}
+	\centering
+	\begin{minipage}[hb]{\linewidth}
+		\begin{subfigure}{\linewidth}
+			\begin{minipage}{\linewidth}
+				\includegraphics[width=\linewidth]{fig/hadoop_net1}
+				\caption{\color{blue}}
+				\label{fig:hadoop_net1}
+			\end{minipage}
+			\begin{minipage}{\linewidth}
+				\includegraphics[width=\linewidth]{fig/hadoop_net2}
+				\caption{\color{blue}}
+				\label{fig:hadoop_net2}
+			\end{minipage}
+		\end{subfigure}
+		\caption{\color{blue}FRQ Model With SCache}
+		\label{fig:hadoop_net}
+	\end{minipage}
+\end{figure}
+
+In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}.
+Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the lab environment.
+The network utilization remains high until shuffle phase is complete.
+This situation is consistent with Figure \ref{fig:model_scache1}.
+Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment.
+The network utilization is 5 regular peaks, this situation is also consistent with Figure \ref{fig:model_scache2}.
+Therefore, we believe that FRQ model is able to accurately describe framework with SCache.
+
+In terms of accuracy, the experimental values are all greater than the calculated values.
+This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on.
+In the case where the input data is small and the total time is short, the error caused by the overhead is amplified.
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance .
+Therefore, We believe that FRQ model can accurately describe DAG framework.
 }

### 2018-10-10 tex/impl.tex
Modify implementation

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache -- an open source cross-framework shuffle data management system with a DAG co-scheduler. 
{\color{red}
Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
}
{\color{blue}
In Subsection \ref{arch}, we will first present the system overview, and then we will detail SCache memory management in Subsection \ref{memorymanage}. In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop Mapreduce and Spark. 
In the last Subsection \ref{fault}, we will introduce the current status of SCache fault tolerance.
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{red}daemon inside Spark.} {\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between {\color{red}Spark} {\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{red}Spark scheduler} {\color{blue} original scheduler in framework master}.

\begin{minipage}{\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in descending order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets$ len$\left(R\right) - 1$
		\While{$idx \geq 0$}
		\Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic swap by locality}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		% \Comment{$m$ is the number of input data}
		% \Comment{$r$ is partition number of reduces}
		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
		% \Comment{$c$ is $r*m$ array of composition data}
		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
		\Return $M$
	\EndProcedure
	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
			\qquad \; $size\_assigned\leq upper\_bound$}
			\State Swap $candidates$ and $reduce$
			\State Update $size$ in $M$
			\State Update $assigned\_host$ in $candidates$ and $reduce$
		\EndIf
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
\begin{minipage}{\columnwidth}
\begin{algorithm}[H]
\caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
		\State $m\gets$ partition number of map tasks
		\Comment $shuffles$ is the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

{\color{red}
When a Spark job starts, the DAG will be first generated. 
During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
}
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
Before the computing tasks begin, the shuffle dependecies are determined based on job configuration.
}
The SCache master recognizes all shuffle dependencies in a RPC call as a shuffle scheduling unit.
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the dependent RDDs. We will elaborate the sampling procedure in the Section \ref{sampling}.

For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from {\color{red}Spark executor's JVM }{\color{blue}framework worker} to the reserved memory through memory copy.
After that the slot will be released without blocking on disk operations.
When the shuffle map output is received, the SCache worker will notify the master of the block ID and reduce size distribution of this block (see map output in Figure \ref{fig:shuffle}).
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} and \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
More specifically, when a map task is finished, each node will receive a broadcast message. SCache worker will filter the reduce tasks ID that will be launched on itself and start pre-fetching shuffle data from the remote. 
{\color{red}
To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
}
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After insertion, DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
}

\subsubsection{Reservoir Sampling}\label{sampling}
If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the {\color{red}daemon in Spark driver} {\color{blue}framework master}. 
The daemon then inserts a sampling job before the {\color{red}corresponding RDD} {\color{blue} submitted computing job}. 
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition {\color{red}of RDD}. 
For the sample number, we set the size to $3 \times number\ of\ partitions$ for balancing overhead and accuracy (it can be tuned by configuration). The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). At the same time, the items number is counted as the weight. These sampling data will be aggregated by reduce ID on SCache master to predict the reduce partition size. After the prediction, SCache master will call Algorithm \ref{mhminheap} and \ref{hminheap} to do the scheduling.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/arch}
	\caption{\color{red}SCache Architecture}
	\label{fig:arch}
	\vspace{-0.5em}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{fig/architecture}
	\caption{\color{blue}SCache Architecture}
	\label{fig:architecture}
	% \vspace{-0.5em}
\end{figure}

\subsection{Memory Management}\label{memorymanage}
As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
When the size of cached blocks reaches the limitation of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- all-or-nothing and context-aware-priority.

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{fig/sample}
	\caption{Reservoir Sampling of One Partition}
	\label{fig:sample}
	\vspace{-1em}
\end{figure}

\subsubsection{All-or-Nothing Constraint}
Memory cached shuffle blocks can speed up the reduce task execution process. But this acceleration of a single task is necessary but insufficient for a shorter stage completion time. Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks. If one task misses a memory cache and exceeds the original bottleneck of this round, that task might become the new bottleneck and further slow down the whole stage. PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least. We refer to this as the all-or-nothing constraint.

According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets corresponding blocks as the minimum unit of storage management.
For those incomplete units, SCache will mark them as the lowest priority.
% Following the all-or-noting constraint can maximum the improvement in stage completion time by using reserved memory efficiently.

\subsubsection{Context-Aware-Priority Constraint}
Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once (without failure) in DAG computing. That is, the effort of improving hit rate in most legacy schemes can not benefit DAG application, while their approaches can easily violate the all-or-nothing constraint.
SCache also leverages application context to select victim storage units when the reserved memory is full.

At first, SCache master searches for the incomplete units and flushes all belonging blocks to disk cluster-widely.

If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle units} and \textit{intra-shuffle unit}.
\begin{itemize}[noitemsep]
	\item Inter-shuffle units: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle unit. For a FIFO scheduler, Spark schedules the task set that is submitted first. So SCache sets the priorities according to the submit time of each shuffle unit.
	\item Intra-shuffle unit: SCache also needs to decide the priority among storage units inside a shuffle unit. According to the task scheduling inside a task set of Spark, the tasks with smaller ID will be scheduled firstly. Based on this, SCache can assign the lower priority to storage units with larger task ID.
\end{itemize}

{\color{red}
\subsection{Cost of adapting DAG frameworks}
SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
}
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order. (b)The shuffle data between the Map task and the Reduce task should be transfer to SCahce Storge Management.

To prove the cross-framework capability of SCache, we implement SCache on Hadoop Mapreduce and Spark respectively. Taking Hadoop Mapreduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC. It takes about 400 lines of code. In Spark, We mainly modified the DAGScheduler and the corresponding data fetcher. It only takes about 500 lines of code. Such hundreds of lines of code modification is very small compared to the hundreds of thousands of lines of code in DAG framework. we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
}

\subsection{Fault tolerance}\label{fault}
Since fault tolerance is not a crucial goal of SCache, we have not implemented fault tolerance mechanism. We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service.  For SCache worker, a promising way to prevent failure is to select some backup nodes to store replications of shuffle data during pre-scheduling. In addition, there are also advanced fast recovery techniques such as FineFRC \cite{finefrc}. We leave this to the future work.

% \subsubsection{Fault Tolerance}
% To prevent the machine failure in cluster leading to inconsistency SCache, the master node will log the meta data of shuffle register and scheduling on the disk. Since we remove the shuffle transfer from the critical path of DAG computing, the disk log will not introduce extra overhead to the DAG framworks. Note that the master can be implemented with Apache ZooKeeper \cite{zookeeper} to provide constantly service to DAG framework.
% At the same time, every work node will send a heartbeat to master to report status. If a failure of work node is detected, the master will the do a simple re-schedule. For those scheduled shuffle units, the master assgins the tasks to other workers with more lightweight workload evenly. Then the new assigned worker will fetch the data again. For the incomplete in memory map blocks on the failure node, SCache simply ignore them since DAG framework will schedule the failure map tasks on another node.

### 2018-10-10 tex/conclusion.tex
Update conclusion.

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
 {\color{red}
 Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
 }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Out evaluation result shows that SCache can provide a promising speedup to the DAG framework.
 }
 We believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks.

### 2018-10-11 tex/relatedwork.tex
Modify relatedwork.

\section{Related Work}
This section describes related work of shuffle optimization.

{\color{blue}
\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel}(BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e. \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Hadoop Madpreduce can also be considered as a special case of only one superstep in BSP model). 
In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce. And then the author uses a greedy algorithm to roughly calculate the max, min and mean execution time of Map and Reduce phases.
In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job. The execution is seperated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. The performance models describe each above-mentioned phases and combine into a overall Mapreduce job model. 
However, none of the above models meet our requirements for analyzing shuffle.
The model in \cite{verma2011aria} is not able to accurately describe the overhead caused by shuffle under different scheduling strategies. The model in \cite{herodotou2011hadoop} calculates overhead of various phases including shuffle, but most of them are redundant. 
Different from these models, our FRQ model quantifies computing and I/O resources and displays them in time dimension. FRQ model focuses on describing the overhead caused by shuffle in different scheduling strategies, which satisfy our demand.
}

\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce \cite{hadoop} is the most classic approach to handle shuffle overhead. Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, map and reduce slot ratio, etc). DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks. All of them left the explicit I/O time in an occupied computation slot. Instead, SCache can start shuffle pre-fetching without consuming slots. iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier. But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.

\textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. At the same time, it achieves better data locality. Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. But all of them can not mitigate explicit I/O in both map and reduce tasks. In addition their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle in-memory caching and pre-fetching.

\textbf{Network layer optimization}: Varys \cite{varys} and Aalo \cite{aalo} provide the network layer optimization for shuffle transfer. Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.

### 2018-10-11 coverletter/coverletter.tex
Add Cover Letter.

\documentclass [14pt,journal,compsoc]{article}

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{cite}

\begin{document}

\title{Summary of Differrence}
\maketitle

This paper is extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper makes the following distinct contribution compared with the conference paper.

\begin{enumerate}
\item 
FRQ model quantifies computing and I/Oresources and displays them in time dimension. 
Furthermore, FRQ model can calculate execution time of DAG framework under difference resources allocation strategies. 
\item 
In conference paper, we only implement SCache on Spark. To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
By employing shuffle data management, SCache can also optimize the computing performance of Hadoop Mapreduce.
\item
In experiment, we append two parts. First we verify FRQ model under two different environments, the error between calculated value and experimental value is basically below 10\%. Furthermore, we evaluate the performance of SCache on Hadoop Mapreduce in the same environment as conference paper.
After utilizing pre-fetching of SCache, Hadoop Mapreduce with SCache optimize overall job execution time by 15\%.
\end{enumerate}

Besides the major contributions, we also revise the paper in many places, including writing and more related work. We believe that the added content makes sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
\bibliography{coverletter}

\end{document}

### 2018-10-11 tex/evaluation.tex
Update evaluation.
Version 1.1.

@@
 This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-{\color{blue}In Spark with SCache, }
-first we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
+First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
 Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.
-{\color{blue}To verify the universality of Scache, we also implemented SCache on Hadoop MapReduce. We use Terasort to evaluate the performance of SCache on Hadoop MapReduce.}
 
@@
 In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+{\color{blue}
+To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
+Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
+}
 At last, we measure the overhead of weighted reservoir sampling. 
-{\color{blue}In terms of universality, we implemented SCache on Hadoop MapReduce and Spark respectively.
-It can be proved that the optimization scheme provided by SCache can adapt to the current mainstream distributed DAG framework without a lot of change cost.}
 In short, SCache can decrease ~$89\%$ time of Spark shuffle.
@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
-{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 25\% and an average of 15\%}
+{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}
 
@@
 {\color{blue}
-\subsection{Hadoop}
+\subsection{Hadoop Mapreduce with SCache}
 
-To prove SCache compatibility as a plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler.
-Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy job on Hadoop can still be optimized.
+To prove SCache compatibility as a cross-framework plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler.
+Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.
 
@@
 Both figures have the same proportion of time.
-Hadoop MapReduce with SCache brings 15\% of total time optimization with input data size 384GB.
-Without SCache, Hadoop writes intermediate data locally in the Map phase.
-Hadoop began to shuffle in the reduce stage.
-Because the large amount of shuffle data reaches the network bottleneck, Hadoop needs to wait for network transfer in the front of reduce stage.
+Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
+As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop Mapreduce without SCache writes intermediate data locally in the Map phase.
+The shuffle phase and reduce phase start simultaneously.
+Because the large amount of shuffle data reaches the network bottleneck, The beginning part of reduce needs to wait needs to wait for network transfer.
 This causes the CPU resources to be idle.
-As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching and pre-scheduling in the Map phase.
+As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase.
 This avoids the Reduce phase waiting for the shuffle data.
 Furthermore, pre-fetching utilize the idle IO throughput in the Map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
 }
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
-	\caption{\color{blue}Hadoop Mapreduce Terasort completion time}
-	\label{fig:hadoop_terasort_time}
-\end{figure}
 
@@
 	\end{minipage}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
+	\caption{\color{blue}Hadoop Mapreduce Terasort completion time}
+	\label{fig:hadoop_terasort_time}
 \end{figure}

### 2018-10-11 tex/abstract.tex
Version 1.2.

@@
 Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node.
-{\color{red}
-We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler.
+% {\color{red}
+% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
-Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
-}
+% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
+% }
 {\color{blue}

### 2018-10-11 tex/conclusion.tex
Version 1.2.

@@
 By scheduling tasks with application context, SCache bridges the gap among computing stages.
- {\color{red}
- Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
- }
+%  {\color{red}
+%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
+%  }
  {\color{blue}

### 2018-10-11 tex/impl.tex
Version 1.2.

@@
 This section presents an overview of the implementation of SCache -- an open source cross-framework shuffle data management system with a DAG co-scheduler. 
-{\color{red}
-Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
-We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
-}
+% {\color{red}
+% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
+% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
+% }
 {\color{blue}
@@
 \subsection{System Overview}\label{arch}
-SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{red}daemon inside Spark.} {\color{blue} worker daemon.
+SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
+{\color{blue} worker daemon.
 As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
@@
 The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-The daemon bridges the communication between {\color{red}Spark} {\color{blue} DAG framework} and SCache.
-The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{red}Spark scheduler} {\color{blue} original scheduler in framework master}.
+The daemon bridges the communication between %{\color{red}Spark}
+{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
+ {\color{blue} original scheduler in framework master}.
 
@@
 
-{\color{red}
-When a Spark job starts, the DAG will be first generated. 
-During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
-}
+% {\color{red}
+% When a Spark job starts, the DAG will be first generated. 
+% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
+% }
 {\color{blue}
@@
 
-For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from {\color{red}Spark executor's JVM }{\color{blue}framework worker} to the reserved memory through memory copy.
+For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from %{\color{red}Spark executor's JVM }
+{\color{blue}framework worker} to the reserved memory through memory copy.
 After that the slot will be released without blocking on disk operations.
@@
 SCache worker will filter the reduce tasks ID that will be launched on itself and start pre-fetching shuffle data from the remote.
-{\color{red}
-To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
-For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
-}
+% {\color{red}
+% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
+% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
+% }
 {\color{blue}
@@
 \subsubsection{Reservoir Sampling}\label{sampling}
-If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the {\color{red}daemon in Spark driver} {\color{blue}framework master}.
-The daemon then inserts a sampling job before the {\color{red}corresponding RDD} {\color{blue} submitted computing job}. 
-The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition {\color{red}of RDD}. 
+If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the %{\color{red}daemon in Spark driver} 
+{\color{blue}framework master}. 
+The daemon then inserts a sampling job before the %{\color{red}corresponding RDD}
+{\color{blue} submitted computing job}. 
+The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition %{\color{red}of RDD}. 
 For the sample number, we set the size to $3 \times number\ of\ partitions$ for balancing overhead and accuracy (it can be tuned by configuration).
@@
 
-{\color{red}
-\subsection{Cost of adapting DAG frameworks}
-SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}.
+% {\color{red}
+% \subsection{Cost of adapting DAG frameworks}
+% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}.
 The concise design makes it easy to adapt DAG frameworks to enable SCache optimization.
@@
 By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
-}
+% }
 {\color{blue}

### 2018-10-11 tex/intro.tex
Version 1.2.

@@
 
-{\color{red}
-We have implemented SCache and a customized Apache Spark \cite{apachespark}.
+% {\color{red}
+% We have implemented SCache and a customized Apache Spark \cite{apachespark}.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
@@
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
-}
+% }
 

### 2018-10-12 tex/abstract.tex
v1.3.2

@@
 To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs).
+{\color{blue}
+During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
+FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
+We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
+}
 By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process.

### 2018-10-12 tex/conclusion.tex
v1.3.2

@@
  {\color{blue}
- At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Out evaluation result shows that SCache can provide a promising speedup to the DAG framework.
+ At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Our evaluation result shows that SCache can provide a promising speedup to the DAG framework. 
+ Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
+At last we use FRQ model to verify SCache shuffle optimization by mathematics.
+ Therefore we believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks. 
  }
- We believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks.

### 2018-10-12 tex/evaluation.tex
v1.3.2

@@
 First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
-Then we use a recognized shuffle intensive benchmark --- Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.
+Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
 
@@
 \subsection{Terasort}
-We also evaluate Terasort \cite{spark-tera} --- a recognized shuffle intensive benchmark for distributed system analysis.
+We also evaluate Terasort --- a recognized shuffle intensive benchmark for distributed system analysis.
 Terasort consists of two consecutive shuffles.
@@
 \subsection{Production Workload}
-We also evaluate some shuffle heavy queries from TPC-DS \cite{tpcds}.
+We also evaluate some shuffle heavy queries from TPC-DS.
 TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g.

### 2018-10-12 tex/intro.tex
v1.3.2

@@
 Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time.
-To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop \cite{hadoop}.
+To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop\footnote{http://hadoop.apache.com/}.
 However, such early start is by no means a panacea.
@@
 {\color{blue}
-In order to visually describe above-mentioned resources scheduling and analyze deficiencies, we propose \textit{Framework Resources Quantification}(FRQ) model.
+In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model.
 FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension.
-We use FRQ model to help us analyze the deficiencies of resources scheduling and optimize it.
+We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
+FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
+According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
+Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
+By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
+I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delay the execution time of reduce phase. 
+This situation will be amplified in shuffle-sensitive tasks.
 }
@@
 In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
+
 Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
@@
 We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
-We have also designed a mathematic model called \textit{Framework Resources Quantification}(FRQ) model.
-We use FRQ model to analyze the principle of SCache and calculate the time of each phase of computing job.
+We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model.
+We use FRQ model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
 On Apache Spark, we conduct basic test GroupByTest.
-We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling.
+We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling.
 On Apache Hadoop, we focus on Terasort benchmark.

### 2018-10-12 tex/model.tex
Complete model caption.
Version 1.1.
v1.3.2

@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed parallel computing frameworks mostly use DAG(Directed acyclic graph) to describe computation logic.
+The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs}(DAGs) to describe computation logic.
 A shuffle phase is required between each adjacent DAG computation phase.
@@
 Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
-\begin{itemize}
+\begin{enumerate}
 	\item Input Data Size\((D)\): The data size of the computation phase.
@@
     Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
-\end{itemize}
+\end{enumerate}
 
@@
 In this environment, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
-In the case of Legacy, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).
+In the previous case, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).
 
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_net1}
-				\caption{\color{blue}}
+				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 				\label{fig:hadoop_net1}
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_net2}
-				\caption{\color{blue}}
+				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
 				\label{fig:hadoop_net2}
@@
 		\end{subfigure}
-		\caption{\color{blue}FRQ Model With SCache}
+		\caption{\color{blue}Network utilization on Hadoop Mapreduce with SCache}
 		\label{fig:hadoop_net}

### 2018-10-12 tex/motivation.tex
v1.3.2

\section{Background and Observations}

In this section, we first study the typical shuffle characteristics (\ref{shuffle pattern}), and then spot the opportunities to achieve shuffle optimization (\ref{observation}).
\subsection{Characteristic of Shuffle} \label{shuffle pattern}

In large scale data parallel computing, shuffle is designed to achieve an all-to-all data blocks transfer among nodes. For a clear illustration, we use \textit{map tasks} to define the tasks that generate shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
% Note that one task may have both shuffle data generation and consumption in modern DAG framework. These tasks contain characteristic of both map task and reduce task. But these tasks won't change the behavior of shuffle. To avoid ambiguity, in the following paper, we will only use term of map task to represent those who produce shuffle output, and reduce task to represent those who consume shuffle output.
% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{fig/shuffle_process}
% 	\caption{Shuffle Overview}
% 	\label{fig:shuffle_process}
% \end{figure}

\textbf{Overview of shuffle process}. Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). The total number of buckets equals the number of tasks in the next step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
The partitioned shuffle output data will be spilled to local persistent storage during shuffle write.
Shuffle read starts at the beginning of reduce tasks. It fetches data as reduce input from both remote and local storage.

\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
	\label{fig:util}
\end{figure}
%In short, shuffle is loosely coupled with application context and it's I/O intensive.

\textbf{Impact of shuffle process}. Shuffle process is I/O intensive, which might introduces a significant latency to the application. Reports show that 60\% of MapReduce jobs at Yahoo!
and 20\% at Facebook are shuffle intensive workloads \cite{shufflewatcher}. For those shuffle intensive jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle intensive jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

\subsection{Observations} \label{observation}
Of course, shuffle is unavoidable in a DAG computing process. But can we mitigate or even remove the overhead of shuffle? To find the answers, we run some typical Spark applications in a 5-node EC2 cluster with \texttt{m4.xlarge}. We then measure the CPU utilization, I/O throughput, and tasks execution information of each node. Here we present the trace of one node running Spark \textit{GroupByTest} in Figure \ref{fig:util} as an example. This job has 2 rounds of tasks for each node.
We have marked the \textit{execution} phase as from the launch time of the first task to the execution finish timestamp of the last one. The \textit{shuffle write} phase is marked from the timestamp of the beginning of the first partitioned data write. The \textit{shuffle read and execution} phase is marked from the start of the first reduce launch timestamp.

% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}

\subsubsection{Coarse Granularity Resource Allocation}
In Figure \ref{fig:util}, when a slot is scheduled to a task, it will not be released until the the task completes \textit{shuffle write}. On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}. Meanwhile, shuffle is I/O intensive. Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without involving much CPU. The current coarse slot --- task mapping results in an inconsistency between resource demands and slot allocation thus decreases the resource utilization. To break this inconsistency, a finer granularity resource allocation scheme must be provided.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start \textit{shuffle read} simultaneously. The synchronized \textit{shuffle read} requests cause a burst of network traffic. As shown in Figure \ref{fig:util}, the data transfer put a great deal of stress on network bandwidth, which may results in network congestion and further hurts the performance of reduce stage.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking style I/O operation. This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in a I/O performance bounded cluster.
Besides, the legacy of spilling shuffle data to disk is too conservative in modern cluster with large memory. Compared to input dataset, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort is less than 25\% of input data. The data reported in \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. On the other hand, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory. 
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

\subsubsection{Multi-round Tasks Execution}\label{multi}
Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html/} 
suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ no. of nodes $\times$ no. of maximum container} per-node seem to be the right level of parallelism. Spark Configuration also recommends $2-3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}.
Since the shuffle data becomes available as soon as the end of map task execution. At the same time, the network is idle during the map stage (network utilization during map stage in Figure \ref{fig:util}). If the destination host of the shuffle data can be predicted in priori, the property of multi-round can be leveraged to overlap the \textit{shuffle read} operation.
% There are at least two persistent storage operations for each shuffle data block. At first, Spark will write shuffle data to the persistent storage after map task execution (i.e. \textit{shuffle write} in Figure \ref{fig:util}). During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation. The persistence of shuffle data was designed for fault tolerance. But we believe it is not necessary for today's cluster. Recall that shuffle data only exist in a short time scale. But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle. In addition, the capacity of memory and network has been increasing rapidly in recent years. As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}. On the other hand, the size of shuffle data is relatively small. For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data. The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%. We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.

Based on these observations, it is straightforward to come up with an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round DAG computing tasks, and uses memory to store the shuffle data for further decreasing shuffle overhead. To achieve this optimization:
\begin{itemize}
	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
\end{itemize}
% In the following section, we elaborate the methodologies to achieve three design goals.

### 2018-10-12 tex/relatedwork.tex
v1.3.2

@@
 \textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel}(BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Hadoop Madpreduce can also be considered as a special case of only one superstep in BSP model).
+\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
 In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
@@
 
-\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce \cite{hadoop} is the most classic approach to handle shuffle overhead.
+\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is the most classic approach to handle shuffle overhead.
 Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g.

### 2018-10-13 tex/abstract.tex
Version 2.0

@@
 
-In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
+In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead.
 Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
-To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs).
+To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
 {\color{blue}
@@
 }
-By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process.
-Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node.
+By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node.
+Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
 % {\color{red}

### 2018-10-13 tex/conclusion.tex
Version 2.0

@@
 \section{Conclusion}
- In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks.
-SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system.
-By scheduling tasks with application context, SCache bridges the gap among computing stages.
+In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
+SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
+By tasks pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
 %  {\color{red}
@@
 {\color{blue}
- At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Our evaluation result shows that SCache can provide a promising speedup to the DAG framework. 
+Our evaluations on Spark and Hadoop Mapreduce with SCache show that SCache can provide a promising speedup. 
 Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
 At last we use FRQ model to verify SCache shuffle optimization by mathematics.
- Therefore we believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks. 
+Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
 }

### 2018-10-13 tex/evaluation.tex
Version 2.0

@@
 This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-First we run a simple DAG job with single shuffle to analyze hardware utilization and impact of shuffle optimization from the scope of a task to a job. 
+First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
 Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
@@
 
-In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS \footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
 {\color{blue}
@@
 }
-At last, we measure the overhead of weighted reservoir sampling. 
-In short, SCache can decrease ~$89\%$ time of Spark shuffle.
-Furthermore, SCache achieves a ~$75\%$ and ~$50\%$ improvement of reduce stage completion time respectively in simple DAG application and Terasort without introducing extra network traffic.
-More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying optimization from SCache.
+Finally, we measure the overhead of weighted reservoir sampling. 
+In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
+More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
 {\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}
@@
 \subsection{Setup}\label{stepup}
-We implement a Spark demon to enable shuffle optimization as a representative.
-We run our experiments on a 50 m4.xlarge nodes cluster on Amazon EC2 \footnote{http://aws.amazon.com/ec2/}.
-Each node has 16GB memory and 4 CPUs.
-The network bandwidth is not specifically provided by Amazon.
-Our evaluations reveal the bandwidth is about 300 Mbps (see Figure \ref{fig:util}).
+We modified Spark to enable shuffle optimization of SCache as a representative.
+The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
+We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
+Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
+Our evaluations reveal the bandwidth is only about 300 Mbps (see Figure \ref{fig:util}).
 
@@
 %\subsubsection{Hardware Utilization}
-We first run the same single shuffle test as mentioned in Figure \ref{fig:util}.
+We first run the same single shuffle test shown in Figure \ref{fig:util}. 
+For each stage, we run 5 rounds of tasks with different input size. 
 As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
@@
 An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. 
-That is, SCache prevents the computing process from being cutting off by the I/O operations with a fine-grained resource allocation.
-It ensures the overall CPU utilization of the cluster stays in a high level.
-In addition, the decoupling of shuffle write helps free the CPU earlier and leads to a faster map task computation.
-At the same time, the shuffle pre-fetching in the early stage of map phase shifts the network transfer completion time, which decreases reduce stage completion time.
-The combination is the main performance gain we achieved on the scope of hardware utilization by SCache.
+It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
+On the one hand, the decoupling of shuffle write helps free the slot earlier, so that it can be re-scheduled to a new map task.
+On the other hand, with the help of shuffle pre-fetching, the decoupling of shuffle read significantly decreases the CPU idle time at the beginning of a reduce task.
+At the same time, SCache manages the hardware resources to store and transfer shuffle data without interrupting the computing process.
+As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark. 
 % \begin{figure}
@@
 % \end{figure}
-The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our analysis on hardware utilization.
-For each stage, we run 5 rounds of tasks with different input size.
-By running spark with SCache, the completion time of map stage can be reduced $10\%$ on average.
-For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
+The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
+% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
+% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
+% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
+For each stage, we pick the task that has median completion time. 
+In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
+It helps eliminate ~40\% of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
+Note that the shuffle write time can be observed even with the optimization of SCache. 
+The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.
 
-A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}.
-For each stage, we pick the median task.
-About 40\% of shuffle write time can be eliminated by SCache (Figure \ref{fig:maptask}) in a map task.
-Because the serialization of data is CPU intensive \cite{makingsense} and it is inevitable while moving data out of JVM, SCache can not eliminate the whole phase of shuffle write.
-It results in a less performance gain in the map stage.
-On the other hand, the network transfer introduces a significantly latency in shuffle read of reduce task (Figure \ref{fig:reducetask}).
-By doing shuffle data pre-fetching for the reduce tasks, the shuffle read time decreases ~$100\%$.
-That is, the explicit network transfer is perfectly overlapped by SCache shuffle pre-fetching.
-In overall, SCache can help Spark decrease by ~$89\%$ time in the whole shuffle process.
-In addition, heuristic reduce tasks scheduling achieves better load balance in cluster than the Spark default FIFO scheduling which may randomly assign two heavy tasks on a single node.
-So that we can have a significant performance gain in the completion time of the reduce stage.
+In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
+By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
+With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
+The in-memory cache of shuffle data further reduce the shuffle read time. 
+As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
+In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).
+
+In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
 
 \subsection{Terasort}
-We also evaluate Terasort --- a recognized shuffle intensive benchmark for distributed system analysis.
+We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort}-a recognized shuffle intensive benchmark for distributed system analysis.
 Terasort consists of two consecutive shuffles. 
-The first shuffle reads the input data and uses a customized hash partition function for re-partitioning.
-The second shuffle partitions the data through a range partitioner.
-As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
+The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
+As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
+It further proves the effectiveness of SCache's optimization.
+
+The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
+% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
 So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
-
-As shown in Figure \ref{fig:terasort}, we present the first shuffle as the evaluation of shuffle optimization.
-At the same time, we use the second shuffle to evaluate in the dimension of scheduling locality (Figure \ref{fig:terashuffle}).
-For the first shuffle, Spark with SCache runs 2 $\times$ faster during the reduce stage with the input data in a range from 10GB to 200GB.
-At the same time, Figure \ref{fig:terashuffle} reveals that SCache pre-scheduling produces exactly same network traffic of the second shuffle as Spark, which implies that SCache pre-scheduling can obtain the best locality while balancing the load.
-In contrast, Spark delays scheduling reduce tasks with the shuffle map output to achieve this optimum.
+In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
+So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
+In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
+By doing this, Spark minimizes the shuffle data through network. 
+At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
+It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load.
 
@@
 \subsection{Production Workload}
-We also evaluate some shuffle heavy queries from TPC-DS.
-TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g.
-ad-hoc, interactive OLAP, data mining, etc.).
+We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
 TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
-We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute.
-As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time.
-Spark with SCache outperforms the original Spark in almost all the queries.
+% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
+As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
+Note that we skip some queries due to the compatible issues. 
+Spark with SCache outperforms the original Spark in almost all tested queries. 
 Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
+It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
 The overall reduction portion of query time that SCache achieved is 40\% on average. 
@@
 \subsection{Overhead of Sampling}
-In this part, we evaluate the overhead of sampling with different input data sizes on one node and cluster scales.
-In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node.
-But it remains relatively stable when the cluster size scales up.
-It makes SCache a scalable system in cluster.
+We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
+In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
+Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
+Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
+So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
+Combined with the sampling overhead evaluation, we believe that SCache is scalable.

### 2018-10-13 tex/impl.tex
v1.3.2
Version 2.0

@@
 \section{Implementation}\label{impl}
-This section presents an overview of the implementation of SCache -- an open source cross-framework shuffle data management system with a DAG co-scheduler. 
+This section presents an overview of the implementation of SCache. 
 % {\color{red}
@@
 {\color{blue}
-In Subsection \ref{arch}, we will first present the system overview, and then we will detail SCache memory management in Subsection \ref{memorymanage}.
+We first present the system overview in Subsection \ref{arch} and the detail of sampling in Subsection\ref{sampling}. 
+The following two subsections focus on the two constraints on memory management.
 In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop Mapreduce and Spark. 
-In the last Subsection \ref{fault}, we will introduce the current status of SCache fault tolerance.
+At last, we discuss the cost of adapting SCache and the fault tolerance. 
 }
@@
 
-\begin{minipage}{\columnwidth}
-\begin{algorithm}[H]
-\caption{Heuristic MinHeap Scheduling for Single Shuffle}
-\label{hminheap}
-	\begin{algorithmic}[1]
-	\small
-	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
-		\State $m\gets$ partition number of map tasks
-		\State $R\gets$ sort $p\_reduces$ by size in descending order
-		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
-		\State $idx\gets$ len$\left(R\right) - 1$
-		\While{$idx \geq 0$}
-		\Comment{Schedule reduces by MinHeap}
-		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
-		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
-		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
-		\State Sift down $M\left[0\right]$ by $size$
-		\State $idx\gets idx-1$
-		\EndWhile
-		\State $max\gets$ maximum size in $M$
-		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
-		\ForAll{$reduce$ in $R$}
-		\Comment{Heuristic swap by locality}
-			\If{$reduce.assigned\_id \neq reduce.host\_id$}
-				\State $p\gets reduce.prob$
-				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
-				\State $upper\_bound \gets \left(1 + norm\right) \times max$
-				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
-			\EndIf
-		\EndFor
-		% \Comment{$m$ is the number of input data}
-		% \Comment{$r$ is partition number of reduces}
-		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
-		% \Comment{$c$ is $r*m$ array of composition data}
-		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
-		\Return $M$
-	\EndProcedure
-	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
-		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
-		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
-		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
-		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
-		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
-		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
-			\qquad \; $size\_assigned\leq upper\_bound$}
-			\State Swap $candidates$ and $reduce$
-			\State Update $size$ in $M$
-			\State Update $assigned\_host$ in $candidates$ and $reduce$
-		\EndIf
-	\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-\end{minipage}
-% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
-\begin{minipage}{\columnwidth}
-\begin{algorithm}[H]
-\caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
-\label{mhminheap}
-	\begin{algorithmic}[1]
-	\small
-	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
-		\State $m\gets$ partition number of map tasks
-		\Comment $shuffles$ is the previous schedule result 
-		\ForAll{$r$ in $p\_reduces$}
-			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
-			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
-				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
-				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
-			\EndIf
-		\EndFor
-		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
-		\ForAll{$host\_id$ in $M$}
-			\Comment Re-shuffle
-			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
-				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
-				\State Re-shuffle data to $host$
-				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
-				\EndIf
-			\EndFor
-		\EndFor
-		\Return $M$
-	\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-\end{minipage}
+SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
+As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
+
+The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
+The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
+The daemon bridges the communication between {\color{blue}DAG framework} and SCache.
+The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.
 
@@
 }
-The SCache master recognizes all shuffle dependencies in a RPC call as a shuffle scheduling unit.
 For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
-If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the dependent RDDs.
+If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}.
 We will elaborate the sampling procedure in the Section \ref{sampling}.
+% \begin{minipage}{\columnwidth}
+% \begin{algorithm}[H]
+% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
+% \label{hminheap}
+% 	\begin{algorithmic}[1]
+% 	\small
+% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
+% 		\State $m\gets$ partition number of map tasks
+% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
+% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
+% 		\State $idx\gets$ len$\left(R\right) - 1$
+% 		\While{$idx \geq 0$}
+% 		\Comment{Schedule reduces by MinHeap}
+% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
+% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
+% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
+% 		\State Sift down $M\left[0\right]$ by $size$
+% 		\State $idx\gets idx-1$
+% 		\EndWhile
+% 		\State $max\gets$ maximum size in $M$
+% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
+% 		\ForAll{$reduce$ in $R$}
+% 		\Comment{Heuristic swap by locality}
+% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
+% 				\State $p\gets reduce.prob$
+% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
+% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
+% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
+% 			\EndIf
+% 		\EndFor
+% 		% \Comment{$m$ is the number of input data}
+% 		% \Comment{$r$ is partition number of reduces}
+% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
+% 		% \Comment{$c$ is $r*m$ array of composition data}
+% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
+% 		\Return $M$
+% 	\EndProcedure
+% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
+% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
+% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
+% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
+% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
+% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
+% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
+% 			\qquad \; $size\_assigned\leq upper\_bound$}
+% 			\State Swap $candidates$ and $reduce$
+% 			\State Update $size$ in $M$
+% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
+% 		\EndIf
+% 	\EndProcedure
+% 	\end{algorithmic}
+% \end{algorithm}
+% \end{minipage}
 
-For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from %{\color{red}Spark executor's JVM }
-{\color{blue}framework worker} to the reserved memory through memory copy.
-After that the slot will be released without blocking on disk operations.
-When the shuffle map output is received, the SCache worker will notify the master of the block ID and reduce size distribution of this block (see map output in Figure \ref{fig:shuffle}).
-If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} and \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
-More specifically, when a map task is finished, each node will receive a broadcast message.
-SCache worker will filter the reduce tasks ID that will be launched on itself and start pre-fetching shuffle data from the remote.
+When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
+After that the slot will be released (without blocking on disk operations).
+When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
+If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
+% After that, when a map task is finished, each node will receive a broadcast message. 
+SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
 % {\color{red}
@@
 In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
-After insertion, DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
+After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
 }
+% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
+% \begin{minipage}{\columnwidth}
+% \begin{algorithm}[H]
+% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
+% \label{mhminheap}
+% 	\begin{algorithmic}[1]
+% 	\small
+% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
+% 		\State $m\gets$ partition number of map tasks
+% 		\Comment $shuffles$ is the previous schedule result 
+% 		\ForAll{$r$ in $p\_reduces$}
+% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
+% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
+% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
+% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
+% 			\EndIf
+% 		\EndFor
+% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
+% 		\ForAll{$host\_id$ in $M$}
+% 			\Comment Re-shuffle
+% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
+% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
+% 				\State Re-shuffle data to $host$
+% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
+% 				\EndIf
+% 			\EndFor
+% 		\EndFor
+% 		\Return $M$
+% 	\EndProcedure
+% 	\end{algorithmic}
+% \end{algorithm}
+% \end{minipage}
 
 \subsubsection{Reservoir Sampling}\label{sampling}
-If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the %{\color{red}daemon in Spark driver} 
-{\color{blue}framework master}. 
-The daemon then inserts a sampling job before the %{\color{red}corresponding RDD}
-{\color{blue} submitted computing job}. 
-The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition %{\color{red}of RDD}. 
-For the sample number, we set the size to $3 \times number\ of\ partitions$ for balancing overhead and accuracy (it can be tuned by configuration).
+If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, {\color{blue}the SCache master will send a sampling request to the framework master}. 
+The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
+For the sample number, it can be tuned to balance the overhead and accuracy. 
 The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). 
 At the same time, the items number is counted as the weight. 
-These sampling data will be aggregated by reduce ID on SCache master to predict the reduce partition size.
-After the prediction, SCache master will call Algorithm \ref{mhminheap} and \ref{hminheap} to do the scheduling.
+These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
+After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{fig/arch}
-	\caption{\color{red}SCache Architecture}
-	\label{fig:arch}
-	\vspace{-0.5em}
-\end{figure}
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.8\linewidth]{fig/arch}
+% 	\caption{\color{red}SCache Architecture}
+% 	\label{fig:arch}
+% 	\vspace{-0.5em}
+% \end{figure}
 
@@
 As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
-When the size of cached blocks reaches the limitation of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
-To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- all-or-nothing and context-aware-priority.
+When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
+To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data-all-or-nothing and context-aware-priority.
 
@@
 \subsubsection{All-or-Nothing Constraint}
-Memory cached shuffle blocks can speed up the reduce task execution process.
-But this acceleration of a single task is necessary but insufficient for a shorter stage completion time.
+This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
 Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks. 
-If one task misses a memory cache and exceeds the original bottleneck of this round, that task might become the new bottleneck and further slow down the whole stage.
+If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
 PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
-Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
-We refer to this as the all-or-nothing constraint.
+Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least. We refer to this as the all-or-nothing constraint.
 
-According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets corresponding blocks as the minimum unit of storage management.
-For those incomplete units, SCache will mark them as the lowest priority.
+According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
+For those incomplete units, SCache marks them as the lowest priority.
 % Following the all-or-noting constraint can maximum the improvement in stage completion time by using reserved memory efficiently.
@@
 \subsubsection{Context-Aware-Priority Constraint}
-Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once (without failure) in DAG computing.
-That is, the effort of improving hit rate in most legacy schemes can not benefit DAG application, while their approaches can easily violate the all-or-nothing constraint.
-SCache also leverages application context to select victim storage units when the reserved memory is full.
+Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once (without failure), but the legacy cache managements are designed to improve the hit rate.
+SCache leverages application context to select victim storage units when the reserved memory is full.
 
-At first, SCache master searches for the incomplete units and flushes all belonging blocks to disk cluster-widely.
-
-If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle units} and \textit{intra-shuffle unit}.
+At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
+If all the units are completed, SCache selects victims based on two factors-\textit{inter-shuffle} and \textit{intra-shuffle}.
 \begin{itemize}[noitemsep]
-	\item Inter-shuffle units: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority.
-For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished.
-So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle unit.
-For a FIFO scheduler, Spark schedules the task set that is submitted first.
-So SCache sets the priorities according to the submit time of each shuffle unit.
-	\item Intra-shuffle unit: SCache also needs to decide the priority among storage units inside a shuffle unit.
-According to the task scheduling inside a task set of Spark, the tasks with smaller ID will be scheduled firstly.
-Based on this, SCache can assign the lower priority to storage units with larger task ID.
+	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
+	For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
+	So SCache sets the priorities according to the submission time of each shuffle.
+	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
+	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
+	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
+	% So SCache sets the priorities according to the submit time of each shuffle unit.
+	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
+	For example Spark schedules tasks with smaller ID at first. 
+	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
 \end{itemize}
@@
 \subsection{Fault tolerance}\label{fault}
-Since fault tolerance is not a crucial goal of SCache, we have not implemented fault tolerance mechanism.
+Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
 We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
-For SCache worker, a promising way to prevent failure is to select some backup nodes to store replications of shuffle data during pre-scheduling.
-In addition, there are also advanced fast recovery techniques such as FineFRC \cite{finefrc}.
-We leave this to the future work.
+If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of DAG computing.
+A possible way to handle this failure is selecting some backup nodes to store replications. 
+But the replications can introduce a significant network overhead \cite{availability}.  
+Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
+We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
+Meanwhile, SCache can still provide shuffle optimization during the recovery.
 

### 2018-10-13 tex/intro.tex
Version 2.0

@@
 \IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-\IEEEPARstart{R}{ecent} years have witnessed widespread use of sophisticated frameworks such as Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
+\IEEEPARstart{R}{ecent} years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
+Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
 Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
-Such shuffle phase places significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance.
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs\cite{managing}.
+Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
+For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs \cite{managing}.
 
-Although continued efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, the shuffle is often poorly optimized in practice.
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
+the shuffle is often poorly optimized in practice.
 % take over shuffle
 %shuffle characteristic
-In particular, we observe that one major deficiency lies in a lack of fine-grained, coordinated management among different system resources.
+In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
 %In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
-As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stage (i.e., map task).
-And the \textit{shuffle read} fetches intermediate results from \emph{remote} disks through network, which is commonly integrated as part of the tasks in descendant stage (i.e., reduce task).
-Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to each of the computation task, and the resources are released only after the task finishes.
+As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
+And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
+Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
 Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
-However, since each phase receives a fixed bundle of resources, attaching the \emph{I/O intensive} shuffle phase to the \emph{CPU/memory intensive} computation phase results in a poor multiplexing between computational and I/O resources.
+However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
 %The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
@@
 Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
-Note that the shuffle read phase starts fetching data only after all the data from its ancestor stage by default.
+Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
+Meanwhile, the reduce tasks belonging to a same execution phase are scheduled at the same time by default. 
 As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
 Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
-To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier such as \textit{early start} from Apache Hadoop\footnote{http://hadoop.apache.com/}.
-However, such early start is by no means a panacea.
-This is because although the reduce tasks can start fetching data earlier, the computation can only take place after all the data is ready.
-Since each phase receives a fixed bundle of resources, starting a reduce task early always introduces an unnecessary early allocation of slot.
+To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce\footnote{http://hadoop.apache.com/}. 
+However, such early-start is by no means a panacea. 
+This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
 
@@
 
-Can we efficiently optimize the data shuffling without significantly changing every framework?
-In this paper, we answer this question in the affirmative with S(huffle)Cache, an opne source plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
-
+Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
+In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
 Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
 SCache's effectiveness lies in the following two key ideas.
-First, SCache decouples the shuffle read and write from both map and reduce tasks.
+First, SCache decouples the shuffle write and read from both map and reduce tasks.
 Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
-In addition, SCache pre-schedules the reduce tasks and pre-fetches the shuffle data to the location of the reduce tasks without launching them.
-Such pre-scheduling and pre-fetching effectively desynchronize the network I/O operation, while avoiding the waste of computational resources compared to the early start mechanism.
+In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
+% for the reduce tasks.
+Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
+and avoid the extra early allocation of slots.
 %In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks.
@@
 
-The workflow of DAG framework with SCache is presented in Figure \ref{fig:workflow}.
-SCache hijacks the intermediate data of a map task in memory space.
-The disk operation is skipped and the slot is released after memory copy.
-The in-memory intermediate data is immediately pre-fetched through network after pre-scheduling.
-By releasing the slot earlier and starting the network transfer ahead of reduce tasks, SCache can help the DAG framework achieve a significant performance gain.
-A by-product optimization of pre-scheduling is that SCache can provide a more balanced load for each node and further benefit the reduce stage by avoiding data skew.
+The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
+SCache replaces the disk operations of shuffle write by the memory copy in map tasks. 
+The slot is released after the memory copy. 
+The shuffle data is stored in the reserved memory of SCache until all reduce tasks are pre-scheduled. 
+Then the shuffle data is pre-fetched according to the pre-scheduling results.  
+The application-context-aware memory management caches the shuffle data in memory before launching the reduce task.
+By applying these optimizations, SCache can help the DAG framework achieve a significant performance gain.
 
-The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks}.
-It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}.
-Unfortunately the complexity of DAG can amplify the defects of na\"{i}ve pre-scheduling schemes.
-In particular, randomly assign reduce tasks might result in a collision of two heavy tasks on one node.
+The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks without launching}. 
+% It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}. 
+First, the complexity of DAG can amplify the defects of na\"{i}ve scheduling schemes. 
+In particular, randomly assigning reduce tasks might result in a collision of two heavy tasks on one node. 
 This collision can aggravate data skew, thus hurting the performance. 
-To address this challenge, we propose a heuristic scheme to predict the shuffle output distribution and pre-schedule reduce tasks (Section \ref{opt}).
+Second, pre-scheduling without launching violates the design of most frameworks that launch a task after scheduling.
+To address the challenges, we propose a heuristic task pre-scheduling scheme with shuffle data prediction and a task co-scheduler (Section \ref{opt}).
 
-The second challenge is the \textit{in-memory data management}.
+Another challenge is the \textit{in-memory data management}. 
 To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
-However, the memory is a precious resource for DAG computing.
-To minimize the reserved memory while maximizing the performance gain of optimization and memory utilization, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
+% However, the memory is a precious resource for DAG computing. 
+To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
 %The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.
@@
 We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
-We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model.
-We use FRQ model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
+We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.

### 2018-10-13 tex/motivation.tex
Version 2.0

@@
 
-In large scale data parallel computing, shuffle is designed to achieve an all-to-all data blocks transfer among nodes.
-For a clear illustration, we use \textit{map tasks} to define the tasks that generate shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
+In large scale data parallel computing, shuffle is designed to achieve an all-to-all data transfer among nodes. 
+For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
 % Note that one task may have both shuffle data generation and consumption in modern DAG framework.
@@
 Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
-The total number of buckets equals the number of tasks in the next step.
+The total number of buckets equals the number of reduce tasks in the successive step.
 % shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
 The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
-The partitioned shuffle output data will be spilled to local persistent storage during shuffle write.
-Shuffle read starts at the beginning of reduce tasks. It fetches data as reduce input from both remote and local storage.
+Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
+Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.
 
-\begin{figure}
-	\includegraphics[width=\linewidth]{fig/util}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
-	\label{fig:util}
-\end{figure}
 %In short, shuffle is loosely coupled with application context and it's I/O intensive.
-
-\textbf{Impact of shuffle process}. Shuffle process is I/O intensive, which might introduces a significant latency to the application. Reports show that 60\% of MapReduce jobs at Yahoo!
-and 20\% at Facebook are shuffle intensive workloads \cite{shufflewatcher}. For those shuffle intensive jobs, the shuffle latency may even dominate Job Completion Time (JCT).
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle intensive jobs \cite{managing}.
+\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduces a significant latency to the application. 
+Reports show that 60\% of MapReduce jobs at Yahoo! and 20\% at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
+For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
+For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
 % Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
@@
 \subsection{Observations} \label{observation}
-Of course, shuffle is unavoidable in a DAG computing process.
-But can we mitigate or even remove the overhead of shuffle?
-To find the answers, we run some typical Spark applications in a 5-node EC2 cluster with \texttt{m4.xlarge}.
-We then measure the CPU utilization, I/O throughput, and tasks execution information of each node.
-Here we present the trace of one node running Spark \textit{GroupByTest} in Figure \ref{fig:util} as an example.
+% Of course, shuffle is unavoidable in a DAG computing process. 
+Can we mitigate or even remove the overhead of shuffle? 
+To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
+Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
 This job has 2 rounds of tasks for each node.
-We have marked the \textit{execution} phase as from the launch time of the first task to the execution finish timestamp of the last one.
-The \textit{shuffle write} phase is marked from the timestamp of the beginning of the first partitioned data write.
-The \textit{shuffle read and execution} phase is marked from the start of the first reduce launch timestamp.
-
+The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
+The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
+The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
 % Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle.
@@
 % \end{figure*}
-
 \subsubsection{Coarse Granularity Resource Allocation}
-In Figure \ref{fig:util}, when a slot is scheduled to a task, it will not be released until the the task completes \textit{shuffle write}.
-On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
-Meanwhile, shuffle is I/O intensive.
-Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without involving much CPU.
-The current coarse slot --- task mapping results in an inconsistency between resource demands and slot allocation thus decreases the resource utilization.
-To break this inconsistency, a finer granularity resource allocation scheme must be provided.
+When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
+On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
+Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
+The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
+Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
+A finer granularity resource allocation scheme should be provided to reduce these delays.
 
 \subsubsection{Synchronized Shuffle Read}
-Almost all reduce tasks start \textit{shuffle read} simultaneously.
-The synchronized \textit{shuffle read} requests cause a burst of network traffic.
-As shown in Figure \ref{fig:util}, the data transfer put a great deal of stress on network bandwidth, which may results in network congestion and further hurts the performance of reduce stage.
+Almost all reduce tasks start shuffle read simultaneously. 
+The synchronized shuffle read requests cause a burst of network traffic. 
+As shown in Figure \ref{fig:util}, 
+the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
+It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
 
+\begin{figure}
+	\includegraphics[width=\linewidth]{fig/util}
+	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
+	\label{fig:util}
+	\vspace{-1em}
+\end{figure}
+
 \subsubsection{Inefficient Persistent Storage Operation}
-At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking style I/O operation.
-This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in a I/O performance bounded cluster.
-Besides, the legacy of spilling shuffle data to disk is too conservative in modern cluster with large memory.
+At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
+This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
+Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
 Compared to input dataset, the size of shuffle data is relatively small. 
-For example, shuffle size of Spark Terasort is less than 25\% of input data.
-The data reported in \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%.
-On the other hand, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory.
+For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than 25\% of input data. 
+The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as 10\%-20\%. 
+On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
+but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
 We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.
@@
 Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
-For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html/} 
-suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ no.
-of nodes $\times$ no.
-of maximum container} per-node seem to be the right level of parallelism.
-Spark Configuration also recommends $2-3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}.
-Since the shuffle data becomes available as soon as the end of map task execution.
-At the same time, the network is idle during the map stage (network utilization during map stage in Figure \ref{fig:util}).
-If the destination host of the shuffle data can be predicted in priori, the property of multi-round can be leveraged to overlap the \textit{shuffle read} operation.
+For a cluster with $n$ slots, the number of tasks should be $n \times k (k \geq 1)$. 
+For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.
+Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
+
+Since the shuffle data becomes available as soon as the end of a task's execution, 
+and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
+the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
+% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
 % There are at least two persistent storage operations for each shuffle data block.
@@
 
-Based on these observations, it is straightforward to come up with an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round DAG computing tasks, and uses memory to store the shuffle data for further decreasing shuffle overhead.
+Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
+To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data.
 To achieve this optimization:

### 2018-10-13 tex/optimization.tex
Version 2.0

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve the three design goals. 
The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
\begin{figure}
	\centering
	\includegraphics[width=0.5\linewidth]{fig/reduce_cdf}
	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
	\label{fig:cdf}
	\vspace{-1em}
\end{figure}
\subsection{Decouple Shuffle from Execution}
% \ifrevision
% \reversemarginpar
% \marginpar{B1,C2}
% \fi
To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% During shuffle write of map tasks, the partitioned shuffle data blocks will be written on the disks.
% Each block contains a part of input data of a particular reduce task. 
To prevent the release of a slot being blocked by shuffle write,  
SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
After the memory copy, the slot will be released immediately.

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
\subsection{Pre-schedule with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
Once the tasks are scheduled, the slots will be occupied to launch them. 
On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling. 
% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}. We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time. Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes. The result is shown in \ref{fig:sim}.
% \begin{figure*}
% 	\centering
% 	\begin{minipage}{0.34\linewidth}
% 		\begin{figure}[H]
% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
% 			\caption{Shuffle Size Comparing with Input Size}
% 			\label{fig:shuffle_size}
% 		\end{figure}
% 	\end{minipage}
% 	\begin{minipage}{0.65\linewidth}
% 		\begin{figure}[H]
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
% 				\caption{Shuffle Time Fraction CDF}
% 				\label{fig:cdf}
% 			\end{subfigure}	
% 			\begin{subfigure}{0.5\textwidth}
% 				\includegraphics[width=\linewidth]{fig/sim}
% 				\caption{Stage Completion Time Improvement}
% 				\label{fig:sim}
% 			\end{subfigure}	
% 			\caption{Emulate Result of OpenCloud Trace}
% 		\end{figure}
% 	\end{minipage}
% \end{figure*}
% \begin{figure}
\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
The average shuffle read time is 3.2\% of total reduce completion time.
\begin{figure}
	\centering
	\includegraphics[width=0.66\linewidth]{fig/sim}
	\caption{Stage Completion Time Improvement of OpenCloud Trace}
	\label{fig:sim}
	\vspace{-1em}
\end{figure}
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{fig/shuffle}
	\caption{Shuffle Data Prediction}
	\label{fig:shuffle}
	\vspace{-1em}
\end{figure}
\begin{figure*}
	\centering
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/hash_pre}
		\caption{Linear Regression Prediction of Hash Partitioner}
		\label{fig:hash_pre}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
	\end{subfigure}
	\begin{subfigure}[b]{0.31\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	\vspace{-1em}
\end{figure*}

\subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
% \ifrevision
% \marginpar{B2,E7}
% \fi
The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$, 
where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}). 
The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
So the pre-scheduling can be made if the "prediction" of size of shuffle block is practical.
% \hlyellow{
% The shuffle size of each reduce task is decided by input data, map task computation, and hash partitioner. 
% Each map task produces a data block for each reduce task. 
% }
% The size of each reduce partition can be calculated $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$ ($m$ is the number of map tasks). 
% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}).
% \ifrevision
% \reversemarginpar
% \marginpar{B2,D6,D8}
% \fi

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark \cite{apachespark}.  
For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
The observed map outputs are randomly picked. 
With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
The prediction results also fit them well. 
However, the data partitioned by Spark RangePartitioner \cite{apachespark} in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew. 
That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.

% Several map outputs (marked as Map Output in Figure \ref{fig:shuffle}) are picked as observation objects to train the model and than predict the final reduce distribution.
% \ifrevision
% \reversemarginpar
% \marginpar{D6,E3}
% \fi
To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
On the other hand, the result of linear regression comes out with a large relative error. 
Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
We will show the overhead evaluation of sampling in Section \ref{evaluation}.

During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
\begin{equation}
\label{equationprob}
\begin{aligned}
	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
    m &= \text{number of map tasks}
\end{aligned}
\end{equation}
This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}

% \ifrevision
% \marginpar{\tiny PC2,C1,D7/9,E4}
% \fi
As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
But ignoring the data locality can introduce extra network transfer. 
In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap scheduling algorithm (Algorithm \ref{hminheap}).

For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$. 
\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Heuristic MinHeap Scheduling for Single Shuffle}
\label{hminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
		\State $m\gets$ partition number of map tasks
		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
		\State $idx\gets 0$
		\While{$idx <$ len$R$}
		% \Comment{Schedule reduces by MinHeap}
		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
		\State Sift down $M\left[0\right]$ by $size$
		\State $idx\gets idx-1$
		\EndWhile
		\State $max\gets$ maximum size in $M$
		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
		\ForAll{$reduce$ in $R$}
		\Comment{Heuristic locality swap}
			\If{$reduce.assigned\_id \neq reduce.host\_id$}
				\State $p\gets reduce.prob$
				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
				\State $upper\_bound \gets \left(1 + norm\right) \times max$
				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
			\EndIf
		\EndFor
		% \Comment{$m$ is the number of input data}
		% \Comment{$r$ is partition number of reduces}
		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
		% \Comment{$c$ is $r*m$ array of composition data}
		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
		\Return $M$
	\EndProcedure
	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
		\State Swap tasks between node $host\_id$ and node $assigned\_id$
		\State of $reduce$ without exceeding the $upper\_bound$
		\State of both nodes.
		\State Return if it is impossible.
		% \State $reduces \gets M\left[reduce.host\_id\right].reduce$	
		% \State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
		% \State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
		% \State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
		% \State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
		% \If{$size\_host\leq upper\_bound$ \textbf{and} \\
		% 	\qquad \; $size\_assigned\leq upper\_bound$}
		% 	\State Swap $candidates$ and $reduce$
		% 	\State Update $size$ in $M$
		% 	\State Update $assigned\_host$ in $candidates$ and $reduce$
		% \EndIf
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}

\noindent
\begin{minipage}{0.95\columnwidth}
\begin{algorithm}[H]
\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
\label{mhminheap}
	\begin{algorithmic}[1]
	\small
	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
		\State $m\gets$ partition number of map tasks
		\Comment \emph{shuffles} is the previous schedule result 
		\ForAll{$r$ in $p\_reduces$}
			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
			\If{$new\_prob\geq r.prob$}
				\State $r.prob\gets new\_prob$
				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
			\EndIf
		\EndFor
		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
		\ForAll{$host\_id$ in $M$}
			\Comment Re-shuffle
			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
				\State Re-shuffle data to $host$
				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
				\EndIf
			\EndFor
		\EndFor
		\Return $M$
	\EndProcedure
	\end{algorithmic}
\end{algorithm}
\end{minipage}
\subsubsection{Cope with Multiple Shuffle Dependencies}
% \ifrevision
% \marginpar{E5}
% \fi
A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
For those pending shuffles, it is impossible to predict their sizes. 
This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
But doing this introduces large overhead such as extra task serialization. 
To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.

As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \emph{shuffles} scheduled by Heuristic MinHeap are counted. 
When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \emph{shuffles}. 
After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
which leads to a higher probability of tasks swap in $SWAP\_TASKS$.

% It means the $SWAP\_TASKS$ can help revise the scheduling to match the previous mapping as much as possible while maintaining the good load balance.

% As for the input of $SCHEDULE$ function in Algorithm \ref{hminheap}, $m$ is the partition number of input data; $h$ is the array of nodes ID in cluster; $p\_reduces$ is the predicted reduce matrix. Each row in $p\_reduces$ contains $rid$ as reduce partition ID; $size$ as predicted size of this partition; $prob$ as the maximum composition portion of reduce data; $host\_id$ as the node ID that produces the maximum portion of reduce data, and $assigned\_id$ as the node ID assigned by Algorithm \ref{hminheap}. As for $M$, it is consists $host\_id$, an array of $reduce$ scheduled on this node and the $size$ of them.

### 2018-10-13 tex/relatedwork.tex
Version 2.0

@@
 \section{Related Work}
-This section describes related work of shuffle optimization.
 
@@
 
-\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is the most classic approach to handle shuffle overhead.
-Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g.
-slow-start, map and reduce slot ratio, etc).
-DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage to decrease the time of waiting for outputs of map tasks.
-All of them left the explicit I/O time in an occupied computation slot.
-Instead, SCache can start shuffle pre-fetching without consuming slots.
+\textbf{Pre-scheduling}: Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
+Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
+DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
+All of them have the explicit I/O time in occupied slots. 
+SCache instead starts shuffle pre-fetching without consuming slots. 
 iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
 But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
-iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages, in order to start fetching data from previous stage earlier.
+iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
 But we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
-Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing by combining DAG information and heuristic algorithms.
+Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.
 
+%  by combining DAG information and heuristic algorithms.
 \textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
@@
 Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
-But all of them can not mitigate explicit I/O in both map and reduce tasks.
-In addition their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle in-memory caching and pre-fetching.
+But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
+In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
 

### 2018-10-13 tex/abstract.tex
Version 2.2

@@
 During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
-FRQ model displays utilization of resources in time dimension and calculate exectuion time of computing jobs on different DAG frameworks. 
+FRQ model displays utilization of resources in time dimension and calculate execution time of computing jobs on different DAG frameworks. 
 We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
@@
 Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
-On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
+On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
 }

### 2018-10-13 tex/evaluation.tex
Version 2.2

@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop Mapreduce with Scache optimize job completion time by up to 15\% and an average of 13\%}
+{\color{blue}Meanwhile, Hadoop Mapreduce with SCache optimize job completion time by up to 15\% and an average of 13\%}
 
@@
 
-To prove SCache compatibility as a cross-framework plug-in, we also implemented Scache on Hadoop MapReduce as the external shuffle service and co-scheduler.
+To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler.
 Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.
@@
 Furthermore, pre-fetching utilize the idle IO throughput in the Map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with Scache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
 }

### 2018-10-13 tex/intro.tex
Version 2.2

@@
 By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
-I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delay the execution time of reduce phase. 
+I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
 This situation will be amplified in shuffle-sensitive tasks.
@@
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark.
-On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
+On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
 }

### 2018-10-15 coverletter/coverletter.tex
Version 2.2

@@
 In conference paper, we only implement SCache on Spark. To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
-By employing shuffle data management, SCache can also optimize the computing performance of Hadoop Mapreduce.
+By employing shuffle data management, SCache can also optimize the computing performance of Hadoop MapReduce.
 \item
@@
 First we verify FRQ model under two different environments, the error between calculated value and experimental value is basically below 10\%.
-Furthermore, we evaluate the performance of SCache on Hadoop Mapreduce in the same environment as conference paper.
-After utilizing pre-fetching of SCache, Hadoop Mapreduce with SCache optimize overall job execution time by 15\%.
+Furthermore, we evaluate the performance of SCache on Hadoop MapReduce in the same environment as conference paper.
+After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize overall job execution time by 15\%.
 \end{enumerate}

### 2018-10-15 tex/conclusion.tex
Version 2.2

@@
 {\color{blue}
-Our evaluations on Spark and Hadoop Mapreduce with SCache show that SCache can provide a promising speedup. 
-Furthermore, we propose \textit{Framework Resources Quantification}(FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
+Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
+Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
 At last we use FRQ model to verify SCache shuffle optimization by mathematics.

### 2018-10-15 tex/evaluation.tex
Version 2.2

@@
 To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop Mapreduce with SCache.
+Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
 }
@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop Mapreduce with SCache optimize job completion time by up to 15\% and an average of 13\%}
+{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimize job completion time by up to 15\% and an average of 13\%}
 
@@
 
-\subsection{Simple DAG Analysis}
+\subsection{Simple DAG Analysis}\label{simpledag}
 %\subsubsection{Hardware Utilization}
@@
 {\color{blue}
-\subsection{Hadoop Mapreduce with SCache}
+\subsection{Hadoop MapReduce with SCache}
 
@@
 
-Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop Mapreduce running Terasort.
+Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort.
 Both figures have the same proportion of time.
 Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
-As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop Mapreduce without SCache writes intermediate data locally in the Map phase.
+As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the Map phase.
 The shuffle phase and reduce phase start simultaneously.
-Because the large amount of shuffle data reaches the network bottleneck, The beginning part of reduce needs to wait needs to wait for network transfer.
+Because the large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait needs to wait for network transfer.
 This causes the CPU resources to be idle.
@@
 This avoids the Reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilize the idle IO throughput in the Map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop Mapreduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
+Furthermore, pre-fetching utilizes the idle IO throughput in the Map phase.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
 }
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-				\caption{\color{blue}Hadoop Mapreduce With SCache}
+				\caption{\color{blue}Hadoop MapReduce With SCache}
 				\label{fig:hadoop_terasort_scache}
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-				\caption{\color{blue}Hadoop Mapreduce Without SCache}
+				\caption{\color{blue}Hadoop MapReduce Without SCache}
 				\label{fig:hadoop_terasort_origin}
@@
 		\end{subfigure}
-		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop Mapreduce Terasort job}
+		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
 		\label{fig:hadoop_terasort}
@@
 	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
-	\caption{\color{blue}Hadoop Mapreduce Terasort completion time}
+	\caption{\color{blue}Hadoop MapReduce Terasort completion time}
 	\label{fig:hadoop_terasort_time}

### 2018-10-15 tex/impl.tex
Version 2.2

@@
 The following two subsections focus on the two constraints on memory management.
-In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop Mapreduce and Spark. 
+In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
 At last, we discuss the cost of adapting SCache and the fault tolerance. 
@@
 When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
-Before the computing tasks begin, the shuffle dependecies are determined based on job configuration.
+Before the computing tasks begin, the shuffle dependencies are determined based on job configuration.
 }
@@
 Shuffle optimization of SCache inevitably requires modification on dependent DAG framework.
-SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}.
+SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
 In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order.
@@
 
-To prove the cross-framework capability of SCache, we implement SCache on Hadoop Mapreduce and Spark respectively.
-Taking Hadoop Mapreduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC.
+To prove the cross-framework capability of SCache, we implement SCache on Hadoop MapReduce and Spark respectively.
+Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC.
 It takes about 400 lines of code.
-In Spark, We mainly modified the DAGScheduler and the corresponding data fetcher.
+In Spark, we mainly modified the DAGScheduler and the corresponding data fetcher.
 It only takes about 500 lines of code.
-Such hundreds of lines of code modification is very small compared to the hundreds of thousands of lines of code in DAG framework.
+Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
 we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.

### 2018-10-15 tex/intro.tex
Version 2.2

@@
 {\color{blue}
-In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model.
+In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
 FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension.
@@
 We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
-We have also designed a performance model called \textit{Framework Resources Quantification}(FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
+We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.

### 2018-10-15 tex/model.tex
Version 2.2

@@
 
-In this chapter, we introduce \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
+In this chapter, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
 FRQ model quantifies computing and I/O resources and displays them in time dimension.
@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs}(DAGs) to describe computation logic.
+The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic.
 A shuffle phase is required between each adjacent DAG computation phase.
@@
 \begin{enumerate}
-	\item Input Data Size\((D)\): The data size of the computation phase.
-	\item Data Conversion Rate\((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
-    \item Computation Round Number\((N)\): The number of rounds needed to complete the computation phase using the current computation resources.
+	\item Input Data Size \((D)\): The data size of the computation phase.
+	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
+    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources.
 The number of rounds depends on the current computation resources and the settings of the computation job.
@@
 Then we need 4 rounds of computation to complete the Map phase.
-    \item Computation Speed\((V_{i})\): 
+    \item Computation Speed \((V_{i})\): 
     The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
-    \item Shuffle Speed\((V_{Shuffle})\): 
+    \item Shuffle Speed \((V_{Shuffle})\): 
     Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
@@
 \(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time, and \(K \times T_{P\_Shuffle}\) represents the calculated overhead.
-\(K\) is empirical value.The overhead depends on the parallel time of shuffle phase and the Reduce phase.The parallel time is denoted by \(T_{P\_Shuffle}\).
+\(K\) is empirical value.
+The overhead depends on the parallel time of shuffle phase and the Reduce phase.The parallel time is denoted by \(T_{P\_Shuffle}\).
 And the total time of shuffle phase is represented by \(T_{Shuffle}\).
-Because the computatinon of the Reduce phase relies on the data transfer results of the Shuffle phase, a portion of the computation in the Reduce phase need to wait for the transfer results.
+Because the computation of the Reduce phase relies on the data transfer results of the Shuffle phase, a portion of the computation in the Reduce phase need to wait for the transfer results.
 The overhead is caused by these waiting.
@@
 Improving IO speed is a effective way to reduce shuffle time.
-Another optimization method is to use the idle IO resources in the Map phase for pre-fetching(see Figure \ref{fig:model_basic}).
+Another optimization method is to use the idle IO resources in the Map phase for pre-fetching (see Figure \ref{fig:model_basic}).
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
@@
 				\includegraphics[width=\linewidth]{fig/model_original}
-				\caption{\color{blue}Full Serial Mapreduce}
+				\caption{\color{blue}Full Serial MapReduce}
 				\label{fig:model_original}
@@
 				\includegraphics[width=\linewidth]{fig/model_hadoop}
-				\caption{\color{blue}Hadoop Mapreduce}
+				\caption{\color{blue}Hadoop MapReduce}
 				\label{fig:model_hadoop}
@@
 		\end{subfigure}
-		\caption{\color{blue}FRQ Model With Different Scheduling Strategies}
+		\caption{\color{blue}FRQ Model with Different Scheduling Strategies}
 		\label{fig:model_strategies}
@@
 First, we analyze a naive scheduling strategy.
-As shown in Figure \ref{fig:model_original}, FRQ model describes a Mapreduce job that is fully serially executed.
+As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed.
 The parallel time of shuffle phase and the Reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
@@
 
-Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop Mapreduce.
-In Hadoop Mapreduce, Shuffle phase and Reduce phase start at the same time.
+Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop MapReduce.
+In Hadoop MapReduce, Shuffle phase and Reduce phase start at the same time.
 In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\).
-Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase(see equation \ref{equation_Treduce}).
-Because the Shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\)(see equation \ref{equation_Tjob}).
+Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase (see equation \ref{equation_Treduce}).
+Because the Shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
 The execution time of Shuffle phase is hidden in the Reduce phase.
@@
 		\end{subfigure}
-		\caption{\color{blue}FRQ Model With SCache}
+		\caption{\color{blue}FRQ Model with SCache}
 		\label{fig:model_scache}
@@
 
-Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop Mapreduce with SCache (Suppose N is 4).
+Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
 SCache starts pre-fetching and pre-scheduling in the Map phase.
@@
     \item 
-    \(V_{Map} \times R \ge V_{Shuffle}\)(Figure \ref{fig:model_scache1}): 
+    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
 	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated.
@@
 
-    \item \(V_{Map} \times R < V_{Shuffle}\)(Figure \ref{fig:model_scache2}): 
-	When the speed of generating shuffle data(\(V_{Map} \times R\)) is less than the shuffle speed(\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated.
+    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
+	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated.
 As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round.
@@
 
-Compared to the original Hadoop Mapreduce resource scheduling strategy, Hadoop Mapreduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \textit{Reduce Time}(\(T_{Reduce}\)).
+Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \textit{Reduce Time} (\(T_{Reduce}\)).
 This is how pre-fetching optimizes the total execution time of job.
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop Mapreduce on 4 nodes cluster in FRQ model}
+\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in FRQ model}
 \label{table1}
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop Mapreduce on 50 AWS m4.xlarge nodes cluster in FRQ model}
+\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in FRQ model}
 \label{table2}
@@
 Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs.
-To simplify the calculation of the FRQ model, we use Hadoop Mapreduce as framwork(only three phases: \textit{Map, Shuffle,} and \textit{Reduce}) and Terasort as experimental application.
-We deploye Hadoop with SCache and without SCache on both environments.
+To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework (only three phases: \textit{Map, Shuffle,} and \textit{Reduce}) and Terasort as experimental application.
+We deployed Hadoop with SCache and without SCache on both environments.
 
@@
 The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
-In the case of SCache, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache1}(\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
+In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
 In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}).
 \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
-The formular of \(Error\) is:
+The formula of \(Error\) is:
 \begin{equation}
@@
 The formulas in the table are all the same except \(T_{P\_Shuffle}\).
-In this environment, Terasort on Hadoop Mapreduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
+In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
 In the previous case, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).
@@
 		\end{subfigure}
-		\caption{\color{blue}Network utilization on Hadoop Mapreduce with SCache}
+		\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
 		\label{fig:hadoop_net}
@@
 Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment.
-The network utilization is 5 regular peaks, this situation is also consistent with Figure \ref{fig:model_scache2}.
+The network utilization has 5 regular peaks.
+This situation is also consistent with Figure \ref{fig:model_scache2}.
 Therefore, we believe that FRQ model is able to accurately describe framework with SCache.
@@
 In the case where the input data is small and the total time is short, the error caused by the overhead is amplified.
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance .
-Therefore, We believe that FRQ model can accurately describe DAG framework.
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance.
+Therefore, we believe that FRQ model can accurately describe DAG framework.
 }

### 2018-10-15 tex/relatedwork.tex
Version 2.2

@@
 {\color{blue}
-\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel}(BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on(Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
+\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
+\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
 In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
-Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification}(FRQ) model to describe the performance of DAG frameworks.
+Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
 In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce.
@@
 In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job.
-The execution is seperated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce.
-The performance models describe each above-mentioned phases and combine into a overall Mapreduce job model.
+The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce.
+The performance models describe each above-mentioned phases and combine into a overall MapReduce job model.
 However, none of the above models meet our requirements for analyzing shuffle.

### 2018-10-16 tex/evaluation.tex
fzw revision

@@
 Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
-As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the Map phase.
+As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
 The shuffle phase and reduce phase start simultaneously.
@@
 This causes the CPU resources to be idle.
-As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the Map phase.
-This avoids the Reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilizes the idle IO throughput in the Map phase.
+As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the map phase.
+This avoids the reduce phase waiting for the shuffle data.
+Furthermore, pre-fetching utilizes the idle IO throughput in the map phase.
 As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.

### 2018-10-16 tex/impl.tex
fzw revision

@@
 {\color{blue}
-We first present the system overview in Subsection \ref{arch} and the detail of sampling in Subsection\ref{sampling}. 
-The following two subsections focus on the two constraints on memory management.
+We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
+The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
 In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
@@
 {\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{blue} original scheduler in framework master}.
+ {\color{blue} original scheduler in framework}.
 
-SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
+% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
 As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
 
-The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-The daemon bridges the communication between {\color{blue}DAG framework} and SCache.
+% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
+% The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
+% The daemon bridges the communication between {\color{blue}DAG framework} and SCache.
 The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.
@@
 {\color{blue}
-When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
-Before the computing tasks begin, the shuffle dependencies are determined based on job configuration.
+When a DAG job is submitted, the DAG information will be generated in framework task scheduler. 
+Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
 }
@@
 When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
-After that the slot will be released (without blocking on disk operations).
+After that the slot will be released (without being blocked on disk operations).
 When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
@@
 SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order.
-(b)The shuffle data between the Map task and the Reduce task should be transfer to SCahce Storge Management.
+In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow pre-scheduled result of SCache.
+(b)The shuffle data between the Map task and the Reduce task should be transfered to SCahce Storge Management.
 
-To prove the cross-framework capability of SCache, we implement SCache on Hadoop MapReduce and Spark respectively.
+To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
 Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC.

### 2018-10-16 tex/intro.tex
fzw revision

@@
 By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
-I/O resource in Map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
-This situation will be amplified in shuffle-sensitive tasks.
+I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
+This situation will be amplified in shuffle-heavy tasks.
 }
@@
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
-On Apache Spark, we conduct basic test GroupByTest.
+On Apache Spark, we conduct basic test \textit{GroupByTest}.
 We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling.
 On Apache Hadoop, we focus on Terasort benchmark.
-In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios.
+In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications.
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark.

### 2018-10-16 tex/model.tex
fzw revision

@@
 	\includegraphics[width=0.85\textwidth]{fig/model_basic}
-	\caption{\color{blue}FRQ Model}
+	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
     \label{fig:model_basic}
@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic.
+The current distributed data parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic.
 A shuffle phase is required between each adjacent DAG computation phase.
@@
 After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies.
-For convenience, we introduce FRQ model by taking a simple MapReduce as an example in this section.
+For convenience, we introduce FRQ model by taking a simple MapReduce job as an example in this section.
 
 Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
-\begin{enumerate}
+\begin{itemize}
 	\item Input Data Size \((D)\): The data size of the computation phase.
@@
 The number of rounds depends on the current computation resources and the settings of the computation job.
-Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the Map phase consists of 200 map tasks.
-Then we need 4 rounds of computation to complete the Map phase.
+Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the map phase consists of 200 map tasks.
+Then we need 4 rounds of computation to complete the map phase.
     \item Computation Speed \((V_{i})\): 
@@
     Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
-\end{enumerate}
+\end{itemize}
 
-We can calculate the execution time of each phase of the job with these five parameters. Obviously, the total execution time of job in this case is the sum of the Map phase time and Reduce phase time:
+We can calculate the execution time of each phase of the job with these five parameters.
+As shown in Figure \ref{fig:model_basic}, in full parallel mapReduce, the total execution time of a job is the sum of the map phase time and reduce phase time:
 \begin{equation}
@@
 \end{equation}
-Map phase time depends on input data size and Map computation speed:
+map phase time depends on input data size and Map computation speed:
 \begin{equation}
@@
 \end{equation}
-The Reduce phase time formula is as follows:
+The reduce phase time formula is as follows:
 \begin{equation}
@@
 \end{equation}
-\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time, and \(K \times T_{P\_Shuffle}\) represents the calculated overhead.
-\(K\) is empirical value.
-The overhead depends on the parallel time of shuffle phase and the Reduce phase.The parallel time is denoted by \(T_{P\_Shuffle}\).
-And the total time of shuffle phase is represented by \(T_{Shuffle}\).
-Because the computation of the Reduce phase relies on the data transfer results of the Shuffle phase, a portion of the computation in the Reduce phase need to wait for the transfer results.
+
+We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
+The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
+This relationship will be shown in the following Subsection \ref{model_analysis}.
+\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
+Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase need to wait for the transfer results.
 The overhead is caused by these waiting.
@@
 For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
-Improving IO speed is a effective way to reduce shuffle time.
-Another optimization method is to use the idle IO resources in the Map phase for pre-fetching (see Figure \ref{fig:model_basic}).
+Improving I/O speed is a effective way to reduce shuffle time.
+Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}).
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
@@
 				\includegraphics[width=\linewidth]{fig/model_hadoop}
-				\caption{\color{blue}Hadoop MapReduce}
+				\caption{\color{blue}Half Parallel MapReduce}
 				\label{fig:model_hadoop}
@@
 		\end{subfigure}
-		\caption{\color{blue}FRQ Model with Different Scheduling Strategies}
+		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
 		\label{fig:model_strategies}
@@
 
-FRQ model can describe a variety of resource scheduling strategies.
+The FRQ model can describe a variety of resource scheduling strategies.
 First, we analyze a naive scheduling strategy.
 As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed.
-The parallel time of shuffle phase and the Reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
-Therefore, the overhead of the Reduce phase is 0.
-But since shuffle and computation are serial execution, the total execution time of job becomes longer:
+The overlap time between shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
+Therefore, the overhead of the reduce phase is 0.
+But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
 \begin{equation}
@@
 \end{equation}
-Obviously, this is an inefficient scheduling strategy.
-No computing framework uses this scheduling method.
-Due to serialization, the IO resource is idle during the Reduce phase and Map phase.
-The scheduling strategy is naive and has a lot of room for optimization.
+Apache Spark uses this scheduling strategy by default.
+Due to serialization, the I/O resource is idle during the reduce phase and map phase.
+The scheduling strategy is simple and has a lot of room for optimization.
 
-Figure \ref{fig:model_hadoop} shows the scheduling strategy of Hadoop MapReduce.
-In Hadoop MapReduce, Shuffle phase and Reduce phase start at the same time.
+Figure \ref{fig:model_hadoop} shows one of the optimization methods.
+In this scheduling strategy, shuffle phase and reduce phase start at the same time.
 In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\).
-Due to the increase in \(T_{P\_Shuffle}\), the time of Reduce phase will increase (see equation \ref{equation_Treduce}).
-Because the Shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
-The execution time of Shuffle phase is hidden in the Reduce phase.
-This scheduling strategy is much more efficient than the one in Figure 1.
-However, after analyzing this model, we found that the IO resource in the Map phase is idle.
+Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}).
+Because the shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
+The execution time of shuffle phase is hidden in the reduce phase.
+This scheduling strategy is used by Hadoop MapReduce.
+After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation.
+Meanwhile, we found that the I/O resource in the map phase is still idle.
 This scheduling strategy can be optimized.
@@
 		\end{subfigure}
-		\caption{\color{blue}FRQ Model with SCache}
+		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
 		\label{fig:model_scache}
@@
 
+Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
+We intuitively think that we can also overlap shuffle phase one and map phases.
+We implemented this idea with SCache.
 Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
-SCache starts pre-fetching and pre-scheduling in the Map phase.
-This scheduling strategy can make better use of resources and avoid IO resources being idle in the Map phase.
+SCache starts pre-fetching and pre-scheduling in the map phase.
+This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase.
 According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
 
-\begin{itemize}
+\begin{enumerate}
     \item 
@@
 The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)).
-When the Round1 of the Map phase ends, the SCache starts shuffling data until the end of the shuffle phase.
+When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase.
 Due to shuffle speed is slower, the shuffle phase is uninterrupted.
-SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase.
+SCache transmit the shuffle data generated in the last round of map phase during the reduce phase.
 Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
@@
 As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round.
-Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase:
+Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
 	\begin{equation}
@@
 	\end{equation}
-\end{itemize}
+\end{enumerate}
 
@@
 % \end{equation}
-% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of Map phase during the Reduce phase.
+% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of map phase during the reduce phase.
 Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase.
 
-% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the Map phase.
+% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase.
 
-Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \textit{Reduce Time} (\(T_{Reduce}\)).
-This is how pre-fetching optimizes the total execution time of job.
+Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \(T_{Reduce}\).
+This is how pre-fetching optimizes the total execution time of a job.
 
@@
 Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs.
-To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework (only three phases: \textit{Map, Shuffle,} and \textit{Reduce}) and Terasort as experimental application.
+To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework and Terasort as experimental application.
 We deployed Hadoop with SCache and without SCache on both environments.
@@
 \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results.
-K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the Reduce phase in the case of SCache.
+K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache.
 The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.

### 2018-10-16 tex/evaluation.tex
Verision 2.3

@@
 It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.85\textwidth]{fig/tpcds}
-	\caption{TPC-DS Benchmark Evaluation}
-	\label{fig:tpcds}
-	\vspace{-1em}
-\end{figure*}
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\linewidth]{fig/sampling}
-	\caption{Sampling Overhead}
-	\label{fig:sampling}
-	\vspace{-1em}
-\end{figure}
-
-{\color{blue}
-\subsection{Hadoop MapReduce with SCache}
-
-To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler.
-Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing in Hadoop MapReduce, some shuffle-heavy jobs on Hadoop Madpreduce can still be optimized by SCache shuffle data management.
-
-Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort.
-Both figures have the same proportion of time.
-Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
-As shown in the Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
-The shuffle phase and reduce phase start simultaneously.
-Because the large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait needs to wait for network transfer.
-This causes the CPU resources to be idle.
-As shown in the Figure \ref{fig:hadoop_terasort_scache}, Hadoop Madpreduce with SCache start pre-fetching in the map phase.
-This avoids the reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilizes the idle IO throughput in the map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
-}
-
 \begin{figure}
@@
 \end{figure}
-
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.85\textwidth]{fig/tpcds}
+	\caption{TPC-DS Benchmark Evaluation}
+	\label{fig:tpcds}
+	\vspace{-1em}
+\end{figure*}
 \begin{figure}
@@
 	\label{fig:hadoop_terasort_time}
+\end{figure}
+
+{\color{blue}
+\subsection{Hadoop MapReduce with SCache}
+
+To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler.
+Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy jobs on Hadoop MapReduce can still be optimized by SCache shuffle data management.
+
+Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort.
+Both figures have the same proportion of time.
+Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
+As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
+The shuffle phase and reduce phase start simultaneously.
+Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer.
+This causes the CPU resources to be idle.
+As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache start pre-fetching in the map phase.
+This avoids the reduce phase waiting for the shuffle data.
+Furthermore, pre-fetching utilizes the idle IO throughput in the map phase.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
+}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.6\linewidth]{fig/sampling}
+	\caption{Sampling Overhead}
+	\label{fig:sampling}
+	\vspace{-1em}
 \end{figure}

### 2018-10-16 tex/impl.tex
Verision 2.3

@@
 In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
-At last, we discuss the cost of adapting SCache and the fault tolerance. 
+At last, we discuss the cost of adapting SCache and fault tolerance. 
 }
@@
 {\color{blue} worker daemon.
-As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
+As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system.
 The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
@@
 When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
-After that the slot will be released (without being blocked on disk operations).
+After that, the slot will be released (without being blocked on disk operations).
 When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
@@
 SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow pre-scheduled result of SCache.
-(b)The shuffle data between the Map task and the Reduce task should be transfered to SCahce Storge Management.
+In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
+(b)The shuffle data between the Map task and the Reduce task should be transferred to SCahce Storge Management.
 

### 2018-10-16 tex/intro.tex
Verision 2.3

@@
 And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
-Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
+Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
 Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
@@
 Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
-Meanwhile, the reduce tasks belonging to a same execution phase are scheduled at the same time by default. 
+Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
 As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
@@
 In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
-FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in time dimension.
+FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension.
 We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
@@
 According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
-Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phases of the computing, including Map, Shuffle, and Reduce.
-By revealing the relationships between the various phases, FRQ model assist us in discovering the irrationality of resource scheduling during computing.
+Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phase of the computing, including Map, Shuffle, and Reduce.
+By revealing the relationships between the various phases, FRQ model assists us in discovering the irrationality of resource scheduling during computing.
 I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
@@
 We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
-We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of computing job.
+We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
@@
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark.
-On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
+On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by 15\%.
 }

### 2018-10-16 tex/model.tex
Verision 2.3

@@
 As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed.
-The overlap time between shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
+The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
 Therefore, the overhead of the reduce phase is 0.
@@
 Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}).
-Because the shuffle phase and the computation phase are executed in parallel, the total execution time of job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
-The execution time of shuffle phase is hidden in the reduce phase.
+Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
+The execution time of the shuffle phase is hidden in the reduce phase.
 This scheduling strategy is used by Hadoop MapReduce.
@@
 \subsection{Model Verification}\label{model_verification}
-In order to verify FRQ model, we run experiment on two environments.
+In order to verify FRQ model, we run experiments on two environments.
 The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}.
 Another environment is in our lab.
-Out lab environment has 4 nodes and each nodes has 128GB and 32 CPUs.
-To simplify the calculation of the FRQ model, we use Hadoop MapReduce as framework and Terasort as experimental application.
-We deployed Hadoop with SCache and without SCache on both environments.
+Our in-house environment has 4 nodes and each node has 128GB and 32 CPUs.
+To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as a experimental application.
+We deployed Hadoop with SCache and without SCache in both environments.
 
-Table \ref{table1} shows the calculational results of FRQ model in the lab environment.
+Table \ref{table1} shows the calculational results of FRQ model in the in-house environment.
 Workload is from 16 GB to 64 GB.
@@
 In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}.
-Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the lab environment.
+Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment.
 The network utilization remains high until shuffle phase is complete.
@@
 This situation is also consistent with Figure \ref{fig:model_scache2}.
-Therefore, we believe that FRQ model is able to accurately describe framework with SCache.
+Therefore, we believe that FRQ model is able to accurately describe the performance of a framework with SCache.
 

### 2018-10-16 tex/optimization.tex
Version 2.2
Verision 2.3

@@
 For the most DAG applications with random large scale input, 
-the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{ishuffle, predict}:
+the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}:
 \begin{equation}
@@
 		\State $m\gets$ partition number of map tasks
-		\Comment \emph{shuffles} is the previous schedule result 
+		\Comment \emph{shuffles} are the previous schedule result 
 		\ForAll{$r$ in $p\_reduces$}

### 2018-10-16 tex/relatedwork.tex
fzw revision
Verision 2.3

@@
 {\color{blue}
-\textbf{Modeling}: Most well-known DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop Madpreduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
+\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
+\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop MapReduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
 In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
-Inspired by \cite{verma2011aria}, \cite{herodotou2011hadoop}, and \cite{polo2010performance}, we present \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-In \cite{verma2011aria}, the author designs a model and divides execution into three parts: Map, Shuffle and Reduce.
-And then the author uses a greedy algorithm to roughly calculate the max, min and mean execution time of Map and Reduce phases.
-In \cite{herodotou2011hadoop}, the author presents a detailed set of mathematical performance models for describing the execution of a MapReduce job.
+There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp}.
+Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
+Khan et al.
+\cite{khan2016hadoop} proposed the HP model which extends the ARIA model.
+The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
+In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the execution of a MapReduce job.
 The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce.
-The performance models describe each above-mentioned phases and combine into a overall MapReduce job model.
-However, none of the above models meet our requirements for analyzing shuffle.
-The model in \cite{verma2011aria} is not able to accurately describe the overhead caused by shuffle under different scheduling strategies.
-The model in \cite{herodotou2011hadoop} calculates overhead of various phases including shuffle, but most of them are redundant.
-Different from these models, our FRQ model quantifies computing and I/O resources and displays them in time dimension.
-FRQ model focuses on describing the overhead caused by shuffle in different scheduling strategies, which satisfy our demand.
+The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model.
+Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
+provisions the resources for the job.
+
+However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
+Different from these models, our FRQ model quantifies computing and I/O resources and displays them in the time dimension.
+FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfy our demand.
 }
@@
 SCache instead starts shuffle pre-fetching without consuming slots. 
-iShuffle \cite{ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
+iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
 But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
@@
 \textbf{Delay-scheduling}: Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
-ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when network is saturated. 
+ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
 At the same time, it achieves better data locality. 

### 2018-10-17 tex/abstract.tex
Version 2.2
SongTao revision.

@@
 {\color{blue}
-During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
-FRQ model displays utilization of resources in time dimension and calculate execution time of computing jobs on different DAG frameworks. 
+During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. 
+The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks. 
 We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
@@
 Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
-On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
+On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
 }

### 2018-10-17 tex/evaluation.tex
SongTao revision.

@@
 	\includegraphics[width=\linewidth]{fig/scache_util}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application With SCache}
+	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
 	\label{fig:scache_util}
@@
 {\color{blue}
-To prove SCache compatibility as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
+To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
 Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimize job completion time by up to 15\% and an average of 13\%}
+{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
 
@@
 In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
-It helps eliminate ~40\% of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
+It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
 Note that the shuffle write time can be observed even with the optimization of SCache. 
@@
 Both figures have the same proportion of time.
-Hadoop MapReduce with SCache brings 15\% of total time optimization with 384GB input data size.
+Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size.
 As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
-The shuffle phase and reduce phase start simultaneously.
+The shuffle phase and the reduce phase start simultaneously.
 Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer.
-This causes the CPU resources to be idle.
-As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache start pre-fetching in the map phase.
+This causes CPU resources to be idle.
+As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
 This avoids the reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilizes the idle IO throughput in the map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimize Terasort overall completion time by up to 15\% and an average of 13\% with input data sizes from 128GB to 512GB.
+Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
 }
@@
 It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
-The overall reduction portion of query time that SCache achieved is 40\% on average. 
+The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
 Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.

### 2018-10-17 tex/impl.tex
SongTao revision.

@@
 We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
-The following \ref{memorymanage} subsection focuses on the two constraints on memory management.
-In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
+The following \ref{memorymanage} subsection focuses on two constraints on memory management.
+In Subsection \ref{crossframework}, we evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
 At last, we discuss the cost of adapting SCache and fault tolerance. 
@@
 The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
+The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
 The daemon bridges the communication between %{\color{red}Spark}
@@
 In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
-After modification, DAG scheduler will consult SCache co-scheduler to get the preferred location for each task.
+After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
 }
@@
 \subsection{Analysis of cross-framework capability}\label{crossframework}
-Shuffle optimization of SCache inevitably requires modification on dependent DAG framework.
-SCache provides API through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
-(b)The shuffle data between the Map task and the Reduce task should be transferred to SCahce Storge Management.
+Shuffle optimization of SCache inevitably requires modification on DAG frameworks.
+SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
+In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
+(b) The shuffle data between the map task and the reduce task should be transferred to SCahce Storge Management.
 
@@
 It takes about 400 lines of code.
-In Spark, we mainly modified the DAGScheduler and the corresponding data fetcher.
+In Spark, we mainly modified DAGScheduler and the corresponding data fetcher.
 It only takes about 500 lines of code.
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
-we believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
+We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
 }

### 2018-10-17 tex/intro.tex
SongTao revision.

@@
 Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% of the job completion time on average, and up to 70\% in shuffle-heavy jobs \cite{managing}.
+For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
 
@@
 In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
-FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension.
-We use FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
-FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
-According to the above five parameters and the scheduling strategy of the DAG framework, FRQ model is able to calculate the execution time of each phase of a computing job. 
-Take Apache Hadoop MapReduce as a simple DAG computing example, we use FRQ to model each phase of the computing, including Map, Shuffle, and Reduce.
-By revealing the relationships between the various phases, FRQ model assists us in discovering the irrationality of resource scheduling during computing.
-I/O resource in map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
+The FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension.
+We use the FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
+The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
+According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to calculate the execution time of each phase of a computing job. 
+Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle and Reduce.
+By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
+I/O resource in the map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
 This situation will be amplified in shuffle-heavy tasks.
@@
 {\color{blue}
-We have implemented SCache, a customized Apache Spark \cite{apachespark} and a customized Apache Hadoop.
+We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce.
 We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
-On Apache Spark, we conduct basic test \textit{GroupByTest}.
-We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling.
+On Apache Spark, we conduct a basic test - \textit{GroupByTest}.
+We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling.
 On Apache Hadoop, we focus on Terasort benchmark.
-In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied applications.
+In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications.
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark.
-On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by 15\%.
+On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
 }

### 2018-10-17 tex/model.tex
SongTao revision.

@@
 
-In this chapter, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-FRQ model quantifies computing and I/O resources and displays them in time dimension.
-According to FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG framework, hardware environment, and so on.
-Therefore FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
-We will first introduce FRQ model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we will use FRQ model to describe three different computation job and analyze their performance.
+In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
+the FRQ model quantifies computing and I/O resources and displays them in time dimension.
+According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
+Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
+We will first introduce the FRQ model in Subsection \ref{model_overview}.
+In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance.
 In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed data parallel computing frameworks mostly use \textit{Directed acyclic graphs} (DAGs) to describe computation logic.
-A shuffle phase is required between each adjacent DAG computation phase.
-In order to better analyze the relationship between the computation phase and the shuffle phase, we propose FRQ model.
-After quantifying computing and I/O resources, FRQ model is able to describe different resource scheduling strategies.
-For convenience, we introduce FRQ model by taking a simple MapReduce job as an example in this section.
+The current distributed data parallel computing frameworks mostly use \textit{Directed Acyclic Graphs} (DAGs) to describe computation logic.
+A shuffle phase is required between each adjacent DAG computation phases.
+In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
+After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies.
+For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
 
-Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. FRQ model has five input parameters:
+Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
 \begin{itemize}
@@
 The number of rounds depends on the current computation resources and the settings of the computation job.
-Take Hadoop MapReduce as an example, suppose we have 50 CPUs and enough memory, the map phase consists of 200 map tasks.
+Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks.
 Then we need 4 rounds of computation to complete the map phase.
@@
     \item Shuffle Speed \((V_{Shuffle})\): 
-    Transmission speed during shuffle. Shuffle speed depends on Network and storage device bandwidth.
+    Transmission speed during shuffle. Shuffle speed depends on network and storage device bandwidth.
 \end{itemize}
@@
 For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
-Improving I/O speed is a effective way to reduce shuffle time.
+Improving I/O speed is an effective way to reduce shuffle time.
 Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}).
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
-When using FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework.
+When using the FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework.
 Different computing frameworks may use different resource scheduling strategies.
-FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.
+The FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.
 
@@
 First, we analyze a naive scheduling strategy.
-As shown in Figure \ref{fig:model_original}, FRQ model describes a MapReduce job that is fully serially executed.
+As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is fully serially executed.
 The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
@@
 In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\).
-Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase will increase (according to equation \ref{equation_Treduce}).
+Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to equation \ref{equation_Treduce}).
 Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
@@
 This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase.
-According to the design of SCache pre-fetching, we found that using FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
+According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
 
@@
 Due to shuffle speed is slower, the shuffle phase is uninterrupted.
-SCache transmit the shuffle data generated in the last round of map phase during the reduce phase.
+SCache transmits the shuffle data generated in the last round of map phase during the reduce phase.
 Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
@@
 As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round.
-Thus \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
+Thus \(T_{P\_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
 	\begin{equation}
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in FRQ model}
+\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
 \label{table1}
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in FRQ model}
+\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
 \label{table2}
@@
 \subsection{Model Verification}\label{model_verification}
-In order to verify FRQ model, we run experiments on two environments.
-The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Section \ref{stepup}.
-Another environment is in our lab.
-Our in-house environment has 4 nodes and each node has 128GB and 32 CPUs.
-To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as a experimental application.
+In order to verify the FRQ model, we run experiments on two environments.
+The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Subsection \ref{stepup}.
+Another in-house environment has 4 nodes and each node has 128GB memory and 32 cores.
+To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as an experimental application.
 We deployed Hadoop with SCache and without SCache in both environments.
 
-Table \ref{table1} shows the calculational results of FRQ model in the in-house environment.
+Table \ref{table1} shows the calculational results of the FRQ model in the in-house environment.
 Workload is from 16 GB to 64 GB.
@@
 
-Table \ref{table2} shows the calculational results of FRQ model in Amazon EC2 environment.
+Table \ref{table2} shows the calculational results of the FRQ model in Amazon EC2 environment.
 \(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
@@
 The formulas in the table are all the same except \(T_{P\_Shuffle}\).
-In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2}(\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
-In the previous case, \(T_{P\_Shuffle}\) is still euqal to \(T_{Shuffle}\).
+In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
+In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).
 
@@
 Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment.
-The network utilization remains high until shuffle phase is complete.
+The network utilization remains high until the shuffle phase is completed.
 This situation is consistent with Figure \ref{fig:model_scache1}.
@@
 This situation is also consistent with Figure \ref{fig:model_scache2}.
-Therefore, we believe that FRQ model is able to accurately describe the performance of a framework with SCache.
+Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
 
@@
 Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance.
-Therefore, we believe that FRQ model can accurately describe DAG framework.
+Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
 }

### 2018-10-17 tex/motivation.tex
Version 2.2
SongTao revision.

@@
 %In short, shuffle is loosely coupled with application context and it's I/O intensive.
-\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduces a significant latency to the application. 
-Reports show that 60\% of MapReduce jobs at Yahoo! and 20\% at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
+\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduce a significant latency to the application. 
+Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
 For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
+For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
 % Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
@@
 Compared to input dataset, the size of shuffle data is relatively small. 
-For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than 25\% of input data. 
-The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as 10\%-20\%. 
+For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than $25\%$ of input data. 
+The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
 On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 

### 2018-10-17 tex/impl.tex
Version 2.4 GaoCe revision.

@@
 The following \ref{memorymanage} subsection focuses on two constraints on memory management.
-In Subsection \ref{crossframework}, we evaluate cross-framework capability of SCache based on Hadoop MapReduce and Spark. 
+In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
 At last, we discuss the cost of adapting SCache and fault tolerance. 
@@
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
+In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
 (b) The shuffle data between the map task and the reduce task should be transferred to SCahce Storge Management.
@@
 To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
-Taking Hadoop MapReduce as an example, we insert codes in ResourceManager and modify codes in MapTask and ReduceTask to call SCache API through RPC.
+Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask and ReduceTask to call SCache APIs through RPC.
 It takes about 400 lines of code.
-In Spark, we mainly modified DAGScheduler and the corresponding data fetcher.
+In Spark, we mainly modify DAGScheduler and the corresponding data fetcher.
 It only takes about 500 lines of code.

### 2018-10-17 tex/intro.tex
Version 2.4 GaoCe revision.

@@
 {\color{blue}
-In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
+In order to analyze above-mentioned resources scheduling strategies, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
 The FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension.

### 2018-10-17 tex/model.tex
Version 2.4 GaoCe revision.

@@
 \end{equation}
-map phase time depends on input data size and Map computation speed:
+
+Map phase time depends on input data size and map computation speed:
 \begin{equation}
@@
 \end{equation}
+
 The reduce phase time formula is as follows:
@@
 \end{equation}
+
 Apache Spark uses this scheduling strategy by default.
@@
 
-In order to verify the above-mentioned two cases when using SCache, we monitor network utilization and plot it in Figure \ref{fig:hadoop_net}.
+In order to verify the above-mentioned two cases when using SCache, we monitor network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment.

### 2018-10-18 tex/abstract.tex
Version 3.0

@@
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
-{\color{blue}
+{\color{black}
 During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model. 
 The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks. 
-We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
+We use the FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
 }
@@
 % }
-{\color{blue}
+{\color{black}
 We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop.

### 2018-10-18 tex/conclusion.tex
SongTao revision.
Version 3.0

@@
 %  }
-{\color{blue}
+{\color{black}
 Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
 Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
-At last we use FRQ model to verify SCache shuffle optimization by mathematics.
+At last we use the FRQ model to verify SCache shuffle optimization by mathematics.
 Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 

### 2018-10-18 tex/evaluation.tex
Version 3.0

@@
 In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-{\color{blue}
+{\color{black}
 To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
+{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
 
@@
 \subsection{Terasort}
-We also evaluate Terasort\footnote{https://github.com/ehiggs/spark-terasort}-a recognized shuffle intensive benchmark for distributed system analysis.
+We also evaluate Terasort-a recognized shuffle intensive benchmark for distributed system analysis. 
 Terasort consists of two consecutive shuffles. 
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-				\caption{\color{blue}Hadoop MapReduce With SCache}
+				\caption{\color{black}Hadoop MapReduce With SCache}
 				\label{fig:hadoop_terasort_scache}
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-				\caption{\color{blue}Hadoop MapReduce Without SCache}
+				\caption{\color{black}Hadoop MapReduce Without SCache}
 				\label{fig:hadoop_terasort_origin}
@@
 		\end{subfigure}
-		\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
+		\caption{\color{black}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
 		\label{fig:hadoop_terasort}
@@
 	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
-	\caption{\color{blue}Hadoop MapReduce Terasort completion time}
+	\caption{\color{black}Hadoop MapReduce Terasort completion time}
 	\label{fig:hadoop_terasort_time}
@@
 
-{\color{blue}
+{\color{black}
 \subsection{Hadoop MapReduce with SCache}

### 2018-10-18 tex/impl.tex
Version 3.0

@@
 % }
-{\color{blue}
+{\color{black}
 We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
@@
 SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
-{\color{blue} worker daemon.
+{\color{black} worker daemon.
 As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system.
@@
 The daemon bridges the communication between %{\color{red}Spark}
-{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{blue} original scheduler in framework}.
+{\color{black} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
+ {\color{black} original scheduler in framework}.
 
-% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
+% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{black} worker daemon}.
 As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
@@
 % The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-% The daemon bridges the communication between {\color{blue}DAG framework} and SCache.
-The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.
+% The daemon bridges the communication between {\color{black}DAG framework} and SCache.
+The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{black} original scheduler in framework master}.
 
@@
 % }
-{\color{blue}
+{\color{black}
 When a DAG job is submitted, the DAG information will be generated in framework task scheduler. 
@@
 For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
-If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}.
+If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{black}computing job}.
 We will elaborate the sampling procedure in the Section \ref{sampling}.
@@
 
-When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
+When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{black}framework worker} through memory copy.
 After that, the slot will be released (without being blocked on disk operations).
@@
 % }
-{\color{blue}
+{\color{black}
 In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
@@
 \subsubsection{Reservoir Sampling}\label{sampling}
-If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, {\color{blue}the SCache master will send a sampling request to the framework master}. 
+If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, {\color{black}the SCache master will send a sampling request to the framework master}. 
 The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
@@
 	\includegraphics[width=0.8\linewidth]{fig/architecture}
-	\caption{\color{blue}SCache Architecture}
+	\caption{\color{black}SCache Architecture}
 	\label{fig:architecture}
@@
 % }
-{\color{blue}
+{\color{black}
 \subsection{Analysis of cross-framework capability}\label{crossframework}

### 2018-10-18 tex/intro.tex
Version 3.0

--- 2018-10-17 tex/intro.tex
@@
 Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
-To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce\footnote{http://hadoop.apache.com/}. 
+To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce
 However, such early-start is by no means a panacea. 
@@
 
-{\color{blue}
-In order to visually analyze above-mentioned resources scheduling, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
-The FRQ model quantifies computing and I/O resources and displays resources scheduling strategy of DAG framework in the time dimension.
+{\color{black}
+In order to analyze above-mentioned resources scheduling strategies, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The FRQ model quantifies computing and I/O resources and displays resources scheduling strategies of DAG frameworks in the time dimension.
 We use the FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
@@
 
-{\color{blue}
+{\color{black}
 We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce.

### 2018-10-18 tex/model.tex
Version 3.0

@@
-{\color{blue}
+{\color{black}
 \section{Framework Resources Quantification Model}\label{model}
@@
 	\includegraphics[width=0.85\textwidth]{fig/model_basic}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
+	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
     \label{fig:model_basic}
@@
 				\includegraphics[width=\linewidth]{fig/model_original}
-				\caption{\color{blue}Full Serial MapReduce}
+				\caption{\color{black}Full Serial MapReduce}
 				\label{fig:model_original}
@@
 				\includegraphics[width=\linewidth]{fig/model_hadoop}
-				\caption{\color{blue}Half Parallel MapReduce}
+				\caption{\color{black}Half Parallel MapReduce}
 				\label{fig:model_hadoop}
@@
 		\end{subfigure}
-		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
+		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
 		\label{fig:model_strategies}
@@
 				\includegraphics[width=\linewidth]{fig/model_scache1}
-				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 				\label{fig:model_scache1}
@@
 				\includegraphics[width=\linewidth]{fig/model_scache2}
-				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
+				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
 				\label{fig:model_scache2}
@@
 		\end{subfigure}
-		\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
+		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
 		\label{fig:model_scache}
@@
 	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated.
-The meaning of the inequality is that the speed of generating shuffle data(\(V_{Map} \times R\)) is greater than or equal to the shuffle speed(\(V_{Shuffle}\)).
+The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)).
 When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase.
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
 \label{table1}
@@
 \renewcommand{\arraystretch}{1.3}
-\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
 \label{table2}
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_net1}
-				\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 				\label{fig:hadoop_net1}
@@
 				\includegraphics[width=\linewidth]{fig/hadoop_net2}
-				\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
+				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
 				\label{fig:hadoop_net2}
@@
 		\end{subfigure}
-		\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
+		\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
 		\label{fig:hadoop_net}

### 2018-10-18 tex/relatedwork.tex
Version 3.0

@@
 
-{\color{blue}
+{\color{black}
 \textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Apache Hadoop MapReduce\footnote{http://hadoop.apache.com/} can also be considered as a special case of only one superstep in BSP model).
+\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model).
 In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.

### 2018-10-18 coverletter/coverletter.tex
Cover letter v3.0.

@@
 
-\title{Summary of Differrence}
+\title{Summary of Difference}
 \maketitle
@@
 This paper is extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
-This paper makes the following distinct contribution compared with the conference paper.
+This paper makes the following distinct contributions compared with the conference paper.
 
@@
 \item 
-FRQ model quantifies computing and I/Oresources and displays them in time dimension. 
-Furthermore, FRQ model can calculate execution time of DAG framework under difference resources allocation strategies. 
+We propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks.
+We use the FRQ model to assist in analyzing the shuffle process and verify SCache shuffle optimization by mathematics.
+% Furthermore, the FRQ model can calculate the execution time of DAG framework under difference resources allocation strategies. 
 \item 
-In conference paper, we only implement SCache on Spark. To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
-By employing shuffle data management, SCache can also optimize the computing performance of Hadoop MapReduce.
+In the conference paper, we only implemented SCache on Spark. To prove the compatibility of SCache as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
+Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
 \item
-In experiment, we append two parts.
-First we verify FRQ model under two different environments, the error between calculated value and experimental value is basically below 10\%.
-Furthermore, we evaluate the performance of SCache on Hadoop MapReduce in the same environment as conference paper.
-After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize overall job execution time by 15\%.
+We append two parts in the evaluation section.
+Firstly, we verify the FRQ model in both our in-house environment and Amazon EC2 environment.
+The error between the calculated value and the experimental value is basically below $10\%$.
+Secondly, we evaluate the performance of Hadoop MapReduce with SCache in the same environment as the conference paper.
+After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize job completion time by up to $15\%$ and an average of $13\%$.
 \end{enumerate}

### 2018-10-21 coverletter/coverletter.tex
Version 3.1

@@
 
-This paper is extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
+This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
 This paper makes the following distinct contributions compared with the conference paper.
@@
 \item 
-We propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
-The FRQ model displays utilization of resources in the time dimension and calculates execution time of computing jobs on different DAG frameworks.
-We use the FRQ model to assist in analyzing the shuffle process and verify SCache shuffle optimization by mathematics.
+We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The proposed model is not only to predict the job completion time, but also to theoretically analyze DAG frameworks.
+The FRQ models DAG frameworks according to the resource scheduling strategy of each DAG framework by mutiple parameters.
+Through modeling, the FRQ model can indicate which parameters of the DAG framework are important and which parts of the DAG framework can be optimized. 
+Furthermore, the FRQ models can classify DAG frameworks based on their scheduling stratagies.
+According to the theoretical analysis results of the FRQ model, we are able to optimize DAG frameworks more accurately.
+% We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The FRQ models utilization of resources in the time dimension and calculates the execution time of computing jobs on different DAG frameworks.
+% We use this FRQ model to assist in analyzing the shuffle process. 
+% The FRQ model can evaluate the scheduling strategies of DAG computing frameworks, such as Hadoop MapReduce and Spark, and help us optimize them. 
+% The FRQ model provides a theoretical basis for performance optimization of SCache.
+% We use the FRQ model to assist in analyzing the shuffle process and verify SCache shuffle optimization by mathematics.  
 % Furthermore, the FRQ model can calculate the execution time of DAG framework under difference resources allocation strategies. 
 \item 
-In the conference paper, we only implemented SCache on Spark. To prove the compatibility of SCache as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
+In the conference paper, we only implemented SCache on Spark. To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
 Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
 \item
-We append two parts in the evaluation section.
-Firstly, we verify the FRQ model in both our in-house environment and Amazon EC2 environment.
-The error between the calculated value and the experimental value is basically below $10\%$.
-Secondly, we evaluate the performance of Hadoop MapReduce with SCache in the same environment as the conference paper.
+We append two parts to the evaluation section.
+Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment.
+The error between the FRQ’s calculated value and the experimental value is below $10\%$.
+Secondly, we evaluate the performance of Hadoop MapReduce with SCache.
+A in the same environment as the conference paper, i.e., 50-node Amazon EC2 cluster.
 After utilizing pre-fetching of SCache, Hadoop MapReduce with SCache optimize job completion time by up to $15\%$ and an average of $13\%$.
@@
 
-Besides the major contributions, we also revise the paper in many places, including writing and more related work.
-We believe that the added content makes sufficient contribution to this journal submission.
+% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
+In summary, we propose a new performance model to provide theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
+We believe that the added content makes a sufficient contribution to this journal submission.
 

### 2018-10-21 tex/conclusion.tex
Version 3.1

@@
 SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
-By tasks pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
+By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
 %  {\color{red}
@@
 Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
-At last we use the FRQ model to verify SCache shuffle optimization by mathematics.
+At last we evaluate the SCache shuffle optimization by this practical model.
 Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 

### 2018-10-21 tex/intro.tex
Version 3.1

@@
 {\color{black}
-In order to analyze above-mentioned resources scheduling strategies, we propose a performance model called \textit{Framework Resources Quantification} (FRQ) model.
-The FRQ model quantifies computing and I/O resources and displays resources scheduling strategies of DAG frameworks in the time dimension.
-We use the FRQ model to assist in analyze the deficiencies of resources scheduling and optimize it.
+In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
+We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it.
 The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
-According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to calculate the execution time of each phase of a computing job. 
-Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle and Reduce.
+According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
+Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
 By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
-I/O resource in the map phase is not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
+I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
 This situation will be amplified in shuffle-heavy tasks.
@@
 We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce.
-We have also designed a performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze the shuffle optimization of SCache and calculate the execution time of each phase of a computing job.
+We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job.
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.

### 2018-10-21 tex/model.tex
Version 3.1

@@
 In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-the FRQ model quantifies computing and I/O resources and displays them in time dimension.
+the FRQ model quantifies computing and I/O resources and visualizes them in time dimension.
 According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed data parallel computing frameworks mostly use \textit{Directed Acyclic Graphs} (DAGs) to describe computation logic.
+The current distributed data parallel computing frameworks mostly use DAGs to describe computation logic.
 A shuffle phase is required between each adjacent DAG computation phases.
@@
 \(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
-Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase need to wait for the transfer results.
+Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results.
 The overhead is caused by these waiting.
@@
 In this case, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\).
-Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to equation \ref{equation_Treduce}).
-Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see equation \ref{equation_Tjob}).
+Due to the increase in \(T_{P\_Shuffle}\), the time of reduce phase increases (according to Equation \ref{equation_Treduce}).
+Because the shuffle phase and the computation phase are executed in parallel, the total execution time of a job is the sum of \(T_{Map}\) and \(T_{Reduce}\) (see Equation \ref{equation_Tjob}).
 The execution time of the shuffle phase is hidden in the reduce phase.
@@
 
-In order to verify the above-mentioned two cases when using SCache, we monitor network utilization as Figure \ref{fig:hadoop_net}.
+In order to verify the above-mentioned two cases when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment.
@@
 In the case where the input data is small and the total time is short, the error caused by the overhead is amplified.
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are within tolerance.
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable.
 Therefore, we believe that the FRQ model can accurately describe DAG frameworks.

### 2018-10-21 tex/relatedwork.tex
Version 3.1

@@
 However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
-Different from these models, our FRQ model quantifies computing and I/O resources and displays them in the time dimension.
-FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfy our demand.
+Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
+FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
 }

### 2018-10-22 tex/relatedwork.tex
Submitted version.

@@
 In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
-There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp}.
+There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
 Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
@@
 provisions the resources for the job.
+Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers.
+The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is uesed to optimize the stragglers.
 

### 2018-12-27 tpds/tex/impl.tex
mkdir tpds

--- 2018-10-18 tex/impl.tex
@@
 \subsection{Analysis of cross-framework capability}\label{crossframework}
-Shuffle optimization of SCache inevitably requires modification on DAG frameworks.
+Shuffle optimization of SCache inevitably requires the modification on DAG frameworks.
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache.
-(b) The shuffle data between the map task and the reduce task should be transferred to SCahce Storge Management.
+In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data between the map task and the reduce task should be transferred to SCache Storage Management.
 
 To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
-Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask and ReduceTask to call SCache APIs through RPC.
+Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC.
 It takes about 400 lines of code.

### 2018-12-28 taco/tex/abstract.tex
Add taco

--- 2018-10-13 tex/abstract.tex
@@
 In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead.
-Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
+Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
 {\color{blue}
-During shuffle optimization process, we propose a performance model called \textit{Framework Resources Quantification}(FRQ) model. 
-FRQ model displays utilization of resources in time dimension and calculate execution time of computing jobs on different DAG frameworks. 
-We use FRQ model to assist in analyzing shuffle process and verify SCache shuffle optimization by mathematics.
+During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
+The FRQ models utilization of resources and predicts the execution time of computing jobs on different DAG frameworks. 
+We use the FRQ model to assist in analyzing DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
 }
@@
 {\color{blue}
-We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop.
-The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
+We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce.
+The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
 Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
-On Apache Hadoop, SCache optimize end-to-end Terasort completion time by 15\%.
+On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
 }

### 2018-12-28 taco/tex/evaluation.tex
Add taco

--- 2018-10-17 tex/evaluation.tex
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{fig/scache_util}
+	\includegraphics[width=.8\linewidth]{fig/scache_util}
 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
@@
 				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
-				\caption{Reduce Stage Completion Time}
+				\caption{Reduce Stage Completion Time\newline}
 				\label{fig:reducestage}	
@@
 				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
-				\caption{Median Task in Reduce Stages}
+				\caption{Median Task in Reduce Stages\newline}
 				\label{fig:reducetask}
@@
 	\centering
-	\begin{minipage}[hb]{\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{subfigure}{.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-				\caption{\color{blue}Hadoop MapReduce With SCache}
+		\caption{\color{blue}Hadoop MapReduce with SCache}
 		\label{fig:hadoop_terasort_scache}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
+	\end{subfigure}
+	\begin{subfigure}{.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-				\caption{\color{blue}Hadoop MapReduce Without SCache}
+		\caption{\color{blue}Hadoop MapReduce without SCache}
 		\label{fig:hadoop_terasort_origin}
-			\end{minipage}
 	\end{subfigure}
@@
 	\label{fig:hadoop_terasort}
-	\end{minipage}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.85\textwidth]{fig/tpcds}
+	\includegraphics[width=\textwidth]{fig/tpcds}
 	\caption{TPC-DS Benchmark Evaluation}
@@
 \end{figure*}
-\begin{figure}
-	\includegraphics[width=\linewidth]{fig/hadoop_terasort_time}
-	\caption{\color{blue}Hadoop MapReduce Terasort completion time}
-	\label{fig:hadoop_terasort_time}
-\end{figure}
 
@@
 Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer.
-This causes CPU resources to be idle.
+This causes the CPU resources to be idle.
 As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
@@
 }
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\linewidth]{fig/sampling}
-	\caption{Sampling Overhead}
-	\label{fig:sampling}
-	\vspace{-1em}
-\end{figure}
 
@@
 Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
-% \begin{figure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/tera}
-% 		\caption{Reduce Stage Completion Time Comparison of First Shuffle}
-% 		\label{fig:terasort}
-% 	\end{subfigure}
-% 	\vspace{0.08cm}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/tera_shuffle}
-% 		\caption{Shuffle Data through Network Comparison of Second Shuffle}
-% 		\label{fig:terashuffle}
-% 	\end{subfigure}
-% 	\caption{Terasort Evaluation}
-% \end{figure}
+
+\begin{figure}
+    \centering
+    \begin{minipage}{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
+        \caption{\color{blue}Hadoop MapReduce Terasort completion time}
+		\label{fig:hadoop_terasort_time}
+    \end{minipage}\hfill
+    \begin{minipage}{0.42\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
+        \caption{Sampling Overhead}
+		\label{fig:sampling}
+    \end{minipage}
+\end{figure}
+
 \subsection{Overhead of Sampling}

### 2018-12-28 taco/tex/impl.tex
Add taco

--- 2018-10-17 tex/impl.tex
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{fig/architecture}
+	\begin{minipage}{.47\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{fig/architecture}
 		\caption{\color{blue}SCache Architecture}
@@
 		% \vspace{-0.5em}
+	\end{minipage}\hfill
+	\begin{minipage}{.42\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{fig/sample}
+		\caption{Reservoir Sampling of One Partition}
+		\label{fig:sample}
+		% \vspace{-1em}
+	\end{minipage}
 \end{figure}
@@
 To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data-all-or-nothing and context-aware-priority.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.6\linewidth]{fig/sample}
-	\caption{Reservoir Sampling of One Partition}
-	\label{fig:sample}
-	\vspace{-1em}
-\end{figure}
 

### 2018-12-28 taco/tex/intro.tex
Add taco

--- 2018-10-21 tex/intro.tex
@@
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-\IEEEPARstart{R}{ecent} years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
+\section{Introduction}\label{sec:introduction}
+Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
 Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
@@
 
-Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay}, 
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator},
 the shuffle is often poorly optimized in practice.
@@
 	\centering
-	\includegraphics[width=\linewidth]{fig/workflow}
+	\includegraphics
+		[width=.6\linewidth]
+		{fig/workflow}
 	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
@@
 
-{\color{black}
+{\color{blue}
 In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
@@
 
-{\color{black}
+{\color{blue}
 We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce.

### 2018-12-28 taco/tex/model.tex
Add taco

--- 2018-10-21 tex/model.tex
@@
-{\color{black}
+{\color{blue}
 \section{Framework Resources Quantification Model}\label{model}
-
-\begin{figure*}
-    \centering
-	\includegraphics[width=0.85\textwidth]{fig/model_basic}
-	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
-    \label{fig:model_basic}
-    \vspace{-1em}
-\end{figure*}
 
@@
 In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
+
+\begin{figure*}
+    \centering
+	\includegraphics[width=0.85\textwidth]{fig/model_basic}
+	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
+    \label{fig:model_basic}
+    \vspace{-1em}
+\end{figure*}
 
@@
 	\centering
-	\begin{minipage}[hb]{\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{subfigure}{0.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_original}
-				\caption{\color{black}Full Serial MapReduce}
+		\caption{\color{blue}Full Serial MapReduce}
 		\label{fig:model_original}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
+	\end{subfigure}
+	\begin{subfigure}{0.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_hadoop}
-				\caption{\color{black}Half Parallel MapReduce}
+		\caption{\color{blue}Half Parallel MapReduce}
 		\label{fig:model_hadoop}
-			\end{minipage}
 	\end{subfigure}
-		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
+	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
 	\label{fig:model_strategies}
-	\end{minipage}
 \end{figure}
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
-	\begin{minipage}[hb]{\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{subfigure}{0.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_scache1}
-				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 		\label{fig:model_scache1}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
+	\end{subfigure}
+	\begin{subfigure}{0.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_scache2}
-				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
 		\label{fig:model_scache2}
-			\end{minipage}
 	\end{subfigure}
-		\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
+	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
 	\label{fig:model_scache}
-	\end{minipage}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{table*}[!t]
-\renewcommand{\arraystretch}{1.3}
-\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\begin{table}[!t]
+% \renewcommand{\arraystretch}{0.8}
+\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
 \label{table1}
+\begin{minipage}{\columnwidth}
 \centering
 \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\scalebox{0.75}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 	\end{tabular}
-\end{table*}
+}
+\end{minipage}
+\end{table}
 % \subsection{Performance Analysis}\label{model_performance_analysis}
@@
 \begin{table*}[!t]
-
-\renewcommand{\arraystretch}{1.3}
-\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
 \label{table2}
@@
 \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\scalebox{0.75}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 	\end{tabular}
+}
 \end{table*}
@@
 	\centering
-	\begin{minipage}[hb]{\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{subfigure}{.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
-				\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 		\label{fig:hadoop_net1}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
+	\end{subfigure}
+	\begin{subfigure}{.47\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
-				\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
 		\label{fig:hadoop_net2}
-			\end{minipage}
 	\end{subfigure}
-		\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
+	\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
 	\label{fig:hadoop_net}
-	\end{minipage}
 \end{figure}

### 2018-12-28 taco/tex/optimization.tex
Add taco

--- 2018-10-16 tex/optimization.tex
@@
 Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
+
 \begin{figure}
     \centering
-	\includegraphics[width=0.5\linewidth]{fig/reduce_cdf}
+    \begin{minipage}{0.42\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
 		\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
 		\label{fig:cdf}
-	\vspace{-1em}
+    \end{minipage}\hfill
+    \begin{minipage}{0.49\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{fig/sim} % second figure itself
+		\caption{Stage Completion Time Improvement of OpenCloud Trace}
+		\label{fig:sim}
+    \end{minipage}
 \end{figure}
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.45\linewidth]{fig/reduce_cdf}
+% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
+% 	\label{fig:cdf}
+% 	\vspace{10em}
+% \end{figure}
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=0.4\linewidth]{fig/sim}
+% 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
+% 	\label{fig:sim}
+% 	\vspace{-1em}
+% \end{figure}
+
 \subsection{Decouple Shuffle from Execution}
@@
 Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
-The average shuffle read time is 3.2\% of total reduce completion time.
+The average shuffle read time is $3.2\%$ of total reduce completion time.
+
 \begin{figure}
 	\centering
-	\includegraphics[width=0.66\linewidth]{fig/sim}
-	\caption{Stage Completion Time Improvement of OpenCloud Trace}
-	\label{fig:sim}
+	\includegraphics[width=0.5\linewidth]{fig/shuffle}
+	\caption{Shuffle Data Prediction}
+	\label{fig:shuffle}
 	\vspace{-1em}
@@
 In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
-\begin{figure}
-	\centering
-	\includegraphics[width=0.75\linewidth]{fig/shuffle}
-	\caption{Shuffle Data Prediction}
-	\label{fig:shuffle}
-	\vspace{-1em}
-\end{figure}
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/hash_pre}
-		\caption{Linear Regression Prediction of Hash Partitioner}
-		\label{fig:hash_pre}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/range_pre_sample}
-		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
-		\label{fig:range_pre_sample}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
-		\caption{Prediction Relative Error of Range Partitioner}
-		\label{fig:prediction_relative_error}
-	\end{subfigure}
-	\caption{Reduction Distribution Prediction}
-	\label{fig:dis}
-	\vspace{-1em}
-\end{figure*}
 
@@
 The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
+
+\begin{figure*}
+	\centering
+	\begin{subfigure}[b]{0.31\linewidth}
+		\includegraphics[width=\linewidth]{fig/hash_pre}
+		\caption{Linear Regression Prediction of Hash Partitioner\newline}
+		\label{fig:hash_pre}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.31\linewidth}
+		\includegraphics[width=\linewidth]{fig/range_pre_sample}
+		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
+		\label{fig:range_pre_sample}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.31\linewidth}
+		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
+		\caption{Prediction Relative Error of Range Partitioner\newline}
+		\label{fig:prediction_relative_error}
+	\end{subfigure}
+	\caption{Reduction Distribution Prediction}
+	\label{fig:dis}
+	\vspace{-1em}
+\end{figure*}
 
@@
 
-For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
-and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
-Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
-After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
-The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
-% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
-Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
-% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
-Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$. 
 \noindent
@@
 	\small
-	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
+	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
 		\State $m\gets$ partition number of map tasks
@@
 		\State $idx\gets 0$
-		\While{$idx <$ len$R$}
+		\State\While{$idx <$ len$R$}
 			% \Comment{Schedule reduces by MinHeap}
@@
 	\EndProcedure
-	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
+	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
 		\State Swap tasks between node $host\_id$ and node $assigned\_id$
@@
 
+For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
+and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
+Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
+% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
+After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
+The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
+% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
+Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
+% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
+Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
+
+\subsubsection{Cope with Multiple Shuffle Dependencies}
+% \ifrevision
+% \marginpar{E5}
+% \fi
+A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
+The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+For those pending shuffles, it is impossible to predict their sizes. 
+This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+But doing this introduces large overhead such as extra task serialization. 
+To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.
+
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \emph{shuffles} scheduled by Heuristic MinHeap are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \emph{shuffles}. 
+After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
+which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
+
 \noindent
@@
 	\small
-	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
+	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
 		\State $m\gets$ partition number of map tasks
@@
 \end{minipage}
-\subsubsection{Cope with Multiple Shuffle Dependencies}
-% \ifrevision
-% \marginpar{E5}
-% \fi
-A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
-The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-For those pending shuffles, it is impossible to predict their sizes. 
-This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-But doing this introduces large overhead such as extra task serialization. 
-To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.
-
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \emph{shuffles} scheduled by Heuristic MinHeap are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \emph{shuffles}. 
-After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
-This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
-which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
 

### 2018-12-30 taco/tex/intro.tex
Cite TACO & Update recent publications

@@
 
-Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator},
-the shuffle is often poorly optimized in practice.
+{\color{yellow}
+Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous}.
+However, the shuffle phase is often poorly optimized in practice.
+% }
+% {\color{red}
+% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator},
+% the shuffle is often poorly optimized in practice.
+% }
 % take over shuffle

### 2018-12-30 taco/tex/intro.tex
Update references

@@
 {\color{yellow}
-Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous}.
+Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive}.
 However, the shuffle phase is often poorly optimized in practice.
-% }
+}
 % {\color{red}

### 2019-01-02 taco/tex/motivation.tex
Add taco
revise some errors

--- 2018-10-17 tex/motivation.tex
@@
 \begin{figure}
-	\includegraphics[width=\linewidth]{fig/util}
+	\includegraphics[width=0.8\linewidth]{fig/util}
 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
@@
 Compared to input dataset, the size of shuffle data is relatively small. 
-For example, the shuffle size of Spark Terasort\footnote{https://github.com/ehiggs/spark-terasort} is less than $25\%$ of input data. 
+For example, the shuffle size of Spark Terasort is less than $25\%$ of input data. 
 The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
@@
 Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
-For a cluster with $n$ slots, the number of tasks should be $n \times k (k \geq 1)$. 
+For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
 For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.

### 2019-01-02 taco/tex/relatedwork.tex
Add taco
revise some errors

--- 2018-10-22 tex/relatedwork.tex
@@
 
-{\color{black}
+{\color{blue}
 \textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
@@
 Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers.
-The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is uesed to optimize the stragglers.
+The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers.
 

### 2019-01-03 taco/tex/evaluation.tex
Major revision

@@
 
-\begin{figure}
-	\includegraphics[width=.8\linewidth]{fig/scache_util}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
-	\label{fig:scache_util}
-\end{figure}
+% \begin{figure}
+% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
+% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
+% 	\label{fig:scache_util}
+% \end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{fig/tpcds}
+	\includegraphics[width=.9\textwidth]{fig/tpcds}
 	\caption{TPC-DS Benchmark Evaluation}
@@
 
-To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce as the external shuffle service and co-scheduler.
-Although \textit{pre-scheduling reduce tasks} is not critical for the simple DAG computing such as Hadoop MapReduce, some shuffle-heavy jobs on Hadoop MapReduce can still be optimized by SCache shuffle data management.
+To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
+Although the effect of \textit{pre-scheduling} will be alleviated by the simple DAG computing, some shuffle-heavy jobs can still be optimized by SCache shuffle data management.
 
-Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort.
-Both figures have the same proportion of time.
-Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size.
+% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
+As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
 As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
@@
 This causes the CPU resources to be idle.
-As shown in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
+On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
 This avoids the reduce phase waiting for the shuffle data.
@@
 
+\subsection{Overhead of Sampling}
+We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
+In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
+Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
+Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
+So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
+Combined with the sampling overhead evaluation, we believe that SCache is scalable.
+
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Overhead of Sampling}
-We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
-In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
-Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
-Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
-So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
-Combined with the sampling overhead evaluation, we believe that SCache is scalable.

### 2019-01-03 taco/tex/impl.tex
Major revision

@@
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
-In order to use SCache, we mainly need to modify two parts of the frameworks: (a) We need to modify codes in the DAG scheduler to let framework provide DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data between the map task and the reduce task should be transferred to SCache Storage Management.
+In order to use SCache, we mainly need to modify two parts of the frameworks: (a) The DAG scheduler should provide the DAG information and follow the pre-scheduled result of SCache; (b) The shuffle data should be transferred to SCache Storage Management.
 
 To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
-Taking Hadoop MapReduce as an example, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC.
-It takes about 400 lines of code.
+In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC.
+It takes about 380 lines of code.
 In Spark, we mainly modify DAGScheduler and the corresponding data fetcher.

### 2019-01-03 taco/tex/intro.tex
Major revision

--- 2018-12-30 taco/tex/intro.tex
@@
+\begin{figure}
+	\centering
+	\includegraphics
+		[width=.5\linewidth]
+		{fig/workflow}
+	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
+	\label{fig:workflow}
+\end{figure}
+
 \section{Introduction}\label{sec:introduction}
@@
 
-{\color{yellow}
-Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous}.
+{\color{blue}
+Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive}.
 However, the shuffle phase is often poorly optimized in practice.
-% }
+}
 % {\color{red}
@@
 %The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
-\begin{figure}
-	\centering
-	\includegraphics
-		[width=.6\linewidth]
-		{fig/workflow}
-	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
-	\label{fig:workflow}
-\end{figure}
 
@@
 By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
-I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
-This situation will be amplified in shuffle-heavy tasks.
+% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
+% This situation will be amplified in shuffle-heavy tasks.
 }

### 2019-01-03 taco/tex/model.tex
revise some errors
Major revision

@@
 In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-the FRQ model quantifies computing and I/O resources and visualizes them in time dimension.
+The FRQ model quantifies computing and I/O resources and visualizes them in time dimension.
 According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
@@
 In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
+
+\subsection{The FRQ Model}\label{model_overview}
+The current distributed computing frameworks mostly use DAGs to describe computation logic. 
+A shuffle phase is required between each adjacent DAG computation phases.
+In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
+After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies.
+For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
+
+Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
+\begin{itemize}
+	\item Input Data Size \((D)\): The data size of the computation phase.
+	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This rate depends on the algorithm used in the computation phase.
+    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase.
+This rounds depends on the current computation resources and the configuration of the framework.
+Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map require 1 CPU.
+Then we need 4 rounds of computation to complete the map phase.
+    \item Computation Speed \((V_{i})\): 
+    The computation speed for each computation phase. This speed depends on the algorithm used in the computation phase.
+    \item Shuffle Speed \((V_{Shuffle})\): 
+    Transmission speed during shuffle. This speed depends on network and storage device bandwidth.
+\end{itemize}
 
@@
 \end{figure*}
-
-\subsection{The FRQ Model}\label{model_overview}
-The current distributed data parallel computing frameworks mostly use DAGs to describe computation logic.
-A shuffle phase is required between each adjacent DAG computation phases.
-In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
-After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies.
-For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
-
-Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
-\begin{itemize}
-	\item Input Data Size \((D)\): The data size of the computation phase.
-	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This conversion rate depends on the algorithm used in the computation phase.
-    \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase using the current computation resources.
-The number of rounds depends on the current computation resources and the settings of the computation job.
-Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks.
-Then we need 4 rounds of computation to complete the map phase.
-    \item Computation Speed \((V_{i})\): 
-    The computation speed for each computation phase. The computation speed depends on the algorithm used in the computation phase.
-    \item Shuffle Speed \((V_{Shuffle})\): 
-    Transmission speed during shuffle. Shuffle speed depends on network and storage device bandwidth.
-\end{itemize}
-
-We can calculate the execution time of each phase of the job with these five parameters.
-As shown in Figure \ref{fig:model_basic}, in full parallel mapReduce, the total execution time of a job is the sum of the map phase time and reduce phase time:
+The FRQ model calculates the execution time of each phase of the job with these five parameters.
+As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
 \begin{equation}
@@
 
+\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
 We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
@@
 This relationship will be shown in the following Subsection \ref{model_analysis}.
-\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and \(K \times T_{P\_Shuffle}\) represents the computing overhead. \(K\) is an empirical value. 
+\(K\) is an empirical value. 
 Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results.
@@
 
+The shuffle phase time formula is as follows:
 \begin{equation}
@@
 
-For shuffle-heavy computing jobs, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
+According to Equation \ref{equation_Tjob}\&\ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
 Improving I/O speed is an effective way to reduce shuffle time.
@@
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
-When using the FRQ model to describe a computation job, we can easily analyze the resource scheduling strategy of the computation framework.
-Different computing frameworks may use different resource scheduling strategies.
-The FRQ model can evaluate the scheduling strategies of these computing frameworks and help us optimize them.
+By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.
 
@@
 
-The FRQ model can describe a variety of resource scheduling strategies.
-First, we analyze a naive scheduling strategy.
+The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
 As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is fully serially executed.
@@
 Therefore, the overhead of the reduce phase is 0.
-But since shuffle and computation are serial execution, the total execution time of a job is different from the above:
+The total execution time of a job is also different from the above:
 \begin{equation}
@@
 
-Apache Spark uses this scheduling strategy by default.
-Due to serialization, the I/O resource is idle during the reduce phase and map phase.
-The scheduling strategy is simple and has a lot of room for optimization.
+Due to serialization, the I/O resource is idle during the reduce phase and map phase. this scheduling strategy is simple and has a lot of room for optimization.
 
-Figure \ref{fig:model_hadoop} shows one of the optimization methods.
+Figure \ref{fig:model_hadoop} shows a more efficient scheduling strategy which is used by Hadoop MapReduce.
 In this scheduling strategy, shuffle phase and reduce phase start at the same time.
@@
 The execution time of the shuffle phase is hidden in the reduce phase.
-This scheduling strategy is used by Hadoop MapReduce.
-After analyzing this model, we believe that this strategy will be more efficient than the above serial strategy in the same situation.
-Meanwhile, we found that the I/O resource in the map phase is still idle.
-This scheduling strategy can be optimized.
+But we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.
 
@@
     \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
-	The meaning of \(V_{Map} \times R\) is the speed at which shuffle data is generated.
 	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
-When the Round1 of the map phase ends, the SCache starts shuffling data until the end of the shuffle phase.
-Due to shuffle speed is slower, the shuffle phase is uninterrupted.
-SCache transmits the shuffle data generated in the last round of map phase during the reduce phase.
-Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase:
+	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{PShuffle}\) is as followed:
 	\begin{equation}
@@
     \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
-	When the speed of generating shuffle data (\(V_{Map} \times R\)) is less than the shuffle speed (\(V_{Shuffle}\)), SCache needs to wait for shuffle data to be generated.
-As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each Round.
-Thus \(T_{P\_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase:
+	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated.
+As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round.
+In this case, the formula of \(T_{PShuffle}\) is as followed:
 	\begin{equation}
@@
 
-% After analyzing the above two situations, we figure out the formula for \(T_{P\_Shuffle}\):
-% \begin{equation}
-%     \label{equation_Tpshuffle}
-%     \begin{aligned}
-%     T_{P\_Shuffle} &=
-%         \begin{cases} 
-%         T_{Shuffle} - \frac{(N - 1)\times T_{Map}}{N} & , V_{Map} \times R \ge V_{Shuffle} \\ 
-%         T_{Shuffle} \times \frac{1}{N} & , V_{Map} \times R < V_{Shuffle}
-%         \end{cases}
-%     \end{aligned}
-% \end{equation}
-% If the shuffle speed is slow(\(V_{Map} \times R \ge V_{Shuffle}\)), SCache transmit the shuffle data generated in the last round of map phase during the reduce phase.
-Therefore \(T_{PShuffle}\) is equal to one-\(N\) of the total time of the shuffle phase.
-
-% If the shuffle speed is fast (\(V_{Map} \times R < V_{Shuffle}\)), \(T_{P_Shuffle}\) is equal to the total time of shuffle (\(T_{Shuffle}\)) minus the time that shuffle is executed in the map phase.
-
-Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache reduces \(T_{P\_Shuffle}\) and thus lessens \(T_{Reduce}\).
+Compared to the original Hadoop MapReduce resource scheduling strategy, Hadoop MapReduce with SCache shortens \(T_{P\_Shuffle}\) and thus shortens \(T_{Reduce}\).
 This is how pre-fetching optimizes the total execution time of a job.
@@
 \begin{table}[!t]
-% \renewcommand{\arraystretch}{0.8}
-\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
-\label{table1}
 \begin{minipage}{\columnwidth}
 \centering
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
 \scalebox{0.75}{
@@
 }
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\label{table1}
 \end{minipage}
@@
 \begin{table*}[!t]
-\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
-\label{table2}
 \centering
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
 \scalebox{0.75}{
@@
 }
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\label{table2}
 \end{table*}
@@
 \subsection{Model Verification}\label{model_verification}
-In order to verify the FRQ model, we run experiments on two environments.
-The first environment is on Amazon EC2 and it has 50 m4.xlarge nodes as shown in Subsection \ref{stepup}.
-Another in-house environment has 4 nodes and each node has 128GB memory and 32 cores.
-To simplify the calculation of the FRQ model, we use Hadoop MapReduce as a framework and use Terasort as an experimental application.
+In order to verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
+(b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
+To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop Mapreduce framework.
 We deployed Hadoop with SCache and without SCache in both environments.
 
-Table \ref{table1} shows the calculational results of the FRQ model in the in-house environment.
-Workload is from 16 GB to 64 GB.
+Table \ref{table1} shows the calculational results of the FRQ model in the in-house environment. The workload is from 16 GB to 64 GB. 
 \(D\) and \(N\) are set according to the application parameters.
@@
 K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache.
-The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
-In the case of SCache, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
-In the case of Legacy, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}).
+% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
+In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
+% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
+In the original Hadoop, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}).
 \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
-The formula of \(Error\) is:
-\begin{equation}
-	\label{equation_error}
-	\begin{aligned}
-		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
-	\end{aligned}
-\end{equation}
+% The formula of \(Error\) is:
+% \begin{equation}
+% 	\label{equation_error}
+% 	\begin{aligned}
+% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
+% 	\end{aligned}
+% \end{equation}
 
 Table \ref{table2} shows the calculational results of the FRQ model in Amazon EC2 environment.
-\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
+\;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
 We also set K to the same empirical value.
@@
 In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
-In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).
+% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).
 
@@
 In order to verify the above-mentioned two cases when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
-Figure \ref{fig:hadoop_net1} shows the utilization of Terasort in the in-house environment.
-The network utilization remains high until the shuffle phase is completed.
-This situation is consistent with Figure \ref{fig:model_scache1}.
-Figure \ref{fig:hadoop_net2} shows the utilization in Amazon EC2 environment.
-The network utilization has 5 regular peaks.
-This situation is also consistent with Figure \ref{fig:model_scache2}.
-Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
+Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
+On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment.
+Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
+% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
 
-In terms of accuracy, the experimental values are all greater than the calculated values.
+In terms of accuracy, the experimental values are all larger than the calculated values.
 This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on.
-In the case where the input data is small and the total time is short, the error caused by the overhead is amplified.
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable.
-Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
+% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
+These overhead will be amplified when the input data is small or the total execution time is short. 
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
 }

### 2019-01-03 taco/tex/motivation.tex
Major revision

@@
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
-
-\begin{figure}
-	\includegraphics[width=0.8\linewidth]{fig/util}
+\begin{figure*}
+	\centering
+	\begin{subfigure}[b]{0.47\linewidth}
+		\includegraphics[width=\linewidth]{fig/util}
+		\caption{Original Spark}
+		\label{fig:util}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.47\linewidth}
+		\includegraphics[width=\linewidth]{fig/scache_util}
+		\caption{Spark With SCache}
+		\label{fig:scache_util}
+	\end{subfigure}
 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
-	\label{fig:util}
-	\vspace{-1em}
-\end{figure}
+\end{figure*}
 
@@
 \subsubsection{Multi-round Tasks Execution}\label{multi}
-Both experience and DAG framework manuals recommend that multi-round execution of each stage will benefit the performance of applications.
+Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
 For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
-For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.
-Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
-
+% For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.
+% Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
 Since the shuffle data becomes available as soon as the end of a task's execution, 
@@
 
-Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
+% Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
 To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data.

### 2019-01-03 taco/tex/relatedwork.tex
Major revision

--- 2018-10-21 tex/relatedwork.tex
@@
 
-{\color{black}
+{\color{blue}
 \textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model).
-In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
-There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp}.
+\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on.
+% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
+% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
+% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
 Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
@@
 The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
-In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the execution of a MapReduce job.
-The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce.
-The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model.
+In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job abd combine them into an overall MapReduce job model.
+% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
+% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
 Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
 provisions the resources for the job.
-
+Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
+% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
 However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
-Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
-FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
+% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
+The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
 }

### 2019-01-03 taco/tex/evaluation.tex
revise some errors

@@
 To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
-Although the effect of \textit{pre-scheduling} will be alleviated by the simple DAG computing, some shuffle-heavy jobs can still be optimized by SCache shuffle data management.
+Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
 
@@
 The shuffle phase and the reduce phase start simultaneously.
-Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce needs to wait for network transfer.
+Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce phase needs to wait for network transfer.
 This causes the CPU resources to be idle.

### 2019-01-03 taco/tex/intro.tex
revise some errors

@@
 {\color{blue}
-In order to analyze above-mentioned resources scheduling strategies, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+To analyze resources scheduling strategies as mentioned above, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
 The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.

### 2019-01-03 taco/tex/model.tex
revise some errors

@@
 In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-The FRQ model quantifies computing and I/O resources and visualizes them in time dimension.
+The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
 According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
@@
 A shuffle phase is required between each adjacent DAG computation phases.
-In order to better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
-After quantifying computing and I/O resources, the FRQ model is able to describe different resource scheduling strategies.
+To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
+After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies.
 For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
@@
     \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase.
-This rounds depends on the current computation resources and the configuration of the framework.
-Taking Hadoop MapReduce as an example, supposing we have 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map require 1 CPU.
+These rounds depend on the current computation resources and the configuration of the framework.
+Take Hadoop MapReduce as an example.
+Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU.
 Then we need 4 rounds of computation to complete the map phase.
@@
     \item Shuffle Speed \((V_{Shuffle})\): 
-    Transmission speed during shuffle. This speed depends on network and storage device bandwidth.
+    Transmission speed in the shuffle phase. This speed depends on network and storage device bandwidth.
 \end{itemize}
@@
 \(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
-We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of shuffle phase. 
+We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
 The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
@@
 Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results.
-The overhead is caused by these waiting.
+This waiting causes the overhead.
 The FRQ model uses K to indicate the extent of the waiting.
@@
 The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
-As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is fully serially executed.
+As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is entirely serially executed.
 The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
@@
 
-Due to serialization, the I/O resource is idle during the reduce phase and map phase. this scheduling strategy is simple and has a lot of room for optimization.
+Due to serialization, the I/O resource is idle during the reduce phase and map phase. This scheduling strategy is simple and has much room for optimization.
 
@@
 The execution time of the shuffle phase is hidden in the reduce phase.
-But we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.
+However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.
 
@@
 \subsection{Model Verification}\label{model_verification}
-In order to verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
+To verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
 (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
@@
 
-In order to verify the above-mentioned two cases when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+In order to verify the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
@@
 
-In terms of accuracy, the experimental values are all larger than the calculated values.
+Regarding accuracy, the experimental values are all larger than the calculated values.
 This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on.
 % In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
-These overhead will be amplified when the input data is small or the total execution time is short. 
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is basically below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
+This overhead will be amplified when the input data is small or the total execution time is short. 
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
 }

### 2019-01-03 taco/coverletter/coverletter.tex
Add coverletter

\documentclass[12pt,reqno]{amsart}
\setlength{\hoffset}{-.5in}
\setlength{\voffset}{-.25in}
\usepackage{amssymb,latexsym}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{url}
\usepackage{amssymb,amsmath,psfrag}
\usepackage{enumerate}
\newcommand\BD{\mathrm{B}}
\newcommand\SD{\mathrm{S}}
\textwidth=6.175in
\textheight=8.5in

\theoremstyle{plain}
\numberwithin{equation}{section}
\newtheorem{thm}{Theorem}[section]
\newtheorem{theorem}[thm]{Theorem}

\theoremstyle{plain}
\numberwithin{equation}{section}

\title{Summary of Difference}

\author{Rui Ren}
\author{Chunghsuan Wu}
\author{Zhouwang Fu}
\author{Tao Song}
\author{Zhengwei Qi}
\author{Haibing Guan}

\begin{document}

\maketitle

% \section{Summary}

This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
This paper makes the following distinct contributions compared with the conference paper.

\begin{enumerate}
\item 
We propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
The FRQ model quantifies computing and I/O resources by five input parameters. 
Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
In this paper, we use the model to analyze the deficiencies of the resources scheduling strategies and then optimize them.

% The proposed model is not only to predict the job completion time, but also to theoretically analyze DAG frameworks.
% The FRQ models DAG frameworks according to the resource scheduling strategy of each DAG framework by mutiple parameters.
% Through modeling, the FRQ model can indicate which parameters of the DAG framework are important and which parts of the DAG framework can be optimized. 
% Furthermore, the FRQ models can classify DAG frameworks based on their scheduling stratagies.
% According to the theoretical analysis results of the FRQ model, we are able to optimize DAG frameworks more accurately.
\item 
In the conference paper, we only implemented SCache on Spark. 
To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
\item
We append two parts to the evaluation section. 
Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper(50-nodes m4.xlarge cluster).
According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
\end{enumerate}

% Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
We believe that the added content makes a sufficient contribution to this journal submission.

\bibliographystyle{IEEEtran}
\bibliography{coverletter}

\end{document}

### 2019-01-04 taco/coverletter/coverletter.tex
Update coverletter

@@
 In this paper, we use the model to analyze the deficiencies of the resources scheduling strategies and then optimize them.
-
-% The proposed model is not only to predict the job completion time, but also to theoretically analyze DAG frameworks.
-% The FRQ models DAG frameworks according to the resource scheduling strategy of each DAG framework by mutiple parameters.
-% Through modeling, the FRQ model can indicate which parameters of the DAG framework are important and which parts of the DAG framework can be optimized. 
-% Furthermore, the FRQ models can classify DAG frameworks based on their scheduling stratagies.
-% According to the theoretical analysis results of the FRQ model, we are able to optimize DAG frameworks more accurately.
 \item 
-In the conference paper, we only implemented SCache on Spark. 
-To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
-Our experiments show that SCache can also optimize the computing performance of Hadoop MapReduce.
+In the conference paper, we only implement SCache on Spark. 
+In this paper, we implement SCache on Hadoop MapReduce. 
+By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
+Meanwhile, our experiments are also consistent with the analysis of the model.
+This result demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
+% To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
 \item
@@
 Firstly, we evaluate the FRQ model in both our in-house environment and Amazon EC2 environment. The error between the FRQ’s calculated value and the experimental value is mainly below $10\%$. 
-Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper(50-nodes m4.xlarge cluster).
+Secondly, we evaluate the performance of Hadoop MapReduce with SCache. We use the same Amazon EC2 environment as the conference paper (50-nodes m4.xlarge cluster).
 According to the experiments, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.

### 2019-01-04 taco/tex/intro.tex
Add TACO

@@
 {\color{blue}
-Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive}.
+Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive, zhang2018simpo, chen2013tiled}.
 However, the shuffle phase is often poorly optimized in practice.

### 2019-03-26 jpdc/SCache.tex
Add jpdc.

%\documentclass[a4paper,fleqn,longmktitle]{cas-dc}
\documentclass[a4paper,fleqn]{cas-dc}
%\usepackage{l3regex}

\usepackage{lipsum}

%\usepackage[authoryear,longnamesfirst]{natbib}
\usepackage[numbers]{natbib}
\usepackage{subcaption} % For subfigures
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{float}
\usepackage{color}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{graphics}
\usepackage{multicol}
\usepackage{varwidth}

\xspaceaddexceptions{]}
\def\tsc#1{\csdef{#1}{\textsc{\lowercase{#1}}\xspace}}
\tsc{WGM}
\tsc{QE}
\tsc{EP}
\tsc{PMS}
\tsc{BEC}
\tsc{DE}

\begin{document}
\let\WriteBookmarks\relax
\def\floatpagepagefraction{1}
\def\textpagefraction{.001}
\shorttitle{Efficient Shuffle Management for DAG Computing Frameworks Based on the FRQ Model}
\shortauthors{R. Rui et al.}
%\begin{frontmatter}

\title [mode = title]{Efficient Shuffle Management for DAG Computing Frameworks Based on the FRQ Model}                      
% \tnotemark[1,2]

%%  \tnoteref{tn1,tn2}

% \tnotetext[1]{This document is the results of the research
%    project funded by the National Science Foundation.}

% \tnotetext[2]{The second title footnote which is a longer text matter
%    to fill through the whole text width and overflow into
%    another line in the footnotes area of the first page.}

\author[1]{Rui Ren}[type=editor,
                        bioid=1,
                        style=chinese]
% \fnmark[1]

\author[1]{Chunghsuan Wu}[style=chinese]
\author[1]{Zhouwang Fu}[style=chinese]
\author[1]{Tao Song}[style=chinese]
\author[1]{Zhengwei Qi}[style=chinese]
\cormark[1]
\ead{qizhwei@sjtu.edu.cn}

\author[1]{Haibing Guan}[style=chinese]

\address[1]{Shanghai Jiao Tong University, China}
\cortext[cor1]{Corresponding author}

\input{./tex/abstract.tex}

\begin{keywords}
  Distributed DAG frameworks \sep Shuffle \sep Optimization \sep Performance model
\end{keywords}

\maketitle

\makeatletter
\renewcommand\section{\@startsection{section}{1}{\z@}%
    {15pt \@plus 3\p@ \@minus 3\p@}%
    {4\p@}%
    {%\let\@hangfrom\relax
     \sectionfont\raggedright\hst[13pt]}}
\renewcommand\subsection{\@startsection{subsection}{2}{\z@}%
    {10pt \@plus 3\p@ \@minus 2\p@}%
    {.1\p@}%
    {%\let\@hangfrom\relax
     \ssectionfont\raggedright }}
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
    {10pt \@plus 1\p@ \@minus .3\p@}%
    {.1\p@}%
    {%\let\@hangfrom\relax
     \sssectionfont\raggedright}}
\makeatother

\input{./tex/intro.tex}
\input{./tex/motivation}
\input{./tex/optimization}
\input{./tex/impl}
\input{./tex/model}
\input{./tex/evaluation}
\input{./tex/relatedwork}
\input{./tex/conclusion}
\input{./tex/acknowledg}

% \printcredits

\footnotesize

\vskip12pt

% \bibliographystyle{ACM-Reference-Format}
\bibliographystyle{IEEEtran}
\bibliography{biblio}

\bio{./fig/author/Rui_Ren}
\textbf{Rui Ren} was born in Shaanxi, China, in 1978. He received the B.S. and M.S. degrees from Shanghai Jiao Tong University, China, in 2000 and 2004, respectively. He is currently a lecturer in the School of Software, Shanghai Jiao Tong University, China.
\endbio

\vskip30pt

\bio{./fig/author/Chunghsuan_Wu}
\textbf{Zhongxuan Wu} received the BE degree from Shanghai Jiao Tong University, China, in 2017. He is currently pursuing a ME degree in Shanghai Jiao Tong University, China. His research interests mainly focus on distributed computing.
\endbio

\vskip30pt

\bio{./fig/author/ZhouWang_Fu}
\textbf{Zhouwang Fu} is a graduated Master student of Shanghai Jiao Tong University in China. He received his Bachelor and Master degree in software engineering Shanghai Jiao Tong University.
\endbio

\vskip30pt

\bio{./fig/author/Tao_Song}
\textbf{Tao Song} is currently working as a postdoc at Shanghai Jiao Tong University in China. He received his Ph.D. degree in computer science and M.Eng. degree in software engineering from Shanghai Jiao Tong University. His research interests include data center networking, cloud computing, artificial intelligence and swarm intelligence.
\endbio

\vskip30pt

\bio{./fig/author/Zhengwei_Qi}
\textbf{Zhengwei Qi} received the BEng and MEng degrees from Northwestern Polytechnical University, in 1999 and 2002, and the PhD degree from Shanghai Jiao Tong University, in 2005. Currently, he is a professor in the School of Software, Shanghai Jiao Tong University (China). His research interests include distributed computing, virtualized security, model checking, program analysis and embedded systems.
\endbio

\vskip30pt

\bio{./fig/author/Haibing_Guan}
\textbf{Haibing Guan} received the PhD degree from Tongji University, in 1999. He is a professor of School of Electronic, Information and Electronic Engineering, Shanghai Jiao Tong University, and the director of the Shanghai Key Laboratory of Scalable Computing and Systems. His research interests include distributed computing, network security, network storage, green IT, and cloud computing.
\endbio

\makeatletter

\def\pct{\expandafter\@gobble\string\%}

\immediate\write\@auxout{\pct\space This is a test line.\pct }

\end{document}

### 2019-03-26 jpdc/tex/abstract.tex
Add jpdc.

--- 2018-12-28 taco/tex/abstract.tex
@@
-\begin{abstract}
+\begin{abstract}[S U M M A R Y]
 
@@
 During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
-The FRQ models utilization of resources and predicts the execution time of computing jobs on different DAG frameworks. 
-We use the FRQ model to assist in analyzing DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
+The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
+We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
 }
@@
 \end{abstract}
+
+% Short abstract 100
+% To optimize shuffle overhead in the DAG computing frameworks, we present SCache, an open source plug-in system.
+We also propose a new performance model called Framework Resources Quantification(FRQ) model.
+The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of jobs.
+We use the model to analyze the deficiencies of the frameworks.
+SCache uses a heuristic pre-scheduling algorithm to pre-fetch shuffle data.
+Meanwhile, SCache uses memory to accelerate the shuffle process.
+We have implemented SCache on both Spark and Hadoop MapReduce.
+The performance of SCache has been evaluated on a 50-node Amazon EC2 cluster.

### 2019-03-26 jpdc/tex/evaluation.tex
Add jpdc.

--- 2019-01-03 taco/tex/evaluation.tex
@@
 		\end{subfigure}
-		\caption{Stage Completion Time of Single Shuffle Test}
+		\vspace{-1em}
+		\caption{Stage Completion Time of\newline Single Shuffle Test}
 		\label{fig:singleshuffle}
@@
 		\end{subfigure}
-		\caption{Median Task Completion Time of Single Shuffle Test}
+		\vspace{-1em}
+		\caption{Median Task Completion\newline Time of Single Shuffle Test}
 		\label{fig:singleshuffletask}
@@
 		\begin{subfigure}{\linewidth}
+			\vspace{-0.5em}
 			\begin{minipage}{\linewidth}
@@
 			\begin{minipage}{\linewidth}
+				\vspace{0.5em}
 				\includegraphics[width=\linewidth]{fig/tera_shuffle}
@@
 		\end{subfigure}
+		% \vspace{0.1em}
 		\caption{Terasort Evaluation}
@@
 With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
-The in-memory cache of shuffle data further reduce the shuffle read time. 
+The in-memory cache of shuffle data further reduces the shuffle read time. 
 As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
@@
 It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\label{fig:hadoop_terasort}
-\end{figure}
+\end{figure*}
 \begin{figure*}
@@
     \centering
-    \begin{minipage}{0.5\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \centering
@@
     \end{minipage}\hfill
-    \begin{minipage}{0.42\textwidth}
+    \begin{minipage}{0.4\textwidth}
         \centering

### 2019-03-26 jpdc/tex/impl.tex
Add jpdc.

--- 2019-01-03 taco/tex/impl.tex
@@
 {\color{blue}
-When a DAG job is submitted, the DAG information will be generated in framework task scheduler. 
+When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
 Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
@@
 
-When a map task finishes computing, the shuffle write implementation of DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
+When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
 After that, the slot will be released (without being blocked on disk operations).
@@
 {\color{blue}
-In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
+In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
 After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
@@
 	\centering
-	\begin{minipage}{.47\textwidth}
+	\begin{minipage}{.4\textwidth}
 		\centering
@@
 	\end{minipage}\hfill
-	\begin{minipage}{.42\textwidth}
+	\begin{minipage}{.4\textwidth}
 		\centering
@@
 \subsection{Analysis of cross-framework capability}\label{crossframework}
-Shuffle optimization of SCache inevitably requires the modification on DAG frameworks.
+Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks.
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
@@
 We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
-If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of DAG computing.
+If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of the DAG computing.
 A possible way to handle this failure is selecting some backup nodes to store replications. 

### 2019-03-26 jpdc/tex/optimization.tex
Add jpdc.

--- 2018-12-28 taco/tex/optimization.tex
@@
     \centering
+    % \begin{minipage}{0.42\textwidth}
+    %     \centering
+    %     \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
+	% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
+	% 	\label{fig:cdf}
+    % \end{minipage}\hfill
     \begin{minipage}{0.42\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
-		\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
-		\label{fig:cdf}
-    \end{minipage}\hfill
-    \begin{minipage}{0.49\textwidth}
         \centering
@@
 	\end{minipage}
+	\begin{minipage}{0.49\textwidth}
+        \centering
+        \includegraphics[width=0.9\textwidth]{fig/shuffle} % first figure itself
+		\caption{Shuffle Data Prediction}
+		\label{fig:shuffle}
+    \end{minipage}\hfill
 \end{figure}
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.45\linewidth]{fig/reduce_cdf}
-% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
-% 	\label{fig:cdf}
-% 	\vspace{10em}
-% \end{figure}
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.4\linewidth]{fig/sim}
-% 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
-% 	\label{fig:sim}
-% 	\vspace{-1em}
-% \end{figure}
 
@@
 In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
+% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
 The average shuffle read time is $3.2\%$ of total reduce completion time.
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.5\linewidth]{fig/shuffle}
-	\caption{Shuffle Data Prediction}
-	\label{fig:shuffle}
-	\vspace{-1em}
-\end{figure}
 As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
@@
 		\includegraphics[width=\linewidth]{fig/range_pre_sample}
-		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
+		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
 		\label{fig:range_pre_sample}
+		\vspace{1em}
 	\end{subfigure}
@@
 % \fi
+
+\noindent
+\begin{minipage}{0.95\columnwidth}
+\begin{algorithm}[H]
+\caption{Heuristic MinHeap Scheduling for Single Shuffle}
+\label{hminheap}
+	\begin{algorithmic}[1]
+	\small
+	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
+		\State $m\gets$ partition number of map tasks
+		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
+		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
+		\State $idx\gets 0$
+		\While{$idx <$ len$R$}
+		% \Comment{Schedule reduces by MinHeap}
+		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
+		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
+		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
+		\State Sift down $M\left[0\right]$ by $size$
+		\State $idx\gets idx-1$
+		\EndWhile
+		\State $max\gets$ maximum size in $M$
+		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
+		\ForAll{$reduce$ in $R$}
+		\Comment{Heuristic locality swap}
+			\If{$reduce.assigned\_id \neq reduce.host\_id$}
+				\State $p\gets reduce.prob$
+				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
+				\State $upper\_bound \gets \left(1 + norm\right) \times max$
+				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
+			\EndIf
+		\EndFor
+		\Return $M$
+	\EndProcedure
+	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
+		\State Swap tasks between node $host\_id$ and node $assigned\_id$
+		\State of $reduce$ without exceeding the $upper\_bound$
+		\State of both nodes.
+		\State Return if it is impossible.
+	\EndProcedure
+	\end{algorithmic}
+\end{algorithm}
+\end{minipage}
+
 To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
@@
 % The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
-In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
-The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
-Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
-On the other hand, the result of linear regression comes out with a large relative error. 
-Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
+% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
+% On the other hand, the result of linear regression comes out with a large relative error. 
+% Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
+{\color{blue}
+Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
 We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
+}
 
@@
 In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap scheduling algorithm (Algorithm \ref{hminheap}).
-
-\noindent
-\begin{minipage}{0.95\columnwidth}
-\begin{algorithm}[H]
-\caption{Heuristic MinHeap Scheduling for Single Shuffle}
-\label{hminheap}
-	\begin{algorithmic}[1]
-	\small
-	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
-		\State $m\gets$ partition number of map tasks
-		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
-		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
-		\State $idx\gets 0$
-		\State\While{$idx <$ len$R$}
-			% \Comment{Schedule reduces by MinHeap}
-			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
-			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
-			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
-			\State Sift down $M\left[0\right]$ by $size$
-			\State $idx\gets idx-1$
-		\EndWhile
-		\State $max\gets$ maximum size in $M$
-		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
-		\ForAll{$reduce$ in $R$}
-		\Comment{Heuristic locality swap}
-			\If{$reduce.assigned\_id \neq reduce.host\_id$}
-				\State $p\gets reduce.prob$
-				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
-				\State $upper\_bound \gets \left(1 + norm\right) \times max$
-				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
-			\EndIf
-		\EndFor
-		% \Comment{$m$ is the number of input data}
-		% \Comment{$r$ is partition number of reduces}
-		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
-		% \Comment{$c$ is $r*m$ array of composition data}
-		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
-		\Return $M$
-	\EndProcedure
-	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
-		\State Swap tasks between node $host\_id$ and node $assigned\_id$
-		\State of $reduce$ without exceeding the $upper\_bound$
-		\State of both nodes.
-		\State Return if it is impossible.
-		% \State $reduces \gets M\left[reduce.host\_id\right].reduce$	
-		% \State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
-		% \State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
-		% \State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
-		% \State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
-		% \If{$size\_host\leq upper\_bound$ \textbf{and} \\
-		% 	\qquad \; $size\_assigned\leq upper\_bound$}
-		% 	\State Swap $candidates$ and $reduce$
-		% 	\State Update $size$ in $M$
-		% 	\State Update $assigned\_host$ in $candidates$ and $reduce$
-		% \EndIf
-	\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-\end{minipage}
 

### 2019-03-27 jpdc/tex/optimization.tex
Fix typo  proposed by reviewer1.

@@
 For the most DAG applications with random large scale input, 
-the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}:
+the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}:
 \begin{equation}
@@
 % The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
-% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
-% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
-% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
-% On the other hand, the result of linear regression comes out with a large relative error. 
-% Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
+Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
+On the other hand, the result of linear regression comes out with a large relative error. 
+Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+We will show the overhead evaluation of sampling in Section \ref{evaluation}.
+% {\color{blue}
+% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
 % We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
-{\color{blue}
-Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
-We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
-}
+% }
 

### 2019-03-27 tii/tex/__latexindent_temp.tex
Add tii.

--- 2019-01-03 taco/tex/evaluation.tex
@@
-\section{Evaluation}\label{evaluation}
-This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
-Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-
+modeling multiple users submitting varied queries (e.g.
+ad-hoc, interactive OLAP, data mining, etc.).
+TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems.
+We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute.
+As shown in Figure \ref{fig:tpcds}, the horizontal axis is query number, and the vertical axis is query completion time.
+Spark with SCache outperforms the original Spark in almost all the queries.
+Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude.
+The overall reduction portion of query time that SCache achieved is 40\% on average.
+Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
 % \begin{figure}
-% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
-% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
-% 	\label{fig:scache_util}
-% \end{figure}
-
-In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-{\color{blue}
-To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
-}
-Finally, we measure the overhead of weighted reservoir sampling. 
-In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
-More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
-
-% Because a complex Spark application consists of multiple stages.
-The completion time of each stage varies under different input data, configurations and different number of stages.
-This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison.
-To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
-\begin{figure*}
-	\centering
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/groupbymapstage}
-				\caption{Map Stage Completion Time}
-				\label{fig:mapstage}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/groupbyreducestage}
-				\caption{Reduce Stage Completion Time\newline}
-				\label{fig:reducestage}	
-			\end{minipage}
-		\end{subfigure}
-		\caption{Stage Completion Time of Single Shuffle Test}
-		\label{fig:singleshuffle}
-	\end{minipage}	
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/groupbymaptask}
-				\caption{Median Task in Map Stages}
-				\label{fig:maptask}
-			\end{minipage}
-
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/groupbyreducetask}
-				\caption{Median Task in Reduce Stages\newline}
-				\label{fig:reducetask}
-			\end{minipage}
-		\end{subfigure}
-		\caption{Median Task Completion Time of Single Shuffle Test}
-		\label{fig:singleshuffletask}
-	\end{minipage}	
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/tera}
-				\caption{Reduce Stage of First Shuffle}
-				\label{fig:terasort}
-			\end{minipage}
-
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/tera_shuffle}
-				\caption{Network Traffic of Second Shuffle}
-				\label{fig:terashuffle}
-			\end{minipage}
-		\end{subfigure}
-		\caption{Terasort Evaluation}
-	\end{minipage}
-\end{figure*}
-
-\subsection{Setup}\label{stepup}
-We modified Spark to enable shuffle optimization of SCache as a representative.
-The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
-We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
-Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
-Our evaluations reveal the bandwidth is only about 300 Mbps (see Figure \ref{fig:util}).
-
-\subsection{Simple DAG Analysis}\label{simpledag}
-%\subsubsection{Hardware Utilization}
-We first run the same single shuffle test shown in Figure \ref{fig:util}. 
-For each stage, we run 5 rounds of tasks with different input size. 
-As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
-Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. 
-An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. 
-It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
-On the one hand, the decoupling of shuffle write helps free the slot earlier, so that it can be re-scheduled to a new map task.
-On the other hand, with the help of shuffle pre-fetching, the decoupling of shuffle read significantly decreases the CPU idle time at the beginning of a reduce task.
-At the same time, SCache manages the hardware resources to store and transfer shuffle data without interrupting the computing process.
-As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark. 
-% \begin{figure}
-% 	%\vspace*{-0.01cm}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbymapstage}
-% 		\caption{Map Stage Completion Time Comparison}
-% 		\label{fig:mapstage}
-% 	\end{subfigure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducestage}
-% 		\caption{Reduce Stage Completion Time Comparison}
-% 		\label{fig:reducestage}
-% 	\end{subfigure}
-% 	\caption{Stage Completion Time of Single Shuffle Test}
-% 	\label{fig:singleshuffle}
-% \end{figure}
-
-% \begin{figure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
-% 		\caption{Median Task Details in Map Stages}
-% 		\label{fig:maptask}
-% 	\end{subfigure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
-% 		\caption{Median Task Details in Reduce Stages}
-% 		\label{fig:reducetask}
-% 	\end{subfigure}
-% 	\caption{Median Task Completion Time of Single Shuffle Test}
-% 	\label{fig:singleshuffletask}
-% \end{figure}
-The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
-% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
-% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
-% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
-For each stage, we pick the task that has median completion time. 
-In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
-It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
-Note that the shuffle write time can be observed even with the optimization of SCache. 
-The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.
-
-In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
-By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
-With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
-The in-memory cache of shuffle data further reduce the shuffle read time. 
-As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
-In addition, the heuristic algorithm can achieve a balanced pre-scheduling result, thus providing ~$80\%$ improvement in reduce stage completion time (Figure \ref{fig:reducestage}).
-
-In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
-
-\subsection{Terasort}
-We also evaluate Terasort-a recognized shuffle intensive benchmark for distributed system analysis. 
-Terasort consists of two consecutive shuffles. 
-The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
-As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
-It further proves the effectiveness of SCache's optimization.
-
-The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
-% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
-So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
-In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
-So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
-In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
-By doing this, Spark minimizes the shuffle data through network. 
-At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
-It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
-\begin{figure}
-	\centering
-	\begin{subfigure}{.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-		\caption{\color{blue}Hadoop MapReduce with SCache}
-		\label{fig:hadoop_terasort_scache}
-	\end{subfigure}
-	\begin{subfigure}{.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-		\caption{\color{blue}Hadoop MapReduce without SCache}
-		\label{fig:hadoop_terasort_origin}
-	\end{subfigure}
-	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
-	\label{fig:hadoop_terasort}
-\end{figure}
-\begin{figure*}
-	\centering
-	\includegraphics[width=.9\textwidth]{fig/tpcds}
-	\caption{TPC-DS Benchmark Evaluation}
-	\label{fig:tpcds}
-	\vspace{-1em}
-\end{figure*}
-
-{\color{blue}
-\subsection{Hadoop MapReduce with SCache}
-
-To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
-Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
-
-% Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
-As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
-As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
-The shuffle phase and the reduce phase start simultaneously.
-Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce phase needs to wait for network transfer.
-This causes the CPU resources to be idle.
-On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
-This avoids the reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
-}
-
-\subsection{Production Workload}
-We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
-TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
-TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
-% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
-As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
-Note that we skip some queries due to the compatible issues. 
-Spark with SCache outperforms the original Spark in almost all tested queries. 
-Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
-The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
-Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
-
-\subsection{Overhead of Sampling}
-We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
-In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
-Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
-Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
-So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
-Combined with the sampling overhead evaluation, we believe that SCache is scalable.
-
-\begin{figure}
-    \centering
-    \begin{minipage}{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
-        \caption{\color{blue}Hadoop MapReduce Terasort completion time}
-		\label{fig:hadoop_terasort_time}
-    \end{minipage}\hfill
-    \begin{minipage}{0.42\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
-        \caption{Sampling Overhead}
-		\label{fig:sampling}
-    \end{minipage}
-\end{figure}

### 2019-03-27 tii/tex/conclusion.tex
Add tii.

--- 2018-10-21 tex/conclusion.tex
@@
 %  }
-{\color{black}
+{\color{blue}
 Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
 Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
-At last we evaluate the SCache shuffle optimization by this practical model.
+At last, we evaluate the SCache shuffle optimization by this practical model.
 Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 

### 2019-03-27 tii/tex/intro.tex
Add tii.

--- 2019-01-04 taco/tex/intro.tex
@@
 	\includegraphics
-		[width=.5\linewidth]
+		[width=1\linewidth]
 		{fig/workflow}
@@
 Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
-To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce
+To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
 However, such early-start is by no means a panacea. 

### 2019-03-27 tii/tex/intro.tex
Fix typo proposed by reviewer2.

@@
 
-To make things worse, we note that the above deficiencies generally exist in most of the DAG computing frameworks. 
-As a result, even we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.
+We note that the above deficiencies generally exist in most of the DAG computing frameworks. 
+As a result, even though we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.
 

### 2019-03-27 tii/tex/model.tex
Add tii.
Fix typo proposed by reviewer2.

--- 2019-01-03 taco/tex/model.tex
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 	\label{fig:model_strategies}
-\end{figure}
+\end{figure*}
 
@@
 	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
-	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{PShuffle}\) is as followed:
+	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{P\_Shuffle}\) is as followed:
 	\begin{equation}
@@
 As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round.
-In this case, the formula of \(T_{PShuffle}\) is as followed:
+In this case, the formula of \(T_{P\_Shuffle}\) is as followed:
 	\begin{equation}
@@
 
-\begin{table}[!t]
-\begin{minipage}{\columnwidth}
+% \begin{table}[!t]
+\begin{table*}
 \centering
-\scalebox{0.75}{
+\scalebox{0.91}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 \label{table1}
-\end{minipage}
-\end{table}
+\end{table*}
 % \subsection{Performance Analysis}\label{model_performance_analysis}
 
-\begin{table*}[!t]
+% \begin{table*}[!t]
+\begin{table*}
 \centering
-\scalebox{0.75}{
+\scalebox{0.9}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
-To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop Mapreduce framework.
+To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework.
 We deployed Hadoop with SCache and without SCache in both environments.
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.42\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
@@
 	\end{subfigure}
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.42\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
@@
 	\label{fig:hadoop_net}
-\end{figure}
+\end{figure*}
 

### 2019-03-27 tii/tex/optimization.tex
Fix typo proposed by reviewer2.

--- 2019-03-27 jpdc/tex/optimization.tex
@@
 		\includegraphics[width=\linewidth]{fig/range_pre_sample}
-		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
+		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
 		\label{fig:range_pre_sample}
@@
 		\State Sift down $M\left[0\right]$ by $size$
-		\State $idx\gets idx-1$
+		\State $idx\gets idx+1$
 		\EndWhile
@@
 % \fi
-A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
+A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks. 
 The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 

### 2019-04-04 tii/tex/abstract.tex
Update intro & abstract.

--- 2019-03-26 jpdc/tex/abstract.tex
@@
-\begin{abstract}[S U M M A R Y]
+\begin{abstract}
 
@@
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
-{\color{blue}
-During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
-The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
-We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
-}
 By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node.
@@
 {\color{blue}
-We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce.
-The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
+We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
+The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
+% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
+}
+{\color{blue}
+We have implemented SCache on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
 Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.

### 2019-04-04 tii/tex/intro.tex
Update intro & abstract.

@@
-\begin{figure}
-	\centering
-	\includegraphics
-		[width=1\linewidth]
-		{fig/workflow}
-	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
-	\label{fig:workflow}
-\end{figure}
-
 \section{Introduction}\label{sec:introduction}
 Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
-Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
-Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
-Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
+{\color{blue}
+According to a MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
+The shuffle phase is crucial and heavily affecting the end-to-end application performance.
+Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
+Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
+}
 
@@
 However, the shuffle phase is often poorly optimized in practice.
+In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
 }
-% {\color{red}
-% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator},
-% the shuffle is often poorly optimized in practice.
-% }
-% take over shuffle
-%shuffle characteristic
-In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
 %In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
@@
 Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
-Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
+{\color{blue}
+Such task aggregation together with the coupled scheduling effectively simplifies task management.
+}
 However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
@@
 To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
-However, such early-start is by no means a panacea. 
-This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
-
+% However, such early-start is by no means a panacea. 
+% This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
+{\color{blue}
+However, such early-start has several deficiencise.
+First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
+Second, the early-start can not fully overlap the shuffle phases and the descendent stage.
+Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start.
+Last but not least, it is hard to find the optimal time to begin the early-start.
+If too early, the descendent stages are not ready to output enough intermediate data for the shuffle.
+If too late, the idle network resource is wasted.
+}
+\begin{figure}
+	\centering
+	\includegraphics
+		[width=1\linewidth]
+		{fig/workflow}
+	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
+	\label{fig:workflow}
+\end{figure}
 %In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.
@@
 
-{\color{blue}
-To analyze resources scheduling strategies as mentioned above, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
-The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
-We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it.
-The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
-According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
-Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
-By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
-% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
-% This situation will be amplified in shuffle-heavy tasks.
-}
-
 Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
@@
 First, SCache decouples the shuffle write and read from both map and reduce tasks.
-Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
+Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
 In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
@@
 % However, the memory is a precious resource for DAG computing. 
-To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
+To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{impl}).
 %The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.
@@
 % }
+{\color{blue}
+We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
+We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it.
+% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
+% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
+% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
+By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing. (Section \ref{model}).
+% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
+% This situation will be amplified in shuffle-heavy tasks.
+}
 
@@
 We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
-We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job.
+% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.

### 2019-04-26 tii/tex/abstract.tex
TII v1.0

@@
 
-In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead.
-Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
+% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
+% {\color{blue}
+In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies usually bring in large overhead.
+Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
@@
 % We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
-}
-{\color{blue}
 We have implemented SCache on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.

### 2019-04-26 tii/tex/evaluation.tex
Add x-­axis in util figures.
TII v1.0

--- 2019-03-26 jpdc/tex/evaluation.tex
@@
 \section{Evaluation}\label{evaluation}
+{\color{blue}
 This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
+To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and  Hadoop MapReduce. 
+First, we evaluate the Spark with SCache in 3 different benchmarks.
+We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
 Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-
-% \begin{figure}
-% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
-% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
-% 	\label{fig:scache_util}
-% \end{figure}
-
 In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-{\color{blue}
-To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
+% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
+Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
 }
 Finally, we measure the overhead of weighted reservoir sampling.
+
 In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
@@
 
-\subsection{Simple DAG Analysis}\label{simpledag}
+\subsection{Spark with SCache}\label{sparkscache}
+
+\subsubsection{Simple DAG Analysis}\label{simpledag}
 %\subsubsection{Hardware Utilization}
@@
 As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark. 
-% \begin{figure}
-% 	%\vspace*{-0.01cm}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbymapstage}
-% 		\caption{Map Stage Completion Time Comparison}
-% 		\label{fig:mapstage}
-% 	\end{subfigure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducestage}
-% 		\caption{Reduce Stage Completion Time Comparison}
-% 		\label{fig:reducestage}
-% 	\end{subfigure}
-% 	\caption{Stage Completion Time of Single Shuffle Test}
-% 	\label{fig:singleshuffle}
-% \end{figure}
-
-% \begin{figure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbymaptask}
-% 		\caption{Median Task Details in Map Stages}
-% 		\label{fig:maptask}
-% 	\end{subfigure}
-% 	\begin{subfigure}{\linewidth}
-% 		\centering
-% 		\includegraphics[width=0.6\linewidth]{fig/groupbyreducetask}
-% 		\caption{Median Task Details in Reduce Stages}
-% 		\label{fig:reducetask}
-% 	\end{subfigure}
-% 	\caption{Median Task Completion Time of Single Shuffle Test}
-% 	\label{fig:singleshuffletask}
-% \end{figure}
 The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
@@
 
-\subsection{Terasort}
-We also evaluate Terasort-a recognized shuffle intensive benchmark for distributed system analysis. 
+\subsubsection{Terasort}
+We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
 Terasort consists of two consecutive shuffles. 
@@
 
+\subsubsection{Production Workload}
+We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
+TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
+% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
+As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
+Note that we skip some queries due to the compatible issues. 
+Spark with SCache outperforms the original Spark in almost all tested queries. 
+Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
+It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
+The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
+Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
+
 {\color{blue}
@@
 }
-
-\subsection{Production Workload}
-We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
-TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
-TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
-% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
-As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
-Note that we skip some queries due to the compatible issues. 
-Spark with SCache outperforms the original Spark in almost all tested queries. 
-Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
-The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
-Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
 

### 2019-04-26 tii/tex/intro.tex
TII v1.0

@@
 \section{Introduction}\label{sec:introduction}
-Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
+\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
 {\color{blue}
+% \cite{ibmreport}.
+% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
+These data come from a variety of industry, e.g., e-commerce, telecommunications, media, retail customers and social networks.
+% \cite{chen2012interactive}.
+% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
+% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
+Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
+% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
+% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
+Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data \cite{lee2014service, lv2017next}. 
+This is because industrial big-data is generated by automated equipment.
+However, according to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing. 
+A small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
 According to a MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
 The shuffle phase is crucial and heavily affecting the end-to-end application performance.
-Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
+Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
 Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics
+		[width=1\linewidth]
+		{fig/workflow}
+	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
+	\label{fig:workflow}
+\end{figure}
 {\color{blue}
-Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive, zhang2018simpo, chen2013tiled}.
-However, the shuffle phase is often poorly optimized in practice.
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{basanta2018efficient, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
 In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
@@
 }
-\begin{figure}
-	\centering
-	\includegraphics
-		[width=1\linewidth]
-		{fig/workflow}
-	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
-	\label{fig:workflow}
-\end{figure}
+
 %In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.

### 2019-04-26 tii/tex/model.tex
Update intro & abstract.
TII v1.0

@@
 In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance.
-In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
+In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.
 
@@
 \centering
-\scalebox{0.91}{
+\scalebox{0.95}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 \centering
-\scalebox{0.9}{
+\scalebox{0.95}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 
-\subsection{Model Verification}\label{model_verification}
-To verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
+\subsection{Model evaluation}\label{model_evaluation}
+To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
 (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
@@
 
-In order to verify the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
@@
 }
+
+\begin{figure}
+	\includegraphics[width=.8\linewidth]{fig/scache_util}
+	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
+	\label{fig:scache_util}
+\end{figure}

### 2019-04-26 tii/tex/motivation.tex
Add x-­axis in util figures.
TII v1.0

--- 2019-01-03 taco/tex/motivation.tex
@@
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{0.47\linewidth}
+\begin{figure}
 	\includegraphics[width=\linewidth]{fig/util}
-		\caption{Original Spark}
+	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
 	\label{fig:util}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/scache_util}
-		\caption{Spark With SCache}
-		\label{fig:scache_util}
-	\end{subfigure}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
-\end{figure*}
+	\vspace{-1em}
+\end{figure}
 
@@
 \subsubsection{Multi-round Tasks Execution}\label{multi}
-Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
+Both experience and DAG framework manuals (e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
 For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 

### 2019-04-28 tii/tex/evaluation.tex
TII v2.0

@@
 
-In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
+Overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
 
@@
 Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
+It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
 The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
@@
         \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
-        \caption{\color{blue}Hadoop MapReduce Terasort completion time}
+        \caption{\color{blue}Hadoop MapReduce Terasort Completion Time}
 		\label{fig:hadoop_terasort_time}

### 2019-04-28 tii/tex/impl.tex
TII v2.0

--- 2019-03-26 jpdc/tex/impl.tex
@@
 {\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{blue} original scheduler in framework}.
+ {\color{blue} the original scheduler in framework}.
 
@@
 In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
-After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
+After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
 }
@@
 For the sample number, it can be tuned to balance the overhead and accuracy. 
-The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). 
+The sampling job randomly selects some items and performs a local shuffle with the partitioner (see Figure \ref{fig:sample}). 
 At the same time, the items number is counted as the weight. 
@@
 At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
-If all the units are completed, SCache selects victims based on two factors-\textit{inter-shuffle} and \textit{intra-shuffle}.
+If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
 \begin{itemize}[noitemsep]
@@
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
-We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
+We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
 }
 
-\subsection{Fault tolerance}\label{fault}
+\subsection{Discussion of Fault Tolerance}\label{fault}
 Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
 We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
-If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of the DAG computing.
+If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
 A possible way to handle this failure is selecting some backup nodes to store replications. 
 But the replications can introduce a significant network overhead \cite{availability}.  
-Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
+Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
 We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 

### 2019-04-28 tii/tex/intro.tex
TII v2.0

@@
 % These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
-These data come from a variety of industry, e.g., e-commerce, telecommunications, media, retail customers and social networks.
+These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
 % \cite{chen2012interactive}.
@@
 {\color{blue}
-However, such early-start has several deficiencise.
+However, such early-start has several deficiencies.
 First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.

### 2019-04-28 tii/tex/model.tex
TII v2.0

@@
 According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
-Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
+Therefore, the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
 We will first introduce the FRQ model in Subsection \ref{model_overview}.
@@
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed computing frameworks mostly use DAGs to describe computation logic. 
+The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
 A shuffle phase is required between each adjacent DAG computation phases.
@@
 \(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
-We use \(T_{P\_Shuffle}\) to represent the overlap time between shuffle phase and reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
+We use \(T_{P\_Shuffle}\) to represent the overlap time between the shuffle phase and the reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
 The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
@@
 Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
-We intuitively think that we can also overlap shuffle phase one and map phases.
+We intuitively think that we can also overlap the shuffle phase and the map phases.
 We implemented this idea with SCache.
@@
 \begin{enumerate}
-    \item 
-    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
+    \item \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1})
+
 	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
@@
 
-    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
+    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2})
+
 	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated.
@@
 \subsection{Model evaluation}\label{model_evaluation}
-To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
-(b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
+To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
 To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework.
@@
 \begin{figure}
-	\includegraphics[width=.8\linewidth]{fig/scache_util}
+	\includegraphics[width=\linewidth]{fig/scache_util}
 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}

### 2019-04-29 tii/tex/conclusion.tex
TII v2.0
TII commit

@@
 {\color{blue}
-Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
+% Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
+The benchmark using in evaluations covers the most situations of industrial big-data analysis.
+The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
 Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks.
-At last, we evaluate the SCache shuffle optimization by this practical model.
-Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to adapt. 
+At last, we evaluate the SCache shuffle optimization by the FRQ model.
+% Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 
 }

### 2019-04-29 tii/tex/intro.tex
TII commit

@@
 {\color{blue}
+In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
+During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
+Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
 % \cite{ibmreport}.
 % These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
-These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
+% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
 % \cite{chen2012interactive}.
@@
 % Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
-Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data \cite{lee2014service, lv2017next}. 
-This is because industrial big-data is generated by automated equipment.
-However, according to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing. 
-A small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
-According to a MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
+Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
+}
+
+{\color{blue}
+According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size.
+According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
 The shuffle phase is crucial and heavily affecting the end-to-end application performance.
@@
 {\color{blue}
-Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{basanta2018efficient, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
 In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
@@
 % Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
-By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing. (Section \ref{model}).
+% By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing (Section \ref{model}).
+In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
 % I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 

### 2019-04-29 tii/coverletter/coverletter.tex
Submit version 1.0

--- 2019-01-04 taco/coverletter/coverletter.tex
@@
 
-\author{Rui Ren}
-\author{Chunghsuan Wu}
-\author{Zhouwang Fu}
-\author{Tao Song}
-\author{Zhengwei Qi}
-\author{Haibing Guan}
+% \author{Rui Ren}
+% \author{Chunghsuan Wu}
+% \author{Zhouwang Fu}
+% \author{Tao Song}
+% \author{Yanqiang Liu}
+% \author{Zhengwei Qi}
+% \author{Haibing Guan}
 
@@
 This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
+% In the manuscript we uploaded, we highlight the new content in blue.
+% We believe that shuffle-heavy jobs are also existed widely in industrial big-data analysis.
+% SCache can also provide considerable optimization in industrial big-data.
+In this paper, we combine the characteristic of the industrial big-data and DAG computing frameworks.
+We provide a new data processing solution for the industrial big-data based on our conference paper.
+Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big-data analysis.
 This paper makes the following distinct contributions compared with the conference paper.
@@
 Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
-In this paper, we use the model to analyze the deficiencies of the resources scheduling strategies and then optimize them.
+In this paper, we use the model to evaluate the deficiencies of different resources scheduling strategies and then optimize them.
 \item 
 In the conference paper, we only implement SCache on Spark. 
-In this paper, we implement SCache on Hadoop MapReduce. 
-By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
-Meanwhile, our experiments are also consistent with the analysis of the model.
-This result demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
+In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big-data analysis.
+% By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 
+% Meanwhile, our experiments are also consistent with the analysis of the model.
+This result also demonstrates the compatibility and adaptability of SCache as a cross-framework plug-in.
 % To demonstrate the compatibility and adaptability of SCache as a cross-framework plug-in, we also extended SCache on Hadoop MapReduce. 
@@
 % Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
-In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
-We believe that the added content makes a sufficient contribution to this journal submission.
+In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
+We believe that the added content makes a sufficient contribution to this special issue.
+% We believe that the added content makes a sufficient contribution to this journal submission.
 

### 2019-04-29 tii/tex/abstract.tex
Submit version 1.0

@@
 % In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
-% {\color{blue}
-In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies usually bring in large overhead.
+% {\color{black}
+In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
 Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
@@
 % }
-{\color{blue}
+{\color{black}
 We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 

### 2019-04-29 tii/tex/evaluation.tex
Submit version 1.0

@@
 \section{Evaluation}\label{evaluation}
-{\color{blue}
-This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and  Hadoop MapReduce. 
+{\color{black}
+This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
+% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
+We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
 First, we evaluate the Spark with SCache in 3 different benchmarks.
@@
 Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
 % To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
@@
 	\centering
-	\begin{subfigure}{.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-		\caption{\color{blue}Hadoop MapReduce with SCache}
-		\label{fig:hadoop_terasort_scache}
-	\end{subfigure}
-	\begin{subfigure}{.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-		\caption{\color{blue}Hadoop MapReduce without SCache}
-		\label{fig:hadoop_terasort_origin}
-	\end{subfigure}
-	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
-	\label{fig:hadoop_terasort}
-\end{figure*}
-\begin{figure*}
-	\centering
 	\includegraphics[width=.9\textwidth]{fig/tpcds}
@@
 
-\subsubsection{Production Workload}
+\subsubsection{Industrial Production Workload}
 We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
@@
 
-{\color{blue}
+\begin{figure*}
+	\centering
+	\begin{subfigure}{.47\linewidth}
+		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
+		\caption{\color{black}Hadoop MapReduce with SCache}
+		\label{fig:hadoop_terasort_scache}
+	\end{subfigure}
+	\begin{subfigure}{.47\linewidth}
+		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
+		\caption{\color{black}Hadoop MapReduce without SCache}
+		\label{fig:hadoop_terasort_origin}
+	\end{subfigure}
+	\caption{\color{black}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
+	\label{fig:hadoop_terasort}
+\end{figure*}
+
+{\color{black}
 \subsection{Hadoop MapReduce with SCache}
@@
         \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
-        \caption{\color{blue}Hadoop MapReduce Terasort Completion Time}
+        \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
 		\label{fig:hadoop_terasort_time}

### 2019-04-29 tii/tex/impl.tex
Submit version 1.0

@@
 The daemon bridges the communication between %{\color{red}Spark}
-{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{blue} the original scheduler in framework}.
+{\color{black} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
+ {\color{black} the original scheduler in framework}.
 
-% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
+% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{black} worker daemon}.
 As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
@@
 % }
-{\color{blue}
+{\color{black}
 When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
@@
 
-When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
+When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{black}framework worker} through memory copy.
 After that, the slot will be released (without being blocked on disk operations).
@@
 % }
-{\color{blue}
+{\color{black}
 In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
@@
 		\includegraphics[width=\linewidth]{fig/architecture}
-		\caption{\color{blue}SCache Architecture}
+		\caption{\color{black}SCache Architecture}
 		\label{fig:architecture}

### 2019-04-29 tii/tex/intro.tex
Submit version 1.0

@@
 \IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
-{\color{blue}
+{\color{black}
 In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
@@
 
-{\color{blue}
+{\color{black}
 According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size.
@@
 \end{figure}
-{\color{blue}
+{\color{black}
 Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
@@
 Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
-{\color{blue}
+{\color{black}
 Such task aggregation together with the coupled scheduling effectively simplifies task management.
@@
 % This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
-{\color{blue}
+{\color{black}
 However, such early-start has several deficiencies.
@@
 % }
-{\color{blue}
+{\color{black}
 We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
@@
 
-{\color{blue}
+{\color{black}
 We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 

### 2019-04-29 tii/tex/model.tex
Submit version 1.0

@@
 The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
-According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
-Therefore, the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
+In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
+The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
 We will first introduce the FRQ model in Subsection \ref{model_overview}.
@@
 		\includegraphics[width=\linewidth]{fig/model_original}
-		\caption{\color{blue}Full Serial MapReduce}
+		\caption{\color{black}Full Serial MapReduce}
 		\label{fig:model_original}
@@
 		\includegraphics[width=\linewidth]{fig/model_hadoop}
-		\caption{\color{blue}Half Parallel MapReduce}
+		\caption{\color{black}Half Parallel MapReduce}
 		\label{fig:model_hadoop}
 	\end{subfigure}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
+	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
 	\label{fig:model_strategies}
@@
 		\includegraphics[width=\linewidth]{fig/model_scache1}
-		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 		\label{fig:model_scache1}
@@
 		\includegraphics[width=\linewidth]{fig/model_scache2}
-		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
+		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
 		\label{fig:model_scache2}
 	\end{subfigure}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
+	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
 	\label{fig:model_scache}
@@
 \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
 \label{table1}
@@
 \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
 \label{table2}
@@
 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
-		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
 		\label{fig:hadoop_net1}
@@
 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
-		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
+		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
 		\label{fig:hadoop_net2}
 	\end{subfigure}
-	\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
+	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
 	\label{fig:hadoop_net}

### 2019-04-29 tii/tex/optimization.tex
Submit version 1.0

@@
 %To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
-\subsection{Pre-schedule with Application Context}
+\subsection{Pre-scheduling with Application Context}
 The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
@@
 On the other hand, the result of linear regression comes out with a large relative error. 
-Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
 We will show the overhead evaluation of sampling in Section \ref{evaluation}.
-% {\color{blue}
+% {\color{black}
 % Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
@@
 But ignoring the data locality can introduce extra network transfer. 
-In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap scheduling algorithm (Algorithm \ref{hminheap}).
+In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
 

### 2019-05-01 tii/tex/optimization.tex
Submit version v1.1

@@
 % The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
-In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
-The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
-Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
-On the other hand, the result of linear regression comes out with a large relative error. 
-Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
+% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
+% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
+% On the other hand, the result of linear regression comes out with a large relative error. 
+% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
+% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
+% {\color{black}
+Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
 We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
-% {\color{black}
-% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
-% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
 % }

### 2019-05-07 tii/tex/evaluation.tex
Reduce the number of ref to 30

@@
 \subsubsection{Terasort}
-We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
+We also evaluate Terasort\footnote{http://sortbenchmark.org/YahooHadoop.pdf} --- a recognized shuffle intensive benchmark for distributed system analysis. 
 Terasort consists of two consecutive shuffles. 

### 2019-05-07 tii/tex/impl.tex
Reduce the number of ref to 30

@@
 {\color{black} worker daemon.
-As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system.
+As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system.
 The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
@@
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
-We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
+We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez, are also low.
 }
@@
 Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
-We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
+We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
 If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
 A possible way to handle this failure is selecting some backup nodes to store replications. 
-But the replications can introduce a significant network overhead \cite{availability}.  
+% But the replications can introduce a significant network overhead \cite{availability}.  
 Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 

### 2019-05-07 tii/tex/intro.tex
Reduce the number of ref to 30

@@
 % Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
-Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
+Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
 % The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
@@
 The shuffle phase is crucial and heavily affecting the end-to-end application performance.
-Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
+Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad}, and Tez\footnote{https://tez.apache.org/}, etc.
 Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
@@
 {\color{black}
-Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
 In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
@@
 {\color{black}
-We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
+We have implemented SCache on both Spark and Hadoop MapReduce. 
 % We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 

### 2019-05-07 tii/tex/motivation.tex
Reduce the number of ref to 30

@@
 
-\textbf{Overview of shuffle process}. 
+% \textbf{Overview of shuffle process}
+
+\subsubsection{Overview of shuffle process}
 Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
@@
 %In short, shuffle is loosely coupled with application context and it's I/O intensive.
-\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduce a significant latency to the application. 
+% \textbf{Impact of shuffle process}
+
+\subsubsection{Impact of shuffle process}
+Shuffle is I/O intensive, which might introduce a significant latency to the application. 
 Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
@@
 The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
-Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
+Unfortunately this defect exists not only in Spark but also Hadoop MapReduce and Tez. 
 A finer granularity resource allocation scheme should be provided to reduce these delays.
@@
 	\includegraphics[width=\linewidth]{fig/util}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
+	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
 	\label{fig:util}
@@
 The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
-On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
-but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
+On the other hand, memory based distributed storage systems have been proposed \cite{tachyon, ramcloud} to move data back to memory, 
+but most of the DAG frameworks still store shuffle data on disks (e.g., Spark, Hadoop MapReduce, Dryad \cite{dryad}, etc).
 We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

### 2019-05-07 tii/tex/optimization.tex
Reduce the number of ref to 30

@@
 Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
-This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
+This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
 Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
@@
 For the most DAG applications with random large scale input, 
-the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}:
+the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
 \begin{equation}
@@
 For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
-and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
+and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
 Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 

### 2019-05-08 tii/tex/motivation.tex
Shorten motivation

@@
 \subsubsection{Impact of shuffle process}
+{\color{blue}
 Shuffle is I/O intensive, which might introduce a significant latency to the application. 
 Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
-For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
-For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
-% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
-% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.
+For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time.
+% For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
+% For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
+}
 
@@
 \subsubsection{Coarse Granularity Resource Allocation}
-When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
-On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
-Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
+{\color{blue}
+As shown in Figure \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
+Both \textit{shuffle write} and \textit{shuffle read} occupy the slot without significantly involving CPU.
 The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization.
-Unfortunately this defect exists not only in Spark but also Hadoop MapReduce and Tez. 
-A finer granularity resource allocation scheme should be provided to reduce these delays.
+
+% {\color{red}
+% When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
+% On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
+% Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
+% The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
+% Unfortunately this defect exists not only in Spark but also Hadoop MapReduce and Tez. 
+% A finer granularity resource allocation scheme should be provided to reduce these delays. 
+% }
 
 \subsubsection{Synchronized Shuffle Read}
-Almost all reduce tasks start shuffle read simultaneously. 
-The synchronized shuffle read requests cause a burst of network traffic. 
-As shown in Figure \ref{fig:util}, 
-the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
-It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
+
+The synchronized shuffle read requests cause several bursts of network traffic, which may result in network congestion and further slow down the network transfer.
+
+% {\color{red}
+% Almost all reduce tasks start shuffle read simultaneously. 
+% The synchronized shuffle read requests cause a burst of network traffic. 
+% As shown in Figure \ref{fig:util}, 
+% the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
+% It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
+% }
+
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
@@
 \subsubsection{Inefficient Persistent Storage Operation}
-At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
-This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
-Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
-Compared to input dataset, the size of shuffle data is relatively small. 
-For example, the shuffle size of Spark Terasort is less than $25\%$ of input data. 
-The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
-On the other hand, memory based distributed storage systems have been proposed \cite{tachyon, ramcloud} to move data back to memory, 
-but most of the DAG frameworks still store shuffle data on disks (e.g., Spark, Hadoop MapReduce, Dryad \cite{dryad}, etc).
-We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.
+Both shuffle write and shuffle read are tightly coupled with task execution, which results in a blocking I/O operation.
+This blocking I/O operation may introduce significant latency, especially in an I/O performance bounded cluster.
+Besides, most of the DAG frameworks store shuffle data on disks (e.g., Spark, Hadoop MapReduce, Dryad, etc).
+We argue that the memory capacity is large enough to store the short-living shuffle data during shuffle phases since several memory-based distributed storage systems have been proposed \cite{tachyon, ramcloud}.
+
+% At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
+% This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
+% Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
+% Compared to input dataset, the size of shuffle data is relatively small. 
+% For example, the shuffle size of Spark Terasort is less than $25\%$ of input data. 
+% The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
+% On the other hand, memory based distributed storage systems have been proposed \cite{tachyon, ramcloud} to move data back to memory, 
+% but most of the DAG frameworks still store shuffle data on disks (e.g., Spark, Hadoop MapReduce, Dryad \cite{dryad}, etc).
+% We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.
 
 \subsubsection{Multi-round Tasks Execution}\label{multi}
-Both experience and DAG framework manuals (e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
-For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
-% For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.
-% Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
-Since the shuffle data becomes available as soon as the end of a task's execution, 
-and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
-the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
-% optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
-% There are at least two persistent storage operations for each shuffle data block.
-At first, Spark will write shuffle data to the persistent storage after map task execution (i.e.
-\textit{shuffle write} in Figure \ref{fig:util}).
-During the \textit{shuffle read}, Spark will read shuffle data from remote and local persistent storage, which is the second operation.
-The persistence of shuffle data was designed for fault tolerance.
-But we believe it is not necessary for today's cluster.
-Recall that shuffle data only exist in a short time scale.
-But the Mean Time To Failure (MTTF) for a server is counted in the scale of year \cite{tachyon}, which is exponential compared with the duration of a shuffle.
-In addition, the capacity of memory and network has been increasing rapidly in recent years.
-As a result, numbers of memory based distributed storage system have been proposed \cite{memcached, tachyon, ramcloud}.
-On the other hand, the size of shuffle data is relatively small.
-For example, shuffle size of Spark Terasort \cite{spark-tera} is less than 25\% of input data.
-The data reported in  \cite{makingsense} also shows that the amount of data shuffled is less than input data, by as much as 10\%-20\%.
-We argue that removing persistent storage and using memory to achieve shuffle fault tolerance is feasible and efficient.
-
-% Based on these observations, most of the DAG frameworks share the execution paradigm as well as the expense of shuffle process. 
-To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce stage to overlap the I/O operations in multi-round map tasks, and uses memory to store the shuffle data.
-To achieve this optimization:
-\begin{itemize}
-	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
-	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
-	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
-\end{itemize}
+Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
+Since the shuffle data becomes available when map tasks complete, 
+and the network is idle during the map stage (\textit{Network TX} during map stage in Figure \ref{fig:util}), 
+we propose an optimization that starts \textit{shuffle read} ahead of reduce stage to overlap the I/O operations in multi-round map tasks. 
+% To achieve this optimization:
+% \begin{itemize}
+% 	\item Shuffle process should be decoupled from task execution to achieve a fine granularity scheduling scheme.
+% 	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
+% 	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
+% \end{itemize}
 % In the following section, we elaborate the methodologies to achieve three design goals.
+}

### 2019-05-08 tii/tex/intro.tex
Shorten spark

@@
 }
-%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
 As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
@@
 Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
-{\color{black}
 Such task aggregation together with the coupled scheduling effectively simplifies task management.
-}
 However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
-%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.
 
@@
 To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
-% However, such early-start is by no means a panacea. 
-% This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
 {\color{black}
-However, such early-start has several deficiencies.
-First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
-Second, the early-start can not fully overlap the shuffle phases and the descendent stage.
+However, such early-start is by no means a panacea.
+This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
+% However, such early-start has several deficiencies.
+% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
+% Second, the early-start can not fully overlap the shuffle phases and the descendent stage.
 Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start.
-Last but not least, it is hard to find the optimal time to begin the early-start.
+% Last but not least, it is hard to find the optimal time to begin the early-start.
 If too early, the descendent stages are not ready to output enough intermediate data for the shuffle.
@@
 
-%In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.
-
-%For example, Apache Hadoop \cite{hadoop} provides an \emph{early start} mechanism that launches reduce tasks after a certain portion (5\% by default) of map tasks has completed, which is adopted in many of the recent works \cite{ihadoop, ishuffle, dynmr}.
-% DAG computing framworks deriving from MapReduce \cite{mapreduce} contains a hard barrier between computing stages.
-The terminology of this barrier is \textit{shuffle}.
-Shuffle contains two parts on the connecting stages -- \textit{shuffle write} and \textit{shuffle read}.
-On the side of ancestor stages, \textit{shuffle write} is resoponsible for writing intermediate results to disk.
-On the side of descendant stage, \textit{shuffle read} fetches intermediate results from remote disks through network.
-Although highly optimized in other factors, the shuffle of framework is still primitive.
-The coarse design of shuffle introduce a significiant performance overhead.
-% % design inconsistent
-% For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for 33\% JCT on average, up to 70\% in shuffle-heavy jobs \cite{managing}.
-% shuffle operations
-% three resource coordinate 不好
-% 计算和I/O couple, why
-% why disk, reason!!!, 不重视
-% common problems
-
-We note that the above deficiencies generally exist in most of the DAG computing frameworks. 
-As a result, even though we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.
-
-% The main defect of current shuffle design is coarse granularity of resource allocation during the task scheduling.
-% Nearly all task scheduling algorithms in DAG frameworks use time slotted model.
-Specifically, when a task is launched, the framework offers it a bundle of resources (i.e.
-CPU and memory), which are dedicated to this task during the time in its "slot".
-% But for a task, the resources demand changes during different phases. The computing phase is CPU and memory intensive. The shuffle, instead, is I/O intensive.
-% As shown in the upper part of Figure \ref{fig:workflow}, this "slot" can be released until the map tasks finish \textit{shuffle write} on disk.
-And the "slot" is occupied when the reduce tasks begin to read shuffle data from remote nodes through network, which is presented as \textit{shuffle read}.
-This inconsistency between demands and allocation results in a severe resource underutilization, which slow down the framework.
-
-% Another drawback of current shuffle is the synchronized shuffle read.
-When all the reduce tasks are scheduled, the shuffle fetch of each task starts almost simultaneously, which may cause congestion of network and delay the shuffle read.
-The straight forward way to avoid network burst is to start reduce tasks earlier.
-Apache Hadoop \cite{hadoop} provides a mechanism that schedules reduce tasks when a certain portion of map tasks completed.
-So that the shuffle delay can be mitigated.
-Other publications also purpose solutions to pre-schedule reduce tasks \cite{ihadoop, ishuffle, dynmr}.
-However this early scheduling of reduce tasks occupies new task slots, which degrades system performance.
-To this end, we proposed a question for this cross-frameworks issue, \textit{can we efficiently optimize shuffle without manually change every DAG framework?}
-
-% 针对性的提出这三个点
-% three resource coordinate 不好
-% 计算和I/O couple, why
-% why disk, reason, 不重视
-% common problems
-% 总起：普适性工具
-% pre-fetch but not pre-execute
-% byproduct: more balance
-% memory instead of disk
-
-% challenge point by point, inside the problem
+% We note that the above deficiencies generally exist in most of the DAG computing frameworks. 
+% As a result, even though we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.
 
@@
 Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
-In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
+In addition, SCache pre-schedules the reduce tasks without launching them and pre-fetches the shuffle data. 
 % for the reduce tasks.
@@
 and avoid the extra early allocation of slots.
-%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks.
-SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks.
-In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch.
-In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.
 
@@
 The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks without launching}. 
-% It is not critical for the simple DAG computing such as Hadoop MapReduce \cite{mapreduce}. 
 First, the complexity of DAG can amplify the defects of na\"{i}ve scheduling schemes. 
@@
 To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
-% However, the memory is a precious resource for DAG computing. 
 To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{impl}).
-%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.
 
-% {\color{red}
-% We have implemented SCache and a customized Apache Spark \cite{apachespark}.
-The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
-We conduct basic test GroupByTest.
-We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling.
-In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios.
-More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
-% }
 {\color{black}
@@
 We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it.
-% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
-% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
-% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
-% By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing (Section \ref{model}).
 In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
-% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
-% This situation will be amplified in shuffle-heavy tasks.
 }
@@
 We have implemented SCache on both Spark and Hadoop MapReduce. 
-% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
 The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.

### 2019-05-08 tii/tex/optimization.tex
Shorten opt

@@
 	\end{minipage}
-	\begin{minipage}{0.49\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{fig/shuffle} % first figure itself
-		\caption{Shuffle Data Prediction}
-		\label{fig:shuffle}
-    \end{minipage}\hfill
+	% \begin{minipage}{0.49\textwidth}
+    %     \centering
+    %     \includegraphics[width=0.9\textwidth]{fig/shuffle} % first figure itself
+	% 	\caption{Shuffle Data Prediction}
+	% 	\label{fig:shuffle}
+    % \end{minipage}\hfill
 \end{figure}
@@
 \subsection{Decouple Shuffle from Execution}
-% \ifrevision
-% \reversemarginpar
-% \marginpar{B1,C2}
-% \fi
 To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
-% During shuffle write of map tasks, the partitioned shuffle data blocks will be written on the disks.
-% Each block contains a part of input data of a particular reduce task. 
 To prevent the release of a slot being blocked by shuffle write,  
@@
 the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
-% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
-%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
+
 \subsection{Pre-scheduling with Application Context}
@@
 The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
-Once the tasks are scheduled, the slots will be occupied to launch them. 
-On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
+% Once the tasks are scheduled, the slots will be occupied to launch them. 
+And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
 We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
 That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.
-% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}.
-We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time.
-Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes.
-The result is shown in \ref{fig:sim}.
-% \begin{figure*}
-% 	\centering
-% 	\begin{minipage}{0.34\linewidth}
-% 		\begin{figure}[H]
-% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
-% 			\caption{Shuffle Size Comparing with Input Size}
-% 			\label{fig:shuffle_size}
-% 		\end{figure}
-% 	\end{minipage}
-% 	\begin{minipage}{0.65\linewidth}
-% 		\begin{figure}[H]
-% 			\begin{subfigure}{0.5\textwidth}
-% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
-% 				\caption{Shuffle Time Fraction CDF}
-% 				\label{fig:cdf}
-% 			\end{subfigure}	
-% 			\begin{subfigure}{0.5\textwidth}
-% 				\includegraphics[width=\linewidth]{fig/sim}
-% 				\caption{Stage Completion Time Improvement}
-% 				\label{fig:sim}
-% 			\end{subfigure}	
-% 			\caption{Emulate Result of OpenCloud Trace}
-% 		\end{figure}
-% 	\end{minipage}
-% \end{figure*}
-% \begin{figure}
+
 \subsubsection{Problem of Random Mapping}\label{randomassign}
@@
 In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
 The average shuffle read time is $3.2\%$ of total reduce completion time.
-
 As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
@@
 \subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
-% \ifrevision
-% \marginpar{B2,E7}
-% \fi
+{\color{blue}
 The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
-Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
-where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
-$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}). 
-The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
-So the pre-scheduling can be made if the "prediction" of size of shuffle block is practical.
-% \hlyellow{
-% The shuffle size of each reduce task is decided by input data, map task computation, and hash partitioner. 
-% Each map task produces a data block for each reduce task. 
-% }
-% The size of each reduce partition can be calculated $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$ ($m$ is the number of map tasks). 
-% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}).
-% \ifrevision
-% \reversemarginpar
-% \marginpar{B2,D6,D8}
-% \fi
-
 For the most DAG applications with random large scale input, 
-the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
-\begin{equation}
-\label{linearregresion}
-\begin{aligned}
-	BlockSize_{ji} = a \times inputSize_j + b
-\end{aligned}
-\end{equation}
-The $inputSize_j$ is the input size of $j$th map task. 
-The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
+the shuffle data size can be predicted accurately by a liner regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.
+% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
+% where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
+% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$. 
+% The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
+% So the pre-scheduling can be made if the prediction of size of shuffle block is practical.
+% For the most DAG applications with random large scale input, 
+% the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
+% \begin{equation}
+% \label{linearregresion}
+% \begin{aligned}
+% 	BlockSize_{ji} = a \times inputSize_j + b
+% \end{aligned}
+% \end{equation}
+% The $inputSize_j$ is the input size of $j$th map task. 
+% The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
 
@@
 \end{figure*}
-
-Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark \cite{apachespark}.  
-For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
-We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
-The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
-% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
-% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
-The observed map outputs are randomly picked. 
-With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
-The prediction results also fit them well. 
-However, the data partitioned by Spark RangePartitioner \cite{apachespark} in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
-That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
-The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
-
-% Several map outputs (marked as Map Output in Figure \ref{fig:shuffle}) are picked as observation objects to train the model and than predict the final reduce distribution.
-% \ifrevision
-% \reversemarginpar
-% \marginpar{D6,E3}
-% \fi
 
@@
 
-To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
+% Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark.  
+However, the linear regression model can fail in some uncertainties introduced by sophisticated frameworks like Spark. 
+For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
+We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
+% The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
+% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
+% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
+% The observed map outputs are randomly picked. 
+With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
+The prediction results also fit them well. 
+However, the data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
+% That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
+% The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
+
+To handle this corner case, we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
 Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
 For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
-After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
+After that, the map function is called locally to process the sampled data. 
 Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
+The $inputSize_j$ is the input size of $j$th map task. 
 Note that sampling does not consume the input data of map tasks. 
-The $BlockSize_{ji}$ can be calculated by:
-\begin{equation}
-\label{equationsample}
-\begin{aligned}
-	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
-	sample_i &= \text{number of samples for $reduce_i$}
-\end{aligned}
-\end{equation}
+% The $BlockSize_{ji}$ can be calculated by:
+% \begin{equation}
+% \label{equationsample}
+% \begin{aligned}
+% 	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
+% 	sample_i &= \text{number of samples for $reduce_i$}
+% \end{aligned}
+% \end{equation}
 % The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
@@
 % {\color{black}
+
 Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
@@
 
-During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
-\begin{equation}
-\label{equationprob}
-\begin{aligned}
-	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
-    m &= \text{number of map tasks}
-\end{aligned}
-\end{equation}
-This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
+% During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
+% \begin{equation}
+% \label{equationprob}
+% \begin{aligned}
+% 	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
+%     m &= \text{number of map tasks}
+% \end{aligned}
+% \end{equation}
+% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling. 
+}
 
 \subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
-
-% \ifrevision
-% \marginpar{\tiny PC2,C1,D7/9,E4}
-% \fi
-As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
-But ignoring the data locality can introduce extra network transfer. 
-In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
-
-For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
-and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
-Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
+% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
+% But ignoring the data locality can introduce extra network transfer. 
+% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
+{\color{blue}
+To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
+For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+}
+Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
 After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
 The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
-% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
 Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
-% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
 Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
@@
 \subsubsection{Cope with Multiple Shuffle Dependencies}
-% \ifrevision
-% \marginpar{E5}
-% \fi
+{\color{blue}
 A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
-The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-For those pending shuffles, it is impossible to predict their sizes. 
-This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-But doing this introduces large overhead such as extra task serialization. 
-To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.
-
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \emph{shuffles} scheduled by Heuristic MinHeap are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \emph{shuffles}. 
+To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
+}
+% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+% For those pending shuffles, it is impossible to predict their sizes. 
+% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+% But doing this introduces large overhead such as extra task serialization. 
+% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
 After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
@@
 	\small
-	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
+	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\textit{shuffles}}$}
 		\State $m\gets$ partition number of map tasks
-		\Comment \emph{shuffles} are the previous schedule result 
+		\Comment \textit{shuffles} are the previous schedule result 
 		\ForAll{$r$ in $p\_reduces$}
-			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
-			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
+			\State $r.size \mathrel{+}= \text{\textit{shuffles}}\left[r.rid\right].size$
+			\State $new\_prob\gets \text{\textit{shuffles}}\left[r.rid\right].size / r.size$
 			\If{$new\_prob\geq r.prob$}
 				\State $r.prob\gets new\_prob$
-				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
+				\State $r.host\_id\gets \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$
 			\EndIf
@@
 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
-				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
+				\If{$host\neq \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$}
 				\State Re-shuffle data to $host$
-				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
+				\State $\text{\textit{shuffles}}\left[r.rid\right].assigned\_host\gets host$
 				\EndIf

### 2019-05-09 tii/tex/impl.tex
Shorten impl

@@
 This section presents an overview of the implementation of SCache. 
-% {\color{red}
-% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
-% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
-% }
 {\color{black}
@@
 The following \ref{memorymanage} subsection focuses on two constraints on memory management.
-In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
-At last, we discuss the cost of adapting SCache and fault tolerance. 
+% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
+% At last, we discuss the cost of adapting SCache and fault tolerance. 
 }
@@
 \subsection{System Overview}\label{arch}
-SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
-{\color{black} worker daemon.
-As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system.
+SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.
+As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system. 
 The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
 The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-The daemon bridges the communication between %{\color{red}Spark}
-{\color{black} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{black} the original scheduler in framework}.
-
-% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{black} worker daemon}.
-As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
-
-% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-% The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-% The daemon bridges the communication between {\color{black}DAG framework} and SCache.
-The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{black} original scheduler in framework master}.
-
-% {\color{red}
-% When a Spark job starts, the DAG will be first generated. 
-% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
-% }
-{\color{black}
+The daemon bridges the communication between DAG framework and SCache.
+The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.
 When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
 Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
-}
 For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
@@
 We will elaborate the sampling procedure in the Section \ref{sampling}.
-% \begin{minipage}{\columnwidth}
-% \begin{algorithm}[H]
-% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
-% \label{hminheap}
-% 	\begin{algorithmic}[1]
-% 	\small
-% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
-% 		\State $m\gets$ partition number of map tasks
-% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
-% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
-% 		\State $idx\gets$ len$\left(R\right) - 1$
-% 		\While{$idx \geq 0$}
-% 		\Comment{Schedule reduces by MinHeap}
-% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
-% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
-% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
-% 		\State Sift down $M\left[0\right]$ by $size$
-% 		\State $idx\gets idx-1$
-% 		\EndWhile
-% 		\State $max\gets$ maximum size in $M$
-% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
-% 		\ForAll{$reduce$ in $R$}
-% 		\Comment{Heuristic swap by locality}
-% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
-% 				\State $p\gets reduce.prob$
-% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
-% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
-% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
-% 			\EndIf
-% 		\EndFor
-% 		% \Comment{$m$ is the number of input data}
-% 		% \Comment{$r$ is partition number of reduces}
-% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
-% 		% \Comment{$c$ is $r*m$ array of composition data}
-% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
-% 		\Return $M$
-% 	\EndProcedure
-% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
-% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
-% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
-% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
-% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
-% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
-% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
-% 			\qquad \; $size\_assigned\leq upper\_bound$}
-% 			\State Swap $candidates$ and $reduce$
-% 			\State Update $size$ in $M$
-% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
-% 		\EndIf
-% 	\EndProcedure
-% 	\end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
 
+{\color{blue}
 When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{black}framework worker} through memory copy.
 After that, the slot will be released (without being blocked on disk operations).
-When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
+When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
 If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
-% After that, when a map task is finished, each node will receive a broadcast message. 
-SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
-% {\color{red}
-% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
-% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
-% }
-{\color{black}
-In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
-After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
+To enforce the DAG framework to run according to the SCache pre-scheduled results, we also insert some lines of codes in framework scheduler.
+% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
 }
-% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
-% \begin{minipage}{\columnwidth}
-% \begin{algorithm}[H]
-% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
-% \label{mhminheap}
-% 	\begin{algorithmic}[1]
-% 	\small
-% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
-% 		\State $m\gets$ partition number of map tasks
-% 		\Comment $shuffles$ is the previous schedule result 
-% 		\ForAll{$r$ in $p\_reduces$}
-% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
-% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
-% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
-% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
-% 			\EndIf
-% 		\EndFor
-% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
-% 		\ForAll{$host\_id$ in $M$}
-% 			\Comment Re-shuffle
-% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
-% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
-% 				\State Re-shuffle data to $host$
-% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
-% 				\EndIf
-% 			\EndFor
-% 		\EndFor
-% 		\Return $M$
-% 	\EndProcedure
-% 	\end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
 
 \subsubsection{Reservoir Sampling}\label{sampling}
-If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, {\color{black}the SCache master will send a sampling request to the framework master}. 
+{\color{blue}
+If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the framework master. 
 The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
-For the sample number, it can be tuned to balance the overhead and accuracy. 
-The sampling job randomly selects some items and performs a local shuffle with the partitioner (see Figure \ref{fig:sample}). 
-At the same time, the items number is counted as the weight. 
-These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
+% For the sample number, it can be tuned to balance the overhead and accuracy. 
+% The sampling job randomly selects some items and performs a local shuffle with the partitioner. 
+% At the same time, the items number is counted as the weight. 
+% These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
+The result will be aggregated on SCache master to predict the reduce partition size.
 After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.8\linewidth]{fig/arch}
-% 	\caption{\color{red}SCache Architecture}
-% 	\label{fig:arch}
-% 	\vspace{-0.5em}
-% \end{figure}
+}
 
@@
 	\centering
-	\begin{minipage}{.4\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{fig/architecture}
+	\includegraphics[width=.7\linewidth]{fig/architecture}
 	\caption{\color{black}SCache Architecture}
 	\label{fig:architecture}
-		% \vspace{-0.5em}
-	\end{minipage}\hfill
-	\begin{minipage}{.4\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{fig/sample}
-		\caption{Reservoir Sampling of One Partition}
-		\label{fig:sample}
-		% \vspace{-1em}
-	\end{minipage}
 \end{figure}
@@
 \subsection{Memory Management}\label{memorymanage}
-As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
+% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
 When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
-To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data-all-or-nothing and context-aware-priority.
+To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
 
 \subsubsection{All-or-Nothing Constraint}
-This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
+% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
+{\color{blue}
 Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
 If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
-PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
-Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least. We refer to this as the all-or-nothing constraint.
-
-According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
-For those incomplete units, SCache marks them as the lowest priority.
-% Following the all-or-noting constraint can maximum the improvement in stage completion time by using reserved memory efficiently.
+% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
+% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
+Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
+We refer to this as the all-or-nothing constraint.
+% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
+}
+% For those incomplete units, SCache marks them as the lowest priority.
 
 \subsubsection{Context-Aware-Priority Constraint}
-Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once (without failure), but the legacy cache managements are designed to improve the hit rate.
+% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
+{\color{blue}
 SCache leverages application context to select victim storage units when the reserved memory is full.
-
 At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
-If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
-\begin{itemize}[noitemsep]
-	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
-	For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
-	So SCache sets the priorities according to the submission time of each shuffle.
-	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
-	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
-	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
-	% So SCache sets the priorities according to the submit time of each shuffle unit.
-	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
-	For example Spark schedules tasks with smaller ID at first. 
-	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
-\end{itemize}
+If all the units are completed, SCache selects victims based on two factors: 
+(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time. 
+(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
+}
+% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
+% \begin{itemize}[noitemsep]
+% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
+% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
+% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
+% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
+% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
+% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
+% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
+% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
+% 	For example Spark schedules tasks with smaller ID at first. 
+% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
+% \end{itemize}
 
@@
 % }
-{\color{black}
-\subsection{Analysis of cross-framework capability}\label{crossframework}
-Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks.
+
+% {\color{black}
+% \subsection{Analysis of cross-framework capability}\label{crossframework}
+% Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks.
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
@@
 
-To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
+% To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively.
 In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC.
@@
 In Spark, we mainly modify DAGScheduler and the corresponding data fetcher.
-It only takes about 500 lines of code.
+% It only takes about 500 lines of code.
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
 We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez, are also low.
-}
+% }
 
-\subsection{Discussion of Fault Tolerance}\label{fault}
-Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
-We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
-If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
-A possible way to handle this failure is selecting some backup nodes to store replications. 
-% But the replications can introduce a significant network overhead \cite{availability}.  
-Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
-We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
-Meanwhile, SCache can still provide shuffle optimization during the recovery.
-
-% \subsubsection{Fault Tolerance}
-% To prevent the machine failure in cluster leading to inconsistency SCache, the master node will log the meta data of shuffle register and scheduling on the disk.
-Since we remove the shuffle transfer from the critical path of DAG computing, the disk log will not introduce extra overhead to the DAG framworks.
-Note that the master can be implemented with Apache ZooKeeper \cite{zookeeper} to provide constantly service to DAG framework.
-% At the same time, every work node will send a heartbeat to master to report status.
-If a failure of work node is detected, the master will the do a simple re-schedule.
-For those scheduled shuffle units, the master assgins the tasks to other workers with more lightweight workload evenly.
-Then the new assigned worker will fetch the data again.
-For the incomplete in memory map blocks on the failure node, SCache simply ignore them since DAG framework will schedule the failure map tasks on another node.
+% \subsection{Discussion of Fault Tolerance}\label{fault}
+% Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
+% We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
+% If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
+% A possible way to handle this failure is selecting some backup nodes to store replications. 
+% % But the replications can introduce a significant network overhead \cite{availability}.  
+% Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
+% We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
+% Meanwhile, SCache can still provide shuffle optimization during the recovery.

### 2019-05-09 tii/tex/model.tex
Shorten model

@@
 The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
-We will first introduce the FRQ model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance.
-In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.
+We first introduce the FRQ model in Subsection \ref{model_overview}.
+In the following Subsection \ref{model_analysis}, we use the FRQ model to describe three different computation jobs and analyze their performance.
+In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.
 
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
-A shuffle phase is required between each adjacent DAG computation phases.
+% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
+% A shuffle phase is required between each adjacent DAG computation phases.
 To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
@@
 \begin{itemize}
-	\item Input Data Size \((D)\): The data size of the computation phase.
+	\item Input Data Size \((D)\): The  Input data size of the job.
 	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This rate depends on the algorithm used in the computation phase.
@@
 
-\begin{figure*}
+\begin{figure}
     \centering
-	\includegraphics[width=0.85\textwidth]{fig/model_basic}
+	\includegraphics[width=\linewidth]{fig/model_basic}
 	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
     \label{fig:model_basic}
-    \vspace{-1em}
-\end{figure*}
+    % \vspace{-1em}
+\end{figure}
 The FRQ model calculates the execution time of each phase of the job with these five parameters.
 As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
+\(T_{Job}=T_{Map}+T_{Reduce}\).
 \begin{equation}
@@
 Map phase time depends on input data size and map computation speed:
+% \(T_{Map}={{\frac{D}{V_{Map}}}}\).
 \begin{equation}
@@
 The reduce phase time formula is as follows:
+% \(T_{Reduce}=\frac{D \times R}{V_{Reduce}}+K\times T_{P\_Shuffle}\).
 \begin{equation}
@@
 Both of the above methods can effectively reduce \(T_{P\_Shuffle}\).
-By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.
+% By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\begin{subfigure}{0.47\linewidth}
+	\begin{subfigure}{\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_original}
@@
 		\label{fig:model_original}
-	\end{subfigure}
-	\begin{subfigure}{0.47\linewidth}
+	\end{subfigure}\hfill
+	\begin{subfigure}{\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_hadoop}
@@
 	\label{fig:model_strategies}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\begin{subfigure}{0.47\linewidth}
+	\begin{subfigure}{\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_scache1}
@@
 	\end{subfigure}
-	\begin{subfigure}{0.47\linewidth}
+	\begin{subfigure}{\linewidth}
 		\includegraphics[width=\linewidth]{fig/model_scache2}
@@
 	\label{fig:model_scache}
-\end{figure*}
+\end{figure}
 
-Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
+% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
 We intuitively think that we can also overlap the shuffle phase and the map phases.
@@
 Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
-SCache starts pre-fetching and pre-scheduling in the map phase.
-This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase.
+SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
+This scheduling strategy avoid the I/O resource being idle in the map phase.
 According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
@@
 
-\begin{figure*}
-	\centering
-	\begin{subfigure}{.42\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_net1}
-		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
-		\label{fig:hadoop_net1}
-	\end{subfigure}
-	\begin{subfigure}{.42\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_net2}
-		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
-		\label{fig:hadoop_net2}
-	\end{subfigure}
-	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
-	\label{fig:hadoop_net}
-\end{figure*}
+% \begin{figure}
+% 	\centering
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
+% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+% 		\label{fig:hadoop_net1}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
+% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+% 		\label{fig:hadoop_net2}
+% 	\end{subfigure}
+% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
+% 	\label{fig:hadoop_net}
+% \end{figure}
 
-In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
 On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment.
-Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
+% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
 % Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
@@
 Regarding accuracy, the experimental values are all larger than the calculated values.
-This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, and so on.
+This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc.
 % In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 

### 2019-05-09 tii/tex/evaluation.tex
Shorten evaluation

--- 2019-04-29 tii/tex/evaluation.tex
@@
 \section{Evaluation}\label{evaluation}
-{\color{black}
 This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
@@
 We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
-First, we evaluate the Spark with SCache in 3 different benchmarks.
-We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
-Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+First, we evaluate the Spark with SCache in 2 different benchmarks.
+% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
+% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
+% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
 % In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
@@
 Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
-}
-Finally, we measure the overhead of weighted reservoir sampling.
+% Finally, we measure the overhead of weighted reservoir sampling.
 
@@
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
+{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.}
 
@@
 	\centering
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{minipage}[t]{.5\textwidth}
+	\begin{subfigure}{.5\linewidth}
 		\includegraphics[width=\linewidth]{fig/groupbymapstage}
@@
 		\label{fig:mapstage}
-			\end{minipage}
-			\begin{minipage}{\linewidth}
+	\end{subfigure}
+	\begin{subfigure}{.49\linewidth}
 		\includegraphics[width=\linewidth]{fig/groupbyreducestage}
-				\caption{Reduce Stage Completion Time\newline}
+		\caption{Reduce Stage Completion Time}
 		\label{fig:reducestage}	
-			\end{minipage}
 	\end{subfigure}
-		\vspace{-1em}
-		\caption{Stage Completion Time of\newline Single Shuffle Test}
+	\caption{Stage Completion Time of Single Shuffle Test}
 	\label{fig:singleshuffle}
 	\end{minipage}	
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{minipage}[t]{.49\textwidth}
+		\begin{subfigure}{.5\linewidth}
 			\includegraphics[width=\linewidth]{fig/groupbymaptask}
@@
 			\label{fig:maptask}
-			\end{minipage}
-
-			\begin{minipage}{\linewidth}
+		\end{subfigure}
+		\begin{subfigure}{.49\linewidth}
 			\includegraphics[width=\linewidth]{fig/groupbyreducetask}
-				\caption{Median Task in Reduce Stages\newline}
+			\caption{Median Task in Reduce Stages}
 			\label{fig:reducetask}
-			\end{minipage}
 		\end{subfigure}
-		\vspace{-1em}
-		\caption{Median Task Completion\newline Time of Single Shuffle Test}
+		% \vspace{-1em}
+		\caption{Median Task Completion Time of Single Shuffle Test}
 		\label{fig:singleshuffletask}
-	\end{minipage}	
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\vspace{-0.5em}
-			\begin{minipage}{\linewidth}
-				\includegraphics[width=\linewidth]{fig/tera}
-				\caption{Reduce Stage of First Shuffle}
-				\label{fig:terasort}
-			\end{minipage}
-
-			\begin{minipage}{\linewidth}
-				\vspace{0.5em}
-				\includegraphics[width=\linewidth]{fig/tera_shuffle}
-				\caption{Network Traffic of Second Shuffle}
-				\label{fig:terashuffle}
-			\end{minipage}
-		\end{subfigure}
-		% \vspace{0.1em}
-		\caption{Terasort Evaluation}
 	\end{minipage}	
@@
 \subsubsection{Simple DAG Analysis}\label{simpledag}
-%\subsubsection{Hardware Utilization}
-We first run the same single shuffle test shown in Figure \ref{fig:util}. 
-For each stage, we run 5 rounds of tasks with different input size. 
-As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
+As shown in Figure \ref{fig:scache_util}, we first run the same single shuffle test shown in Figure \ref{fig:util}. 
+% We first run the same single shuffle test shown in Figure \ref{fig:util}. 
+% For each stage, we run 5 rounds of tasks with different input size. 
+% As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job.  
 Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. 
@@
 As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark.
-The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
-% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
-% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
-% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
-For each stage, we pick the task that has median completion time. 
+
+% The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
+% For each stage, we pick the task that has median completion time. 
 In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
@@
 By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
-With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
-The in-memory cache of shuffle data further reduces the shuffle read time. 
+% With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
+% The in-memory cache of shuffle data further reduces the shuffle read time. 
 As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
@@
 
-\subsubsection{Terasort}
-We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
-Terasort consists of two consecutive shuffles. 
-The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
-As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
-It further proves the effectiveness of SCache's optimization.
+% \subsubsection{Terasort}
+% We also evaluate Terasort\footnote{http://sortbenchmark.org/YahooHadoop.pdf} --- a recognized shuffle intensive benchmark for distributed system analysis. 
+% Terasort consists of two consecutive shuffles. 
+% The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
+% As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
+% It further proves the effectiveness of SCache's optimization.
 
-The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
-% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
+% The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
+% % As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
 So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
-In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
-So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
-In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
-By doing this, Spark minimizes the shuffle data through network. 
-At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
-It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
+% In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
+% So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
+% In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
+% By doing this, Spark minimizes the shuffle data through network. 
+% At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
+% It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
 \begin{figure*}
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.8\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
@@
 	\end{subfigure}
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.8\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
@@
 	\label{fig:hadoop_terasort}
-\end{figure*}
+\end{figure}
 
@@
 
-\subsection{Overhead of Sampling}
-We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
-In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
-Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
-Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
-So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
-Combined with the sampling overhead evaluation, we believe that SCache is scalable.
+% \subsection{Overhead of Sampling}
+% We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
+% In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
+% Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
+% Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
+% So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
+% Combined with the sampling overhead evaluation, we believe that SCache is scalable.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
+        \includegraphics[width=.8\linewidth]{fig/hadoop_terasort_time} % first figure itself
         \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
@@
     \end{minipage}\hfill
-    \begin{minipage}{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
-        \caption{Sampling Overhead}
-		\label{fig:sampling}
-    \end{minipage}
+    % \begin{minipage}{0.4\textwidth}
+    %     \centering
+    %     \includegraphics[width=.8\linewidth]{fig/sampling} % second figure itself
+    %     \caption{Sampling Overhead}
+	% 	\label{fig:sampling}
+    % \end{minipage}
 \end{figure}

### 2019-05-09 tii/tex/impl.tex
Modify some fig.

@@
 If all the units are completed, SCache selects victims based on two factors: 
-(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time. 
+(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time;
 (b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.

### 2019-05-10 tii/tex/abstract.tex
Shorten abstract

@@
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
-By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node.
+SCache adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
+% By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node.
 Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
@@
 % We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
-We have implemented SCache on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
+We have implemented SCache on both Spark and Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
 Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.

### 2019-05-10 tii/tex/motivation.tex
Shorten all

@@
-\section{Background and Observations}
+\section{Background and Observations}\label{motivation}
 
@@
 
+{\color{black}
 In large scale data parallel computing, shuffle is designed to achieve an all-to-all data transfer among nodes.
-For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
+The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
+Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
+Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.
+Thus, Shuffle is I/O intensive, which might introduce a significant latency to the application. 
+Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
+For those shuffle-heavy jobs, the shuffle latency may even dominate the completion time of jobs.
+}
+% For a clear illustration, we use \textit{map tasks} to define the tasks that produce shuffle data and use \textit{reduce tasks} to define the tasks that consume shuffle data.
 % Note that one task may have both shuffle data generation and consumption in modern DAG framework.
@@
 
-\subsubsection{Overview of shuffle process}
-Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
-The total number of buckets equals the number of reduce tasks in the successive step.
-% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
-The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
-Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
-Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.
+% \subsubsection{Overview of shuffle process}
+% Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
+% The total number of buckets equals the number of reduce tasks in the successive step.
+% % shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
+% The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
+% Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
+% Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.
 
@@
 
-\subsubsection{Impact of shuffle process}
-{\color{blue}
-Shuffle is I/O intensive, which might introduce a significant latency to the application. 
-Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
-For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time.
+% \subsubsection{Impact of shuffle process}
+% {\color{black}
+% Shuffle is I/O intensive, which might introduce a significant latency to the application. 
+% Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
+% For those shuffle-heavy jobs, the shuffle latency may even dominate the completion time of jobs.
 % For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
 % For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
-}
+% }
 
@@
 Can we mitigate or even remove the overhead of shuffle?
-To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
-Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
+To analyze the design and implementation of shuffle, we run some Spark's \textit{GroupByTest} on a 5-node m4.xlarge EC2 cluster.
+% To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
+Figure \ref{fig:util} shows the hardware utilization trace of one node of the experiment.
+% Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
 This job has 2 rounds of tasks for each node.
@@
 \subsubsection{Coarse Granularity Resource Allocation}
-{\color{blue}
+{\color{black}
 As shown in Figure \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
@@
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
-\begin{figure}
-	\includegraphics[width=\linewidth]{fig/util}
-	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
-	\label{fig:util}
-	\vspace{-1em}
-\end{figure}
 

### 2019-05-24 scache/jpdc/tex/impl.tex
mkdir scache

--- 2019-03-26 jpdc/tex/impl.tex
@@
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
-We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also very low.
+We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
 }
@@
 We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
-If a failure happened inside the SCache worker, SCache daemon could block the shuffle write/read operations until the worker process restarted without violating the correctness of the DAG computing.
+If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
 A possible way to handle this failure is selecting some backup nodes to store replications. 
 But the replications can introduce a significant network overhead \cite{availability}.  
-Currently, we left the sever faults (e.g., the failure of a node) to the DAG frameworks. 
+Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
 We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 

### 2019-05-24 scache/taco/tex/relatedwork.tex
mkdir scache

--- 2019-01-03 taco/tex/relatedwork.tex
@@
 {\color{blue}
-\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e.
-\textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on.
+\textbf{Modeling}: Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase, i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on.
 % (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
@@
 The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
-In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job abd combine them into an overall MapReduce job model.
+In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
 % The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 

### 2019-05-24 scache/tii/tex/abstract.tex
mkdir scache

--- 2019-04-26 tii/tex/abstract.tex
@@
 % {\color{blue}
-In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies usually bring in large overhead.
+In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
 Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.

### 2019-05-24 scache/tii/tex/evaluation.tex
mkdir scache

--- 2019-03-26 jpdc/tex/evaluation.tex
@@
 \section{Evaluation}\label{evaluation}
-This section reveals the evaluation of SCache with comprehensive workloads and benchmarks. 
-First we run a job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
+{\color{blue}
+This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
+% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
+We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
+First, we evaluate the Spark with SCache in 3 different benchmarks.
+We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
 Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-
-% \begin{figure}
-% 	\includegraphics[width=.8\linewidth]{fig/scache_util}
-% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
-% 	\label{fig:scache_util}
-% \end{figure}
-
-In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-{\color{blue}
-To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
+To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
+Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
 }
 Finally, we measure the overhead of weighted reservoir sampling.
+
 In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
@@
 
-In overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
+Overall, SCache can help Spark decrease by ~$89\%$ overhead of the whole shuffle process.
 
-\subsection{Terasort}
-We also evaluate Terasort-a recognized shuffle intensive benchmark for distributed system analysis. 
+\subsubsection{Terasort}
+We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
 Terasort consists of two consecutive shuffles. 
@@
 	\centering
+	\includegraphics[width=.9\textwidth]{fig/tpcds}
+	\caption{TPC-DS Benchmark Evaluation}
+	\label{fig:tpcds}
+	\vspace{-1em}
+\end{figure*}
+
+\subsubsection{Industrial Production Workload}
+We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
+TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
+% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
+As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
+Note that we skip some queries due to the compatible issues. 
+Spark with SCache outperforms the original Spark in almost all tested queries. 
+Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
+It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
+The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
+Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
+
+\begin{figure*}
+	\centering
 	\begin{subfigure}{.47\linewidth}
@@
 	\label{fig:hadoop_terasort}
-\end{figure*}
-\begin{figure*}
-	\centering
-	\includegraphics[width=.9\textwidth]{fig/tpcds}
-	\caption{TPC-DS Benchmark Evaluation}
-	\label{fig:tpcds}
-	\vspace{-1em}
 \end{figure*}
@@
 
-\subsection{Production Workload}
-We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
-TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
-TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
-% We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
-As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
-Note that we skip some queries due to the compatible issues. 
-Spark with SCache outperforms the original Spark in almost all tested queries. 
-Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-It is because that those queries contain shuffle-heavy operations such as "groupby", "union", etc.
-The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
-Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
-
 \subsection{Overhead of Sampling}

### 2019-05-24 scache/tii/tex/model.tex
mkdir scache

--- 2019-01-03 taco/tex/model.tex
@@
 The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
-According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on.
-Therefore the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance.
+In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
+The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
 We will first introduce the FRQ model in Subsection \ref{model_overview}.
 In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance.
-In the last Subsection \ref{model_verification}, we will use the actual experimental results to verify the FRQ model.
+In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.
 
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed computing frameworks mostly use DAGs to describe computation logic. 
+The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
 A shuffle phase is required between each adjacent DAG computation phases.
@@
 \begin{enumerate}
-    \item 
-    \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1}): 
+    \item \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1})
+
 	The meaning of the inequality is that the speed of generating shuffle data (\(V_{Map} \times R\)) is greater than or equal to the shuffle speed (\(V_{Shuffle}\)). 
-	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{PShuffle}\) is as followed:
+	In this situation, the shuffle phase is uninterrupted. The I/O resource will be fully utilized during the whole shuffle phase. As a result, the formula of \(T_{P\_Shuffle}\) is as followed:
 	\begin{equation}
@@
 
-    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2}): 
+    \item \(V_{Map} \times R < V_{Shuffle}\) (Figure \ref{fig:model_scache2})
+
 	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated.
 As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round.
-In this case, the formula of \(T_{PShuffle}\) is as followed:
+In this case, the formula of \(T_{P\_Shuffle}\) is as followed:
 	\begin{equation}
@@
 
-\begin{table}[!t]
-\begin{minipage}{\columnwidth}
+% \begin{table}[!t]
+\begin{table*}
 \centering
-\scalebox{0.75}{
+\scalebox{0.95}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 \label{table1}
-\end{minipage}
-\end{table}
+\end{table*}
 % \subsection{Performance Analysis}\label{model_performance_analysis}
 
-\begin{table*}[!t]
+% \begin{table*}[!t]
+\begin{table*}
 \centering
-\scalebox{0.75}{
+\scalebox{0.95}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 
-\subsection{Model Verification}\label{model_verification}
-To verify the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}.
-(b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
-To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop Mapreduce framework.
+\subsection{Model evaluation}\label{model_evaluation}
+To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
+To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework.
 We deployed Hadoop with SCache and without SCache in both environments.
@@
 	\label{fig:hadoop_net}
-\end{figure}
+\end{figure*}
 
-In order to verify the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
@@
 }
+
+\begin{figure}
+	\includegraphics[width=\linewidth]{fig/scache_util}
+	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
+	\label{fig:scache_util}
+\end{figure}

### 2019-05-24 scache/tii/tex/motivation.tex
mkdir scache

--- 2019-01-03 taco/tex/motivation.tex
@@
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{0.47\linewidth}
+\begin{figure}
 	\includegraphics[width=\linewidth]{fig/util}
-		\caption{Original Spark}
+	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
 	\label{fig:util}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/scache_util}
-		\caption{Spark With SCache}
-		\label{fig:scache_util}
-	\end{subfigure}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
-\end{figure*}
+	\vspace{-1em}
+\end{figure}
 

### 2019-05-24 scache/tii/tex/optimization.tex
mkdir scache

--- 2019-03-27 jpdc/tex/optimization.tex
@@
 On the other hand, the result of linear regression comes out with a large relative error. 
-Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
 We will show the overhead evaluation of sampling in Section \ref{evaluation}.

### 2019-05-24 scache/tpds/tex/abstract.tex
mkdir scache

--- 2018-12-28 taco/tex/abstract.tex
@@
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
-{\color{blue}
+{\color{black}
 During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
@@
 % }
-{\color{blue}
+{\color{black}
 We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce.

### 2019-05-27 ops/tex/introduction.tex
Add ops

\section{Introduction}
In recent years, multiple computing frameworks, such as Hadoop MapReduce \cite{}, Spark \cite{} and Dryad \cite{}, are widely used to analyze big data.
Many existing studies are focused on improving the performance of the frameworks.
For example, \dots

Most of the computing frameworks use the directed acyclic graphs (DAGs) to define the execution logic of jobs.
The communication between stages of the most computing frameworks follows the bulk-synchronous parallel (BSP) model, such as the shuffle phases in the Hadoop MapReduce and Spark.
According to the BSP model, the shuffle phases are burdens between the adjacent computing phases.
Since the communication relies on plenty of disk and network I/O, the shuffle phases usually have a heavily affect on the end-to-end application performance.
In the production workload \cite{}, the shuffle phases occupy 33\% of the job completion time on average., and up to 70\% in shuffle-heavy jobs.

Several efforts are made to optimize the shuffle phases.

However, such early-start has several deficiencies.
First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.

### 2019-08-13 ops/tex/abstract.tex
Update

\begin{abstract}
In distributed computing frameworks like MapReduce and Spark, shuffle phases are barriers between the adjacent computing phases. 
Since the transmission of the massive data, shuffle phases account for more than 33\% of job completion time.
In this paper, we optimize shuffle phases in two ways: 
(1) we decouple the shuffle from the computing phases to increase the resource utilization, and
(2) we optimize the network scheduling to decrease the communication time in the shuffle phases.
We present \textit{OPS}, a system that enables the common computing frameworks to use scheduling algorithms to optimize the whole data shuffle progress.
We show that \textit{OPS} improves the end-to-end job completion time by up to ??.
We also show \dots
\end{abstract}

### 2019-08-13 scache/tii/coverletter/coverletter.tex
mkdir scache

--- 2019-01-04 taco/coverletter/coverletter.tex
@@
 
-This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
+% This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
+This paper is the extension of our conference paper at PPoPP. 
+% In the manuscript we uploaded, we highlight the new content in blue.
+% We believe that shuffle-heavy jobs are also existed widely in industrial big-data analysis.
+% SCache can also provide considerable optimization in industrial big-data.
+In this paper, we combine the characteristic of the industrial big-data and DAG computing frameworks.
+We provide a new data processing solution for the industrial big-data based on our conference paper.
+Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big-data analysis.
 This paper makes the following distinct contributions compared with the conference paper.
@@
 % Besides the major contributions, we also revise the paper in many places, including writing and more related work. 
-In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve experiments by adding experiments on Hadoop MapReduce. 
-We believe that the added content makes a sufficient contribution to this journal submission.
+In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
+We believe that the added content makes a sufficient contribution to this special issue.
+% We believe that the added content makes a sufficient contribution to this journal submission.
 
 \bibliographystyle{IEEEtran}
-\bibliography{coverletter}
+% \bibliography{coverletter}
 

### 2019-08-13 scache/tii/tex/conclusion.tex

--- 2019-04-29 tii/tex/conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion}\label{conclusion}
 In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
@@
 %  }
-{\color{blue}
+{\color{black}
 % Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
-The benchmark using in evaluations covers the most situations of industrial big-data analysis.
+% The benchmark using in evaluations covers the most situations of industrial big-data analysis.
 The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
 Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. 
-At last, we evaluate the SCache shuffle optimization by the FRQ model.
+% At last, we evaluate the SCache shuffle optimization by the FRQ model.
 % Therefore, with the shared defects of shuffle among different frameworks, we believe that the optimization of SCache is general and easy to be adapted. 

### 2019-08-13 scache/tii/tex/evaluation.tex

@@
 \section{Evaluation}\label{evaluation}
-{\color{blue}
+
 This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
@@
 We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
-First, we evaluate the Spark with SCache in 3 different benchmarks.
-We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
-Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% First, we evaluate the Spark with SCache in two different benchmarks.
+% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
+% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
+% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
 % In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
 % To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
-}
-Finally, we measure the overhead of weighted reservoir sampling.
-
-In summary, SCache can decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
+% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
+% Finally, we measure the overhead of weighted reservoir sampling. 
+In summary, SCache decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
 More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{blue}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$}
+{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.}
 
@@
 To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
+
+\begin{figure}
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/util}
+		\caption{Spark without SCache}
+		\label{fig:util}
+	\end{subfigure}
+	% \vspace{-1em}
+	\begin{subfigure}{\linewidth}
+		\includegraphics[width=\linewidth]{fig/scache_util}
+		\caption{Spark with SCache}
+		\label{fig:scache_util}
+	\end{subfigure}
+	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
+	\label{fig:simple_spark}
+\end{figure}
+
 \begin{figure*}
 	\centering
-	\begin{minipage}[t]{.32\linewidth}
-		\begin{subfigure}{\linewidth}
-			\begin{minipage}{\linewidth}
+	\begin{minipage}[t]{.5\textwidth}
+	\begin{subfigure}{.5\linewidth}
 		\includegraphics[width=\linewidth]{fig/groupbymapstage}
@@
 \subsection{Setup}\label{stepup}
-We modified Spark to enable shuffle optimization of SCache as a representative.
+% We modified Spark to enable shuffle optimization of SCache as a representative.
 The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
@@
 Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
-Our evaluations reveal the bandwidth is only about 300 Mbps (see Figure \ref{fig:util}).
+Our evaluations reveal the bandwidth is only about 300 Mbps.
+%  (see Figure \ref{fig:util}).
 
@@
 \subsubsection{Simple DAG Analysis}\label{simpledag}
-%\subsubsection{Hardware Utilization}
-We first run the same single shuffle test shown in Figure \ref{fig:util}. 
-For each stage, we run 5 rounds of tasks with different input size. 
-As shown in Figure \ref{fig:scache_util}, the hardware utilization is captured from one node during the job. 
-Note that since the completion time of whole job is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is cut in half as well. 
-An overlap among CPU, disk, and network can be easily observed in Figure \ref{fig:scache_util}. 
+% As shown in Figure \ref{fig:scache_util}, we first run the same single shuffle test shown in Figure \ref{fig:util}. 
+We first run Spark's \textit{GroupByTest} on Amazon EC2.
+This job has 2 rounds of tasks for each node.
+% We first run the same single shuffle test shown in Figure \ref{fig:util}. 
+% For each stage, we run 5 rounds of tasks with different input size. 
+As shown in Figure \ref{fig:simple_spark}, the hardware utilization is captured from one node during the job. 
+Note that since the completion time of the job with SCache is about $50\%$ less than Spark without SCache, the duration of Figure \ref{fig:scache_util} is only half of Figure \ref{fig:util}.
+As shown in \ref{fig:util}, the network transfer of shuffle data introduces an explicit I/O delay during \textit{shuffle read}.
+And the several bursts of network traffic in \textit{shuffle read} result in network congestion.
+As shown in Figure \ref{fig:scache_util}, an overlap among CPU, disk, and network can be easily observed. 
 It is because the decoupling of shuffle prevents the computing resource from being blocked by I/O operations. 
@@
 As a result, the utilization and multiplexing of hardware resource are increased, thus improving the performance of Spark.
-The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
-% By running Spark with SCache, the completion time of map stage can be reduced $10\%$ on average. 
-% For reduce stage, instead, SCache achieves a ~$75\%$ performance gain in the completion time of the reduce stage.
-% A detail analysis into the nutshell of varied overall performance gain on different stages is presented with Figure \ref{fig:singleshuffletask}. 
-For each stage, we pick the task that has median completion time. 
-In the map task, the disk operations are replaced by the memory copies to decouple the shuffle write. 
+
+% The performance evaluation in Figure \ref{fig:singleshuffletask} shows the consistent results with our observation of hardware utilization. 
+% For each stage, we pick the task that has median completion time. 
+In the map stage, the disk operations are replaced by the memory copies to decouple the shuffle write. 
 It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
-Note that the shuffle write time can be observed even with the optimization of SCache. 
-The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}.
-
-In the reduce task, most of the shuffle overhead is introduced by network transfer delay. 
-By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
-With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
-The in-memory cache of shuffle data further reduces the shuffle read time. 
+% Note that the shuffle write time can be observed even with the optimization of SCache. 
+% The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}. 
+In the reduce stage, most of the shuffle overhead is introduced by network transfer delay. 
+By doing shuffle data pre-fetching, the explicit network transfer is perfectly overlapped in the map stage. 
+% By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
+% With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
+% The in-memory cache of shuffle data further reduces the shuffle read time. 
 As a result, the combination of these optimizations decreases ~$100\%$ overhead of the shuffle read in a reduce task (Figure \ref{fig:reducetask}). 
@@
 
-\subsubsection{Terasort}
-We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
-Terasort consists of two consecutive shuffles. 
-The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
-As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
-It further proves the effectiveness of SCache's optimization.
+% \subsubsection{Terasort}
+% We also evaluate Terasort\footnote{http://sortbenchmark.org/YahooHadoop.pdf} --- a recognized shuffle intensive benchmark for distributed system analysis. 
+% Terasort consists of two consecutive shuffles. 
+% The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
+% As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
+% It further proves the effectiveness of SCache's optimization.
 
-The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
-% As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
+% The second shuffle of Terasort partitions the data through a Spark RangePartitioner. 
+% % As the range bounds set by range partitioner almost match the same pattern of the first shuffle, almost $93\%$ of input data is from one particular map task for each reduce task.
 So we take the second shuffle as an extreme case to evaluate the scheduling locality for SCache.
-In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
-So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
-In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
-By doing this, Spark minimizes the shuffle data through network. 
-At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
-It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
+% In the second shuffle, almost $93\%$ of input data of a reduce task is produced by one particular map task. 
+% So we take the second shuffle as an extreme case to evaluate the heuristic locality swap of SCache.
+% In this shuffle, Spark schedules a reduce task to the node that produces most input data. 
+% By doing this, Spark minimizes the shuffle data through network. 
+% At the same time, Figure \ref{fig:terashuffle} reveals that SCache produces exactly same network traffic as Spark. 
+% It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load. 
 \begin{figure*}
 	\centering
-	\includegraphics[width=.9\textwidth]{fig/tpcds}
+	\includegraphics[width=.8\textwidth]{fig/tpcds}
 	\caption{TPC-DS Benchmark Evaluation}
@@
 \subsubsection{Industrial Production Workload}
-We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
-TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
-TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
+% We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+% TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
+% TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
+TPC-DS\footnote{http://www.tpc.org/tpcds/} contains 99 queries and is considered as a standardized industry benchmark for testing big data systems. 
 % We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
@@
 Spark with SCache outperforms the original Spark in almost all tested queries. 
-Furthermore, in many queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
+Furthermore, in some shuffle-heavy queries, Spark with SCache outperforms original Spark by an order of magnitude. 
+% It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
 The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.8\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_scache}
-		\caption{\color{blue}Hadoop MapReduce with SCache}
+		\caption{\color{black}Hadoop MapReduce with SCache}
 		\label{fig:hadoop_terasort_scache}
 	\end{subfigure}
-	\begin{subfigure}{.47\linewidth}
+	\begin{subfigure}{.8\linewidth}
 		\includegraphics[width=\linewidth]{fig/hadoop_terasort_origin}
-		\caption{\color{blue}Hadoop MapReduce without SCache}
+		\caption{\color{black}Hadoop MapReduce without SCache}
 		\label{fig:hadoop_terasort_origin}
 	\end{subfigure}
-	\caption{\color{blue}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
+	\caption{\color{black}CPU utilization and I/O throughput of a node during a Hadoop MapReduce Terasort job}
 	\label{fig:hadoop_terasort}
-\end{figure*}
+\end{figure}
 
-{\color{blue}
+{\color{black}
 \subsection{Hadoop MapReduce with SCache}
@@
 % Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
-As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
-As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase.
-The shuffle phase and the reduce phase start simultaneously.
-Because a large amount of shuffle data reaches the network bottleneck, the beginning part of reduce phase needs to wait for network transfer.
+% As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
+As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
+The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck.
 This causes the CPU resources to be idle.
@@
 Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after better fine-grained utilization of hardware resources, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
 }
 
-\subsection{Overhead of Sampling}
-We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
-In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
-Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
-Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
-So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
-Combined with the sampling overhead evaluation, we believe that SCache is scalable.
+% \subsection{Overhead of Sampling}
+% We evaluate the overhead of sampling with different input sizes and numbers of nodes. 
+% In Figure \ref{fig:sampling}, the overhead of sampling only grows with the increase of input size on each node, but remains relatively stable when the cluster size scales up.
+% Since the shuffle data is short-lived, write-once, and read-once, the central controller of SCache does not have to collect and manage complex metadata. 
+% Meanwhile, most of the optimizations such as fetching and storing shuffle data are finished by workers independently. 
+% So the cost of pre-scheduling algorithm and memory management are unlikely to make the master become the bottleneck of the scalability.
+% Combined with the sampling overhead evaluation, we believe that SCache is scalable.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{fig/hadoop_terasort_time} % first figure itself
-        \caption{\color{blue}Hadoop MapReduce Terasort Completion Time}
+        \includegraphics[width=.8\linewidth]{fig/hadoop_terasort_time} % first figure itself
+        \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
 		\label{fig:hadoop_terasort_time}
     \end{minipage}\hfill
-    \begin{minipage}{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{fig/sampling} % second figure itself
-        \caption{Sampling Overhead}
-		\label{fig:sampling}
-    \end{minipage}
+    % \begin{minipage}{0.4\textwidth}
+    %     \centering
+    %     \includegraphics[width=.8\linewidth]{fig/sampling} % second figure itself
+    %     \caption{Sampling Overhead}
+	% 	\label{fig:sampling}
+    % \end{minipage}
 \end{figure}

### 2019-08-13 scache/tii/tex/impl.tex

--- 2019-05-09 tii/tex/impl.tex
@@
 The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
+% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
 The daemon bridges the communication between DAG framework and SCache.
@@
 For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
-If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{black}computing job}.
-We will elaborate the sampling procedure in the Section \ref{sampling}.
+If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling job before the computing job.
+The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition.
+The result will be aggregated on SCache master to predict the reduce partition size.
+% We will elaborate the sampling procedure in the Section \ref{sampling}.
 
-{\color{blue}
-When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{black}framework worker} through memory copy.
-After that, the slot will be released (without being blocked on disk operations).
+{\color{black}
+When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
+% After that, the slot will be released (without being blocked on disk operations).
 When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
@@
 
-\subsubsection{Reservoir Sampling}\label{sampling}
-{\color{blue}
-If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the framework master. 
-The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
-% For the sample number, it can be tuned to balance the overhead and accuracy. 
-% The sampling job randomly selects some items and performs a local shuffle with the partitioner. 
-% At the same time, the items number is counted as the weight. 
-% These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
-The result will be aggregated on SCache master to predict the reduce partition size.
-After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
-}
+% \subsubsection{Reservoir Sampling}\label{sampling}
+% {\color{black}
+% If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the framework master. 
+% The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
+% % For the sample number, it can be tuned to balance the overhead and accuracy. 
+% % The sampling job randomly selects some items and performs a local shuffle with the partitioner. 
+% % At the same time, the items number is counted as the weight. 
+% % These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
+% The result will be aggregated on SCache master to predict the reduce partition size.
+% After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
+% }
 
@@
 % This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
-{\color{blue}
-Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
+{\color{black}
+% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
+Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
 If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
@@
 % Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
-{\color{blue}
+{\color{black}
 SCache leverages application context to select victim storage units when the reserved memory is full.

### 2019-08-13 scache/tii/tex/intro.tex

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
% Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
% Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, lineage of resilient distributed datasets (RDDs) in Spark\footnote{https://spark.apache.org/}, vertices and edges in Dryad \cite{dryad}, and Tez\footnote{https://tez.apache.org/}, etc.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce\footnote{http://hadoop.apache.com/}, \textit{RDDs} in Spark\footnote{https://spark.apache.org/}, vertices in Dryad \cite{dryad}, etc.
Shuffle phase is always essential as communication between successive computation stages.
% Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=.85\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
% As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk.  
% And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
And the \textit{shuffle read} fetches intermediate results from remote disks through network. 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
Such task aggregation together with the coupled scheduling effectively simplifies task management.
% However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
However, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
% Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Moreover, since the shuffle read phase starts fetching data only after the corresponding reduce task starts, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
% Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
% Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
% As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
% To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as \textit{slow-start} from Hadoop MapReduce.
{\color{black}
% However, such early-start is by no means a panacea.
% This is mainly because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% However, such early-start has several deficiencies.
% First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
% Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
% Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

% We note that the above deficiencies generally exist in most of the DAG computing frameworks. 
% As a result, even though we can effectively resolve the above deficiencies by modifying one framework, updating one application at a time is impractical given the sheer number of computing frameworks available today.

{\color{black}
To optimize the data shuffling without significantly changing DAG frameworks, we propose S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework.
The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
SCache replaces the disk operations of shuffle write by the memory copy in map tasks and pre-fetch the shuffle data.
% Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
% In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
% Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
Second, SCache pre-schedules the reduce tasks without launching them and pre-fetches the shuffle data. 
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.

We evaluate SCache on a 50-node Amazon EC2 cluster on both Spark and Hadoop MapReduce.
In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS\footnote{http://www.tpc.org/tpcds/}, a standardized industry benchmark, on average on Apache Spark.

The rest of the paper is organized as follows:
% We discuss the opportunities to optimize shuffle in Section \ref{motivation}.
Section \ref{opt} presents the detail of methodologies which using by SCache to gain shuffle optimization, including two heuristic algorithms and a co-scheduler.
We present the implementation of SCache in Section \ref{impl} and do comprehensive evaluations in Section \ref{evaluation}.
We discuss some related work in Section \ref{related} and conclude in Section \ref{conclusion}.
}

% The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
% SCache replaces the disk operations of shuffle write by the memory copy in map tasks. 
% The slot is released after the memory copy. 
% The shuffle data is stored in the reserved memory of SCache until all reduce tasks are pre-scheduled. 
% Then the shuffle data is pre-fetched according to the pre-scheduling results.  
% The application-context-aware memory management caches the shuffle data in memory before launching the reduce task.
% By applying these optimizations, SCache can help the DAG framework achieve a significant performance gain.

% The main challenge to achieve this optimization is \textit{pre-scheduling reduce tasks without launching}. 
% Pre-scheduling without launching violates the design of most frameworks that launch a task after scheduling.
% Furthermore, randomly assigning reduce tasks using by na\"{i}ve scheduling schemes might result in a collision of two heavy tasks on one node.
% First, the complexity of DAG can amplify the defects of na\"{i}ve scheduling schemes. 
% In particular, randomly assigning reduce tasks might result in a collision of two heavy tasks on one node. 
% This collision can aggravate data skew, thus hurting the performance. 
% Second, pre-scheduling without launching violates the design of most frameworks that launch a task after scheduling.
% To address the above problems, we propose a heuristic task pre-scheduling scheme with shuffle data prediction and a task co-scheduler (Section \ref{opt}).
% To address the above problems, we propose a heuristic task pre-scheduling scheme (Section \ref{opt}).

% Another challenge is the \textit{in-memory data management}. 
% To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
% To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{impl}).

% {\color{black}
% We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
% The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
% We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
% }
% \begin{figure}
% 	\includegraphics[width=\linewidth]{fig/util}
% 	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
% 	\label{fig:util}
% 	\vspace{-1em}
% \end{figure}

% {\color{black}
% % We implement SCache on both Spark and Hadoop MapReduce. 
% The performance of SCache is evaluated with both simulations and test-bed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
% We evaluate SCahce in three different benchmarks, including a standardized industry benchmark --- TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
% % On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark.
% In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
% }

### 2019-08-13 scache/tii/tex/limitation.tex

\section{Limitation and Future Work}
SCache aims to mitigate shuffle overhead between DAG computing stages. And the evaluation results show a promising improvement. But we realize some limitations of SCache.

\textbf{Fault tolerance of SCache}: When a failure happens on the SCache master, the whole system will stop working. To prevent the inconsistency caused by failure, the master node logs the meta data of shuffle register and pre-scheduling results on the disk. Since we remove the shuffle transfer from the critical path of DAG computing, the disk logging will not introduce extra overhead to the DAG frameworks. Note that the master can be implemented with Apache ZooKeeper to provide constantly service. If a failure happens on a worker, the optimization of tasks on that node will fail. It also violates the all-or-nothing constraint. A promising way to solve the failure on a worker is to select some backup nodes to store replications of shuffle data during pre-scheduling to prevent the worker failure. In addition, there are also advanced fast recovery techniques such as FineFRC \cite{finefrc}. As for now, fault tolerance is not a crucial goal of SCache,  we leave it to the future work.

%\textbf{Scheduling with different frameworks}: A cluster for data parallel computing always contains more than one frameworks. Setting priority among jobs submitted from different framework is challenging. However, associating with the resource management facilities in data center such as Mesos \cite{mesos} may be a good direction.

\textbf{Future optimization of Network}: Since the shuffle is decoupled, the network layer optimization, such as Varys \cite{varys} and Aalo \cite{aalo}, can be easily applied on SCache to further improve the performance of shuffle.

### 2019-08-13 scache/tii/tex/model.tex

@@
 In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
-The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
+% The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
 In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
-The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
-We will first introduce the FRQ model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance.
-In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.
+% The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
+We first introduce the FRQ model in Subsection \ref{model_overview}.
+In the following Subsection \ref{model_analysis}, we use the FRQ model to describe three different computation jobs and analyze their performance.
+In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.
 
 \subsection{The FRQ Model}\label{model_overview}
-The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
-A shuffle phase is required between each adjacent DAG computation phases.
+% The current distributed computing frameworks mostly use DAGs to describe the computation logic. 
+% A shuffle phase is required between each adjacent DAG computation phases.
 To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
@@
 \begin{itemize}
-	\item Input Data Size \((D)\): The data size of the computation phase.
-	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase. This rate depends on the algorithm used in the computation phase.
+	\item Input Data Size \((D)\): The  Input data size of the job.
+	\item Data Conversion Rate \((R)\): The conversion rate of the input data to the shuffle data during a computation phase.
+	% This rate depends on the algorithm used in the computation phase.
     \item Computation Round Number \((N)\): The number of rounds needed to complete the computation phase.
@@
     \item Computation Speed \((V_{i})\): 
-    The computation speed for each computation phase. This speed depends on the algorithm used in the computation phase.
+	The computation speed for each computation phase.
+	% This speed depends on the algorithm used in the computation phase.
     \item Shuffle Speed \((V_{Shuffle})\): 
-    Transmission speed in the shuffle phase. This speed depends on network and storage device bandwidth.
+	Transmission speed in the shuffle phase.
+	% This speed depends on network and storage device bandwidth.
 \end{itemize}
 
-\begin{figure*}
+\begin{figure}
     \centering
-	\includegraphics[width=0.85\textwidth]{fig/model_basic}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
+	\includegraphics[width=\linewidth]{fig/model_basic}
+	\caption{\color{black}Framework Resources Quantification Model\newline with Full Parallel MapReduce (\(V_{Map} \times R > V_{Shuffle}\))}
     \label{fig:model_basic}
-    \vspace{-1em}
-\end{figure*}
+    % \vspace{-1em}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{fig/model_hadoop}
+	\caption{\color{black}The FRQ Model with Half Parallel MapReduce}
+	\label{fig:model_hadoop}
+\end{figure}
+
 The FRQ model calculates the execution time of each phase of the job with these five parameters.
 As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
+% \(T_{Job}=T_{Map}+T_{Reduce}\).
 \begin{equation}
@@
 
-Map phase time depends on input data size and map computation speed:
+The formulas of map phase time and shuffle phase time are as follow:
+% \(T_{Map}={{\frac{D}{V_{Map}}}}\).
 \begin{equation}
@@
 \end{aligned}
+\begin{aligned}
+    T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
+\end{aligned}
 \end{equation}
@@
 We use \(T_{P\_Shuffle}\) to represent the overlap time between the shuffle phase and the reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
-The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
+% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
 This relationship will be shown in the following Subsection \ref{model_analysis}.
@@
 
-The shuffle phase time formula is as follows:
-\begin{equation}
-\label{equation_Tshuffle}
-\begin{aligned}
-    T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
-\end{aligned}
-\end{equation}
+% The shuffle phase time formula is as follows:
+% \begin{equation}
+% \label{equation_Tshuffle}
+% \begin{aligned}
+%     T_{Shuffle} &= {{\frac{D}{V_{Shuffle}}}}
+% \end{aligned}
+% \end{equation}
 
@@
 
-\begin{figure*}
-	\centering
-	\begin{subfigure}{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/model_original}
-		\caption{\color{blue}Full Serial MapReduce}
-		\label{fig:model_original}
-	\end{subfigure}
-	\begin{subfigure}{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/model_hadoop}
-		\caption{\color{blue}Half Parallel MapReduce}
-		\label{fig:model_hadoop}
-	\end{subfigure}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
-	\label{fig:model_strategies}
-\end{figure*}
+% \begin{figure}
+% 	\centering
+% 	\begin{subfigure}{\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/model_original}
+% 		\caption{\color{black}Full Serial MapReduce}
+% 		\label{fig:model_original}
+% 	\end{subfigure}\hfill
+% 	\begin{subfigure}{\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/model_hadoop}
+% 		\caption{\color{black}Half Parallel MapReduce}
+% 		\label{fig:model_hadoop}
+% 	\end{subfigure}
+% 	\caption{\color{black}The FRQ Model with Different Scheduling Strategies}
+% 	\label{fig:model_strategies}
+% \end{figure}
 
-The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
-As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is entirely serially executed.
+% The FRQ model can describe a variety of resource scheduling strategies. First, we analyze a simple scheduling strategy which used by Apache Spark by default. 
+% As shown in Figure \ref{fig:model_original}, the FRQ model describes a MapReduce job that is entirely serially executed.
 The overlap time between the shuffle phase and the reduce phase is \(0\), in which case \(T_{P\_Shuffle}\) is \(0\).
@@
 The total execution time of a job is also different from the above:
-\begin{equation}
-\label{equation_Tjob2}
-\begin{aligned}
-    T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
-\end{aligned}
-\end{equation}
+% \begin{equation}
+% \label{equation_Tjob2}
+% \begin{aligned}
+%     T_{Job} &= T_{Map} + T_{Shuffle} + T_{Reduce}
+% \end{aligned}
+% \end{equation}
 
-Due to serialization, the I/O resource is idle during the reduce phase and map phase. This scheduling strategy is simple and has much room for optimization.
+% Due to serialization, the I/O resource is idle during the reduce phase and map phase. This scheduling strategy is simple and has much room for optimization.
 
-Figure \ref{fig:model_hadoop} shows a more efficient scheduling strategy which is used by Hadoop MapReduce.
+Figure \ref{fig:model_hadoop} shows a scheduling strategy which is used by Hadoop MapReduce.
 In this scheduling strategy, shuffle phase and reduce phase start at the same time.
@@
 
-\begin{figure*}
+% \begin{figure}
+% 	\centering
+% 	\begin{subfigure}{\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/model_scache1}
+% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+% 		\label{fig:model_scache1}
+% 	\end{subfigure}
+% 	\begin{subfigure}{\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/model_scache2}
+% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+% 		\label{fig:model_scache2}
+% 	\end{subfigure}
+% 	\caption{\color{black}The FRQ Model with Full Parallel MapReduce in Different Environments}
+% 	\label{fig:model_scache}
+% \end{figure}
+\begin{figure}
 	\centering
-	\begin{subfigure}{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/model_scache1}
-		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
-		\label{fig:model_scache1}
-	\end{subfigure}
-	\begin{subfigure}{0.47\linewidth}
 	\includegraphics[width=\linewidth]{fig/model_scache2}
-		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
+	\caption{\color{black}Framework Resources Quantification Model\newline with Full Parallel MapReduce (\(V_{Map} \times R < V_{Shuffle}\))}
 	\label{fig:model_scache2}
-	\end{subfigure}
-	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
-	\label{fig:model_scache}
-\end{figure*}
+\end{figure}
 
-Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
+% Hadoop MapReduce overlaps shuffle phase with reduce phase and utilizes idle resources.
 We intuitively think that we can also overlap the shuffle phase and the map phases.
 We implemented this idea with SCache.
-Figure \ref{fig:model_scache} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
-SCache starts pre-fetching and pre-scheduling in the map phase.
-This scheduling strategy can make better use of resources and avoid the I/O resource being idle in the map phase.
+Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
+SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
+This scheduling strategy avoid the I/O resource being idle in the map phase.
 According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:
@@
 \begin{enumerate}
-    \item \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_scache1})
+    \item \(V_{Map} \times R \ge V_{Shuffle}\) (Figure \ref{fig:model_basic})
 
@@
 \subsection{Model evaluation}\label{model_evaluation}
-To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster as shown in Subsection \ref{stepup}; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
-To simplify the calculation of the FRQ model, we run the Terasort as an experimental application on a Hadoop MapReduce framework.
-We deployed Hadoop with SCache and without SCache in both environments.
+To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
+We run the Terasort as an experimental application on a Hadoop MapReduce framework.
+% We deployed Hadoop with SCache and without SCache in both environments.
 
-Table \ref{table1} shows the calculational results of the FRQ model in the in-house environment. The workload is from 16 GB to 64 GB. 
+Table \ref{table1} shows the results of the FRQ model in the in-house environment.
+% The workload is from 16 GB to 64 GB. 
 \(D\) and \(N\) are set according to the application parameters.
-\(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are calculated based on experimental results.
-K is the empirical value, we set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase in the case of SCache.
+We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
+We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache.
 % The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
-In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_scache1} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
+In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
 % thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
-In the original Hadoop, since pre-fetching is not used, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tshuffle}).
+In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
 \(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
@@
 
-Table \ref{table2} shows the calculational results of the FRQ model in Amazon EC2 environment.
-\;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
-We also set K to the same empirical value.
-The formulas in the table are all the same except \(T_{P\_Shuffle}\).
+Table \ref{table2} shows the results in Amazon EC2 environment.
+% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
+We set K to the same empirical value.
+% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
 In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
@@
 
-\begin{figure*}
-	\centering
-	\begin{subfigure}{.42\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_net1}
-		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
-		\label{fig:hadoop_net1}
-	\end{subfigure}
-	\begin{subfigure}{.42\linewidth}
-		\includegraphics[width=\linewidth]{fig/hadoop_net2}
-		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
-		\label{fig:hadoop_net2}
-	\end{subfigure}
-	\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
-	\label{fig:hadoop_net}
-\end{figure*}
+% \begin{figure}
+% 	\centering
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
+% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+% 		\label{fig:hadoop_net1}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
+% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+% 		\label{fig:hadoop_net2}
+% 	\end{subfigure}
+% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
+% 	\label{fig:hadoop_net}
+% \end{figure}
 
-In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
 Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
 On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment.
-Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
+% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
 % Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
@@
 }
-
-\begin{figure}
-	\includegraphics[width=\linewidth]{fig/scache_util}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application with SCache}
-	\label{fig:scache_util}
-\end{figure}

### 2019-08-13 scache/tii/tex/optimization.tex

--- 2019-03-26 jpdc/tex/optimization.tex
@@
 	\centering
-    % \begin{minipage}{0.42\textwidth}
-    %     \centering
-    %     \includegraphics[width=0.9\textwidth]{fig/reduce_cdf} % first figure itself
-	% 	\caption{Shuffle Time Fraction CDF of OpenCloud Trace}
-	% 	\label{fig:cdf}
-    % \end{minipage}\hfill
-    \begin{minipage}{0.42\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{fig/sim} % second figure itself
+	\includegraphics[width=.6\linewidth]{fig/sim} % second figure itself
 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
 	\label{fig:sim}
-	\end{minipage}
-	\begin{minipage}{0.49\textwidth}
-        \centering
-        \includegraphics[width=0.9\textwidth]{fig/shuffle} % first figure itself
-		\caption{Shuffle Data Prediction}
-		\label{fig:shuffle}
-    \end{minipage}\hfill
 \end{figure}
@@
 \subsection{Decouple Shuffle from Execution}
-% \ifrevision
-% \reversemarginpar
-% \marginpar{B1,C2}
-% \fi
 To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
-% During shuffle write of map tasks, the partitioned shuffle data blocks will be written on the disks.
-% Each block contains a part of input data of a particular reduce task. 
 To prevent the release of a slot being blocked by shuffle write,  
 SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
-Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
-After the memory copy, the slot will be released immediately.
+Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
+% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
+% After the memory copy, the slot will be released immediately.
 
@@
 the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
-% Instead, the original implementation of shuffle read will trigger an all-to-all network transfer that keeps CPU idle.
-%To this end, all I/O operations are managed outside of the DAG framework, and the slot is occupied only by the CPU intensive phases of task.
-\subsection{Pre-schedule with Application Context}
+
+\subsection{Pre-scheduling with Application Context}
 The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
 The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
-Once the tasks are scheduled, the slots will be occupied to launch them. 
-On the other hand, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
+% Once the tasks are scheduled, the slots will be occupied to launch them. 
+And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
 We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
 That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.
-% We explore several pre-scheduling schemes in different scenarios, and evaluate the performance calculating the improvement of reduce tasks completion time with trace of OpenCloud \cite{opencloudtrace}.
-We first emulate the scheduling algorithm of Spark to schedule the reduce tasks of one job, and take the bottleneck of the task set as the completion time.
-Then we remove the shuffle read time as the assumption of shuffle data pre-fetch and emulate under different schemes.
-The result is shown in \ref{fig:sim}.
-% \begin{figure*}
-% 	\centering
-% 	\begin{minipage}{0.34\linewidth}
-% 		\begin{figure}[H]
-% 			\includegraphics[width=\textwidth]{fig/shuffle_size}
-% 			\caption{Shuffle Size Comparing with Input Size}
-% 			\label{fig:shuffle_size}
-% 		\end{figure}
-% 	\end{minipage}
-% 	\begin{minipage}{0.65\linewidth}
-% 		\begin{figure}[H]
-% 			\begin{subfigure}{0.5\textwidth}
-% 				\includegraphics[width=\linewidth]{fig/reduce_cdf}
-% 				\caption{Shuffle Time Fraction CDF}
-% 				\label{fig:cdf}
-% 			\end{subfigure}	
-% 			\begin{subfigure}{0.5\textwidth}
-% 				\includegraphics[width=\linewidth]{fig/sim}
-% 				\caption{Stage Completion Time Improvement}
-% 				\label{fig:sim}
-% 			\end{subfigure}	
-% 			\caption{Emulate Result of OpenCloud Trace}
-% 		\end{figure}
-% 	\end{minipage}
-% \end{figure*}
-% \begin{figure}
-\subsubsection{Problem of Random Mapping}\label{randomassign}
-The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
-In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-% Note that most of the traces from OpenCloud are shuffle-light workload as shown in Figure \ref{fig:cdf}. 
-The average shuffle read time is $3.2\%$ of total reduce completion time.
 
-As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
-We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
-Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
-This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
-Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
-In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
-
-\subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
-% \ifrevision
-% \marginpar{B2,E7}
-% \fi
-The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
-Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
-where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
-$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}). 
-The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
-So the pre-scheduling can be made if the "prediction" of size of shuffle block is practical.
-% \hlyellow{
-% The shuffle size of each reduce task is decided by input data, map task computation, and hash partitioner. 
-% Each map task produces a data block for each reduce task. 
-% }
-% The size of each reduce partition can be calculated $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$ ($m$ is the number of map tasks). 
-% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$ (e.g., block `1-1' in Figure \ref{fig:shuffle}).
-% \ifrevision
-% \reversemarginpar
-% \marginpar{B2,D6,D8}
-% \fi
-
-For the most DAG applications with random large scale input, 
-the $BlockSize_{ji}$ in a particular shuffle can be predicted with decent accuracy by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}:
-\begin{equation}
-\label{linearregresion}
-\begin{aligned}
-	BlockSize_{ji} = a \times inputSize_j + b
-\end{aligned}
-\end{equation}
-The $inputSize_j$ is the input size of $j$th map task. 
-The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
-
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/hash_pre}
-		\caption{Linear Regression Prediction of Hash Partitioner\newline}
-		\label{fig:hash_pre}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/range_pre_sample}
-		\caption{Linear Regression and Sampling Prediction of Range Partitioner2222}
-		\label{fig:range_pre_sample}
-		\vspace{1em}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.31\linewidth}
-		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
-		\caption{Prediction Relative Error of Range Partitioner\newline}
-		\label{fig:prediction_relative_error}
-	\end{subfigure}
-	\caption{Reduction Distribution Prediction}
-	\label{fig:dis}
-	\vspace{-1em}
-\end{figure*}
-
-Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark \cite{apachespark}.  
-For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
-We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
-The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
-% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
-% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
-The observed map outputs are randomly picked. 
-With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
-The prediction results also fit them well. 
-However, the data partitioned by Spark RangePartitioner \cite{apachespark} in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
-That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
-The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
-
-% Several map outputs (marked as Map Output in Figure \ref{fig:shuffle}) are picked as observation objects to train the model and than predict the final reduce distribution.
-% \ifrevision
-% \reversemarginpar
-% \marginpar{D6,E3}
-% \fi
-
-\noindent
 \begin{minipage}{0.95\columnwidth}
@@
 
-To handle this corner case, we introduce another methodology, named \emph{weighted reservoir sampling}, as a substitution of linear regression. 
+\subsubsection{Problem of Random Mapping}\label{randomassign}
+The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
+We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% The average shuffle read time is $3.2\%$ of total reduce completion time.
+We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
+As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+The performance of random mapping drops as the round number grows. 
+% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
+This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
+Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
+In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
+
+\begin{figure}
+	% \centering
+	% \begin{subfigure}[b]{0.31\linewidth}
+	% 	\includegraphics[width=\linewidth]{fig/hash_pre}
+	% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
+	% 	\label{fig:hash_pre}
+	% \end{subfigure}
+	\begin{subfigure}[b]{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/range_pre_sample}
+		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
+		\label{fig:range_pre_sample}
+		% \vspace{1em}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
+		\caption{Prediction Relative Error of Range Partitioner\newline}
+		\label{fig:prediction_relative_error}
+	\end{subfigure}
+	\caption{Reduction Distribution Prediction}
+	\label{fig:dis}
+	% \vspace{-1em}
+\end{figure}
+\subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
+{\color{black}
+The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
+For the most DAG applications with random large scale input, 
+the shuffle data size can be predicted accurately by a liner regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.
+% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
+% where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
+% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$. 
+% The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
+% So the pre-scheduling can be made if the prediction of size of shuffle block is practical.
+% For the most DAG applications with random large scale input, 
+% the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
+% \begin{equation}
+% \label{linearregresion}
+% \begin{aligned}
+% 	BlockSize_{ji} = a \times inputSize_j + b
+% \end{aligned}
+% \end{equation}
+% The $inputSize_j$ is the input size of $j$th map task. 
+% The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
+% Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark.  
+However, the linear regression model can fail in some uncertainties introduced by sophisticated frameworks like Spark. 
+For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
+We present a particular example with 20 tasks respectively in Figure \ref{fig:range_pre_sample}. 
+The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
+% We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
+% The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
+% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
+% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
+% The observed map outputs are randomly picked. 
+% With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
+% The prediction results also fit them well. 
+% However, the data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
+% That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
+% The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
+
+To handle this corner case, we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
 Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
 For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
-After that, the map function is called locally to process the sampled data (\textit{Sampling} in Figure \ref{fig:shuffle}). 
+After that, the map function is called locally to process the sampled data. 
 Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
+The $inputSize_j$ is the input size of $j$th map task. 
 Note that sampling does not consume the input data of map tasks. 
-The $BlockSize_{ji}$ can be calculated by:
-\begin{equation}
-\label{equationsample}
-\begin{aligned}
-	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
-	sample_i &= \text{number of samples for $reduce_i$}
-\end{aligned}
-\end{equation}
+Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
+% The $BlockSize_{ji}$ can be calculated by:
+% \begin{equation}
+% \label{equationsample}
+% \begin{aligned}
+% 	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
+% 	sample_i &= \text{number of samples for $reduce_i$}
+% \end{aligned}
+% \end{equation}
 % The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
@@
 % On the other hand, the result of linear regression comes out with a large relative error. 
-% Though the weighted reservoir sampling is precise, it also introduced extra overhead. 
+% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
 % We will show the overhead evaluation of sampling in Section \ref{evaluation}.
-{\color{blue}
-Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
-We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
+% {\color{black}
+
+% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
+% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
+% }
+
+% During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
+% \begin{equation}
+% \label{equationprob}
+% \begin{aligned}
+% 	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
+%     m &= \text{number of map tasks}
+% \end{aligned}
+% \end{equation}
+% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling. 
 }
 
-During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
-\begin{equation}
-\label{equationprob}
-\begin{aligned}
-	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
-    m &= \text{number of map tasks}
-\end{aligned}
-\end{equation}
-This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
-
 \subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
-
-% \ifrevision
-% \marginpar{\tiny PC2,C1,D7/9,E4}
-% \fi
-As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
-But ignoring the data locality can introduce extra network transfer. 
-In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap scheduling algorithm (Algorithm \ref{hminheap}).
-
-For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
-and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
-Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
+% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
+% But ignoring the data locality can introduce extra network transfer. 
+% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
+{\color{black}
+To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
+For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+}
+Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
 After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
 The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
-% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
 Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
-% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
 Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
 
-\subsubsection{Cope with Multiple Shuffle Dependencies}
-% \ifrevision
-% \marginpar{E5}
-% \fi
-A reduce stage can have more than one shuffle dependencies in the current DAG computing frameworks. 
-The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-For those pending shuffles, it is impossible to predict their sizes. 
-This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-But doing this introduces large overhead such as extra task serialization. 
-To avoid violating the optimization from framework, we present the Accumulated Heuristic Scheduling algorithm to cope with multiple shuffle dependencies.
-
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \emph{shuffles} scheduled by Heuristic MinHeap are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \emph{shuffles}. 
-After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
-This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
-which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
-
-\noindent
 \begin{minipage}{0.95\columnwidth}
@@
 		\small
-	\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\emph{shuffles}}$}
+		\Procedure{m\_schedule}{$m, host\_id, p\_reduces, \text{\textit{shuffles}}$}
 			\State $m\gets$ partition number of map tasks
-		\Comment \emph{shuffles} are the previous schedule result 
+			\Comment \textit{shuffles} are the previous schedule result 
 			\ForAll{$r$ in $p\_reduces$}
-			\State $r.size \mathrel{+}= \text{\emph{shuffles}}\left[r.rid\right].size$
-			\State $new\_prob\gets \text{\emph{shuffles}}\left[r.rid\right].size / r.size$
+				\State $r.size \mathrel{+}= \text{\textit{shuffles}}\left[r.rid\right].size$
+				\State $new\_prob\gets \text{\textit{shuffles}}\left[r.rid\right].size / r.size$
 				\If{$new\_prob\geq r.prob$}
 					\State $r.prob\gets new\_prob$
-				\State $r.host\_id\gets \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$
+					\State $r.host\_id\gets \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$
 				\EndIf
@@
 				\ForAll{$r$ in $M\left[host\_id\right].reduces$}
-				\If{$host\neq \text{\emph{shuffles}}\left[r.rid\right].assigned\_host$}
+					\If{$host\neq \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$}
 					\State Re-shuffle data to $host$
-				\State $\text{\emph{shuffles}}\left[r.rid\right].assigned\_host\gets host$
+					\State $\text{\textit{shuffles}}\left[r.rid\right].assigned\_host\gets host$
 					\EndIf
@@
 
+\subsubsection{Cope with Multiple Shuffle Dependencies}
+{\color{black}
+A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
+To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
+}
+% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+% For those pending shuffles, it is impossible to predict their sizes. 
+% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+% But doing this introduces large overhead such as extra task serialization. 
+% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
+After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
+which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
+
 % It means the $SWAP\_TASKS$ can help revise the scheduling to match the previous mapping as much as possible while maintaining the good load balance.

### 2019-08-13 scache/tii/tex/relatedwork.tex

\section{Related Work}\label{related}

{\color{black}
\textbf{Modeling} 
% Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
% , i.e., \textit{stage} in Spark, \textit{superstep} in Pregel\cite{malewicz2010pregel} and so on. 
% (Hadoop MapReduce can also be considered as a special case of only one superstep in BSP model). 
% In the process of optimizing the shuffle phases between adjacent computing phases, we design a performance model to assist in analyzing computing process.
% There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
Khan et al. \cite{khan2016hadoop} proposed the HP model which extends the ARIA model. The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
% The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
% The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
% provisions the resources for the job.
Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
% The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
% \cite{khan2016hadoop, farhat2016stochastic, chen2014cresp} have proposed several methods to model the DAG computing process.
However, the above models are not able to accurately describe the overhead caused by the shuffle process under different scheduling strategies. 
% Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.

\textbf{Industrial big-data}
% In the \textit{Industry 4.0} which leading by the German Government, industrial big-data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
Industrial big-data refers to huge time-series data generated by industrial equipment in smart factories.
More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
Nowadays, the real challenge of big-data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
Several distributed computing frameworks become efficient tools in industrial big-data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
}

\textbf{Pre-scheduling} 
Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
% Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
% All of them have the explicit I/O time in occupied slots. 
% SCache instead starts shuffle pre-fetching without consuming slots. 
iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
% But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
% Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
However, we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

%  by combining DAG information and heuristic algorithms.
% \textbf{Delay-scheduling} 
% Delay Scheduling \cite{delay} delays tasks assignment to get better data locality, which can reduce the network traffic. 
% ShuffleWatcher \cite{shufflewatcher} delays shuffle fetching when the network is saturated. 
% At the same time, it achieves better data locality. 
% Both Quincy \cite{quincy} and Fair Scheduling \cite{preemptive} can reduce shuffle data by optimizing data locality of map tasks. 
% But all of them cannot mitigate explicit I/O in both map and reduce tasks. 
% In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.

\textbf{Network layer optimization} 
% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
% BASS\cite{qin2017bandwidth} combines SDN (Software-defined networking) with Hadoop and provides a bandwidth-aware task scheduling to optimize shuffle phases.
% Hybrid SDN \cite{huang2018survey} can also be seen as a solution to improve the performance.
% We think that it can be applied on SCache to further improve the performace.
% To increase the scalability, hybrid SDN\cite{huang2018survey} can 
% Though the efforts above are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
% Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.

### 2019-08-13 scache/tii/tex/impl.tex
Fix typos

@@
 If all the units are completed, SCache selects victims based on two factors: 
-(a) For the tasks in the different stages, SCache sets the higher priority to storage units with a earlier submission time;
+(a) For the tasks in the different stages, SCache sets the higher priority to storage units with an earlier submission time;
 (b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.

### 2019-08-13 scache/tii/tex/model.tex
Fix typos

@@
 We implemented this idea with SCache.
-Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} shows the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
+Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} show the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
 SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
-This scheduling strategy avoid the I/O resource being idle in the map phase.
+This scheduling strategy avoids the I/O resource being idle in the map phase.
 According to the design of SCache pre-fetching, we found that using the FRQ model to describe the scheduling strategy of SCache needs to distinguish two situations:

### 2019-08-13 scache/tii/tex/relatedwork.tex
Fix typos

@@
 % provisions the resources for the job.
-Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focus on stragglers and try to optimize them. 
+Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
 % The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
@@
 % Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
-However, we have proved that randomly assign tasks may hurt the overall performance in Section \ref{randomassign}. 
+However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
 Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.

### 2019-09-11 scache/tii/tex/abstract.tex
Fix typos
Revision for re-submit.

--- 2019-05-10 tii/tex/abstract.tex
@@
 In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
-Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
+% Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
 To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
-SCache adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
+SCache adopts heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
 % By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node.
@@
 We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
-The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
+The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of DAG jobs. 
 % We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.

### 2019-09-11 scache/tii/tex/evaluation.tex
Fix typos
Revision for re-submit.

@@
-\section{Evaluation}\label{evaluation}
-
-This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
-% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
-We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
-% First, we evaluate the Spark with SCache in two different benchmarks.
-% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
-% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
-% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
-% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
-% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
-% Finally, we measure the overhead of weighted reservoir sampling. 
-In summary, SCache decrease ~$89\%$ time of Spark shuffle without introducing extra network transfer.
-More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by applying the optimization from SCache.
-{\color{black}Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.}
-
-% Because a complex Spark application consists of multiple stages.
-The completion time of each stage varies under different input data, configurations and different number of stages.
-This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison.
-To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
-
 \begin{figure}
@@
 
+\section{Evaluation}\label{evaluation}
+
+% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
+{\color{blue}
+This section reveals a representative evaluation of SCache performance on both Spark and Hadoop MapReduce.
+% To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
+% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
+In industrial big-data, SQL-based big-data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
+% SQL-Based Big Data Systems are widely used on industrial application.
+% Because of the limited time and resource, 
+To prove the performance gain of SCache in industry, 
+we evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/}.
+TPC-DS is a standard benchmark which focus on modeling industrial workload.
+% TPC-DS, TPCx-BB, HiBench, BigDataBenchmark, and so on are popular standard big data benchmarks which evaluate big data systems.
+% TPC-DS models queries and data maintenance of a retail product supplier and provides a representative evaluation of performance.
+% We believe using TPC-DS is able to evaluate the performance of SCache in industry. 
+% First, we evaluate the Spark with SCache in two different benchmarks.
+% We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
+% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
+% To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% In order to prove the performance gain of SCache with a real production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
+% To prove the compatibility of SCache as a cross-framework plug-in, we implemented SCache on both Hadoop MapReduce and Spark. 
+% Second, due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
+% Finally, we measure the overhead of weighted reservoir sampling. 
+% In summary, SCache decreases ~$89\%$ time of Spark shuffle without introducing extra network transfer.
+% More impressively, the overall completion time of TPC-DS can be improved ~$40\%$ on average by SCache.
+%  applying the optimization from SCache.
+In summary, SCache decreases ~$89\%$ time of Spark shuffle and improves ~$40\%$ of the overall completion time of TPC-DS on average.
+Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
+}
+
+% Because a complex Spark application consists of multiple stages.
+The completion time of each stage varies under different input data, configurations and different number of stages.
+This uncertainty leads to the dilemma that dramatic fluctuation occurs in overall performance comparison.
+To present a straightforward illustration, we limit the scope of most evaluations in a single stage.
+
 \subsection{Setup}\label{stepup}
 % We modified Spark to enable shuffle optimization of SCache as a representative.
+We use Spark version 1.6.2 and Hadoop MapReduce version 2.8.5.
 The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
@@
 
-To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
-Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
-
+{\color{blue}
+% To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
+% Although the simple DAG computing alleviates the effect of \textit{pre-scheduling}, the shuffle-heavy jobs can still be optimized by the SCache shuffle data management.
+Unlike Spark, Hadoop MapReduce has only one Map and one Reduce phase.
+Such a simple workflow alleviates the defect of the naive scheduling schemes and reduce the benefits of \textit{pre-scheduling}.
+However, SCache can still provide considerable optimization on shuffle-heavy workloads.
+We use Terasort benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
+% Although the simple workflow alleviates the benefits of \textit{pre-scheduling}, SCache can still .
+% Due to the simple DAG computing in Hadoop MapReduce, we only use Terasort as a shuffle-heavy benchmark to evaluate the performance of Hadoop MapReduce with SCache.
 % Figure \ref{fig:hadoop_terasort} shows the hardware resource utilization of Hadoop MapReduce running Terasort. Both figures have the same proportion of time. 
 % As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size. 
+}
+
 As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
@@
 \end{figure}
+
+\subsection{The FRQ Model Evaluation}\label{model_evaluation}
+% To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
+We run the Terasort as an experimental application on a Hadoop MapReduce framework.
+% We deployed Hadoop with SCache and without SCache in both environments.
+
+Table \ref{table1} shows the results of the FRQ model in the in-house environment.
+% The workload is from 16 GB to 64 GB. 
+\(D\) and \(N\) are set according to the application parameters.
+We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
+We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache.
+% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
+In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
+% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
+In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
+\(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
+% The formula of \(Error\) is:
+% \begin{equation}
+% 	\label{equation_error}
+% 	\begin{aligned}
+% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
+% 	\end{aligned}
+% \end{equation}
+
+Table \ref{table2} shows the results in Amazon EC2 environment.
+% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
+We set K to the same empirical value.
+% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
+In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
+% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).
+
+% \begin{figure}
+% 	\centering
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
+% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
+% 		\label{fig:hadoop_net1}
+% 	\end{subfigure}
+% 	\begin{subfigure}{0.49\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
+% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
+% 		\label{fig:hadoop_net2}
+% 	\end{subfigure}
+% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
+% 	\label{fig:hadoop_net}
+% \end{figure}
+
+% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
+Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
+On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment.
+% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
+% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
+
+Regarding accuracy, the experimental values are all larger than the calculated values.
+This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc.
+% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
+This overhead will be amplified when the input data is small or the total execution time is short. 
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
+}
+
+\begin{table*}
+\centering
+\scalebox{0.95}{
+	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+	\hline
+	&
+	\(D\) &	
+	\(R\) &	
+	\(N\) &	
+	\(V_{Map}\) &	
+	\(V_{Reduce}\) &	
+	\(V_{Shuffle}\) &	
+	\(K\) &	
+	\(T_{Map}\) &	
+	\(T_{Shuffle}\) &	
+	\(T_{P\_Shuffle}\) &
+	\(T_{Reduce}\) & 
+	\(T_{Job}\) & 
+	\(Exp T_{Job}\) &
+	\(Error\)\\
+
+	\hline
+	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
+	SCache
+	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
+	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
+	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
+	\hline
+	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
+	Legacy
+	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
+	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
+	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
+	\hline
+	\end{tabular}
+}
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\label{table1}
+\end{table*}
+% \subsection{Performance Analysis}\label{model_performance_analysis}
+
+% \begin{table*}[!t]
+\begin{table*}
+\centering
+\scalebox{0.95}{
+	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+	\hline
+	&
+	\(D\) &	
+	\(R\) &	
+	\(N\) &	
+	\(V_{Map}\) &	
+	\(V_{Reduce}\) &	
+	\(V_{Shuffle}\) &	
+	\(K\) &	
+	\(T_{Map}\) &	
+	\(T_{Shuffle}\) &	
+	\(T_{P\_Shuffle}\) &
+	\(T_{Reduce}\) & 
+	\(T_{Job}\) & 
+	\(Exp T_{Job}\) &
+	\(Error\)\\
+
+	\hline
+	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
+	SCache
+	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
+	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
+	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
+	\hline
+	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
+	Legacy
+	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
+	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
+	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
+
+	\hline
+	\end{tabular}
+}
+\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\label{table2}
+\end{table*}

### 2019-09-11 scache/tii/tex/impl.tex
Revision for re-submit.

@@
 This section presents an overview of the implementation of SCache. 
-{\color{black}
 We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
@@
 % At last, we discuss the cost of adapting SCache and fault tolerance. 
+{\color{blue}
+In Subsection \ref{fault}, we discuss the fault tolerance of the system.
 }
@@
 \subsection{System Overview}\label{arch}
-SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.
-As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system. 
-The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
+{\color{blue}
+As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
+As a plug-in system, SCache needs to rely on a DAG framework. 
+The master node of SCache includes a DAG co-scheduler and a storage manager.
+The DAG co-scheduler is responsible for pre-scheduling the reduce tasks assignment and then forcing the DAG framework to assign reduce tasks according to this assignment.
+The storage manager is used for managing the shuffle blocks saved in worker nodes.
+% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
 % The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-The daemon bridges the communication between DAG framework and SCache.
+% The daemon bridges the communication between DAG framework and SCache.
 The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.
-When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
-Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
-For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
-If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling job before the computing job.
-The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition.
-The result will be aggregated on SCache master to predict the reduce partition size.
-% We will elaborate the sampling procedure in the Section \ref{sampling}.
 
-{\color{black}
-When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
+When a DAG job is submitted, the DAG information is generated in the framework task scheduler. 
+% Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
+% For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
+If the RangePartitioner or a customized non-hash partitioner is used, SCache will insert an extra sampling job before the job starts.
+The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
+SCache master predicts the reduce partition size based on the data and then call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
+
+% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
+After a map task finishes computing, the shuffle writes in the map task is modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
 % After that, the slot will be released (without being blocked on disk operations).
-When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
-If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
-To enforce the DAG framework to run according to the SCache pre-scheduled results, we also insert some lines of codes in framework scheduler.
+The SCahce records the block ID and the size and sends them to the master.
+% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
+% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
+If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
+After pre-scheduling, SCahce workers start pre-fetching shuffle blocks according to the assignment from the master.
+To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
+}
 % After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
-}
 
@@
 % As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
-When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
-To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
+{\color{blue}
+SCache uses bellowed memory management to ensure performance.
+If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
+SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
+% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
+% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
+}
 
@@
 % This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
-{\color{black}
+{\color{blue}
 % Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
-Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
-If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
+% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
+As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
+If one of the task in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
+% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
 % PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
 % Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
+}
 Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
@@
 % According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
-}
 % For those incomplete units, SCache marks them as the lowest priority.
@@
 
-% \subsection{Discussion of Fault Tolerance}\label{fault}
+{\color{blue}
+\subsection{Discussion of Fault Tolerance}\label{fault}
+% how to handle faults? -> maybe replication -> tradeoff
+For now, SCache only restarts failed workers without recovering their data.
+SCache leaves the fault handling to the DAG frameworks.
+If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
+During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
+A possible way to avoid this re-computing is to use replications to recover the data.
+However, such replications can introduce a significant network overhead.
+We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
+% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
+}
+
 % Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present.

### 2019-09-11 scache/tii/tex/intro.tex
Revision for re-submit.

@@
 The rest of the paper is organized as follows:
+{\color{blue}
 % We discuss the opportunities to optimize shuffle in Section \ref{motivation}.
-Section \ref{opt} presents the detail of methodologies which using by SCache to gain shuffle optimization, including two heuristic algorithms and a co-scheduler.
-We present the implementation of SCache in Section \ref{impl} and do comprehensive evaluations in Section \ref{evaluation}.
-We discuss some related work in Section \ref{related} and conclude in Section \ref{conclusion}.
+We present the methodologies of optimization which using by SCache in Section \ref{opt} and detail the implementation of SCache in Section \ref{impl}.
+We introduce the FRQ performance model in Section \ref{model}.
+In Section \ref{evaluation}, we present comprehensive evaluations about SCache and the FRQ model.
+% We present the implementation of SCache in Section \ref{impl} and do comprehensive evaluations in Section \ref{evaluation}.
+We also discuss the related work in Section \ref{related} and conclude in Section \ref{conclusion}.
+}
 }

### 2019-09-11 scache/tii/tex/model.tex
Revision for re-submit.

@@
 We first introduce the FRQ model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we use the FRQ model to describe three different computation jobs and analyze their performance.
-In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.
+In the following Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
+% In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.
 
@@
 % A shuffle phase is required between each adjacent DAG computation phases.
-To better analyze the relationship between the computation phase and the shuffle phase, we propose the FRQ model.
-After quantifying computing and I/O resources, the FRQ model can describe different resource scheduling strategies.
-For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
+{\color{blue}
+We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
+The FRQ model focuses on describing the overhead caused by the shuffle process.
+This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
+% By using the FRQ model, we can analyze the advantages of each strategy in various situations.
+After quantifying computing and I/O resources, the FRQ model can evaluate different resource scheduling strategies by using different formulas.
+% For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
 
-Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce task. The FRQ model has five input parameters:
+Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
+As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
+The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
+The FRQ model use these overlaps to describe different scheduling strategies.
+For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
+And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
+
+% As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
+Firstly, we introduces five input parameters of the FRQ model:
+}
 \begin{itemize}
@@
 The FRQ model calculates the execution time of each phase of the job with these five parameters.
-As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
+% As shown in Figure \ref{fig:model_basic}
+The total execution time of a job is the sum of the map phase time and reduce phase time:
 % \(T_{Job}=T_{Map}+T_{Reduce}\).
@@
 
-\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
-We use \(T_{P\_Shuffle}\) to represent the overlap time between the shuffle phase and the reduce phase. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
-% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
-This relationship will be shown in the following Subsection \ref{model_analysis}.
-\(K\) is an empirical value. 
-Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation in the reduce phase needs to wait for the transfer results.
-This waiting causes the overhead.
-The FRQ model uses K to indicate the extent of the waiting.
-
 % The shuffle phase time formula is as follows:
@@
 
+{\color{blue}
+\(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.
+\(T_{P\_Shuffle}\) represents the overlap time between the shuffle phase and the reduce phase as shown in Figure \ref{fig:model_basic}. \(T_{Shuffle}\) represents the total time of the shuffle phase. 
+% The relationship between \(T_{P\_Shuffle}\) and \(T_{Shuffle}\) is determined by the resources scheduling strategy of DAG frameworks.
+This relationship will be shown in the following Subsection \ref{model_analysis}.
+\(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
+Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results.
+This waiting causes the overhead.
+
 According to Equation \ref{equation_Tjob}\&\ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
-Improving I/O speed is an effective way to reduce shuffle time.
+By using different resource scheduling strategies, the formulas of \(T_{P\_Shuffle}\) are different.
+In the next subsection, we show the formulas and discuss the performance of different strategies.
+% Improving I/O speed is an effective way to reduce shuffle time.
 Another optimization method is to use the idle I/O resources in the map phase for pre-fetching (see Figure \ref{fig:model_basic}).
@@
 % By using the FRQ model to describe a MapReduce job, the users can analyze the resource scheduling strategy of the computation framework.
+}
 
@@
 The execution time of the shuffle phase is hidden in the reduce phase.
-However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.
+% However, we also found that the I/O resource in the map phase is still idle. This scheduling strategy can still be optimized.
 
@@
 This is how pre-fetching optimizes the total execution time of a job.
-
-% \begin{table}[!t]
-\begin{table*}
-\centering
-\scalebox{0.95}{
-	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
-	\hline
-	&
-	\(D\) &	
-	\(R\) &	
-	\(N\) &	
-	\(V_{Map}\) &	
-	\(V_{Reduce}\) &	
-	\(V_{Shuffle}\) &	
-	\(K\) &	
-	\(T_{Map}\) &	
-	\(T_{Shuffle}\) &	
-	\(T_{P\_Shuffle}\) &
-	\(T_{Reduce}\) & 
-	\(T_{Job}\) & 
-	\(Exp T_{Job}\) &
-	\(Error\)\\
-
-	\hline
-	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
-	SCache
-	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
-	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
-	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
-	\hline
-	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
-	Legacy
-	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
-	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
-	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
-	\hline
-	\end{tabular}
-}
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
-\label{table1}
-\end{table*}
-% \subsection{Performance Analysis}\label{model_performance_analysis}
-
-% \begin{table*}[!t]
-\begin{table*}
-\centering
-\scalebox{0.95}{
-	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
-	\hline
-	&
-	\(D\) &	
-	\(R\) &	
-	\(N\) &	
-	\(V_{Map}\) &	
-	\(V_{Reduce}\) &	
-	\(V_{Shuffle}\) &	
-	\(K\) &	
-	\(T_{Map}\) &	
-	\(T_{Shuffle}\) &	
-	\(T_{P\_Shuffle}\) &
-	\(T_{Reduce}\) & 
-	\(T_{Job}\) & 
-	\(Exp T_{Job}\) &
-	\(Error\)\\
-
-	\hline
-	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
-	SCache
-	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
-	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
-	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
-	\hline
-	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
-	Legacy
-	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
-	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
-	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
-
-	\hline
-	\end{tabular}
-}
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
-\label{table2}
-\end{table*}
-
-\subsection{Model evaluation}\label{model_evaluation}
-To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
-We run the Terasort as an experimental application on a Hadoop MapReduce framework.
-% We deployed Hadoop with SCache and without SCache in both environments.
-
-Table \ref{table1} shows the results of the FRQ model in the in-house environment.
-% The workload is from 16 GB to 64 GB. 
-\(D\) and \(N\) are set according to the application parameters.
-We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
-We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache.
-% The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
-In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
-% thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
-In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
-\(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
-% The formula of \(Error\) is:
-% \begin{equation}
-% 	\label{equation_error}
-% 	\begin{aligned}
-% 		Error &= \frac{ExpT_{Job} - T_{Job}}{T_{Job}}
-% 	\end{aligned}
-% \end{equation}
-
-Table \ref{table2} shows the results in Amazon EC2 environment.
-% \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
-We set K to the same empirical value.
-% The formulas in the table are all the same except \(T_{P\_Shuffle}\).
-In this environment, Terasort on Hadoop MapReduce satisfies the situation in Figure \ref{fig:model_scache2} (\(V_{Map} \times R < V_{Shuffle}\)), thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle2}.
-% In the previous case, \(T_{P\_Shuffle}\) is still equal to \(T_{Shuffle}\).
-
-% \begin{figure}
-% 	\centering
-% 	\begin{subfigure}{0.49\linewidth}
-% 		\includegraphics[width=\linewidth]{fig/hadoop_net1}
-% 		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
-% 		\label{fig:hadoop_net1}
-% 	\end{subfigure}
-% 	\begin{subfigure}{0.49\linewidth}
-% 		\includegraphics[width=\linewidth]{fig/hadoop_net2}
-% 		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
-% 		\label{fig:hadoop_net2}
-% 	\end{subfigure}
-% 	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
-% 	\label{fig:hadoop_net}
-% \end{figure}
-
-% In order to evaluate the two cases as mentioned above when using SCache, we monitor the network utilization as Figure \ref{fig:hadoop_net}.
-Figure \ref{fig:hadoop_net1} shows that, in the in-house environment, the network utilization remains high until the shuffle phase is completed.
-On the other hand, Figure \ref{fig:hadoop_net2} shows that the network utilization has 5 regular peaks in Amazon EC2 environment.
-% Both these two situations are consistent with the FRQ model in Figure \ref{fig:model_scache}. 
-% Therefore, we believe that the FRQ model is able to accurately describe the performance of a framework with SCache.
-
-Regarding accuracy, the experimental values are all larger than the calculated values.
-This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc.
-% In the case where the input data is small and the total time is short, the error caused by the overhead is amplified. 
-This overhead will be amplified when the input data is small or the total execution time is short. 
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
-}

### 2019-09-11 scache/tii/tex/optimization.tex
Revision for re-submit.

@@
 \label{opt}
-This section presents the detailed methodologies to achieve the three design goals. 
-The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
-Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
+This section presents the detailed methodologies to achieve shuffle optimization. 
+{\color{blue}
+Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
+In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
+And we propose the pre-scheduling and pre-fetching to hide shuffle overhead into multi-round map tasks.
+Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
+}
+
+% The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
+% Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
 
@@
 
+\begin{figure}
+	% \centering
+	% \begin{subfigure}[b]{0.31\linewidth}
+	% 	\includegraphics[width=\linewidth]{fig/hash_pre}
+	% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
+	% 	\label{fig:hash_pre}
+	% \end{subfigure}
+	\begin{subfigure}[b]{0.5\linewidth}
+		\includegraphics[width=\linewidth]{fig/range_pre_sample}
+		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
+		\label{fig:range_pre_sample}
+		% \vspace{1em}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.49\linewidth}
+		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
+		\caption{Prediction Relative Error of Range Partitioner\newline}
+		\label{fig:prediction_relative_error}
+	\end{subfigure}
+	\caption{Reduction Distribution Prediction}
+	\label{fig:dis}
+	% \vspace{-1em}
+\end{figure}
+
+{\color{blue}
+\subsection{Observations}\label{observation}
+% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory
+
+In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
+For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce phase.
+In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
+On the reduce side, the shuffle data transfer introduces an explicit overhead during shuffle read.
+Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
+Furthermore, because all reduce tasks start shuffle read simultaneously, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.
+
+% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\).
+\(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase.
+% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
+% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
+To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce phase to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data.
+To achieve this optimization:
+\begin{itemize}
+	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
+	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
+\end{itemize}
+% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
+}
+
 \subsection{Decouple Shuffle from Execution}
-To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
-To prevent the release of a slot being blocked by shuffle write,  
-SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
+{\color{blue}
+To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
+SCache provides two APIs named $putBlock$ and $putBlock$ to manage the shuffle data.
+On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache instead of keeping them on local storage.
 Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
+SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
+% SCache leverages the property of multi-round tasks to 
+On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from the local memory of SCache.
+
+SCache takes over all shuffle data and keep them on the memory instead of storing on disk liked the DAG frameworks.
+In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
+}
+% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
+% To prevent the release of a slot being blocked by shuffle write,  
+% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
+% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
 % Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
@@
 
-From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
-With the precondition of shuffle data pre-fetching, 
-the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
+% From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
+% With the precondition of shuffle data pre-fetching, 
+% the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.
 
-\subsection{Pre-scheduling with Application Context}
+% \subsection{Pre-scheduling with Application Context}
+{\color{blue}
+\subsection{Pre-scheduling and Pre-fetching Shuffle Data}
+% multi-round -> how to optimize? -> pre-schedule -> pre-fetch -> formula
 The pre-scheduling and pre-fetching are the most critical aspects of the optimization.
-The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
+Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
+Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
+SCache starts pre-fetching and hides shuffle overhead into multi-round map tasks.
+However, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
+To pre-scheduling the mapping, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
+The DAG frameworks follow the co-scheduler to starts reduce tasks.
+}
+% The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
+% The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
 % Once the tasks are scheduled, the slots will be occupied to launch them. 
-And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
-We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
-That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.
+% And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
+% We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
+% That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.
+
+\subsubsection{Problem of Random Mapping}\label{randomassign}
+{\color{blue}
+% Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
+To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
+The performance of random mapping drops as the round number grows. 
+This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
+Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
+In addition, randomly mapping also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
+}
+% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
+% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% The average shuffle read time is $3.2\%$ of total reduce completion time.
+% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
+% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+% The performance of random mapping drops as the round number grows. 
+% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
+% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
+% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
+% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
+
+\subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
+{\color{blue}
+The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
+For the most DAG applications with random large scale input, 
+the shuffle output can be predicted accurately by a linear regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.
+% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
+% where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
+% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$. 
+% The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
+% So the pre-scheduling can be made if the prediction of size of shuffle block is practical.
+% For the most DAG applications with random large scale input, 
+% the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
+% \begin{equation}
+% \label{linearregresion}
+% \begin{aligned}
+% 	BlockSize_{ji} = a \times inputSize_j + b
+% \end{aligned}
+% \end{equation}
+% The $inputSize_j$ is the input size of $j$th map task. 
+% The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
+% Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark.  
+However, the linear regression model can fail in some scenarios. 
+For example, some customized partitions may cause large inconsistency between observed map output distribution and the final reduce input distribution. 
+To illustrate the case, we present a particular spark job which using the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 
+The observed map outputs are picked randomly. 
+The job uses the Spark RangePartitioner and introduce an extreme high data skew.
+Due to the extreme high data skew introducing by the partition, linear regression model cannot fit the result well.
+% The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
+% We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
+% The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
+% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
+% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
+% The observed map outputs are randomly picked. 
+% With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
+% The prediction results also fit them well. 
+% However, the data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
+That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
+The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
+
+To solve this problem, we propose a new methodology named \textit{weighted reservoir sampling}.
+SCache uses this method instead of the linear regression to predict output when using a RangePartitioner or a customized non-hash partitioner.
+% we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
+% Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
+For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
+After that, the map function is called locally to process the sampled data. 
+Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
+The $inputSize_j$ is the input size of $j$th map task. 
+% Note that sampling does not consume the input data of map tasks. 
+The $BlockSize_{ji}$ can be calculated by:
+\begin{equation}
+\label{equationsample}
+\begin{aligned}
+	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
+	sample_i &= \text{number of samples for $reduce_i$}
+\end{aligned}
+\end{equation}
+In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide a much more accurate result than the linear regression. 
+% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
+% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
+% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
+% On the other hand, the result of linear regression comes out with a large relative error. 
+% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
+% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
+% {\color{black}
+
+% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
+% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
+% }
+
+}
+During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
+\begin{equation}
+\label{equationprob}
+\begin{aligned}
+	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
+    m &= \text{number of map tasks}
+\end{aligned}
+\end{equation}
+This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
 
@@
 
-\subsubsection{Problem of Random Mapping}\label{randomassign}
-The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
-We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-% The average shuffle read time is $3.2\%$ of total reduce completion time.
-We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
-As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
-The performance of random mapping drops as the round number grows. 
-% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
-This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
-Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
-In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
-
-\begin{figure}
-	% \centering
-	% \begin{subfigure}[b]{0.31\linewidth}
-	% 	\includegraphics[width=\linewidth]{fig/hash_pre}
-	% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
-	% 	\label{fig:hash_pre}
-	% \end{subfigure}
-	\begin{subfigure}[b]{0.5\linewidth}
-		\includegraphics[width=\linewidth]{fig/range_pre_sample}
-		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
-		\label{fig:range_pre_sample}
-		% \vspace{1em}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.49\linewidth}
-		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
-		\caption{Prediction Relative Error of Range Partitioner\newline}
-		\label{fig:prediction_relative_error}
-	\end{subfigure}
-	\caption{Reduction Distribution Prediction}
-	\label{fig:dis}
-	% \vspace{-1em}
-\end{figure}
-\subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
-{\color{black}
-The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
-For the most DAG applications with random large scale input, 
-the shuffle data size can be predicted accurately by a liner regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.
-% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
-% where the $m$ is the number of map tasks that can be easily extracted from DAG information; 
-% $BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$. 
-% The final sizes of reduce tasks can be calculated by aggregating $reduceSize_i$ by reduce ID among all shuffle dependencies. 
-% So the pre-scheduling can be made if the prediction of size of shuffle block is practical.
-% For the most DAG applications with random large scale input, 
-% the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}:
-% \begin{equation}
-% \label{linearregresion}
-% \begin{aligned}
-% 	BlockSize_{ji} = a \times inputSize_j + b
-% \end{aligned}
-% \end{equation}
-% The $inputSize_j$ is the input size of $j$th map task. 
-% The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.
-% Though the linear regression is stable in most scenarios, it can fail in some uncertainties introduced by sophisticated frameworks like Spark.  
-However, the linear regression model can fail in some uncertainties introduced by sophisticated frameworks like Spark. 
-For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
-We present a particular example with 20 tasks respectively in Figure \ref{fig:range_pre_sample}. 
-The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
-% We present two particular examples with 20 tasks respectively in Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}. 
-% The data in are normalized to $0-1$ because the prediction of SCache only produces the data distribution instead of the real size. 
-% In Figure \ref{fig:range_pre_sample}, we use the distribution of second shuffle of Spark Terasort \cite{spark-tera} that are partitioned by Spark RangePartitioner \cite{apachespark}. 
-% In Figure \ref{fig:hash_pre} and Figure \ref{fig:range_pre_sample}, we use different datasets with different partitioners, and normalize the distribution to $0-1$ to fit in one figure. 
-% The observed map outputs are randomly picked. 
-% With a random input and a hash partitioner in Figure \ref{fig:hash_pre}, the distribution of observed map output is close to the final reduce input distribution. 
-% The prediction results also fit them well. 
-% However, the data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
-% That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
-% The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.
-
-To handle this corner case, we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
-Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
-For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
-After that, the map function is called locally to process the sampled data. 
-Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
-The $inputSize_j$ is the input size of $j$th map task. 
-Note that sampling does not consume the input data of map tasks. 
-Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
-% The $BlockSize_{ji}$ can be calculated by:
-% \begin{equation}
-% \label{equationsample}
-% \begin{aligned}
-% 	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
-% 	sample_i &= \text{number of samples for $reduce_i$}
-% \end{aligned}
-% \end{equation}
-% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
-% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
-% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example.
-% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
-% On the other hand, the result of linear regression comes out with a large relative error. 
-% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
-% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
-% {\color{black}
-
-% Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
-% We will show the overhead evaluation of sampling in Section \ref{evaluation}. 
-% }
-
-% During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
-% \begin{equation}
-% \label{equationprob}
-% \begin{aligned}
-% 	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
-%     m &= \text{number of map tasks}
-% \end{aligned}
-% \end{equation}
-% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling. 
-}
-
 \subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
@@
 % In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
-{\color{black}
 To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
-For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+{\color{blue}
+% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.2., line $6-11$).
+We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+Spark FIFO only can achieve $2\text{-}approximation$ optimum.
 }
-Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
+% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
 After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
@@
 Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
+
+{\color{blue}
+As shown in Figure \ref{fig:sim}, \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
+Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
+}
+
+\subsubsection{Cope with Multiple Shuffle Dependencies}
+{\color{black}
+A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
+To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
+}
+% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+% For those pending shuffles, it is impossible to predict their sizes. 
+% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+% But doing this introduces large overhead such as extra task serialization. 
+% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
+After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
+which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
+
+To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.
 
@@
 \end{minipage}
-
-\subsubsection{Cope with Multiple Shuffle Dependencies}
-{\color{black}
-A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
-To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
-}
-% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-% For those pending shuffles, it is impossible to predict their sizes. 
-% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-% But doing this introduces large overhead such as extra task serialization. 
-% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
-After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
-This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
-which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
-
-% It means the $SWAP\_TASKS$ can help revise the scheduling to match the previous mapping as much as possible while maintaining the good load balance.
-
-% As for the input of $SCHEDULE$ function in Algorithm \ref{hminheap}, $m$ is the partition number of input data; $h$ is the array of nodes ID in cluster; $p\_reduces$ is the predicted reduce matrix.
-Each row in $p\_reduces$ contains $rid$ as reduce partition ID; $size$ as predicted size of this partition; $prob$ as the maximum composition portion of reduce data; $host\_id$ as the node ID that produces the maximum portion of reduce data, and $assigned\_id$ as the node ID assigned by Algorithm \ref{hminheap}.
-As for $M$, it is consists $host\_id$, an array of $reduce$ scheduled on this node and the $size$ of them.

### 2019-09-11 scache/tii/tex/relatedwork.tex
Revision for re-submit.

@@
 {\color{black}
-\textbf{Modeling} 
+\textbf{Modeling.} 
 % Most representative DAG computing frameworks use similar \textit{Bulk Synchronize Parallel} (BSP)\cite{valiant1990bridging} model to control data synchronization in each computing phase. 
@@
 
-\textbf{Industrial big-data}
+\textbf{Industrial big-data.}
 % In the \textit{Industry 4.0} which leading by the German Government, industrial big-data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
@@
 
-\textbf{Pre-scheduling} 
+{\color{blue}
+\textbf{DAG Optimization.} 
+There are a number of studies on DAG optimization.
 Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
-% Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
-% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
+Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
+DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
 % All of them have the explicit I/O time in occupied slots. 
@@
 iShuffle \cite{guo2017ishuffle} decouples shuffle from reducers and designs a centralized shuffle controller. 
-% But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
+But it can neither handle multiple shuffles nor schedule multiple rounds of reduce tasks. 
 iHadoop \cite{ihadoop} aggressively pre-schedules tasks in multiple successive stages to start fetching shuffle. 
@@
 However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
-Different from these works, SCache pre-schedules multiple shuffles without breaking load balancing.
-
+In data skew mitigation, 
+Skewtune \cite{skewtune} partitions the data dynamically. When a straggler task happens, it re-partitions the data and forces them to transfer to other nodes.
+% But moving data may cause extra I/O overhead in computing.
+LIBRA \cite{chen2014libra} proposed a new sampling method for DAG frameworks.
+Based on this sampling method, it uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
+ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.
+Different from these works, SCache pre-schedules multiple shuffles and uses pre-fetching to gain optimization without breaking load balancing. 
 %  by combining DAG information and heuristic algorithms.
@@
 % In addition, their optimizations fluctuate under different network performances and data distributions, whereas SCache can provide a stable performance gain by shuffle data pre-fetching and in-memory caching.
+}
 
-\textbf{Network layer optimization} 
+% \textbf{DAG Scheduling}
+% DAG on Monetary Cost？
+% What is? -> examples -> SCache 適用於所有DAG的優化方法
+
+% \textbf{Network layer optimization.} 
 % Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
@@
 % Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
-According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.
+% According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.

### 2019-09-11 scache/tii/coverletter/coverletter.tex
Fix the typo provided by JungleX

@@
 % In the manuscript we uploaded, we highlight the new content in blue.
-% We believe that shuffle-heavy jobs are also existed widely in industrial big-data analysis.
-% SCache can also provide considerable optimization in industrial big-data.
-In this paper, we combine the characteristic of the industrial big-data and DAG computing frameworks.
-We provide a new data processing solution for the industrial big-data based on our conference paper.
-Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big-data analysis.
+% We believe that shuffle-heavy jobs are also existed widely in industrial big data analysis.
+% SCache can also provide considerable optimization in industrial big data.
+In this paper, we combine the characteristic of the industrial big data and DAG computing frameworks.
+We provide a new data processing solution for the industrial big data based on our conference paper.
+Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big data analysis.
 This paper makes the following distinct contributions compared with the conference paper.
@@
 In the conference paper, we only implement SCache on Spark. 
-In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big-data analysis.
+In this paper, we also implement SCache on Hadoop MapReduce, since Spark and Hadoop MapReduce are the two most distributed computing frameworks using in industrial big data analysis.
 % By using the FRQ model to analyze Hadoop MapReduce, we can figure out that SCache is feasible to optimize the shuffle phases. 

### 2019-09-11 scache/tii/tex/abstract.tex
Fix the typo provided by JungleX

@@
 % {\color{black}
-In industrial large-scale data-parallel analytics, shuffle, or the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
+In industrial large-scale data-parallel analytics, shuffle, namely the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
 % Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.
-To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
+To reduce shuffle overhead, we present \textit{SCache}, an open-source plug-in system that particularly focuses on shuffle optimization. 
 SCache adopts heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 

### 2019-09-11 scache/tii/tex/evaluation.tex
Fix the typo provided by JungleX

@@
 
-% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big-data analysis. 
+% This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big data analysis. 
 {\color{blue}
@@
 % To show the compatibility of SCache as a cross-framework plug-in, we implement and evaluate SCache on both Spark and Hadoop MapReduce. 
-% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big-data analysis.
-In industrial big-data, SQL-based big-data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
+% We implement and evaluate SCache on Spark and Hadoop MapReduce, since they are the two most distributed computing frameworks using in industrial big data analysis.
+In industrial big data, SQL-based big data technologies are widely used in these systems, such as data mining, predictive analytics, text analytics, and statistical analysis \cite{poess2017analysis}.
 % SQL-Based Big Data Systems are widely used on industrial application.
@@
 We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
-Each node has 16GB memory and 4 CPUs. The network bandwidth provided by Amazon is insufficient. 
-Our evaluations reveal the bandwidth is only about 300 Mbps.
+Each node has 16GB memory and 4 CPUs.
+The network bandwidth each node is about 300 Mbps.
+% The network bandwidth provided by Amazon is insufficient. 
+% Our evaluations reveal the bandwidth is only about 300 Mbps.
 %  (see Figure \ref{fig:util}).
@@
 Unlike Spark, Hadoop MapReduce has only one Map and one Reduce phase.
-Such a simple workflow alleviates the defect of the naive scheduling schemes and reduce the benefits of \textit{pre-scheduling}.
+Such a simple workflow alleviates the defect of the naive scheduling schemes and reduces the benefits of \textit{pre-scheduling}.
 However, SCache can still provide considerable optimization on shuffle-heavy workloads.
@@
 % To evaluate the FRQ model, we run experiments on two environments: (a) 50 Amazon EC2 m4.xlarge nodes cluster; (b) 4 in-house nodes cluster with 128GB memory and 32 cores per node.
-We run the Terasort as an experimental application on a Hadoop MapReduce framework.
+% We run the Terasort as an experimental application on a Hadoop MapReduce framework.
 % We deployed Hadoop with SCache and without SCache in both environments.
-
-Table \ref{table1} shows the results of the FRQ model in the in-house environment.
+To evaluate the FRQ model, we run Terasort with Hadoop MapReduce with two different environments and use the FRQ to model the jobs.
 % The workload is from 16 GB to 64 GB. 
-\(D\) and \(N\) are set according to the application parameters.
-We calculate \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
-We set \(K\) to 0.5 and 0.6, which reflects that \(T_{P\_Shuffle}\) has less impact on the reduce phase when enabling SCache.
+% \(D\) and \(N\) are set according to the application parameters. We set \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
+The parameters \(D\), \(N\), \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are set according to the application and the environment.
+We set \(K\) to 0.5 and 0.6 since SCache alleviates the defect on the reduce phase
+Table \ref{table1} shows the results in the in-house environment.
 % The formulas of \(T_{Job}, T_{Map}, T_{Reduce}\) and \(T_{Shuffle}\) are according to Equation \ref{equation_Tjob}, Equation \ref{equation_Tmap}, Equation \ref{equation_Treduce} and Equation \ref{equation_Tshuffle}, respectively.
-In the Hadoop with SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
+While enabling SCache, Terasort satisfies the situation in Figure \ref{fig:model_basic} (\(V_{Map} \times R \ge V_{Shuffle}\)). 
 % thus the formula of \(T_{P\_Shuffle}\) is Equation \ref{equation_Tpshuffle1}.
-In the original Hadoop, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
-\(ExpT_{Job}\) represents the actual experiment data, we calculate \(Error\) according to \(T_{Job}\) and \(ExpT_{Job}\).
+While without SCache, \(T_{P\_Shuffle}\) is equal to \(T_{Shuffle}\)(see Equation \ref{equation_Tmap}).
+\(ExpT_{Job}\) represents the actual experiment job times and
+\(Error\) represents the error between \(T_{Job}\) and \(ExpT_{Job}\). 
 % The formula of \(Error\) is:
@@
 % \end{equation}
-
 Table \ref{table2} shows the results in Amazon EC2 environment.
 % \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
-We set K to the same empirical value.
+% We set K to the same value.
 % The formulas in the table are all the same except \(T_{P\_Shuffle}\).
@@
 
-Regarding accuracy, the experimental values are all larger than the calculated values.
+As shown in Table \ref{table1}\&\ref{table2}, the experimental values are all larger than the calculated values.
 This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc.
@@
 This overhead will be amplified when the input data is small or the total execution time is short. 
-Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. Therefore, we believe that the FRQ model can accurately describe DAG frameworks.
+Overall, the error between \(T_{Job}\) and \(ExpT_{Job}\) is mainly below 10\%, such errors are acceptable. 
+% We believe that the FRQ model can accurately describe DAG frameworks.
 }
@@
 	\hline
-	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
+	% & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
 	SCache
@@
 	\hline
-	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
+	% & 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
 	Legacy
@@
 \end{table*}
+
 % \subsection{Performance Analysis}\label{model_performance_analysis}
@@
 % \begin{table*}[!t]
+
 \begin{table*}

### 2019-09-11 scache/tii/tex/intro.tex
Fix the typo provided by JungleX

@@
 During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
-Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
+Using distributed computing frameworks to analyze industrial big data is an inevitable trend \cite{lee2014service}.
 % \cite{ibmreport}.
@@
 % Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
-% Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
+% Several sophisticated frameworks are used in industrial big data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
 % The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
 % Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
-Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
+Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
 }
@@
 {\color{black}
-According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size.
+According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size.
 According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
@@
 % And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
-And the \textit{shuffle read} fetches intermediate results from remote disks through network. 
+And the \textit{shuffle read} fetches intermediate results from remote disks through the network. 
 Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and \textit{slot}s are released only after the task finishes.
@@
 % We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
-% In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
+% In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big data analysis by revealing the relationships between the various phases (Section \ref{model}).
 % }

### 2019-09-11 scache/tii/tex/model.tex
Fix the typo provided by JungleX

@@
 The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
-The FRQ model use these overlaps to describe different scheduling strategies.
+The FRQ model uses these overlaps to describe different scheduling strategies.
 For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
@@
 % As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
-Firstly, we introduces five input parameters of the FRQ model:
+Firstly, we introduce five input parameters of the FRQ model:
 }
@@
 Figure \ref{fig:model_basic} and Figure \ref{fig:model_scache2} show the scheduling strategy for Hadoop MapReduce with SCache (Suppose N is 4).
-SCache also overlap the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
+SCache also overlaps the shuffle phase and the map phases by starting pre-fetching and pre-scheduling in the map phase.
 This scheduling strategy avoids the I/O resource being idle in the map phase.

### 2019-09-11 scache/tii/tex/optimization.tex
Fix the typo provided by JungleX

@@
 \label{opt}
-This section presents the detailed methodologies to achieve shuffle optimization. 
+This section presents detailed methodologies to achieve shuffle optimization. 
 {\color{blue}
@@
 In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
-And we propose the pre-scheduling and pre-fetching to hide shuffle overhead into multi-round map tasks.
+And we propose the pre-scheduling and pre-fetching to hide shuffle overhead in multi-round map tasks.
 Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
@@
 In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
-For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce phase.
+For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
 In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
@@
 
-SCache takes over all shuffle data and keep them on the memory instead of storing on disk liked the DAG frameworks.
+SCache takes over all shuffle data and keeps them on the memory instead of storing on disk liked the DAG frameworks.
 In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
@@
 
-\subsubsection{Problem of Random Mapping}\label{randomassign}
+\subsubsection{Random Mapping Problem}\label{randomassign}
 {\color{blue}
@@
 The performance of random mapping drops as the round number grows. 
-This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
+This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
 Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
-In addition, randomly mapping also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
+In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
 }
@@
 The observed map outputs are picked randomly. 
-The job uses the Spark RangePartitioner and introduce an extreme high data skew.
-Due to the extreme high data skew introducing by the partition, linear regression model cannot fit the result well.
+The job uses the Spark RangePartitioner and introduces an extremely high data skew.
+Due to the extremely high data skew introducing by the partition, the linear regression model cannot fit the result well.
 % The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
@@
 When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
-After scheduling, if the new $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
 This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 

### 2019-09-11 scache/tii/tex/relatedwork.tex
Fix the typo provided by JungleX

@@
 % Different from these models, our FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. 
-The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
+% The FRQ model focuses on describing the overhead caused by the shuffle process in different scheduling strategies, which satisfies our demand.
 
-\textbf{Industrial big-data.}
-% In the \textit{Industry 4.0} which leading by the German Government, industrial big-data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
-Industrial big-data refers to huge time-series data generated by industrial equipment in smart factories.
+\textbf{Industrial big data.}
+% In the \textit{Industry 4.0} which leading by the German Government, industrial big data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
+Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
 More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
-Nowadays, the real challenge of big-data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
-Several distributed computing frameworks become efficient tools in industrial big-data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
+Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
+Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
 }

### 2019-09-13 scache/tii/tex/conclusion.tex
Fix the typo provided by JungleX
Revision

@@
 \section{Conclusion}\label{conclusion}
-In this paper, we present SCache, a cross-framework shuffle optimization for DAG computing frameworks. 
-SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
-By task pre-scheduling and shuffle data pre-fetching with application context, SCache significantly mitigates the shuffle overhead. 
+In this paper, we present SCache, a plug-in shuffle optimization for DAG computing frameworks. 
+% SCache decouples the shuffle from computing tasks and leverages memory to store shuffle data. 
+By task pre-scheduling and shuffle data pre-fetching with application context, SCache decouples the shuffle from computing tasks and mitigates the shuffle overhead. 
 %  {\color{red}
@@
 % Our evaluations on Spark and Hadoop MapReduce with SCache show that SCache can provide a promising speedup. 
-% The benchmark using in evaluations covers the most situations of industrial big-data analysis.
-The evaluations show that SCache can provide a promising speedup in both traditional and industrial big-data workloads. 
-Furthermore, we propose \textit{Framework Resources Quantification} (FRQ) model to assist in analyzing shuffle process of DAG computing frameworks. 
+% The benchmark using in evaluations covers the most situations of industrial big data analysis.
+We also propose \textit{Framework Resources Quantification} (FRQ) model to evaluate the shuffle process of DAG computing frameworks. 
+The evaluations show that SCache can provide a promising speedup in industrial production workloads. 
 % At last, we evaluate the SCache shuffle optimization by the FRQ model.

### 2019-09-13 scache/tii/tex/evaluation.tex
Revision

@@
 The shuffle configuration of Spark is set to the default\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}. 
-We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2\footnote{http://aws.amazon.com/ec2/}. 
+We run the experiments on a 50-node m4.xlarge cluster on Amazon EC2.
+% \footnote{http://aws.amazon.com/ec2/}. 
 Each node has 16GB memory and 4 CPUs.
@@
 
-As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
+As shown in Figure \ref{fig:hadoop_terasort_origin}, Hadoop MapReduce without SCache starts shuffle and reduce simultaneously.
+% writes intermediate data locally in the map phase and the shuffle phase and the reduce phase start simultaneously.
 The beginning part of reduce phase needs to wait for network transfer because a large amount of shuffle data reaches the network bottleneck.
 This causes the CPU resources to be idle. 
-On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache starts pre-fetching in the map phase.
-This avoids the reduce phase waiting for the shuffle data.
-Furthermore, pre-fetching utilizes the idle I/O throughput in the map phase.
-As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling shuffle, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
+On the other hand, in Figure \ref{fig:hadoop_terasort_scache}, Hadoop MapReduce with SCache decouples shuffle from reduce and starts pre-fetching in the map phase.
+% This avoids the reduce phase waiting for the shuffle data.
+SCache utilizes the idle I/O throughput in the map phase.
+As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
 }
@@
 
-\begin{figure}
-    \centering
-    \begin{minipage}{0.4\textwidth}
-        \centering
-        \includegraphics[width=.8\linewidth]{fig/hadoop_terasort_time} % first figure itself
-        \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
-		\label{fig:hadoop_terasort_time}
-    \end{minipage}\hfill
-    % \begin{minipage}{0.4\textwidth}
-    %     \centering
-    %     \includegraphics[width=.8\linewidth]{fig/sampling} % second figure itself
-    %     \caption{Sampling Overhead}
-	% 	\label{fig:sampling}
-    % \end{minipage}
-\end{figure}
-
 \subsection{The FRQ Model Evaluation}\label{model_evaluation}
@@
 % We deployed Hadoop with SCache and without SCache in both environments.
-To evaluate the FRQ model, we run Terasort with Hadoop MapReduce with two different environments and use the FRQ to model the jobs.
+To evaluate the FRQ model, we run Terasort with Hadoop MapReduce with two different environments.
+%  and use the FRQ to model the jobs.
 % The workload is from 16 GB to 64 GB. 
@@
 % \end{equation}
-Table \ref{table2} shows the results in Amazon EC2 environment.
+Table \ref{table2} shows the results in Amazon EC2.
 % \;\(V_{Map}, V_{Shuffle},\) and \(V_{Reduce}\) are modified because of the different hardware devices.
@@
 
+\begin{figure}
+    \centering
+    \begin{minipage}{0.4\textwidth}
+        \centering
+        \includegraphics[width=.8\linewidth]{fig/hadoop_terasort_time} % first figure itself
+        \caption{\color{black}Hadoop MapReduce Terasort Completion Time}
+		\label{fig:hadoop_terasort_time}
+    \end{minipage}\hfill
+    % \begin{minipage}{0.4\textwidth}
+    %     \centering
+    %     \includegraphics[width=.8\linewidth]{fig/sampling} % second figure itself
+    %     \caption{Sampling Overhead}
+	% 	\label{fig:sampling}
+    % \end{minipage}
+\end{figure}
+
 \begin{table*}
 \centering
-\scalebox{0.95}{
+\scalebox{0.85}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 	SCache
-	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
-	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
-	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
+	& 32 GB & 1	& 4 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	49.23 &		68.09  s &	31.16 s &	47.58 s &	96.81	s & 104 s & 	6.91\% \\
+	& 48 GB	& 1	& 6 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	73.85 &		102.13 s &	40.59 s &	68.29 s &	142.14	s & 151 s & 	5.87\% \\
+	& 64 GB	& 1	& 8 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	98.46 &		136.17 s &	50.02 s &	89.01 s &	187.47	s & 193 s & 	2.87\% \\
 	\hline
-	% & 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
+	% & 16	& 1 & 2 &	0.65 GB/s &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
 	Legacy
-	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
-	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
-	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
+	& 32 GB	& 1 & 4 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	49.23 s &		68.09 s &	68.09 s		&	72.85	s &	122.08 s	&	135 s	&	9.57\%	\\
+	& 48 GB	& 1 & 6 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	73.85 s &		102.13 s &	102.13 s	&	109.28	s &	183.12 s	&	188 s	&	2.59\%	\\
+	& 64 GB	& 1 & 8 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	98.46 s &		136.17 s &	136.17 s	&	145.70	s &	244.16 s	&	249 s	&	1.94\%	\\
 	\hline
@@
 }
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
 \caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
@@
 \centering
-\scalebox{0.95}{
+\scalebox{0.85}{
 	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
@@
 	\hline
-	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
 	SCache
-	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
-	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
-	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
+	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
+	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
+	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
+	% & 512	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
 	\hline
-	& 128	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	111.30 &	91.43	&	91.43	&	142.53	&	253.83	&	266 &	4.57\%	\\
 	Legacy
-	& 256	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	222.61 &	182.86	&	182.86	&	285.06	&	507.67	&	524 &	3.12\%	\\
-	& 384	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	333.91 &	274.29	&	274.29	&	427.59	&	761.50	&	776 &	1.87\%	\\
+	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	111.30 s &	91.43	s &	91.43	s &	142.53	s &	253.83	s &	266 s &	4.57\%	\\
+	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	222.61 s &	182.86	s &	182.86	s &	285.06	s &	507.67	s &	524 s &	3.12\%	\\
+	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	333.91 s &	274.29	s &	274.29	s &	427.59	s &	761.50	s &	776 s &	1.87\%	\\
 	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
@@
 }
-\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
 \caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}

### 2019-09-13 scache/tii/tex/impl.tex
Revision

@@
 % After that, the slot will be released (without being blocked on disk operations).
-The SCahce records the block ID and the size and sends them to the master.
+The SCache records the block ID and the size and sends them to the master.
 % When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
@@
 If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
-After pre-scheduling, SCahce workers start pre-fetching shuffle blocks according to the assignment from the master.
+After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
 To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
@@
 As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
-If one of the task in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
+If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
 % If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 

### 2019-09-13 scache/tii/tex/model.tex
Revision

@@
 
-In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
+In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to evaluate the performance of DAG frameworks.
 % The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
-In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
+The FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
 % The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
-We first introduce the FRQ model in Subsection \ref{model_overview}.
-In the following Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
+We first introduce the FRQ model in Subsection \ref{model_overview}. In Subsection \ref{model_analysis}, we use the FRQ model to describe different computation jobs and discuss their performance.
 % In the last Subsection \ref{model_evaluation}, we use the actual experimental results to evaluate the FRQ model.
@@
 We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
-The FRQ model focuses on describing the overhead caused by the shuffle process.
-This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
+% The FRQ model focuses on describing the overhead caused by the shuffle process.
+The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
+% This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
 % By using the FRQ model, we can analyze the advantages of each strategy in various situations.
-After quantifying computing and I/O resources, the FRQ model can evaluate different resource scheduling strategies by using different formulas.
+After quantifying computing and I/O resources, we use the FRQ model to evaluate different resource scheduling strategies.
 % For convenience, we introduce the FRQ model by taking a simple MapReduce job as an example in this section.
 
-Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
+% Figure \ref{fig:model_basic} shows how the FRQ model describes a MapReduce job. 
 As Figure \ref{fig:model_basic} shows, the FRQ model divides the job into three phases: map, shuffle, and reduce.
-The horizontal axis represents time and the overlaps between phases represent they execute in parallel.
-The FRQ model uses these overlaps to describe different scheduling strategies.
-For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
-And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
-
+The horizontal axis represents time and the vertical axis represents different phases.
 % As shown in Figure \ref{fig:model_basic}, the FRQ model introduce five parameters:
@@
 	\includegraphics[width=\linewidth]{fig/model_hadoop}
-	\caption{\color{black}The FRQ Model with Half Parallel MapReduce}
+	\caption{\color{black}Framework Resources Quantification Model with Half Parallel MapReduce}
 	\label{fig:model_hadoop}
 \end{figure}
+
+% The FRQ model uses these overlaps to describe different scheduling strategies.
+{\color{blue}
+Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
+The FRQ model needs to know the start time of each phases.
+For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
+And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
+}
 
@@
 
-\subsection{Model Analysis}\label{model_analysis}
+\subsection{Different Scheduling Strategies on the FRQ Model}\label{model_analysis}
 

### 2019-09-13 scache/tii/tex/optimization.tex
Revision

@@
 % Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.6\linewidth]{fig/sim} % second figure itself
-	\caption{Stage Completion Time Improvement of OpenCloud Trace}
-	\label{fig:sim}
-\end{figure}
 
@@
 \end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[width=.6\linewidth]{fig/sim} % second figure itself
+	\caption{Stage Completion Time Improvement of OpenCloud Trace}
+	\label{fig:sim}
+\end{figure}
 
@@
 In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
-On the reduce side, the shuffle data transfer introduces an explicit overhead during shuffle read.
-Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
-Furthermore, because all reduce tasks start shuffle read simultaneously, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.
+On the reduce side, shuffle introduces an explicit overhead during shuffle read.
+% Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
+% because all reduce tasks start shuffle read simultaneously, 
+Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.
 
@@
 % In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
-To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce phase to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data.
-To achieve this optimization:
+To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data. To achieve this optimization:
 \begin{itemize}
@@
 To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
-SCache provides two APIs named $putBlock$ and $putBlock$ to manage the shuffle data.
-On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache instead of keeping them on local storage.
+SCache provides two APIs named $putBlock$ and $getBlock$ to manage the shuffle data.
+On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache.
+%  instead of keeping them on local storage.
 Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
-SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
+After getting the shuffle data, SCache starts to shuffling data immediately.
+% SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
 % SCache leverages the property of multi-round tasks to 
-On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from the local memory of SCache.
+On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from SCache.
 
-SCache takes over all shuffle data and keeps them on the memory instead of storing on disk liked the DAG frameworks.
+SCache cache the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
 In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
@@
 The pre-scheduling and pre-fetching are the most critical aspects of the optimization.
-Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
-Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
+% Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
+% Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
 SCache starts pre-fetching and hides shuffle overhead into multi-round map tasks.
 However, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
-To pre-scheduling the mapping, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
+
+To optimize shuffle phase, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
 The DAG frameworks follow the co-scheduler to starts reduce tasks.
@@
 
-\subsubsection{Random Mapping Problem}\label{randomassign}
-{\color{blue}
-% Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
-To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
-We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
-The performance of random mapping drops as the round number grows. 
-This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
-Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
-In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
-}
+% \subsubsection{Random Mapping Problem}\label{randomassign}
+% {\color{blue}
+% % Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
+% To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+% We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
+% The performance of random mapping drops as the round number grows. 
+% This is because the data skew commonly exists in data-parallel computing \cite{skewtune}. 
+% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
+% In addition, randomly mapping also ignores the data locality between shuffle map output and reduce input, which may introduce extra network traffic in the cluster.
+% }
 % The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
@@
 {\color{blue}
-The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
+% The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
+The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly.
+But without considering job context, the random mapping scheduling shows poor performance due to data skew and ignoring data locality.
 For the most DAG applications with random large scale input, 
@@
 % Note that sampling does not consume the input data of map tasks. 
-The $BlockSize_{ji}$ can be calculated by:
+% The $BlockSize_{ji}$ can be calculated by:
+$BlockSize_{ji}$ represents the size of block which is produced by map $task_j$ for reduce $task_i$:
 \begin{equation}
@@
 \end{equation}
-This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
+% Note that a balanced schedule decision can be made under the consideration of the size of each reduce task, and the size of a reduce task produced by one shuffle $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$,
+% where the $m$ is the number of map tasks that can be easily extracted from DAG information;
+The $reduceSize_i$ represents the size of a reduce task, which is represented by $reduceSize_i = \sum_{j=0}^{m} {BlockSize_{ji}}$.
+We use $prob_i$ to achieve a better data locality while performing shuffle pre-scheduling. 
+% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
+
+\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
+% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
+% But ignoring the data locality can introduce extra network transfer. 
+% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
+To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
+{\color{blue}
+% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
+We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+Spark FIFO only can achieve $2\text{-}approximation$ optimum.
+}
+% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
+After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
+The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
+Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
+Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
+Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
+
+{\color{blue}
+To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+As shown in Figure \ref{fig:sim}, we run the simulation under three scheduling schemes: Random Mapping, Spark FIFO, and heuristic MinHeap.
+After balancing load based on the job context (e.g.
+shuffle size, data locality), \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than Spark (average 2.7\%) and Random Mapping.
+%  (becomes negative after the round one).
+}
 
@@
 
-\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
-% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
-% But ignoring the data locality can introduce extra network transfer. 
-% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
-To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
-{\color{blue}
-% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
-To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.2., line $6-11$).
-We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
-Spark FIFO only can achieve $2\text{-}approximation$ optimum.
-}
-% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
-The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
-Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
-Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
-
-{\color{blue}
-As shown in Figure \ref{fig:sim}, \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
-}
-
-\subsubsection{Cope with Multiple Shuffle Dependencies}
-{\color{black}
-A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
-To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
-}
-% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-% For those pending shuffles, it is impossible to predict their sizes. 
-% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-% But doing this introduces large overhead such as extra task serialization. 
-% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
-After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
-This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
-which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
-
-To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.
-
 \begin{minipage}{0.95\columnwidth}
@@
 \end{minipage}
+
+\subsubsection{Cope with Multiple Shuffle Dependencies}
+{\color{black}
+A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
+To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
+}
+% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+% For those pending shuffles, it is impossible to predict their sizes. 
+% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+% But doing this introduces large overhead such as extra task serialization. 
+% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
+After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
+which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
+
+To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.

### 2019-09-13 scache/tii/tex/relatedwork.tex
Revision

@@
 % In the \textit{Industry 4.0} which leading by the German Government, industrial big data refers to a huge amount of time-series data which generated by industrial equipment in smart factories.
-Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
+% Industrial big data refers to huge time-series data generated by industrial equipment in smart factories.
 More than 1000 Exabytes industrial data is annually generated by smart factories and the data is expected to increase 20-fold in the next ten years \cite{yin2015big}.
 Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
-Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
+Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific}.
+% , ur2018big}.
 }
@@
 \textbf{DAG Optimization.} 
-There are a number of studies on DAG optimization.
-Slow-start from Apache Hadoop MapReduce is a classic approach to handle shuffle overhead. 
+% There are a number of studies on DAG optimization.
+Slow-start from Hadoop MapReduce is a classic approach to handle shuffle overhead. 
 Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
-DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
+% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
 % All of them have the explicit I/O time in occupied slots. 
@@
 % Besides \textit{slow-start} from Hadoop MapReduce, \cite{starfish, ihadoop, guo2017ishuffle, dynmr} have also proposed several methods to improve the DAG frameworks.
-However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
+% However, we have proved that randomly assigned tasks may hurt the overall performance in Section \ref{randomassign}. 
 In data skew mitigation, 
@@
 % But moving data may cause extra I/O overhead in computing.
-LIBRA \cite{chen2014libra} proposed a new sampling method for DAG frameworks.
-Based on this sampling method, it uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
+LIBRA \cite{chen2014libra} proposes a new sampling method for DAG frameworks and uses an innovative approach, which supports the split of large keys, to balance the load among the reduce tasks.
 ToF \cite{zhou2014transformation} proposed a DAG optimization system to address the performance and monetary cost optimizations in the cloud.

### 2019-09-14 scache/tii/tex/impl.tex
Remove blue words

@@
 % At last, we discuss the cost of adapting SCache and fault tolerance. 
-{\color{blue}
+{\color{black}
 In Subsection \ref{fault}, we discuss the fault tolerance of the system.
@@
 \subsection{System Overview}\label{arch}
-{\color{blue}
+{\color{black}
 As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
@@
 % As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
-{\color{blue}
+{\color{black}
 SCache uses bellowed memory management to ensure performance.
@@
 % This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
-{\color{blue}
+{\color{black}
 % Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
@@
 
-{\color{blue}
+{\color{black}
 \subsection{Discussion of Fault Tolerance}\label{fault}

### 2019-09-14 scache/tii/tex/model.tex
Remove blue words

@@
 % A shuffle phase is required between each adjacent DAG computation phases.
-{\color{blue}
+{\color{black}
 We propose the FRQ model to better analyze the relationship between the computation phase and the shuffle phase in the DAG computing.
@@
 % The FRQ model uses these overlaps to describe different scheduling strategies.
-{\color{blue}
+{\color{black}
 Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
@@
 
-{\color{blue}
+{\color{black}
 \(\frac{D \times R}{V_{Reduce}}\) represents the ideal computation time of a reduce phase, and (\(K \times T_{P\_Shuffle}\)) represents the computing overhead.

### 2019-09-14 scache/tii/tex/optimization.tex
Remove blue words

@@
 This section presents detailed methodologies to achieve shuffle optimization. 
-{\color{blue}
+{\color{black}
 Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
@@
 
-{\color{blue}
+{\color{black}
 \subsection{Observations}\label{observation}
@@
 \subsection{Decouple Shuffle from Execution}
-{\color{blue}
+{\color{black}
 To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
@@
 % \subsection{Pre-scheduling with Application Context}
-{\color{blue}
+{\color{black}
 \subsection{Pre-scheduling and Pre-fetching Shuffle Data}
@@
 % \subsubsection{Random Mapping Problem}\label{randomassign}
-% {\color{blue}
+% {\color{black}
 % % Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
@@
 \subsubsection{Shuffle Output Prediction}\label{shuffleprediction}
-{\color{blue}
+{\color{black}
 % The problem of random mapping is obviously caused by application context (e.g., shuffle data size) ignorance. 
@@
 To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
-{\color{blue}
+{\color{black}
 % For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
@@
 
-{\color{blue}
+{\color{black}
 To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.

### 2019-09-15 scache/tii/response_letter.md
Resubmittion version

# Response to Reviewers

Dear Editor and Reviewers,

Thank you for the reviewers’ comments concerning our manuscript entitled *“Efficient Shuffle Management for DAG Computing Frameworks Based on the FRQ Model”* (ID TII-19-1638).
Those comments are all valuable and helpful for revising and improving our paper.
We have studied the comments carefully and have made our best to improve the paper.
The main corrections in the paper and the responses to the reviewer’s comments are as following:

### List of Revisions

1. We add a new subsection about fault tolerance in the Implementation Section.
2. We extend the related work Section and add more discussion about shuffle optimization and DAG scheduling.
3. We add new content and modify each subsection in Section II to better detail the shuffle optimization.
4. We modify some paragraphs and add some new ones in Section 5 to better explain the FRQ model.
5. We update the description of Algorithm 1&2 and also discuss their complexity in Section II.
6. We modify Section V to explain how and why we choose TPC-DS as a standard benchmark to simulate the realistic industrial workload.
7. We modify Subsection V.C to discuss the different performance gain between Spark and Hadoop MapReduce.
8. In addition to the above modifications, we also paraphrase all other parts of the paper to ensure the similarity is low enough.

### Responses to Reviewer #1

<!-- - Discussion about fault tolerant:
   - What happens if some workers fail before reading the shuffle data by getBlock API?
   - Do you need to change the code of MapReduce for guaranteeing the fault tolerance? -->
- **Comment #1:**
    The proposed approach uses the system memory for keeping the shuffle data. But, the impact of this strategy on “fault tolerance” is not clear. What happens if some workers fail before reading the shuffle data by getBlock API? Do you need to change the code of MapReduce for guaranteeing the fault tolerance?

    **Response:** We add a new subsection about fault tolerance in the Implementation Section.
    SCache only restarts failed workers without recovering the data.
    If a failure happens, the *getBlock* API called by DAG frameworks  will return a data not found error. This will cause the DAG frameworks to re-compute the current stage.
    We leave the fault handling to the DAG frameworks.
    As a result, we do not need any changes in MapReduce for guaranteeing the fault tolerance.

- **Comment #2:**
    In Page 4, we read: “After scheduling, if the new assigned id of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host.”. Why the assigned id of a reduce task may be different than the original one? If happened, what is the impact of this re-shuffling on performance?

    **Response:**
    1. In the multi-shuffle dependencies, when a new shuffle starts, the predicted parameters are accumulated with previous shuffles. And then SCache uses these parameters to re-schedule the assignment. Therefore, the new assignment may be different from the original ones.
    2. If re-shuffle happens, it will cause extra data shuffle overhead. But this re-shuffle is rare and can only affect the performance slightly.
    <!-- **Response**: 1.在多轮shuffle的情况下，每当预测完新的shuffle数据分布，新的预测会与先前的结果叠加，算法会重新进行计算。因此有可能出现原本分配的结果不同。
    2.如果re-shuffle发生会产生额外网络开销用于重新传输数据，但是这种情况出现几率很低，我们认为并不会影响整体性能，在实际benchmark实验结果中也没有看到平凡re-shuffle造成的额外网络开销。 -->

- **Comment #3:** I don’t understand why SCache obtains better performance gains in Spark than MapReduce. It is known that Spark is more optimized than MapReduce, so logically there should be less place for more optimizations in Spark than MapReduce. Please discuss this in the paper.

    <!-- different workflow and benchmarks -->
    **Response**:
    The main reason causes the different performance gain in Spark and MapReduce is that they have quite different DAG workflows.
    Unlike Spark's complex DAG computing, Hadoop MapReduce has a simple DAG computing workflow which has only one Map phase and one Reduce phase.
    Such simple DAG of MapReduce alleviates the performance gain of SCache's shuffle data prediction.
    Besides, the Terasort benchmark we used generates input data by its own, which means that heavy data skew is unlikely to happen. 
    Therefore, the performance gain of in MapReduce is mainly rely on SCache' pre-fetching strategy and this is also why we choose Terasort benchmark which is a shuffle-heavy task.
    We also modify Subsection V.C to discuss the different performance gain between Spark and Hadoop MapReduce.
    <!-- **Response**: (较难回答)*根本原因是因为Hadoop实验时的优化在pre-shuffle的数据没有放在Memory，而是放在disk，所以效果没那么明显，只体现了pre-shuffle的优化。而Spark的实验中shuffle数据是in-memory，所以省去了disk读，实验结果不仅体现了pre-shuffle，还体现了in-memory的优化。* -->

- **Comment #4:** I think, the subsection “Model evaluation” should be moved to the “evaluation” Section. If you agree, pleas move it there.

    **Response**: OK, we move the subsection into the Evaluation.

### Responses to Reviewer #2

- **Comment #1&3:** The paper optimizes data shuffling. However, little related work has been reviewed on this dimension. Please check out the below paper and its related papers and review them in related work section.

    - S. Ibrahim, H. Jin, L. Lu, S. Wu, B. He and L. Qi, "LEEN: Locality/Fairness-Aware Key Partitioning for MapReduce in the Cloud," 2010 IEEE Second International Conference on Cloud Computing Technology and Science, Indianapolis, IN, 2010, pp. 17-24.

    DAG-aware scheduling is also a hot research area. The author should review the related work carefully. Below paper is a paper for you to start with.

    - A. C. Zhou and B. He, "Transformation-Based Monetary CostOptimizations for Workflows in the Cloud," in IEEE Transactions on Cloud Computing, vol. 2, no. 1, pp. 85-98, Jan.-March 2014.

    **Response**: We extend the related work Section and add more discussion about shuffle optimization and DAG scheduling.
    We add a new subsection which names _DAG Optimization_.
    In the new subsection, we discuss the related work in shuffle optimization, including slow-start, Starfish [24], iHadoop [26], iShuffle [15], and so on.
    We also discuss some related work about DAG scheduling, including Skewtune [14], LIBRA [27], and ToF [28].

- **Comment #2:** About experiments:
   - it is unclear which versions of Hadoop and Spark are used.
   - please evaluate the scalability of the proposed approach with the number of nodes varied.
   - can you evaluate your approach with more realistic industrial workload besides benchmarks like TPC-DS?

    <!-- big data in industry -> TPC family -> we choose DS -> we believe  -->
    <!-- In industry, big data technologies are widely used on these systems, such as data mining, predictive analytics, text analytics, and statistical analysis. -->
    **Response**: 
    SQL-Based Big Data Systems are widely used in industrial application, such as data mining, predictive analytics, text analytics, and statistical analysis.
    Because of the limited time and resource, we use standard benchmark instead of realistic industrial workload to evaluate SCache.
    TPC-DS models queries and data maintenance of a retail product supplier and provide a representative evaluation of performance.
    We believe using TPC-DS is able to evaluate the performance of SCache in industry.
    We also modify the first paragraph of Section V to explain how and why we choose TPC-DS as a standard benchmark to simulate the realistic industrial workload.

### Responses to Reviewer #3

- **Comment #1:** The shuffle optimization is an important contribution in this work. In particular, it is interesting to present the detailed mathematical problem formulation regarding the shuffle optimization. Thus, could this paper provide a detailed mathematical optimization framework in Section II regarding the shuffle optimization, e.g., by specifying the detailed objective function and the constraints?

    **Response**: We add new content and modify each subsection in Section II to better detail the shuffle optimization. We first discuss the reason which causes the shuffle overhead.
    Then we detail our _Heuristic MinHeap Scheduling_ algorithm with mathematical formulas and explain how we mitigate the overhead.
    <!-- We propose the _Heuristic MinHeap Scheduling_ algorithm to predict shuffle and do pre-scheduling. -->
    <!-- Then we present how we use proposed methodologies to mitigate the overhead. -->
    <!-- , so that gain the optimization. -->
- **Comment #2:** It will be more convincing if the paper could discuss the complexity of Algorithm 1 and Algorithm 2 in Section II.

    **Response**: We update the description of Algorithm 1&2 and also discuss their complexity in Section II. 
    For Algorithm 1, the algorithm needs *O(n)* operations because it maintains a min-heap and traverses *reduce* for swapping.
    For Algorithm 2, the algorithm also needs *O(n)* operations because it only traverses *reduce* for accumulating previous *shuffle* and re-shuffling data.

- **Comment #3:** The proposed FRQ model (for evaluating the performance of DAG frameworks) in Figure 5 needs more explanations. In particular, what the rationale behind the proposed FRQ model? How can it fit the requirements for evaluating the proposed SCache? More explanations are thus required.

   **Response**: As discussed in the paper, the FRQ model focuses on describing the shuffle overhead which is significantly affected by the scheduling strategy.
   <!-- This overhead not only depends on the input data size, computation speed and other parameters but also on which scheduling strategy it takes. -->
   By using the FRQ model, we can analyze the advantages of each strategy in various situations.
   Take the pre-fetching strategy in SCache as an example, the FRQ model shows that pre-fetching can get better performance than the original Hadoop MapReduce strategy by reducing T<sub>P_Shuffle</sub>.
   We also modify some paragraphs and add some new ones in Section 5 to better explain the FRQ model.

### Responses to Reviewer #4

- **Comment #1:** Although authors declare that this is an extended paper, there is a high similarity score (roughly 50%) with previous published papers. This score is too high and must be reduced before to reconsider the paper.

     **Response**: To ensure the similarity is low enough, we paraphrase all other parts of the paper, including Introduction, Optimization, and Implementation.

We have tried our best to improve the manuscript and make sure these changes will not influence the content and framework of the paper.
We appreciate for Editors/Reviewers’ warm work earnestly, and hope that the correction will meet with approval.

Once again, thank you very much for your comments and suggestions.

### 2019-09-15 scache/tii/tex/evaluation.tex
Remove blue words
Resubmittion version

@@
 % This section reveals the evaluation of SCache with comprehensive workloads and benchmarks which include common operations in the industrial big data analysis. 
-{\color{blue}
+{\color{black}
 This section reveals a representative evaluation of SCache performance on both Spark and Hadoop MapReduce.
@@
 we evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/}.
-TPC-DS is a standard benchmark which focus on modeling industrial workload.
+TPC-DS is a standard benchmark which focuses on modeling industrial workload.
 % TPC-DS, TPCx-BB, HiBench, BigDataBenchmark, and so on are popular standard big data benchmarks which evaluate big data systems.
@@
 Each node has 16GB memory and 4 CPUs.
-The network bandwidth each node is about 300 Mbps.
+The network bandwidth of each node is about 300 Mbps.
 % The network bandwidth provided by Amazon is insufficient. 
@@
 
-{\color{blue}
+{\color{black}
 % To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
@@
 % \(D\) and \(N\) are set according to the application parameters. We set \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) according to the environment.
-The parameters \(D\), \(N\), \(R, V_{Map}, V_{Shuffle},\)and \(V_{Reduce}\) are set according to the application and the environment.
-We set \(K\) to 0.5 and 0.6 since SCache alleviates the defect on the reduce phase
+The parameters \(D\), \(N\), \(R\), \(V_{Map}\), \(V_{Shuffle}\), and \(V_{Reduce}\) are set according to the application and the environment.
+We set \(K\) to 0.5 and 0.6 since SCache alleviates the defect on the reduce phase.
 Table \ref{table1} shows the results in the in-house environment.

### 2019-09-15 scache/tii/tex/impl.tex
Resubmittion version

@@
 % After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
-After a map task finishes computing, the shuffle writes in the map task is modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
+After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
 % After that, the slot will be released (without being blocked on disk operations).

### 2019-09-15 scache/tii/tex/intro.tex
Revision
Remove blue words
Resubmittion version

@@
 The workflow of a DAG framework with SCache is presented in Figure \ref{fig:workflow}. 
-SCache replaces the disk operations of shuffle write by the memory copy in map tasks and pre-fetch the shuffle data.
+SCache replaces the disk operations of shuffle write by the memory copy in map tasks and pre-fetches the shuffle data.
 % Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
@@
 The rest of the paper is organized as follows:
-{\color{blue}
+{\color{black}
 % We discuss the opportunities to optimize shuffle in Section \ref{motivation}.
@@
 % The performance of SCache is evaluated with both simulations and test-bed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop.
-% We evaluate SCahce in three different benchmarks, including a standardized industry benchmark --- TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+% We evaluate SCache in three different benchmarks, including a standardized industry benchmark --- TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
 % % On Apache Spark, we conduct a basic test - \textit{GroupByTest}.

### 2019-09-15 scache/tii/tex/model.tex
Resubmittion version

@@
 % The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension.
-The FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc.
+The FRQ model is able to predict the execution time required by the application under most circumstances, including different DAG frameworks, hardware environments, etc.
 % The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance.
@@
 % The FRQ model focuses on describing the overhead caused by the shuffle process.
-The FRQ model focuses on describing the shuffle overhead which significantly effected by the scheduling strategy.
+The FRQ model focuses on describing the shuffle overhead which is significantly affected by the scheduling strategy.
 % This overhead does not only depends on the input data size, computation speed, complexity of algorithms, and other parameters but also on which scheduling strategy the job takes.
@@
 
-The formulas of map phase time and shuffle phase time are as follow:
+The formulas of map phase time and shuffle phase time are as follows:
 % \(T_{Map}={{\frac{D}{V_{Map}}}}\).

### 2019-09-15 scache/tii/tex/optimization.tex
Resubmittion version

@@
 For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
-In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
+In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
 On the reduce side, shuffle introduces an explicit overhead during shuffle read.
@@
 % because all reduce tasks start shuffle read simultaneously, 
-Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.
+Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.
 
@@
 % In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
-To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data. To achieve this optimization:
+To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
 \begin{itemize}
@@
 
-SCache cache the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
+SCache caches the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
 In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
@@
 To optimize shuffle phase, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
-The DAG frameworks follow the co-scheduler to starts reduce tasks.
+The DAG frameworks follow the co-scheduler to start reduce tasks.
 }
@@
 For example, some customized partitions may cause large inconsistency between observed map output distribution and the final reduce input distribution. 
-To illustrate the case, we present a particular spark job which using the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 
+To illustrate the case, we present a particular spark job which uses the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 
 The observed map outputs are picked randomly. 
 The job uses the Spark RangePartitioner and introduces an extremely high data skew.
-Due to the extremely high data skew introducing by the partition, the linear regression model cannot fit the result well.
+Due to the extremely high data skew introduced by the partition, the linear regression model cannot fit the result well.
 % The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew.
@@
 }
-During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
+During both predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
 \begin{equation}
@@
 \begin{aligned}
-	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
+	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{ji}}{reduceSize_i} \\
 	m &= \text{number of map tasks}
@@
 To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
-We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+We use the min-heap to simulate the load of each node and apply the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
 Spark FIFO only can achieve $2\text{-}approximation$ optimum.
@@
 			\EndIf
-		\EndFor
+		\EndFor\newline
 		\Return $M$
@@
 		\State of $reduce$ without exceeding the $upper\_bound$
-		\State of both nodes.
-		\State Return if it is impossible.
+		\State of both nodes.\newline
+		% \State Return if it is impossible.
+		\Return
 	\EndProcedure
@@
 When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
-After scheduling, if the newly $assigned\_id$ of a reduce task did not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
 This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 

### 2019-09-15 scache/tii/tex/relatedwork.tex
Remove blue words
Resubmittion version

@@
 % The set of performance models describe each above-mentioned phases and combine into an overall MapReduce job model. 
-Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then 
-% provisions the resources for the job.
-Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and try to optimize them. 
+Chen et al. \cite{chen2014cresp} proposed the CRESP model which is a cost model that estimates the performance of a job then provisions the resources for the job.
+Farshid Farhat et al.\cite{farhat2016stochastic} proposed a closed-form queuing model which focuses on stragglers and tries to optimize them. 
 % The proposed model is parameterized by the task inter-arrival times to the mappers, the delayed tailed service times, and the number of mappers, which is used to optimize the stragglers. 
@@
 Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently \cite{lv2017next}.
-Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific}.
-% , ur2018big}.
+Several distributed computing frameworks become efficient tools in industrial big data analysis \cite{lade2017manufacturing, li2016scientific, ur2018big}.
 }
 
-{\color{blue}
+{\color{black}
 \textbf{DAG Optimization.} 

### 2020-04-02 scache/jpdc/highlights/highlights.tex
jpdc

\documentclass[12pt,reqno]{amsart}
\setlength{\hoffset}{-.5in}
\setlength{\voffset}{-.25in}
\usepackage{amssymb,latexsym}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{cancel}
\usepackage{url}
\usepackage{amssymb,amsmath,psfrag}
\usepackage{enumerate}
\newcommand\BD{\mathrm{B}}
\newcommand\SD{\mathrm{S}}
\textwidth=6.175in
\textheight=8.5in

\theoremstyle{plain}
\numberwithin{equation}{section}
\newtheorem{thm}{Theorem}[section]
\newtheorem{theorem}[thm]{Theorem}

\theoremstyle{plain}
\numberwithin{equation}{section}

\title{Highlights}

\author{Rui Ren}
\author{Chunghsuan Wu}
\author{Zhouwang Fu}
\author{Tao Song}
\author{Yanqiang Liu}
\author{Zhengwei Qi}
\author{Haibing Guan}

\begin{document}

\maketitle

In large-scale data-parallel analytics, the shuffle phase is crucial and heavily affecting the end-to-end application performance.
To reduce shuffle overhead, we present \textit{SCache}, an open-source plug-in system that particularly focuses on shuffle optimization.
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG computing frameworks and evaluate the SCache shuffle optimization. 
The main contributions of this manuscript are:
\begin{enumerate}
    \item 
    SCache decouples the shuffle write and read from both map and reduce tasks.
    Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
    \item
    SCache pre-schedules the reduce tasks without launching them and pre-fetches the shuffle data. 
    Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
    and avoid the extra early allocation of slots.
    \item
    The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension.
    We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
    \item
    The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
    Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
\end{enumerate}

In summary, we propose a new data processing solution for the big data analytics and a new performance model.
We believe that the content makes a sufficient contribution to this journal submission.

% \bibliographystyle{IEEEtran}
% \bibliography{coverletter}

\end{document}

### 2020-04-02 scache/jpdc/tex/abstract.tex
jpdc

--- 2019-09-11 scache/tii/tex/abstract.tex
@@
-\begin{abstract}
+\begin{abstract}[S U M M A R Y]
 
-% In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. 
-% {\color{black}
-In industrial large-scale data-parallel analytics, shuffle, namely the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
+In large-scale data-parallel analytics, shuffle, namely the cross-network read and the aggregation of partitioned data between tasks with data dependencies, usually bring in large overhead.
 % Due to the dependency constraints, execution of those descendant tasks could be delayed by long shuffles.

### 2020-04-02 scache/jpdc/tex/impl.tex
jpdc

@@
 This section presents an overview of the implementation of SCache. 
-% {\color{red}
-% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
-% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
-% }
-{\color{blue}
 We first present the system overview and the detail of sampling in Subsection \ref{arch}. 
 The following \ref{memorymanage} subsection focuses on two constraints on memory management.
-In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
-At last, we discuss the cost of adapting SCache and fault tolerance. 
+% In Subsection \ref{crossframework}, we evaluate the cross-framework capability of SCache. 
+% At last, we discuss the cost of adapting SCache and fault tolerance. 
+{\color{black}
+In Subsection \ref{fault}, we discuss the fault tolerance of the system.
 }
@@
 \subsection{System Overview}\label{arch}
-SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
-{\color{blue} worker daemon.
-As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system.
-The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-The daemon bridges the communication between %{\color{red}Spark}
-{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
- {\color{blue} original scheduler in framework}.
+{\color{black}
+As shown in Figure \ref{fig:architecture}, SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a worker daemon.
+As a plug-in system, SCache needs to rely on a DAG framework. 
+The master node of SCache includes a DAG co-scheduler and a storage manager.
+The DAG co-scheduler is responsible for pre-scheduling the reduce tasks assignment and then forcing the DAG framework to assign reduce tasks according to this assignment.
+The storage manager is used for managing the shuffle blocks saved in worker nodes.
+% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
+% The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
+% The daemon bridges the communication between DAG framework and SCache.
+The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to the original scheduler in framework.
 
-% SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{blue} worker daemon}.
-As shown in Figure \ref{fig:arch}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system.
+When a DAG job is submitted, the DAG information is generated in the framework task scheduler. 
+% Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
+% For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
+If the RangePartitioner or a customized non-hash partitioner is used, SCache will insert an extra sampling job before the job starts.
+The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
+SCache master predicts the reduce partition size based on the data and then call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
 
-% The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
-% The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
-% The daemon bridges the communication between {\color{blue}DAG framework} and SCache.
-The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{blue} original scheduler in framework master}.
+% After a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API to move all the blocks out of framework worker through memory copy and release the slot immediately.
+After a map task finishes computing, the shuffle writes in the map task are modified to use SCache API to memory copy all shuffle blocks to the SCache worker reserved memory.
+% After that, the slot will be released (without being blocked on disk operations).
+The SCache records the block ID and the size and sends them to the master.
+% When a block of the map output is received, the SCache worker will send the block ID and the size to the master.
+% If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
+If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
+After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
+To enforce the DAG framework to assign tasks according to the SCache pre-scheduled results, we also insert some lines of codes in the framework scheduler.
+}
+% After modification, the DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
 
-% {\color{red}
-% When a Spark job starts, the DAG will be first generated. 
-% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
+% \subsubsection{Reservoir Sampling}\label{sampling}
+% {\color{black}
+% If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the framework master. 
+% The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
+% % For the sample number, it can be tuned to balance the overhead and accuracy. 
+% % The sampling job randomly selects some items and performs a local shuffle with the partitioner. 
+% % At the same time, the items number is counted as the weight. 
+% % These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
+% The result will be aggregated on SCache master to predict the reduce partition size.
+% After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
 % }
-{\color{blue}
-When a DAG job is submitted, the DAG information is generated in framework task scheduler. 
-Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
-}
-For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
-If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the {\color{blue}computing job}.
-We will elaborate the sampling procedure in the Section \ref{sampling}.
-% \begin{minipage}{\columnwidth}
-% \begin{algorithm}[H]
-% \caption{Heuristic MinHeap Scheduling for Single Shuffle}
-% \label{hminheap}
-% 	\begin{algorithmic}[1]
-% 	\small
-% 	\Procedure{\Large schedule}{$m, host\_ids, p\_reduces$}
-% 		\State $m\gets$ partition number of map tasks
-% 		\State $R\gets$ sort $p\_reduces$ by size in descending order
-% 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
-% 		\State $idx\gets$ len$\left(R\right) - 1$
-% 		\While{$idx \geq 0$}
-% 		\Comment{Schedule reduces by MinHeap}
-% 		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
-% 		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
-% 		\State $R\left[idx\right].assigned\_host \gets M \left[0\right].host\_id$
-% 		\State Sift down $M\left[0\right]$ by $size$
-% 		\State $idx\gets idx-1$
-% 		\EndWhile
-% 		\State $max\gets$ maximum size in $M$
-% 		\State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
-% 		\ForAll{$reduce$ in $R$}
-% 		\Comment{Heuristic swap by locality}
-% 			\If{$reduce.assigned\_id \neq reduce.host\_id$}
-% 				\State $p\gets reduce.prob$
-% 				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
-% 				\State $upper\_bound \gets \left(1 + norm\right) \times max$
-% 				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
-% 			\EndIf
-% 		\EndFor
-% 		% \Comment{$m$ is the number of input data}
-% 		% \Comment{$r$ is partition number of reduces}
-% 		% \Comment{$hosts$ is array of (hostid, partitionids[], size)}
-% 		% \Comment{$c$ is $r*m$ array of composition data}
-% 		% \Comment{$pSize$ is $r$ size array of predicted size of reduces}
-% 		\Return $M$
-% 	\EndProcedure
-% 	\Procedure{\Large swap\_tasks}{$M, reduce, upper\_bound$}
-% 		\State $reduces \gets M\left[reduce.host\_id\right].reduce$	
-% 		\State $candidates \gets$ Select from $reduces$ that $assigned\_id \neq host\_id$ \textbf{and} total size closest to $reduce.size$
-% 		\State $\Delta size \gets sizeOf\left(candidates\right) - reduce.size$
-% 		\State $size\_host \gets M\left[reduce.host\_id\right].size - \Delta size$
-% 		\State $size\_assigned \gets M\left[reduce.assigned\_id\right].size + \Delta size$
-% 		\If{$size\_host\leq upper\_bound$ \textbf{and} \\
-% 			\qquad \; $size\_assigned\leq upper\_bound$}
-% 			\State Swap $candidates$ and $reduce$
-% 			\State Update $size$ in $M$
-% 			\State Update $assigned\_host$ in $candidates$ and $reduce$
-% 		\EndIf
-% 	\EndProcedure
-% 	\end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
-
-When a map task finishes computing, the shuffle write implementation of the DAG framework is modified to call the SCache API and move all the blocks out of {\color{blue}framework worker} through memory copy.
-After that, the slot will be released (without being blocked on disk operations).
-When a block of the map output (i.e., "map output" in Figure \ref{fig:shuffle}) is received, the SCache worker will send the block ID and the size to the master.
-If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
-% After that, when a map task is finished, each node will receive a broadcast message. 
-SCache worker will filter the reduce tasks' IDs that are scheduled on itself and start pre-fetching shuffle data from the remote. 
-% {\color{red}
-% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
-% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
-% }
-{\color{blue}
-In order to force the DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
-After modification, DAG scheduler consults SCache co-scheduler to get the preferred location for each task.
-}
-% In the case of extreme skew scenario, such as Figure \ref{fig:range_pre_sample}, Heuristic MinHeap trades about 0.05\% percent of stage completion time for 99\% reduction of shuffle data transmission through network by heuristicly swapping tasks.
-% \begin{minipage}{\columnwidth}
-% \begin{algorithm}[H]
-% \caption{Accumulate Heuristic Scheduling for Multi-Shuffles}
-% \label{mhminheap}
-% 	\begin{algorithmic}[1]
-% 	\small
-% 	\Procedure{\Large m\_schedule}{$m, host\_id, p\_reduces, shuffles$}
-% 		\State $m\gets$ partition number of map tasks
-% 		\Comment $shuffles$ is the previous schedule result 
-% 		\ForAll{$r$ in $p\_reduces$}
-% 			\State $r.size \mathrel{+}= shuffles\left[r.rid\right].size$
-% 			\If{$shuffles\left[r.rid\right].size\geq r.size \times r.prob$}
-% 				\State $r.prob\gets shuffles\left[r.rid\right].size / r.size$
-% 				\State $r.host\_id\gets shuffles\left[r.rid\right].assigned\_host$
-% 			\EndIf
-% 		\EndFor
-% 		\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
-% 		\ForAll{$host\_id$ in $M$}
-% 			\Comment Re-shuffle
-% 			\ForAll{$r$ in $M\left[host\_id\right].reduces$}
-% 				\If{$host\neq shuffles\left[r.rid\right].assigned\_host$}
-% 				\State Re-shuffle data to $host$
-% 				\State $shuffles\left[r.rid\right].assigned\_host\gets host$
-% 				\EndIf
-% 			\EndFor
-% 		\EndFor
-% 		\Return $M$
-% 	\EndProcedure
-% 	\end{algorithmic}
-% \end{algorithm}
-% \end{minipage}
-
-\subsubsection{Reservoir Sampling}\label{sampling}
-If the submitted shuffle dependencies contained a RangePartitioner or a customized non-hash partitioner, {\color{blue}the SCache master will send a sampling request to the framework master}. 
-The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition. 
-For the sample number, it can be tuned to balance the overhead and accuracy. 
-The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). 
-At the same time, the items number is counted as the weight. 
-These sampling data will be aggregated by reduce task ID on SCache master to predict the reduce partition size. 
-After the prediction, SCache master will call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=0.8\linewidth]{fig/arch}
-% 	\caption{\color{red}SCache Architecture}
-% 	\label{fig:arch}
-% 	\vspace{-0.5em}
-% \end{figure}
 
@@
 	\centering
-	\begin{minipage}{.4\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{fig/architecture}
-		\caption{\color{blue}SCache Architecture}
+	\includegraphics[width=.8\linewidth]{fig/architecture}
+	\caption{\color{black}SCache Architecture}
 	\label{fig:architecture}
-		% \vspace{-0.5em}
-	\end{minipage}\hfill
-	\begin{minipage}{.4\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{fig/sample}
-		\caption{Reservoir Sampling of One Partition}
-		\label{fig:sample}
-		% \vspace{-1em}
-	\end{minipage}
 \end{figure}
@@
 \subsection{Memory Management}\label{memorymanage}
-As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
-When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
-To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data-all-or-nothing and context-aware-priority.
+% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
+{\color{black}
+SCache uses bellowed memory management to ensure performance.
+If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
+SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
+% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched.
+% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
+}
 
 \subsubsection{All-or-Nothing Constraint}
-This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
-Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks. 
-If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
-PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
-Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least. We refer to this as the all-or-nothing constraint.
-
-According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
-For those incomplete units, SCache marks them as the lowest priority.
-% Following the all-or-noting constraint can maximum the improvement in stage completion time by using reserved memory efficiently.
+% This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
+{\color{black}
+% Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
+% Both experience and DAG framework manuals (e.g., Hadoop and Spark) recommend that multi-round execution of each stage will benefit the performance of applications.
+As discussed in the observation in Subsection \ref{observation}, it is common to have multi-round execution of each stage. 
+If one of the tasks in a round missed a memory cache, the re-fetch overhead will become a bottleneck and then slow down the whole stage. 
+% If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
+% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
+% Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
+}
+Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
+We refer to this as the all-or-nothing constraint.
+% According to all-or-nothing constraint, SCache master leverages the pre-scheduled results to determine the bound of each round, and sets blocks of one round as the minimum unit of storage management.
+% For those incomplete units, SCache marks them as the lowest priority.
 
 \subsubsection{Context-Aware-Priority Constraint}
-Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once (without failure), but the legacy cache managements are designed to improve the hit rate.
+% Unlike the traditional cache replacement schemes such as MIN \cite{min}, the cached shuffle data will only be used once, but the legacy cache managements are designed to improve the hit rate.
+{\color{black}
 SCache leverages application context to select victim storage units when the reserved memory is full.
-
 At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
-If all the units are completed, SCache selects victims based on two factors-\textit{inter-shuffle} and \textit{intra-shuffle}.
-\begin{itemize}[noitemsep]
-	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
-	For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
-	So SCache sets the priorities according to the submission time of each shuffle.
-	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
-	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
-	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
-	% So SCache sets the priorities according to the submit time of each shuffle unit.
-	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
-	For example Spark schedules tasks with smaller ID at first. 
-	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
-\end{itemize}
+If all the units are completed, SCache selects victims based on two factors: 
+(a) For the tasks in the different stages, SCache sets the higher priority to storage units with an earlier submission time;
+(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
+}
+% If all the units are completed, SCache selects victims based on two factors --- \textit{inter-shuffle} and \textit{intra-shuffle}.
+% \begin{itemize}[noitemsep]
+% 	\item Inter-shuffle: SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority. 
+% 	% For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
+% 	SCache sets the priorities of tasks according to the submission time of each shuffle.
+% 	% For a FAIR scheduler, Spark balances the resource among task sets, which leads to a higher priority for those having more tasks unfinished. 
+% 	% So SCache sets priorities from high to low in a descending order of remaining storage units of a shuffle. 
+% 	% For a FIFO scheduler, Spark schedules the task set that is submitted first. 
+% 	% So SCache sets the priorities according to the submit time of each shuffle unit.
+% 	\item Intra-shuffle: The intra-shuffle priorities are determined according to the task scheduling inside a stage.
+% 	For example Spark schedules tasks with smaller ID at first. 
+% 	Based on this, SCache can assign the lower priority to storage units with a larger task ID.
+% \end{itemize}
 
@@
 % }
-{\color{blue}
-\subsection{Analysis of cross-framework capability}\label{crossframework}
-Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks.
+
+% {\color{black}
+% \subsection{Analysis of cross-framework capability}\label{crossframework}
+% Shuffle optimization of SCache inevitably requires the modification on the DAG frameworks.
 SCache provides APIs through RPC, such as \textit{putBlock (blockId)}, \textit{getBlock (blockId)}, and \textit{getScheduleResult (shuffleId)}.
@@
 In Spark, we mainly modify DAGScheduler and the corresponding data fetcher.
-It only takes about 500 lines of code.
+% It only takes about 500 lines of code.
 Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework.
-We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
+We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez, are also low.
+% }
+
+{\color{black}
+\subsection{Discussion of Fault Tolerance}\label{fault}
+% how to handle faults? -> maybe replication -> tradeoff
+For now, SCache only restarts failed workers without recovering their data.
+SCache leaves the fault handling to the DAG frameworks.
+If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
+During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
+A possible way to avoid this re-computing is to use replications to recover the data.
+However, such replications can introduce a significant network overhead.
+We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
+% Meanwhile, SCache can still provide shuffle optimization during the re-computing.
 }
 
-\subsection{Fault tolerance}\label{fault}
-Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
-We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
-If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
-A possible way to handle this failure is selecting some backup nodes to store replications. 
-But the replications can introduce a significant network overhead \cite{availability}.  
-Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
-We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
-Meanwhile, SCache can still provide shuffle optimization during the recovery.
-
-% \subsubsection{Fault Tolerance}
-% To prevent the machine failure in cluster leading to inconsistency SCache, the master node will log the meta data of shuffle register and scheduling on the disk.
-Since we remove the shuffle transfer from the critical path of DAG computing, the disk log will not introduce extra overhead to the DAG framworks.
-Note that the master can be implemented with Apache ZooKeeper \cite{zookeeper} to provide constantly service to DAG framework.
-% At the same time, every work node will send a heartbeat to master to report status.
-If a failure of work node is detected, the master will the do a simple re-schedule.
-For those scheduled shuffle units, the master assgins the tasks to other workers with more lightweight workload evenly.
-Then the new assigned worker will fetch the data again.
-For the incomplete in memory map blocks on the failure node, SCache simply ignore them since DAG framework will schedule the failure map tasks on another node.
+% Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present.
+% We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
+% If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
+% A possible way to handle this failure is selecting some backup nodes to store replications. 
+% % But the replications can introduce a significant network overhead \cite{availability}.  
+% Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
+% We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
+% Meanwhile, SCache can still provide shuffle optimization during the recovery.

### 2020-04-02 scache/jpdc/tex/intro.tex
jpdc

--- 2019-09-15 scache/tii/tex/intro.tex
@@
 \section{Introduction}\label{sec:introduction}
-\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
+We are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
 {\color{black}
@@
 % Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
-Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
+% Industrial big data is more structured, correlated, and ready for analytics than traditional big data, because industrial big data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
 }
@@
 	\includegraphics
-		[width=.85\linewidth]
+		[width=.95\linewidth]
 		{fig/workflow}
@@
 \end{figure}
-Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
-In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
+Although continuous efforts of performance optimization have been made among a variety of computing frameworks \cite{chen2017parallel, sync, babu, tachyon, pacman, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
+% In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
+One of the major deficiency of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.
+% In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
 % As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
@@
 More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS\footnote{http://www.tpc.org/tpcds/}, a standardized industry benchmark, on average on Apache Spark.
+On Apache Hadoop MapReduce, SCache also optimizes end-to-end Terasort completion time by $15\%$.
+
+% This paper is the extension of our conference paper at PPoPP'18 \cite{fu2018efficient}.
+% In this extended paper, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model.
+% We use the model to evaluate the deficiencies of different resource scheduling strategies and optimize them.
+% We also update the existing experiments with more comprehensive benchmarks and implement SCache on Hadoop MapReduce to demonstrates its compatibility and adaptability.
 

### 2020-04-02 scache/jpdc/tex/relatedwork.tex
jpdc

--- 2019-09-15 scache/tii/tex/relatedwork.tex
@@
 % There are also lots of performance models for MapReduce have been proposed, such as \cite{verma2011aria, khan2016hadoop, herodotou2011hadoop, chen2014cresp, farhat2016stochastic}.
-% Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
+Verma et al. \cite{verma2011aria} proposed the ARIA model to estimate the required resources based on the job information, the amount of input data and a specified soft deadline.
 Khan et al.
@@
 The HP model adds scaling factors and uses a simple linear regression to estimate the job execution time on larger datasets.
-% In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
+In \cite{herodotou2011hadoop}, Herodotou proposed a detailed set of mathematical performance models for describing the five phases of a MapReduce job and combine them into an overall MapReduce job model.
 % The execution is separated into the phases: Read, Map, Collect, Spill, Merge, Shuffle, Merge, and Reduce. 
@@
 Starfish \cite{starfish} gets sampled data statics for self-tuning system parameters (e.g. slow-start, etc). 
-% DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
+DynMR \cite{dynmr} dynamically starts reduce tasks in late map stage. 
 % All of them have the explicit I/O time in occupied slots. 
@@
 
-% \textbf{Network layer optimization.} 
+\textbf{Network layer optimization.} 
 % Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
@@
 % Though the efforts above are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
-% Varys \cite{varys} and Aalo \cite{aalo} also provide the network layer optimization for shuffle transfer. 
-% Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
-% According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.
+Varys \cite{varys} and Aalo \cite{aalo} provide the network layer optimization for shuffle transfer. 
+Though the efforts are limited throughout whole shuffle process, they can be easily applied on SCache to further improve the performance.
+According to \cite{qin2017bandwidth, huang2018survey}, we can also combine SDN with SCache to further improve the performance on the network later.

### 2020-04-02 scache/tii/coverletter/coverletter.tex
jpdc

@@
 
-% \author{Rui Ren}
-% \author{Chunghsuan Wu}
-% \author{Zhouwang Fu}
-% \author{Tao Song}
-% \author{Yanqiang Liu}
-% \author{Zhengwei Qi}
-% \author{Haibing Guan}
+\author{Rui Ren}
+\author{Chunghsuan Wu}
+\author{Zhouwang Fu}
+\author{Tao Song}
+\author{Yanqiang Liu}
+\author{Zhengwei Qi}
+\author{Haibing Guan}
 
@@
 
-% This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
-This paper is the extension of our conference paper at PPoPP. 
+This paper is the extension of our conference paper at PPoPP '18 \cite{fu2018efficient}. 
+% This paper is the extension of our conference paper at PPoPP. 
 % In the manuscript we uploaded, we highlight the new content in blue.
@@
 % SCache can also provide considerable optimization in industrial big data.
-In this paper, we combine the characteristic of the industrial big data and DAG computing frameworks.
-We provide a new data processing solution for the industrial big data based on our conference paper.
-Besides, we use the credible benchmark to demonstrate that our solution is effective in the industrial big data analysis.
+% In this paper, we combine the characteristic of the industrial big data and DAG computing frameworks.
+In this paper, we provide a new data processing solution for the industrial big data based on our conference paper.
+Besides, we use the credible benchmark to demonstrate that our solution is effective in the big data analysis.
 This paper makes the following distinct contributions compared with the conference paper.
@@
 The FRQ model quantifies computing and I/O resources by five input parameters. 
-Furthermore, the FRQ model visualizes the resources scheduling strategies of the DAG frameworks in the time dimension. 
+Furthermore, the FRQ model visualizes the resource scheduling strategies of the DAG frameworks in the time dimension. 
 In this paper, we use the model to evaluate the deficiencies of different resources scheduling strategies and then optimize them.
@@
 In summary, we propose a new performance model to provide a theoretical basis for performance optimization and improve evaluations by adding experiments on Hadoop MapReduce. 
-We believe that the added content makes a sufficient contribution to this special issue.
-% We believe that the added content makes a sufficient contribution to this journal submission.
+% We believe that the added content makes a sufficient contribution to this special issue.
+We believe that the added content makes a sufficient contribution to this journal submission.
 
 \bibliographystyle{IEEEtran}
-% \bibliography{coverletter}
+\bibliography{coverletter}
 

### 2020-04-02 scache/jpdc/tex/impl.tex
some minor fixes

@@
 The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
-SCache master predicts the reduce partition size based on the data and then call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
+SCache master predicts the reduce partition size based on the data and then \edited{calls} Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.
 
@@
 {\color{black}
-SCache uses bellowed memory management to ensure performance.
+SCache uses \edited{memory management described below} to ensure performance.
 If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.

### 2020-04-02 scache/jpdc/tex/model.tex
some minor fixes

--- 2019-09-15 scache/tii/tex/model.tex
@@
 Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
-The FRQ model needs to know the start time of each phases.
+The FRQ model needs to know the start time of each \edited{phase}.
 For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
@@
 	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated.
-As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round.
+As Figure \ref{fig:model_scache2} \edited{shows}, the shuffle phase will be interrupted in each round.
 In this case, the formula of \(T_{P\_Shuffle}\) is as followed:

### 2020-04-02 scache/jpdc/tex/optimization.tex
jpdc
some minor fixes

--- 2019-09-15 scache/tii/tex/optimization.tex
@@
 \begin{figure}
-	% \centering
+	\centering
 	% \begin{subfigure}[b]{0.31\linewidth}
@@
 	% \end{subfigure}
-	\begin{subfigure}[b]{0.5\linewidth}
+	\begin{subfigure}{0.75\linewidth}
 		\includegraphics[width=\linewidth]{fig/range_pre_sample}
@@
 	\end{subfigure}
-	\begin{subfigure}[b]{0.49\linewidth}
+	\begin{subfigure}{0.75\linewidth}
 		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
@@
 	\centering
-	\includegraphics[width=.6\linewidth]{fig/sim} % second figure itself
+	\includegraphics[width=0.75\linewidth]{fig/sim} % second figure itself
 	\caption{Stage Completion Time Improvement of OpenCloud Trace}
@@
 
-SCache caches the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
+SCache caches the shuffle data on the memory instead of storing on disk \edited{like} Spark or Hadoop MapReduce.
 In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
@@
 
-\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
-% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
-% But ignoring the data locality can introduce extra network transfer. 
-% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
-To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
-{\color{black}
-% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
-To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
-We use the min-heap to simulate the load of each node and apply the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
-Spark FIFO only can achieve $2\text{-}approximation$ optimum.
-}
-% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
-% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
-After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
-The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
-Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
-Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
-Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
-
-{\color{black}
-To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
-% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
-As shown in Figure \ref{fig:sim}, we run the simulation under three scheduling schemes: Random Mapping, Spark FIFO, and heuristic MinHeap.
-After balancing load based on the job context (e.g.
-shuffle size, data locality), \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than Spark (average 2.7\%) and Random Mapping.
-%  (becomes negative after the round one).
-}
-
 \begin{minipage}{0.95\columnwidth}
@@
 \end{minipage}
+
+\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
+% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
+% But ignoring the data locality can introduce extra network transfer. 
+% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
+To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
+{\color{black}
+% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.e., line 6-11).
+We use the min-heap to simulate the load of each node and apply the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
+Spark FIFO only can achieve $2\text{-}approximation$ optimum.
+}
+% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
+% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
+After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
+The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
+Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
+Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
+Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
+
+{\color{black}
+To evaluate \textit{Heuristic MinHeap Scheduling} algorithm, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
+% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
+As shown in Figure \ref{fig:sim}, we run the simulation under three scheduling schemes: Random Mapping, Spark FIFO, and heuristic MinHeap.
+After balancing load based on the job context (e.g.
+shuffle size, data locality), \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than Spark (average 2.7\%) and Random Mapping.
+%  (becomes negative after the round one).
+}
 

### 2020-04-03 scache/jpdc/tex/model.tex
update

@@
 \begin{aligned}
-    T_{Job} &= T_{Map} + T_{Reduce}
+    T_{Job} &= T_{Map} + T_{Reduce} + \edited{T_{Penalty}}
 \end{aligned}
@@
 \(K\) is an empirical value which represents the overhead caused by shuffle waiting. 
-Because the computation of the reduce phase relies on the data transfer results of the shuffle phase, a portion of the computation needs to wait for the transfer results.
+Because the computation of the reduce phase relies on the \edited{results of data transferring} of the shuffle phase, a portion of the computation needs to wait for the \edited{results of transferring}.
 This waiting causes the overhead.

### 2020-04-05 scache/jpdc/tex/evaluation.tex
jpdc
some minor fixes
update

--- 2019-09-15 scache/tii/tex/evaluation.tex
@@
 
+\begin{figure*}
+	\centering
+	\includegraphics[width=.8\textwidth]{fig/tpcds}
+	\caption{TPC-DS Benchmark Evaluation}
+	\label{fig:tpcds}
+	\vspace{-1em}
+\end{figure*}
+
 \section{Evaluation}\label{evaluation}
@@
 % Because of the limited time and resource,
-To prove the performance gain of SCache in industry, 
-we evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/}.
+
+% To prove the performance gain of SCache in industry, 
+We \edited{first} evaluate SCache with TPC-DS\footnote{http://www.tpc.org/tpcds/} \edited{to prove the performance gain of SCache in industry}.
 TPC-DS is a standard benchmark which focuses on modeling industrial workload.
@@
 % We run a Spark job with single shuffle to analyze hardware utilization and see the impacts of different components from the scope of a task to a job. 
-% Then we use a recognized shuffle intensive benchmark --- Terasort to evaluate SCache with different data partition schemes.
+\edited{Then we use a recognized shuffle intensive benchmark Terasort \cite{spark-tera} to evaluate SCache with different data partition schemes.}
 % To prove the performance gain of SCache with a industrial production workload, we also evaluate Spark TPC-DS\footnote{https://github.com/databricks/spark-sql-perf} and present the overall performance improvement.
@@
 % It implies that the heuristic locality swap of SCache can obtain the best locality while balancing the load.
-\begin{figure*}
-	\centering
-	\includegraphics[width=.8\textwidth]{fig/tpcds}
-	\caption{TPC-DS Benchmark Evaluation}
-	\label{fig:tpcds}
-	\vspace{-1em}
-\end{figure*}
 
 \subsubsection{Industrial Production Workload}
-% We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
-% TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.). 
-% TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
-TPC-DS\footnote{http://www.tpc.org/tpcds/} contains 99 queries and is considered as a standardized industry benchmark for testing big data systems. 
+\edited{
+We also evaluate some queries from TPC-DS\footnote{http://www.tpc.org/tpcds/}. 
+TPC-DS benchmark is designed for modeling multiple users submitting varied queries (e.g. ad-hoc, interactive OLAP, data mining, etc.).}
+TPC-DS contains 99 queries and is considered as the standardized industry benchmark for testing big data systems. 
 % We evaluate the performance of Spark with SCache by picking some of the TPC-DS queries with shuffle intensive attribute. 
 As shown in Figure \ref{fig:tpcds}, the horizontal axis is query name and the vertical axis is query completion time. 
-Note that we skip some queries due to the compatible issues. 
+Note that we skip some queries due to \edited{compatible issues}. 
 Spark with SCache outperforms the original Spark in almost all tested queries. 
@@
 Since this evaluation presents the overall job completion time of queries, we believe that our shuffle optimization is promising.
+
+\begin{table*}
+\centering
+\scalebox{0.85}{
+	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+	\hline
+	&
+	\(D\) &	
+	\(R\) &	
+	\(N\) &	
+	\(V_{Map}\) &	
+	\(V_{Reduce}\) &	
+	\(V_{Shuffle}\) &	
+	\(K\) &	
+	\(T_{Map}\) &	
+	\(T_{Shuffle}\) &	
+	\(T_{P\_Shuffle}\) &
+	\(T_{Reduce}\) & 
+	\(T_{Job}\) & 
+	\(Exp T_{Job}\) &
+	\(Error\)\\
+
+	\hline
+	% & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
+	SCache
+	& 32 GB & 1	& 4 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	49.23 &		68.09  s &	31.16 s &	47.58 s &	96.81	s & 104 s & 	6.91\% \\
+	& 48 GB	& 1	& 6 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	73.85 &		102.13 s &	40.59 s &	68.29 s &	142.14	s & 151 s & 	5.87\% \\
+	& 64 GB	& 1	& 8 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	98.46 &		136.17 s &	50.02 s &	89.01 s &	187.47	s & 193 s & 	2.87\% \\
+	\hline
+	% & 16	& 1 & 2 &	0.65 GB/s &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
+	Legacy
+	& 32 GB	& 1 & 4 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	49.23 s &		68.09 s &	68.09 s		&	72.85	s &	122.08 s	&	135 s	&	9.57\%	\\
+	& 48 GB	& 1 & 6 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	73.85 s &		102.13 s &	102.13 s	&	109.28	s &	183.12 s	&	188 s	&	2.59\%	\\
+	& 64 GB	& 1 & 8 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	98.46 s &		136.17 s &	136.17 s	&	145.70	s &	244.16 s	&	249 s	&	1.94\%	\\
+	\hline
+	\end{tabular}
+}
+% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
+\label{table1}
+\end{table*}
+
+\begin{table*}
+\centering
+\scalebox{0.85}{
+	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
+	\hline
+	&
+	\(D\) &	
+	\(R\) &	
+	\(N\) &	
+	\(V_{Map}\) &	
+	\(V_{Reduce}\) &	
+	\(V_{Shuffle}\) &	
+	\(K\) &	
+	\(T_{Map}\) &	
+	\(T_{Shuffle}\) &	
+	\(T_{P\_Shuffle}\) &
+	\(T_{Reduce}\) & 
+	\(T_{Job}\) & 
+	\(Exp T_{Job}\) &
+	\(Error\)\\
+
+	\hline
+	SCache
+	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
+	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
+	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
+	% & 512	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
+	\hline
+	Legacy
+	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	111.30 s &	91.43	s &	91.43	s &	142.53	s &	253.83	s &	266 s &	4.57\%	\\
+	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	222.61 s &	182.86	s &	182.86	s &	285.06	s &	507.67	s &	524 s &	3.12\%	\\
+	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	333.91 s &	274.29	s &	274.29	s &	427.59	s &	761.50	s &	776 s &	1.87\%	\\
+	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
+
+	\hline
+	\end{tabular}
+}
+% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
+\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
+\label{table2}
+\end{table*}
 
@@
 
-{\color{black}
 \subsection{Hadoop MapReduce with SCache}
 
-{\color{black}
 % To prove SCache compatibility as a cross-framework plug-in, we also implemented SCache on Hadoop MapReduce. 
@@
 However, SCache can still provide considerable optimization on shuffle-heavy workloads.
-We use Terasort benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
+
+We use Terasort \edited{\cite{spark-tera}} benchmark to evaluate the performance gain of SCache and also prove the cross-framework ability of SCache.
+\edited{Terasort consists of two consecutive shuffles. 
+The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
+The second shuffle partitions the data through a Spark \texttt{RangePartitioner}. 
+}
 % Although the simple workflow alleviates the benefits of \textit{pre-scheduling}, SCache can still .
@@
 % As Figure \ref{fig:hadoop_terasort} shows, Hadoop MapReduce with SCache brings $15\%$ of total time optimization with 384GB input data size.
-}
 
@@
 As shown in Figure \ref{fig:hadoop_terasort_time}, after decoupling, Hadoop MapReduce with SCache optimizes Terasort overall completion time by up to $15\%$ and an average of $13\%$ with input data sizes from 128GB to 512GB.
-}
 
@@
 \end{figure}
-
-\begin{table*}
-\centering
-\scalebox{0.85}{
-	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
-	\hline
-	&
-	\(D\) &	
-	\(R\) &	
-	\(N\) &	
-	\(V_{Map}\) &	
-	\(V_{Reduce}\) &	
-	\(V_{Shuffle}\) &	
-	\(K\) &	
-	\(T_{Map}\) &	
-	\(T_{Shuffle}\) &	
-	\(T_{P\_Shuffle}\) &
-	\(T_{Reduce}\) & 
-	\(T_{Job}\) & 
-	\(Exp T_{Job}\) &
-	\(Error\)\\
-
-	\hline
-	% & 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
-	SCache
-	& 32 GB & 1	& 4 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	49.23 &		68.09  s &	31.16 s &	47.58 s &	96.81	s & 104 s & 	6.91\% \\
-	& 48 GB	& 1	& 6 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	73.85 &		102.13 s &	40.59 s &	68.29 s &	142.14	s & 151 s & 	5.87\% \\
-	& 64 GB	& 1	& 8 &	0.65 GB/s &	1 GB/s  &	0.47 GB/s &	0.5 &	98.46 &		136.17 s &	50.02 s &	89.01 s &	187.47	s & 193 s & 	2.87\% \\
-	\hline
-	% & 16	& 1 & 2 &	0.65 GB/s &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
-	Legacy
-	& 32 GB	& 1 & 4 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	49.23 s &		68.09 s &	68.09 s		&	72.85	s &	122.08 s	&	135 s	&	9.57\%	\\
-	& 48 GB	& 1 & 6 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	73.85 s &		102.13 s &	102.13 s	&	109.28	s &	183.12 s	&	188 s	&	2.59\%	\\
-	& 64 GB	& 1 & 8 &	0.65 GB/s &	1 GB/s &	0.47 GB/s &	0.6 &	98.46 s &		136.17 s &	136.17 s	&	145.70	s &	244.16 s	&	249 s	&	1.94\%	\\
-	\hline
-	\end{tabular}
-}
-% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
-\label{table1}
-\end{table*}
-
-% \subsection{Performance Analysis}\label{model_performance_analysis}
-
-% \begin{table*}[!t]
-
-\begin{table*}
-\centering
-\scalebox{0.85}{
-	\begin{tabular}{|c||c|c|c|c|c|c|c||c|c|c|c|c|c|c|}
-	\hline
-	&
-	\(D\) &	
-	\(R\) &	
-	\(N\) &	
-	\(V_{Map}\) &	
-	\(V_{Reduce}\) &	
-	\(V_{Shuffle}\) &	
-	\(K\) &	
-	\(T_{Map}\) &	
-	\(T_{Shuffle}\) &	
-	\(T_{P\_Shuffle}\) &
-	\(T_{Reduce}\) & 
-	\(T_{Job}\) & 
-	\(Exp T_{Job}\) &
-	\(Error\)\\
-
-	\hline
-	SCache
-	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	111.30 &	91.43	&	18.29	&	96.81	&	208.12	&	232	&	10.29\%	\\
-	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	222.61 &	182.86	&	36.57	&	193.63	&	416.24	&	432	&	3.65\%	\\
-	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	333.91 &	274.29	&	54.86	&	290.44	&	624.36	&	685 &	8.85\%	\\
-	% & 512	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.5 &	445.22 &	365.71	&	91.43	&			&	841.62	&	1135 &	25.85\%	\\
-	\hline
-	Legacy
-	& 128 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	111.30 s &	91.43	s &	91.43	s &	142.53	s &	253.83	s &	266 s &	4.57\%	\\
-	& 256 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	222.61 s &	182.86	s &	182.86	s &	285.06	s &	507.67	s &	524 s &	3.12\%	\\
-	& 384 GB	& 1 & 5 &	1.15 GB/s &	1.46 GB/s	&	1.4 GB/s &	0.6 &	333.91 s &	274.29	s &	274.29	s &	427.59	s &	761.50	s &	776 s &	1.87\%	\\
-	% & 512	& 1 & 5 &	1.15 &	1.46	&	1.4 &	0.6 &	445.22 &	365.71	&	365.71	&	588.40	&	1033.62	&	1312 &	21.22\%	\\
-
-	\hline
-	\end{tabular}
-}
-% \(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
-\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
-\label{table2}
-\end{table*}

### 2020-04-05 scache/jpdc/tex/impl.tex
update

@@
 % If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
-If the collected shuffle blocks reach a threshold, the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
+If the collected shuffle blocks reach a threshold, \edited{which is defined by the memory usage,} the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
 After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
@@
 % This acceleration of in-memory cache of a single task is necessary but insufficient for a shorter stage completion time. 
-{\color{black}
 % Based on the observation in Section \ref{multi}, in most cases one single stage contains multi-rounds of tasks.
@@
 % Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
-}
 Therefore, SCache master sets blocks of one round as the minimum unit of storage management.
@@
 % how to handle faults? -> maybe replication -> tradeoff
-For now, SCache only restarts failed workers without recovering their data.
-SCache leaves the fault handling to the DAG frameworks.
-If a failure happens in a SCache worker during shuffle phases, the $getBlock$ API will return a data not found error which causes the DAG framework restarts the current stage.
+\edited{Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once),}
+% For now, 
+SCache only restarts failed workers without recovering their data \edited{and} leaves the fault handling to the DAG frameworks.
+If a failure happens in a SCache worker during shuffle phases, the \edited{\texttt{getBlock}} API will return a \edited{data-not-found} error which causes the DAG framework restarts the current stage.
 During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
+
+\edited{We believe that }
+
 A possible way to avoid this re-computing is to use replications to recover the data.

### 2020-04-05 scache/jpdc/tex/optimization.tex
update

@@
 
-{\color{black}
-\subsection{Observations}\label{observation}
-% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory
+% {\color{black}
+% \subsection{Observations}\label{observation}
+% % DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory
 
-In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
-For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
-In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
-On the reduce side, shuffle introduces an explicit overhead during shuffle read.
-% Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
-% because all reduce tasks start shuffle read simultaneously, 
-Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.
+% In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
+% For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce.
+% In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is coupled with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
+% On the reduce side, shuffle introduces an explicit overhead during shuffle read.
+% % Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
+% % because all reduce tasks start shuffle read simultaneously, 
+% Furthermore, the synchronized shuffle read causes a burst of network traffic and further enlarges the overhead.
 
-% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\).
+% % To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\).
 \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase.
-% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
-% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
-To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
-\begin{itemize}
-	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
-	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
-\end{itemize}
-% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
-}
+% % We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
+% % In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
+% To mitigate the shuffle overhead, we propose an optimization to overlap the shuffle data transfer in multi-round map tasks, and use memory to cache the shuffle data. To achieve this optimization:
+% \begin{itemize}
+% 	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
+% 	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
+% \end{itemize}
+% % In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
+% }
 
@@
 		\State $m\gets$ partition number of map tasks
-		\State $R\gets$ sort $p\_reduces$ by size in non-increasing order
+		\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
 		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$

### 2020-04-06 scache/jpdc/tex/intro.tex
some minor fixes
update

@@
 % In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
-One of the major deficiency of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.
+One of the major \edited{deficiencies} of the shuffle phase is lacking coordinated management among different system resources \cite{fu2018efficient}.
 % In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
@@
 {\color{black}
-To optimize the data shuffling without significantly changing DAG frameworks, we propose S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system for different DAG computing frameworks.
+To optimize the data shuffling without significantly changing DAG frameworks, we propose \emph{S(huffle)Cache}, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system for different DAG computing frameworks.
 Specifically, SCache takes over the whole shuffle phase from the underlying framework.

### 2020-04-06 scache/jpdc/tex/motivation.tex
update

--- 2019-01-03 taco/tex/motivation.tex
@@
 
-In this section, we first study the typical shuffle characteristics (\ref{shuffle pattern}), and then spot the opportunities to achieve shuffle optimization (\ref{observation}).
-\subsection{Characteristic of Shuffle} \label{shuffle pattern}
+% In this section, we first study the typical shuffle characteristics (\ref{shuffle pattern}), and then spot the opportunities to achieve shuffle optimization (\ref{observation}).
+% \subsection{Characteristic of Shuffle} \label{shuffle pattern}
 
@@
 % Of course, shuffle is unavoidable in a DAG computing process. 
-Can we mitigate or even remove the overhead of shuffle? 
-To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
+% Can we mitigate or even remove the overhead of shuffle? 
+% To find the answers, 
+We ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
 Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
@@
 % The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
-\begin{figure*}
-	\centering
-	\begin{subfigure}[b]{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/util}
-		\caption{Original Spark}
-		\label{fig:util}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.47\linewidth}
-		\includegraphics[width=\linewidth]{fig/scache_util}
-		\caption{Spark With SCache}
-		\label{fig:scache_util}
-	\end{subfigure}
-	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
-\end{figure*}
+% \begin{figure*}
+% 	\centering
+% 	\begin{subfigure}[b]{0.47\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/util}
+% 		\caption{Original Spark}
+% 		\label{fig:util}
+% 	\end{subfigure}
+% 	\begin{subfigure}[b]{0.47\linewidth}
+% 		\includegraphics[width=\linewidth]{fig/scache_util}
+% 		\caption{Spark With SCache}
+% 		\label{fig:scache_util}
+% 	\end{subfigure}
+% 	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
+% \end{figure*}
 
@@
 
-\subsubsection{Multi-round Tasks Execution}\label{multi}
-Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
-For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
+% \subsubsection{Multi-round Tasks Execution}\label{multi}
+% Both experience and DAG framework manuals(e.g., Hadoop\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} and Spark\footnote{http://spark.apache.org/docs/1.6.2/configuration.html}) recommend that multi-round execution of each stage will benefit the performance of applications.
+% For a cluster with $n$ slots, the number of tasks should be $n \times k \; (k \geq 1)$. 
 % For example, Hadoop MapReduce Tutorial\footnote{http://hadoop.apache.org/docs/current/hadoop-mapreduce-client/hadoop-mapreduce-client-core/MapReduceTutorial.html} suggests that \textit{10-100 maps} per-node and \textit{0.95 or 1.75 $\times$ number of nodes $\times$ number of maximum container reduces} per-node seem to be the right level of parallelism.
 % Spark configuration also recommends $2\text{-}3$ tasks per CPU core\footnote{http://spark.apache.org/docs/1.6.2/configuration.html} (i.e., $k = 2\text{-}3$).
-Since the shuffle data becomes available as soon as the end of a task's execution, 
-and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
-the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
+% Since the shuffle data becomes available as soon as the end of a task's execution, 
+% and the network is idle during the map stage ("Network TX" during map stage in Figure \ref{fig:util}), 
+% the property of multi-round tasks can be leveraged to hide the cost by starting shuffle data transfer at the end rounds of map tasks. 
 % optimize the shuffle read operations if the destination host of the shuffle data can be predicted a priori. 
@@
 	\item Reduce tasks should be pre-scheduled without launching to achieve shuffle data pre-fetching.
-	\item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
+	% \item Shuffle process should be taken over and managed outside DAG frameworks to achieve a cross-framework optimization.
 \end{itemize}

### 2020-04-07 scache/jpdc/tex/evaluation.tex
update

@@
 Meanwhile, Hadoop MapReduce with SCache optimizes job completion time by up to $15\%$ and an average of $13\%$.
+\edited{We performed the experiments for about three to five times each variously, which ensured the accuracy of the evaluation.}
 }
@@
 It helps eliminate $40\%$ of shuffle write time (Figure \ref{fig:maptask}), which leads to a $10\%$ improvement of map stage completion time in Figure \ref{fig:mapstage}. 
-% Note that the shuffle write time can be observed even with the optimization of SCache. 
-% The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}. 
+\edited{Note that the shuffle write time can be observed even with the optimization of SCache.
+The reason is that before moving data out of Spark's JVM, the serialization is inevitable and CPU intensive \cite{makingsense}. 
+}
+
 In the reduce stage, most of the shuffle overhead is introduced by network transfer delay. 
@@
 % By doing shuffle data pre-fetching based on the pre-scheduling results, the explicit network transfer is perfectly overlapped in the map stage. 
-% With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching. 
+\edited{With the help of the co-scheduling scheme, SCache guarantees that each reduce task has the benefit of shuffle pre-fetching.}
 % The in-memory cache of shuffle data further reduces the shuffle read time. 
@@
 Furthermore, in some shuffle-heavy queries, Spark with SCache outperforms original Spark by an order of magnitude. 
-% It is because that those queries contain shuffle-heavy operations such as \textit{groupby}, \textit{union}, etc.
+\edited{It is because that those queries contain shuffle-heavy operations such as \texttt{groupby}, \texttt{union}, etc.}
 The overall reduction portion of query time that SCache achieved is $40\%$ on average. 
@@
 
-As shown in Table \ref{table1}\&\ref{table2}, the experimental values are all larger than the calculated values.
+As shown in Table \ref{table1} \edited{and} \ref{table2}, the experimental values are all larger than the calculated values.
 This is because the application has some extra overhead at runtime, such as network warm-up, the overhead of allocating slots, etc.

### 2020-04-07 scache/jpdc/tex/impl.tex
update

@@
 % If one task missed a memory cache and exceeded the original bottleneck of this round, that task might become the new bottleneck and then slow down the whole stage. 
-% PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously. 
+\edited{PACMan \cite{pacman} has also proved that for multi-round stage/job, the completion time improves in steps when $n\times number\ of\ tasks\ in\ one\ round$ of tasks have data cached simultaneously.}
 % Therefore, the cached shuffle blocks need to match the demand of all tasks in one running round at least.
@@
 At first, SCache flushes blocks of the incomplete units to disk cluster-widely.
-If all the units are completed, SCache selects victims based on two factors: 
-(a) For the tasks in the different stages, SCache sets the higher priority to storage units with an earlier submission time;
-(b) For the tasks in the same stage, SCache sets the higher priority to storage units with a smaller task ID.
+\edited{SCache master follows the scheduling scheme of Spark to determine the inter-shuffle priority.
+For example, Spark FIFO scheduler schedules the tasks of different stages according to the submission order. 
+}
+If all the units are completed, SCache selects victims \edited{(i.e., tasks with lower priority)} based on two factors: 
+(a) For the tasks in the different stages, SCache sets the \edited{lower} priority to storage units with an earlier submission time;
+(b) For the tasks in the same stage, SCache sets the \edited{lower} priority to storage units with a smaller task ID.
 }
@@
 
-\edited{We believe that }
-
+\edited{Although the entire computing task has to be re-computed, we consider that there is a trade-off between the efficiency and the overhead of fault recovery with SCache.}
 A possible way to avoid this re-computing is to use replications to recover the data.

### 2020-04-07 scache/jpdc/tex/model.tex
update

@@
 Take Hadoop MapReduce as an example.
-Suppose we have a cluster with 50 CPUs and enough memory, the map phase consists of 200 map tasks, and each map requires 1 CPU.
+Suppose we have a cluster with 50 CPUs and enough memory \edited{(i.e., sufficient for the input data and the run-time memory of the frameworks)}, the map phase consists of 200 map tasks, and each map requires 1 CPU.
 Then we need 4 rounds of computation to complete the map phase.
@@
 
+\edited{$T_{Penalty}$ is defined as the penalty time of fault recovery, which depends on the fault tolerance mechanism of the frameworks.
+With SCache, since the intermediate data is stored in memory, when fault occurs the entire computing task need to be re-computed from the beginning.
+}
+
 The reduce phase time formula is as follows:
@@
 
-According to Equation \ref{equation_Tjob}\&\ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
+According to Equation \ref{equation_Tjob} \edited{and} \ref{equation_Treduce}, we can optimize the job completion time by reducing \(T_{P\_Shuffle}\).
 By using different resource scheduling strategies, the formulas of \(T_{P\_Shuffle}\) are different.

### 2020-04-07 scache/jpdc/tex/motivation.tex
update

@@
 We ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
-Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
+Here we present the hardware utilization trace of one node running Spark's \texttt{GroupByTest}.
+% in Figure \ref{fig:util} as an example. 
 This job has 2 rounds of tasks for each node.
@@
 \subsubsection{Coarse Granularity Resource Allocation}
-When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
-On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
-Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
+When a slot is assigned to a task, it will not be released until the task completes.
+% (i.e., the end of shuffle write in Figure \ref{fig:util}). 
+On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read.
+% (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
+Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU.
+% as presented in Figure \ref{fig:util}. 
 The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
@@
 The synchronized shuffle read requests cause a burst of network traffic. 
-As shown in Figure \ref{fig:util}, 
-the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
+% As shown in Figure \ref{fig:util}, 
+The data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
 It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.

### 2020-07-16 scache/jpdc/tex/impl.tex
*: update

@@
 If the collected shuffle blocks reach a threshold, \edited{which is defined by the memory usage,} the SCache co-scheduler will run the scheduling Algorithm \ref{hminheap} or \ref{mhminheap} to pre-schedule the reduce tasks.
+\reedited{The lower the threshold is set, the more shuffle requests are issued since the amount of data to be shuffled remains the same.}
 After pre-scheduling, SCache workers start pre-fetching shuffle blocks according to the assignment from the master.
@@
 \subsection{Discussion of Fault Tolerance}\label{fault}
-% how to handle faults? -> maybe replication -> tradeoff
-\edited{Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once),}
-% For now, 
-SCache only restarts failed workers without recovering their data \edited{and} leaves the fault handling to the DAG frameworks.
-If a failure happens in a SCache worker during shuffle phases, the \edited{\texttt{getBlock}} API will return a \edited{data-not-found} error which causes the DAG framework restarts the current stage.
-During the re-computing, the DAG frameworks still use SCache to gain shuffle optimization.
+
+\reedited{For fault tolerance,} SCache only restarts failed workers without recovering their data.
+If a failure happens in a SCache worker during shuffle phases, \reedited{SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing}.
+During the re-computing, \reedited{the DAG frameworks can still use SCache to gain benefits in the shuffle phase.}
 
 \edited{Although the entire computing task has to be re-computed, we consider that there is a trade-off between the efficiency and the overhead of fault recovery with SCache.}
-A possible way to avoid this re-computing is to use replications to recover the data.
-However, such replications can introduce a significant network overhead.
-We believe that the current way is more promising because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark. 
+\reedited{SCache brings significant performance benefits due to the in-memory shuffle management, although the overhead such as re-computing is also introduced when failure occurs, we believe such drawback is tolerable.
+A possible soltion to avoid re-computing is to use replicas to recover the data.
+However, such a strategy can introduce significant network overhead.}
+% However, such replications can introduce a significant network overhead.
+
+\reedited{Moreover, in the current design of SCache, we leave the server faults (e.g., node failures) to the DAG frameworks, due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once).}
+We believe \reedited{this} way is more promising \reedited{since} most DAG frameworks have more advanced fast recovery schemes on the application layer, such as the paralleled recovery of Spark.
 % Meanwhile, SCache can still provide shuffle optimization during the re-computing.

### 2020-07-16 scache/jpdc/tex/optimization.tex
update
*: update

@@
 % Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
-For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
+For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable \reedited{parameter}. 
 After that, the map function is called locally to process the sampled data. 
@@
 \end{equation}
-In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
+
+\reedited{It can be discovered that as the increase of parameter $s$, more samples are included in the sampling, that is, the result of sampling is more accurate.
+Based on our experiment, we discover that when $s$ is set to $3$, the result of sampling prediction is the best and much better than linear regression, as shown in Figure \ref{fig:range_pre_sample}.}
+% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
 Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide a much more accurate result than the linear regression. 
@@
 % This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.
-
-\begin{minipage}{0.95\columnwidth}
-\begin{algorithm}[H]
-\caption{Heuristic MinHeap Scheduling for Single Shuffle}
-\label{hminheap}
-	\begin{algorithmic}[1]
-	\small
-	\Procedure{schedule}{$m, host\_ids, p\_reduces$}
-		\State $m\gets$ partition number of map tasks
-		\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
-		\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
-		\State $idx\gets 0$
-		\While{$idx <$ len$R$}
-		% \Comment{Schedule reduces by MinHeap}
-		\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
-		\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
-		\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
-		\State Sift down $M\left[0\right]$ by $size$
-		\State $idx\gets idx+1$
-		\EndWhile
-		\State $max\gets$ maximum size in $M$
-		% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
-		\ForAll{$reduce$ in $R$}
-		\Comment{Heuristic locality swap}
-			\If{$reduce.assigned\_id \neq reduce.host\_id$}
-				\State $p\gets reduce.prob$
-				\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
-				\State $upper\_bound \gets \left(1 + norm\right) \times max$
-				\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
-			\EndIf
-		\EndFor\newline
-		\Return $M$
-	\EndProcedure
-	\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
-		\State Swap tasks between node $host\_id$ and node $assigned\_id$
-		\State of $reduce$ without exceeding the $upper\_bound$
-		\State of both nodes.\newline
-		% \State Return if it is impossible.
-		\Return
-	\EndProcedure
-	\end{algorithmic}
-\end{algorithm}
-\end{minipage}
 
@@
 	\begin{algorithm}[H]
+	\caption{Heuristic MinHeap Scheduling for Single Shuffle}
+	\label{hminheap}
+		\begin{algorithmic}[1]
+		\small
+		\Procedure{schedule}{$m, host\_ids, p\_reduces$}
+			\State $m\gets$ partition number of map tasks
+			\State $R\gets$ sort $p\_reduces$ by size in \edited{decreasing} order
+			\State $M\gets$ min-heap $\left\{ host\_id \rightarrow \left( \left[ reduces \right], size \right) \right\}$
+			\State $idx\gets 0$
+			\While{$idx <$ len$R$}
+			% \Comment{Schedule reduces by MinHeap}
+			\State $M\left[0\right].size \mathrel{+}= R\left[idx\right].size$
+			\State $M\left[0\right].reduces.append\left(R\left[idx\right]\right)$
+			\State $R\left[idx\right].assigned\_id \gets M \left[0\right].host\_id$
+			\State Sift down $M\left[0\right]$ by $size$
+			\State $idx\gets idx+1$
+			\EndWhile
+			\State $max\gets$ maximum size in $M$
+			% \State Convert $M$ to mapping $\left\{ host\_id \rightarrow \left( \left[ rid\_arr \right], size \right) \right\}$
+			\ForAll{$reduce$ in $R$}
+			\Comment{Heuristic locality swap}
+				\If{$reduce.assigned\_id \neq reduce.host\_id$}
+					\State $p\gets reduce.prob$
+					\State $norm\gets \left(p-1/m\right)/\left(1-1/m\right)/10$
+					\State $upper\_bound \gets \left(1 + norm\right) \times max$
+					\State SWAP\_TASKS$\left(M, reduce, upper\_bound\right)$
+				\EndIf
+			\EndFor
+			\State
+			\reedited{\Return $M$}
+		\EndProcedure
+		\Procedure{swap\_tasks}{$M, reduce, upper\_bound$}
+			\State Swap tasks between node $host\_id$ and node $assigned\_id$
+			\State of $reduce$ without exceeding the $upper\_bound$
+			\State of both nodes.
+			\State
+			\reedited{\Return}
+		\EndProcedure
+		\end{algorithmic}
+	\end{algorithm}
+	\end{minipage}
+
+\subsubsection{Cope with Multiple Shuffle Dependencies}
+{\color{black}
+A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
+To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
+}
+
+% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
+% For those pending shuffles, it is impossible to predict their sizes. 
+% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
+% But doing this introduces large overhead such as extra task serialization. 
+% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
+As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
+When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
+After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
+This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
+which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
+
+To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.
+
+\begin{minipage}{0.95\columnwidth}
+	\begin{algorithm}[H]
 	\caption{Accumulated Heuristic Scheduling for Multi-Shuffles}
@@
 			\State $M\gets$ $SCHEDULE\left(m, host\_id, p\_reduces\right)$
-			\ForAll{$host\_id$ in $M$}
+			\ForAll{\reedited{$host$} in $M$}
 				\Comment Re-shuffle
-				\ForAll{$r$ in $M\left[host\_id\right].reduces$}
+				\ForAll{$r$ in $M\left[\reedited{host}\right].reduces$}
 					\If{$host\neq \text{\textit{shuffles}}\left[r.rid\right].assigned\_host$}
@@
 			\EndFor
-			\Return $M$
+			\State
+			\reedited{\Return $M$}
 		\EndProcedure
@@
 \end{minipage}
-
-\subsubsection{Cope with Multiple Shuffle Dependencies}
-{\color{black}
-A reduce stage can have more than one shuffle dependency in the current DAG computing frameworks.
-To cope with multiple shuffle dependencies, we present the \textit{Accumulated Heuristic Scheduling} algorithm.
-}
-% The technique mentioned in Section \ref{shuffleprediction} can only handle an ongoing shuffle. 
-% For those pending shuffles, it is impossible to predict their sizes. 
-% This problem can be solved by having all map tasks of pending shuffles launched simultaneously. 
-% But doing this introduces large overhead such as extra task serialization. 
-% To avoid violating the optimization from framework, we present the \textit{Accumulated Heuristic Scheduling} algorithm to cope with multiple shuffle dependencies.
-As illustrated in Algorithm \ref{mhminheap}, the sizes of previous \textit{shuffles} scheduled by \textit{Heuristic MinHeap Scheduling} are counted. 
-When a new shuffle starts, the predicted $size$, $prob$, and $host\_id$ in $p\_reduces$ are accumulated with previous \textit{shuffles}. 
-After scheduling, if the new $assigned\_id$ of a reduce task is not equal the original one, a re-shuffle will be triggered to transfer data to the new host. 
-This re-shuffle is rare since the previous shuffle data contributes a huge composition (i.e., high $prob$) after the accumulation, 
-which leads to a higher probability of tasks swap in $SWAP\_TASKS$.
-
-To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.
